### 2024-11-25 paper/paper.qmd
paper inital

---
title: "Global Life Expectancy: Unraveling Health and Economic Determinants (2000-2015)"
subtitle: "Analyzing Critical Factors Shaping Mortality and Well-Being Across 193 Nations"
author: 
  - Yanfei Huang
thanks: "Code and data are available at: [https://github.com/wendyhuan/lifeexpectancy](https://github.com/wendyhuan/lifeexpectancy)."
date: 26 November 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-25 paper/paper.qmd
intro

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper analyze life expectancy and its determinants through 193 countries and make the prediction of people from both developed and developing country.
+Multiple Linear regression is used to deploying the health and socio-economic factors.
+Predictions of life expectancy of people from developed or developing country is made according to the essential predictors.
+The finding indicates that the developed countries tend to live longer life as assumed.
+And we predict that the average age of persons in developed country is 82, while those in underdeveloped countries are 75.
+The result of this paper will help in suggesting a country which area should be given importance in order to efficiently improve the life expectancy of its population."
 format: pdf
@@
 
+# Install Packages if not downloaded:
+required_packages <- c(
+  "tidyverse", "sf", "dplyr", "here", "arrow", "ggplot2", "janitor", "purrr", "knitr", "kableExtra", "ggcorrplot", "modelsummary"
+)
+for (p in required_packages) {
+  if (!require(p, character.only = TRUE)) {
+    install.packages(p, character.only = TRUE)
+  }
+}
+
+#load libraries
 library(tidyverse)
+library(sf)
+library(dplyr)
+library(here)
+library(arrow)
+library(ggplot2)
+library(janitor)
+library(purrr)
+library(knitr)
+library(kableExtra)
+library(ggcorrplot)
+library(modelsummary)
+
+# load data
+cleaned_expectancy <- read_parquet(here:here("data/02-analysis_data/analysis_data.parquet"))
 
@@
 # Introduction
+This paper analyze life expectancy and its determinants through 193 countries and make the prediction of people from both developed and developing country.
+Multiple Linear regression is used to deploying the health and socio-economic factors.
+Predictions of life expectancy of people from developed or developing country is made according to the essential predictors.
+The finding indicates that the developed countries tend to live longer life as assumed.
+And we predict that the average age of persons in developed country is 82, while those in underdeveloped countries are 75.
+The result of this paper will help in suggesting a country which area should be given importance in order to efficiently improve the life expectancy of its population.
 
-Overview paragraph
-
-Estimand paragraph
-
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The structure of the paper is as follows: [@sec-data] outlines the data sources and variables considered, followed by the model setup in [@sec-modset] and justification in [@sec-modjust].
+The results in [@sec-result] presents the key findings of the analysis, with a discussion on the implications.
+[@sec-discussion] then discusses potential limitations and suggestions for future research.
+[@sec-appx] provides additional detailed information about the data, model and methodology.
 
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+The data used in this analysis comes from a
 
-Overview text
+combination of publicly available polling data for the 2024 U.S.
+Presidential election [@FiveThirtyEightPolls].
+The analysis uses the statistical programming language R [@citeR] and several libraries, including `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `dplyr` [@dplyr], `arrow` [@arrow], `purrr` [@purrr], `sf` [@sf], and `here` [@here] for data manipulation.
+`ggplot2` [@ggplot], `ggcorrplot` [@ggcorrplot] and `kableExtra` [@kableExtra] for visualization.
+The dataset covers various polls conducted across multiple states, capturing the support for each major candidate—Donald Trump and Kamala Harris—along with detailed attributes of the polls.
 
@@
 
-## Outcome variables
+## Data Cleaning
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+## Outcome Variables
+
+The main outcome variable of interest is the Expectancy of Life, which represents the predicted age of people from either developed country or developing country. This variable is needed
+
+Percentage of support each candidate has in a given poll, which represents the proportion of respondents who favor one candidate over the other.
+This variable is needed to estimate both the popular vote and Electoral College outcomes.
+We see a bimodal distribution in @fig-percentage.
+This indicates that candidates are either recieveing very high percentages of support or very low percentages of support.
+When we pull out Harris and Trump and view their distributions versus all candidates in @fig-candidatepercentage, we see that these two candidates see statistically high percentages of support, indicating they are leading the polls.
+
+```{r}
+#| label: fig-percentage
+#| fig-cap: This histogram shows the distribution of the percentage of support each candidate receives in various polls.
+The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+# create plot for Distribution of Percentage
+ggplot(cleaned_expectancy, aes(x = Percentage)) +
+  geom_histogram(
+    bins = 30,
+    fill = "orange",
+    color = "black",
+    alpha = 0.7
+  ) +
+  labs(
+    x = "Percentage",
+    y = "Frequency"
+  ) +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-candidatepercentage
+#| fig-cap:  Violin plot comparing the distribution of support between Donald Trump, Kamala Harris, and all other candidates.
+The two candidates exhibit higher-than-average support levels, with Harris and Trump leading the polls in terms of percentage of backing.
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+# filter for trump/harris
+harris_trump_selection <- cleaned_data %>%
+  filter(CandidateName %in% c(
+    "Donald Trump",
+    "Kamala Harris"
+  ))
+
+all_candidates <- cleaned_data %>%
+  mutate(CandidateName = "All Candidates")
+
+# create data frame with trump vs harris vs all candidates
+combined_data <- bind_rows(
+  harris_trump_selection,
+  all_candidates
+)
+
+# create plot for Distribution of Percentage by candidate
+ggplot(combined_data, aes(
+  x = CandidateName,
+  y = Percentage,
+  fill = CandidateName
+)) +
+  geom_violin(alpha = 0.5) +
+  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA) +
+  labs(
+    x = "Candidate",
+    y = "Percentage"
+  ) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_fill_manual(values = c("grey", "salmon", "blue")) +
+  facet_wrap(~CandidateName, scales = "free_x") +
+  theme_minimal()
+```
+
+## Predictor Variables
 
@@
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
+To predict the outcome of the life expectancy of people from different regions, we developed tow linear regression models: one for the developed country and one for developing country.
+These models aim to estimate the life expectancy of people under different environment.
 
@@
 
-## Model set-up
+## Model set-up {#sec-modset}
+
+This paper utilizes linear regression models: 
+$$LifeExpecetancy_I = \beta_0 + \beta_1 $$
+$$LifeExpectancy_D = \beta_0 + \beta_1$$
 

### 2024-11-25 paper/paper.qmd
number

@@
 format: pdf
+toc: true
+toc-depth: 3
 number-sections: true

### 2024-11-26 paper/paper.qmd
paper introduction

@@
 # Introduction
-This paper analyze life expectancy and its determinants through 193 countries and make the prediction of people from both developed and developing country.
-Multiple Linear regression is used to deploying the health and socio-economic factors.
-Predictions of life expectancy of people from developed or developing country is made according to the essential predictors.
-The finding indicates that the developed countries tend to live longer life as assumed.
-And we predict that the average age of persons in developed country is 82, while those in underdeveloped countries are 75.
-The result of this paper will help in suggesting a country which area should be given importance in order to efficiently improve the life expectancy of its population.
+Life expectancy is a critical measure of a population's overall health and well-being, shaped by various factors such as personal health, government healthcare access, economic stability, and social structures.
+The index of life expectancy is generally served as a benchmark for development, indicating the effectiveness of interventions in reducing mortality and improving well-being.
+Higher life expectancy is believed to linked to better living standards, access to education, and equitable healthcare.
+Conversely, low life expectancy often signals systemic challenges such as poverty, disease burden, and inadequate healthcare access.
+Policymakers and researchers rely on life expectancy data to design targeted strategies, allocate resources, and monitor progress toward achieving global health and development goals.
+
+This study focuses on understanding the relationship between country status(developed or developing), personal average expenditure on health based on GDP, general BMI of entire population, percentage of government expenditure on health, GDP, income composition of resources and year of schooling in predicting life expectancy across different countries.
+By identifying and analyzing these predictors, the study aims to highlight actionable aspects for policymakers to target in their efforts to improve population longevity effectively.
+
+Related Research has shown that higher healthcare expenditure of government positively impact life expectancy [@valueofvaccination].
+Additionally, addressing social determinants such as education and income inequality has been identified as a vital pathway to improving longevity [@healthequity].
+Studies also highlight the role of global collaboration in tackling health crises, which can disproportionately affect lower-income nations, mostly developing countries, further influencing life expectancy disparities [@World_Health_Organization].
+
+The ultimate goal is to assist policymakers in developing evidence-based strategies that can enhance population health outcomes.
+The approach of this paper not only emphasizes the importance of equitable access to healthcare but also contributes to a broader understanding of the multifaceted factors shaping life expectancy globally.
+By highlighting the interplay between various determinants, this study contributes to a broader understanding of the challenges and opportunities in improving life expectancy on a global scale.
 
@@
 
-The data used in this analysis comes from a
-
-combination of publicly available polling data for the 2024 U.S.
-Presidential election [@FiveThirtyEightPolls].
+The data used in this analysis originates from The World Health Organization’s (WHO) and Global Health Observatory (GHO), as compiled and merged by Kumar Rajarshi on Kaggle.
+[@lifeexpectancykaggle].
 The analysis uses the statistical programming language R [@citeR] and several libraries, including `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `dplyr` [@dplyr], `arrow` [@arrow], `purrr` [@purrr], `sf` [@sf], and `here` [@here] for data manipulation.
 `ggplot2` [@ggplot], `ggcorrplot` [@ggcorrplot] and `kableExtra` [@kableExtra] for visualization.
-The dataset covers various polls conducted across multiple states, capturing the support for each major candidate—Donald Trump and Kamala Harris—along with detailed attributes of the polls.
+The dataset covers various predictors conducted across multiple countries, capturing the support for a country to determine the predicting factor which is contributing to lower value of life expectancy.
 

### 2024-11-27 paper/paper.qmd
introduction

@@
 # load data
-cleaned_expectancy <- read_parquet(here:here("data/02-analysis_data/analysis_data.parquet"))
+cleaned_expectancy <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
 
@@
 Higher life expectancy is believed to linked to better living standards, access to education, and equitable healthcare.
-Conversely, low life expectancy often signals systemic challenges such as poverty, disease burden, and inadequate healthcare access.
-Policymakers and researchers rely on life expectancy data to design targeted strategies, allocate resources, and monitor progress toward achieving global health and development goals.
+Conversely, low life expectancy often signals systemic challenges such as poverty, disease burden, and inadequate healthcare access [@socialdeterminantsofhealth].
 
-This study focuses on understanding the relationship between country status(developed or developing), personal average expenditure on health based on GDP, general BMI of entire population, percentage of government expenditure on health, GDP, income composition of resources and year of schooling in predicting life expectancy across different countries.
+The primary goal of this paper is to determine which factors play a statistically significant role in driving lower life expectancy values and to offer actionable insights based on country status.
+Using Multiple Linear Regression model, this study focuses on understanding the relationship between country status(developed or developing), personal average expenditure on health based on GDP, general BMI of entire population, percentage of government expenditure on health, GDP, income composition of resources and year of schooling in predicting life expectancy across different countries.
 By identifying and analyzing these predictors, the study aims to highlight actionable aspects for policymakers to target in their efforts to improve population longevity effectively.
@@
 Studies also highlight the role of global collaboration in tackling health crises, which can disproportionately affect lower-income nations, mostly developing countries, further influencing life expectancy disparities [@World_Health_Organization].
+
+Findings from this paper reveal that countries with greater healthcare spending tend to achieve higher life expectancy, while factors like income inequality and absence of education emerge as significant obstacles.
+The analysis underscores the importance of targeted interventions in key areas such as healthcare accessibility and economic equity to address disparities in life expectancy.
+This study further contributes to a deeper understanding of how predictive modeling under different country status can inform public health strategies and policy-making on a global scale.
 

### 2024-11-27 scripts/03-clean_data.R
data cleaning

@@ -8,18 +8,22 @@
 # Any other information needed? No
 
 #### Workspace setup ####
+install.packages("countrycode")
 library(tidyverse)
 library(dplyr)
 library(janitor)
 library(arrow)
+library(countrycode)
 
 #### Clean data ####
 #Load the dataset
 raw_expectancy <- read_csv("data/01-raw_data/raw_data.csv")
 
 # Data cleaning by Filter and select relevant columns, renaming complex names, 
-# filtering invalid entries, 
-cleaned_expectancy <-raw_expectancy |> 
+# filtering invalid entries, round columns into specific decimals 
+cleaned_expectancy <- tryCatch(
+  {
+    raw_expectancy |> 
   select(Country, Year, Status, Life.expectancy, percentage.expenditure, BMI, Total.expenditure, GDP,
          Income.composition.of.resources, Schooling) |>
   rename(LifeExpectancy = Life.expectancy,
@@ -27,6 +31,7 @@ cleaned_expectancy <-raw_expectancy |>
          TotalExpenditure = Total.expenditure,
          IncomeComposition = Income.composition.of.resources) |>
   filter (
+    # filtering invalid entries 
     !is.na(GDP), 
     !is.na(Year),
     !is.na(Status),
@@ -35,7 +40,29 @@ cleaned_expectancy <-raw_expectancy |>
     !is.na(BMI),
     !is.na(TotalExpenditure),
     !is.na(IncomeComposition),
-    !is.na(Schooling) )
+    !is.na(Schooling) ) |>
+  mutate(
+    #Round specific columns to varying decimal places
+    LifeExpectancy = round(LifeExpectancy, 2),
+    PercentageExpenditure = round(PercentageExpenditure, 4),
+    TotalExpenditure = round(TotalExpenditure, 2),
+    GDP = round(GDP, 4),
+    IncomeComposition = round(IncomeComposition, 3),
+    Schooling = round(Schooling, 1)) |>
+  mutate(
+    #Change the name of South Korea avoiding misunderstanding
+    Country = ifelse(Country == "Republic of Korea",
+                           "South Korea", Country) )|>
+  mutate(
+    #create continent variable and check the continent of each country
+    Continent = countrycode(Country, "country.name", "continent")) %>%
+      ungroup() 
+    cleaned_expectancy}, # error handling to mitigate any cleaning issues
+  error = function(e) { 
+    message("An error occurred during data cleaning: ", e)
+    NULL  # Return NULL if error occurs
+    })
+
   
   
 #### Save data ####

### 2024-11-27 scripts/00-simulate_data.R
initial

@@ -12,6 +12,7 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
+library(countrycode)
 set.seed(853)
 
 
@@ -49,16 +50,6 @@ simulated_expectancy <- tibble(
                            #for developing countries, draw normal distribution with mean 65 and standard deviation of 10
                            rnorm(n, mean = 65, sd = 10)),
   
-  #using a normal distribution with a mean of 25 and a standard deviation of 5 for all observations of BMI
-  BMI = rnorm(n, mean = 25, sd = 5),
-  
-  
-  GDP = ifelse(status == "Developed",
-               #for developed countries, draw normal distribution with mean 40,000 and standard deviation of 10,000
-               rnorm(n, mean = 40000, sd = 10000),
-               #for developing countries, draw normal distribution with mean 5,000 and standard deviation of 2,000
-               rnorm(n, mean = 5000, sd = 2000)),
-  
   #random value between 1 to 100,000 of Expenditure on health as a percentage of Gross Domestic Product per capita(%)
   percentage_expenditure = runif(n, min = 1, max = 100000),
   
@@ -79,8 +70,6 @@ simulated_expectancy <- tibble(
 simulated_expectancy <- simulated_expectancy %>%
   mutate(
     life_expectancy = ifelse(life_expectancy < 0, 0, life_expectancy),
-    BMI = ifelse(BMI < 0, 0, BMI),
-    GDP = ifelse(GDP < 0, 0, GDP),
     schooling = ifelse(schooling < 0, 0, schooling)
   )
 

### 2024-11-27 scripts/01-test_simulated_data.R

@@ -12,6 +12,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(countrycode)
 
 simulated_expectancy <- read_csv("data/00-simulated_data/simulated_data.csv")
 

### 2024-11-27 scripts/03-clean_data.R

@@ -24,7 +24,7 @@ raw_expectancy <- read_csv("data/01-raw_data/raw_data.csv")
 cleaned_expectancy <- tryCatch(
   {
     raw_expectancy |> 
-  select(Country, Year, Status, Life.expectancy, percentage.expenditure, BMI, Total.expenditure, GDP,
+  select(Country, Year, Status, Life.expectancy, percentage.expenditure, Total.expenditure,
          Income.composition.of.resources, Schooling) |>
   rename(LifeExpectancy = Life.expectancy,
          PercentageExpenditure = percentage.expenditure,
@@ -32,12 +32,10 @@ cleaned_expectancy <- tryCatch(
          IncomeComposition = Income.composition.of.resources) |>
   filter (
     # filtering invalid entries 
-    !is.na(GDP), 
     !is.na(Year),
     !is.na(Status),
     !is.na(LifeExpectancy),
     !is.na(PercentageExpenditure),
-    !is.na(BMI),
     !is.na(TotalExpenditure),
     !is.na(IncomeComposition),
     !is.na(Schooling) ) |>
@@ -46,7 +44,6 @@ cleaned_expectancy <- tryCatch(
     LifeExpectancy = round(LifeExpectancy, 2),
     PercentageExpenditure = round(PercentageExpenditure, 4),
     TotalExpenditure = round(TotalExpenditure, 2),
-    GDP = round(GDP, 4),
     IncomeComposition = round(IncomeComposition, 3),
     Schooling = round(Schooling, 1)) |>
   mutate(
@@ -63,7 +60,5 @@ cleaned_expectancy <- tryCatch(
     NULL  # Return NULL if error occurs
     })
 
-  
-  
 #### Save data ####
 write_csv(cleaned_expectancy, "data/02-analysis_data/analysis_data.parquet")

### 2024-11-27 scripts/06-model_data.R

@@ -14,6 +14,7 @@ library(rstanarm)
 library(car)
 library(arrow)
 library(dplyr)
+library(countrycode)
 
 #### Read data ####
 cleaned_expectancy <- read_csv("data/02-analysis_data/analysis_data.parquet")
@@ -24,9 +25,8 @@ cleaned_expectancy <- cleaned_expectancy %>%
     LifeExpectancy = as.numeric(LifeExpectancy),
     Status = as.factor(Status),
     PercentageExpenditure = as.numeric(PercentageExpenditure),
-    BMI = as.numeric(BMI),
+    Continent = as.factor(Continent),
     TotalExpenditure = as.numeric(TotalExpenditure),
-    GDP = as.numeric(GDP),
     IncomeComposition = as.numeric(IncomeComposition),
     Schooling = as.numeric(Schooling)
   )
@@ -34,12 +34,12 @@ cleaned_expectancy <- cleaned_expectancy %>%
 
 ### Model for developing country based on various predictors ###
 lm_model_developing <-
-  lm(LifeExpectancy ~ PercentageExpenditure + BMI + TotalExpenditure + GDP + IncomeComposition + Schooling,
+  lm(LifeExpectancy ~ PercentageExpenditure + Continent + TotalExpenditure + IncomeComposition + Schooling,
      data = cleaned_expectancy %>% filter (Status == 'Developing') )
 
 ### Model for developed country based on various predictors###
 lm_model_developed <-
-  lm(LifeExpectancy ~ PercentageExpenditure + BMI + TotalExpenditure + GDP + IncomeComposition + Schooling,
+  lm(LifeExpectancy ~ PercentageExpenditure + Continent + TotalExpenditure + IncomeComposition + Schooling,
      data = cleaned_expectancy %>% filter (Status == 'Developed') )
 
 

### 2024-11-27 paper/paper.qmd
inital

@@
 The finding indicates that the developed countries tend to live longer life as assumed.
-And we predict that the average age of persons in developed country is 82, while those in underdeveloped countries are 75.
+And we predict that the average age of persons in developed country is 80, while those in underdeveloped countries are 75.
 The result of this paper will help in suggesting a country which area should be given importance in order to efficiently improve the life expectancy of its population."
@@
 library(modelsummary)
+library(countrycode)
 
@@
 # Introduction
-Life expectancy is a critical measure of a population's overall health and well-being, shaped by various factors such as personal health, government healthcare access, economic stability, and social structures.
+Life expectancy is a critical measure of a population's overall health and well-being, shaped by various factors such as personal expenditure on health, government healthcare access, economic stability, and social structures.
 The index of life expectancy is generally served as a benchmark for development, indicating the effectiveness of interventions in reducing mortality and improving well-being.
@@
 The primary goal of this paper is to determine which factors play a statistically significant role in driving lower life expectancy values and to offer actionable insights based on country status.
-Using Multiple Linear Regression model, this study focuses on understanding the relationship between country status(developed or developing), personal average expenditure on health based on GDP, general BMI of entire population, percentage of government expenditure on health, GDP, income composition of resources and year of schooling in predicting life expectancy across different countries.
+Using Multiple Linear Regression model, this study focuses on understanding the relationship between country status(developed or developing), continent, personal average expenditure on health based on GDP, percentage of government expenditure on health, income composition of resources and year of schooling in predicting life expectancy across different countries.
 By identifying and analyzing these predictors, the study aims to highlight actionable aspects for policymakers to target in their efforts to improve population longevity effectively.
@@
 Additionally, addressing social determinants such as education and income inequality has been identified as a vital pathway to improving longevity [@healthequity].
-Studies also highlight the role of global collaboration in tackling health crises, which can disproportionately affect lower-income nations, mostly developing countries, further influencing life expectancy disparities [@World_Health_Organization].
+Studies also highlight the role of global collaboration in tackling health crises, which can disproportionately affect lower-income nations, mostly developing countries under certain continents, further influencing life expectancy disparities [@World_Health_Organization].
 

### 2024-11-27 scripts/04-test_analysis_data.R

@@ -12,6 +12,7 @@
 library(tidyverse)
 library(testthat)
 library(arrow)
+library(countrycode)
 
 cleaned_expectancy <- read_csv("data/02-analysis_data/analysis_data.parquet")
 

### 2024-11-28 paper/paper.qmd
data cleaning

@@
 thanks: "Code and data are available at: [https://github.com/wendyhuan/lifeexpectancy](https://github.com/wendyhuan/lifeexpectancy)."
-date: 26 November 2024
+date: 30 November 2024
 date-format: long
@@
 required_packages <- c(
-  "tidyverse", "sf", "dplyr", "here", "arrow", "ggplot2", "janitor", "purrr", "knitr", "kableExtra", "ggcorrplot", "modelsummary"
+  "tidyverse", "sf", "dplyr", "here", "arrow", "ggplot2", "janitor", "purrr", "knitr", "kableExtra", "ggcorrplot", "modelsummary", "countrycode"
 )
@@
 # Introduction
+
 Life expectancy is a critical measure of a population's overall health and well-being, shaped by various factors such as personal expenditure on health, government healthcare access, economic stability, and social structures.
@@
 
-The data used in this analysis originates from The World Health Organization’s (WHO) and Global Health Observatory (GHO), as compiled and merged by Kumar Rajarshi on Kaggle.
-[@lifeexpectancykaggle].
-The analysis uses the statistical programming language R [@citeR] and several libraries, including `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `dplyr` [@dplyr], `arrow` [@arrow], `purrr` [@purrr], `sf` [@sf], and `here` [@here] for data manipulation.
+The data used in this analysis originates from The World Health Organization’s (WHO) and Global Health Observatory (GHO) [@lifeexpectancy].
+This data-set related to life expectancy, health factors for 193 countries has been collected from WHO data repository website and its corresponding economic data was collected from United Nation website.
+Among all categories of health-related factors only those socio-economic factors on the national level were chosen for global scale analysis.
+
+This analysis uses the statistical programming language R [@citeR] and several libraries, including `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `dplyr` [@dplyr], `arrow` [@arrow], `purrr` [@purrr], `sf` [@sf], and `here` [@here] for data manipulation.
 `ggplot2` [@ggplot], `ggcorrplot` [@ggcorrplot] and `kableExtra` [@kableExtra] for visualization.
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The measurement process refers to how real-world factors—such as the status of a country, average personal health care investment, average year of education,  geographic location of a country and social determinants (country's healthcare investment, human development index of income) — are translated into numerical entries representing life expectancy in a dataset.
+Each entry captures the average life expectancy of individuals in a specific country during a given year.
+
+Life Expectancy (`LifeExpectancy`): This variable represents the average number of years a person is expected to live, assuming current mortality conditions persist.
+It is derived using data from national health records, the World Health Organization (WHO) and Global Health Observatory (GHO).
+The values are calculated and represented in age between 36.3 to 89.
+
+Percentage Expenditure on Health (`PercentageExpenditure`): This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
+The data is typically collected from government reports, economic surveys, and global health databases.
+It indicates the level of personal financial investment in the health sector and is expressed as a percentage.
+
+Schooling (`Schooling`): This variable captures the average number of years of education received by individuals in a country.
+Data is obtained from educational surveys and censuses conducted by international and national organizations.
+The values are recorded in years and used to assess the link between education and health outcomes like life expectancy.
+The data range from 0 to 20.7
+
+Status (`Status`): This is a categorical variable that classifies countries as "Developed" or "Developing," based on various socio-economic and health indicators accepted globally.
+It provides context for comparing life expectancy across different stages of national development.
+
+Continent(`Continent`): This is a categorical variable that classifies the geographic location of the countries.
+It is detected by the name of the country using rpackage `countrycode`.
+The data is stored as the name of the continent(‘Africa’, ‘Oceania’, ‘Asia’, ‘Europe’, ‘North America’, ‘South America’)
+
+Total expenditure (`TotalExpenditure`): This is a numerical variable that shows the general government expenditure on health as a percentage of total government expenditure.
+The number drop of the percentage and shows as the number between 0 to 100, where higher values indicate a greater share of government spending allocated to health.
+
+Income composition of resource (`IncomeComposition`): This is a numerical variable representing the income component of the Human Development Index (HDI).
+It reflects the contribution of income to human development, with values ranging from 0 to 1, where higher values signify a greater income contribution to overall development.
 
 ## Data Cleaning
+
+The raw life expectancy data underwent a several cleaning steps to ensure it was accurate, consistent and ready for analysis.
+We first select and rename key variables from raw data to focus on relevant information.
+The key variables of interest in our analysis include Country, Year, Status of the country, Life expectancy, Percentage expenditure, Total expenditure, Income composition of resources and the year of education.
+Additionally, we develop a new predictor named "Continent" to monitor each nation's geographic data.
+To make the subsequent analysis easier, we then convert variables to the proper data types and eliminate the rows that have missing data values.
+To keep things neat, we organize the decimal for every piece of numerical data.
+The cleaned dataset was then saved as a Parquet file for efficient storage and further analysis.
+
+More information on the data cleaning process can be found in @sec-appx.
 
@@
 
-# Appendix {-}
+# Appendix {#sec-appendix}
+
+## Data Cleaning Notes
+
+We began by importing the raw dataset using the read_csv function from the tidyverse package.
+To focus our analysis on more relevant variables, we selected specific columns, such as percentage of expenditure of the country, total health expenditure by government .etc., omitting any unnecessary columns.
+
+We filter out the rows containing NA values in any of the selected columns for reducing the noise and simpler further analysis..
+
+We then renaming columns for clarity.
+For example, we changed ‘Income.composition.of.resources’ into ‘IncomeComposition’ , making it easier for anyone working with the data to read and understand what each variable represents.
+
+Each column is rounded using the round function, specifying the desired number of decimal places for each.
+Columns not mentioned in mutate remain unchanged.
+This ensures a flexible and precise cleaning process tailored to further compairation and graphing.
+
+We also modified the country name of ‘Republic of Korea’ under Country variable to ‘South Korea’ to avoid misunderstanding of North Korea.
+
+We also created a new variable called Continent, which indicates which continent does the country comes from in order to provide a geographical context to the analysis.
+Life expectancy may be higher in developed regions like Europe or North America compared to regions like Sub-Saharan Africa due to differences in healthcare, living standards, and economic development.
+
+We also wrapped the cleaning process in a tryCatch block in order to mitigate any errors that arose throughout the cleaning process.
+
+After completing the cleaning, we saved the final dataset in both Parquet and CSV formats for later analysis.
 

### 2024-11-28 paper/paper.qmd
inital

@@
 
-The main outcome variable of interest is the Expectancy of Life, which represents the predicted age of people from either developed country or developing country. This variable is needed
-
-Percentage of support each candidate has in a given poll, which represents the proportion of respondents who favor one candidate over the other.
-This variable is needed to estimate both the popular vote and Electoral College outcomes.
-We see a bimodal distribution in @fig-percentage.
-This indicates that candidates are either recieveing very high percentages of support or very low percentages of support.
-When we pull out Harris and Trump and view their distributions versus all candidates in @fig-candidatepercentage, we see that these two candidates see statistically high percentages of support, indicating they are leading the polls.
+The outcome variable is `LifeExpendency`.
+This is the primary dependent variable that the model is designed to predict.
+It represents the average number of years a person is expected to live, under the condition that current mortality conditions persist.
+The model seeks to identify the variables affecting this average.
+To examine the differences in life expectancy under the same variables, we separate the data into developed and developing countries, where developed country are generally believed to have higher life expectancy.
+@fig-expectancy displays the historical data of life expectancy across 195 countries from 2000 to 2015, comparing developing to developed countries.
+According to the graph, under the same variables, developed countries often have longer life expectancy than developing nations as assumption.
 
 ```{r}
-#| label: fig-percentage
-#| fig-cap: This histogram shows the distribution of the percentage of support each candidate receives in various polls.
-The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
+#| label: fig-expectancy
+#| fig-cap: This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries.
+The graph shows that more developed countries are tend to have higher average of ages than developing countries.
+#| 
+#| . The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
 #| echo: false
@@
 
-# create plot for Distribution of Percentage
-ggplot(cleaned_expectancy, aes(x = Percentage)) +
-  geom_histogram(
-    bins = 30,
-    fill = "orange",
-    color = "black",
-    alpha = 0.7
+# create plot of historical 193 countries life expectancy dividing by country status. 
+ggplot(cleaned_expectancy, aes(x = LifeExpectancy)) +
+  geom_histogram(aes(y = ..density..), 
+                 bins = 70, fill = "brown", color = "white", alpha = 0.7) +
+  geom_density(color = "royalblue", fill = "lightblue", alpha = 0.6) +
+  labs(
+    title = "Distribution of Life Expectancy by Status",
+    x = "Life Expectancy", y = "Density"
   ) +
-  labs(
-    x = "Percentage",
-    y = "Frequency"
-  ) +
-  theme_minimal()
-```
+  theme_minimal() +
+  facet_wrap(~Status)
 
-```{r}
-#| label: fig-candidatepercentage
-#| fig-cap:  Violin plot comparing the distribution of support between Donald Trump, Kamala Harris, and all other candidates.
-The two candidates exhibit higher-than-average support levels, with Harris and Trump leading the polls in terms of percentage of backing.
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-# filter for trump/harris
-harris_trump_selection <- cleaned_data %>%
-  filter(CandidateName %in% c(
-    "Donald Trump",
-    "Kamala Harris"
-  ))
-
-all_candidates <- cleaned_data %>%
-  mutate(CandidateName = "All Candidates")
-
-# create data frame with trump vs harris vs all candidates
-combined_data <- bind_rows(
-  harris_trump_selection,
-  all_candidates
-)
-
-# create plot for Distribution of Percentage by candidate
-ggplot(combined_data, aes(
-  x = CandidateName,
-  y = Percentage,
-  fill = CandidateName
-)) +
-  geom_violin(alpha = 0.5) +
-  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA) +
-  labs(
-    x = "Candidate",
-    y = "Percentage"
-  ) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_fill_manual(values = c("grey", "salmon", "blue")) +
-  facet_wrap(~CandidateName, scales = "free_x") +
-  theme_minimal()
 ```
@@
 Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
 
@@
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+model_developed <-
+  readRDS(file = here::here("models/lm_model_developed.rds"))
 ```
@@
   list(
-    "First model" = first_model
+    "developed model" = model_developed
   ),
@@
 
-pp_check(first_model) +
+pp_check(model_developed) +
   theme_classic() +
@@
 
-posterior_vs_prior(first_model) +
+posterior_vs_prior(model_developed) +
   theme_minimal() +
@@
 
-plot(first_model, "trace")
+plot(model_developed, "trace")
 
-plot(first_model, "rhat")
+plot(model_developed, "rhat")
 ```

### 2024-11-28 paper/paper.qmd
inital

@@
 The graph shows that more developed countries are tend to have higher average of ages than developing countries.
-#| 
-#| . The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
+The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
 #| echo: false
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+#analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+#analysis_data |> 
+  #ggplot(aes(x = width, y = length)) +
+  #geom_point(alpha = 0.8) +
+  #theme_minimal() +
+  #labs(x = "Wing width (mm)",
+      # y = "Wing length (mm)")
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "developed model" = model_developed
-  ),
-  statistic = "mad",
-  fmt = 2
-)
+#modelsummary::modelsummary(
+  #list(
+    #"developed model" = #model_developed
+  #),
+  #statistic = "mad",
+  #fmt = 2
+#)
 ```
@@
 
-pp_check(model_developed) +
-  theme_classic() +
-  theme(legend.position = "bottom")
+#pp_check(model_developed) +
+  #theme_classic() +
+  #theme(legend.position = "bottom")
 
-posterior_vs_prior(model_developed) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+#posterior_vs_prior(model_developed) +
+  #theme_minimal() +
+  #scale_color_brewer(palette = "Set1") +
+  #theme(legend.position = "bottom") +
+  #coord_flip()
 ```
@@
 
-plot(model_developed, "trace")
+#plot(model_developed, "trace")
 
-plot(model_developed, "rhat")
+#plot(model_developed, "rhat")
 ```

### 2024-11-29 paper/paper.qmd
initial

@@
 To examine the differences in life expectancy under the same variables, we separate the data into developed and developing countries, where developed country are generally believed to have higher life expectancy.
-@fig-expectancy displays the historical data of life expectancy across 195 countries from 2000 to 2015, comparing developing to developed countries.
-According to the graph, under the same variables, developed countries often have longer life expectancy than developing nations as assumption.
+@fig-expectancy displays density of the historical data of life expectancy across 195 countries from 2000 to 2015, comparing developing to developed countries.The average age of most developed country is approximately 80, while the majority developing countries typically have average life expectancy around mid-seventies.
 
@@
 #| fig-cap: This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries.
-The graph shows that more developed countries are tend to have higher average of ages than developing countries.
-The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
+The graph of developed countries shows narrower spread with density curve located on the rightside of the x-axis.
+The graph of developing countries performs a wider spread while the highest density position at mid-seventies.
 #| echo: false
@@
   geom_histogram(aes(y = ..density..), 
-                 bins = 70, fill = "brown", color = "white", alpha = 0.7) +
+                 bins = 70, fill = "salmon", color = "pink", alpha = 0.9) +
   geom_density(color = "royalblue", fill = "lightblue", alpha = 0.6) +
@@
 ## Predictor Variables
+
+The **predictor variables** (or independent variables) are the factors believed to influence the life expectancy:
+
+1. **Status(`Status`)**:
+
+2. **Continent(`Continent`)**:
+
+3. **Percentage Expenditure on Health (`PercentageExpenditure`)**:
+
+4. **Total expenditure (`TotalExpenditure`)**:
+
+5. **Income composition of resource (`IncomeComposition`)**:
+
+6.**Schooling (`Schooling`)**:
 
@@
 ```
-
-Talk way more about it.
-
-## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
 

### 2024-11-29 paper/paper.qmd
inital

@@
 title: "Global Life Expectancy: Unraveling Health and Economic Determinants (2000-2015)"
-subtitle: "Analyzing Critical Factors Shaping Mortality and Well-Being Across 193 Nations"
+subtitle: "Analyzing Critical Factors Shaping Mortality and Well-Being Across 155 Nations"
 author: 
@@
 date-format: long
-abstract: "This paper analyze life expectancy and its determinants through 193 countries and make the prediction of people from both developed and developing country.
+abstract: "This paper analyze life expectancy and its determinants through 155 countries and make the prediction of people from both developed and developing country.
 Multiple Linear regression is used to deploying the health and socio-economic factors.
@@
 The data used in this analysis originates from The World Health Organization’s (WHO) and Global Health Observatory (GHO) [@lifeexpectancy].
-This data-set related to life expectancy, health factors for 193 countries has been collected from WHO data repository website and its corresponding economic data was collected from United Nation website.
+This data-set related to life expectancy, health factors for 155 countries has been collected from WHO data repository website and its corresponding economic data was collected from United Nation website.
 Among all categories of health-related factors only those socio-economic factors on the national level were chosen for global scale analysis.
@@
 
-Life Expectancy (`LifeExpectancy`): This variable represents the average number of years a person is expected to live, assuming current mortality conditions persist.
+**Life Expectancy (`LifeExpectancy`)**: This variable represents the average number of years a person is expected to live, assuming current mortality conditions persist.
 It is derived using data from national health records, the World Health Organization (WHO) and Global Health Observatory (GHO).
@@
 
-Percentage Expenditure on Health (`PercentageExpenditure`): This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
+**Percentage Expenditure on Health (`PercentageExpenditure`)**: This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
 The data is typically collected from government reports, economic surveys, and global health databases.
@@
 
-Schooling (`Schooling`): This variable captures the average number of years of education received by individuals in a country.
+**Schooling (`Schooling`)**: This variable captures the average number of years of education received by individuals in a country.
 Data is obtained from educational surveys and censuses conducted by international and national organizations.
@@
 
-Status (`Status`): This is a categorical variable that classifies countries as "Developed" or "Developing," based on various socio-economic and health indicators accepted globally.
+**Status (`Status`)**: This is a categorical variable that classifies countries as "Developed" or "Developing," based on various socio-economic and health indicators accepted globally.
 It provides context for comparing life expectancy across different stages of national development.
 
-Continent(`Continent`): This is a categorical variable that classifies the geographic location of the countries.
+**Continent(`Continent`)**: This is a categorical variable that classifies the geographic location of the countries.
 It is detected by the name of the country using rpackage `countrycode`.
@@
 
-Total expenditure (`TotalExpenditure`): This is a numerical variable that shows the general government expenditure on health as a percentage of total government expenditure.
+**Total expenditure (`TotalExpenditure`)**: This is a numerical variable that shows the general government expenditure on health as a percentage of total government expenditure.
 The number drop of the percentage and shows as the number between 0 to 100, where higher values indicate a greater share of government spending allocated to health.
 
-Income composition of resource (`IncomeComposition`): This is a numerical variable representing the income component of the Human Development Index (HDI).
+**Income composition of resource (`IncomeComposition`)**: This is a numerical variable representing the income component of the Human Development Index (HDI).
 It reflects the contribution of income to human development, with values ranging from 0 to 1, where higher values signify a greater income contribution to overall development.
@@
 
-The outcome variable is `LifeExpendency`.
+The outcome variable is **`LifeExpendency`**.
 This is the primary dependent variable that the model is designed to predict.
@@
 #| label: fig-expectancy
-#| fig-cap: This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries.
+#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries.
 The graph of developed countries shows narrower spread with density curve located on the rightside of the x-axis.
-The graph of developing countries performs a wider spread while the highest density position at mid-seventies.
+The graph of developing countries performs a wider spread while the highest density position at mid-seventies."
 #| echo: false
@@
 
-# create plot of historical 193 countries life expectancy dividing by country status. 
+# create plot of historical 155 countries life expectancy dividing by country status. 
 ggplot(cleaned_expectancy, aes(x = LifeExpectancy)) +
@@
 
-1. **Status(`Status`)**:
+1.
+**Status(`Status`)**: The status of a country is the key factor influencing the life expectancy.
+We divide the life expectancy by the status of a country as it is believed that developed country generally have higher life expectancy due to better healthcare access, sanitation, and living standards, while developing countries face greater health challenges.
+This variable provides context for comparing life expectancy between different levels of country development.
+@fig-statusdistribution includes 28 developed countries and 127 developing countries.
+The graph on left shows that we've got much greater representation of developing nations across the dataset.
+Comparing both graph, we still could tell that the dataset contains significantly more data for developing countries than for developed countries, even relative to the difference in the number of countries themselves.
 
-2. **Continent(`Continent`)**:
+2.  **Continent(`Continent`)**: This is the categorical variable showing the geographic information of each country. Continent usually
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-statusdistribution
+#| fig-cap: "Distribution of country status, showing 28 dveloped countries and 127 developing countries, with a substantial difference in the number of data points.
+From 2000 to 2015, notably, the number of data entries for developing countries far exceeds that of developed countries, reflecting the greater representation of developing nations across the dataset."
 #| echo: false
+#| eval: true
 #| warning: false
@@
 
-#analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+# Count the number of unique countries for each Status
+country_counts <- cleaned_expectancy %>%
+  distinct(Country, Status) %>%  # Ensure each country is only counted once
+  count(Status)  # Count the number of countries in each Status category
 
-#analysis_data |> 
-  #ggplot(aes(x = width, y = length)) +
-  #geom_point(alpha = 0.8) +
-  #theme_minimal() +
-  #labs(x = "Wing width (mm)",
-      # y = "Wing length (mm)")
+#Plot1: create bar plot of count of status
+numberrows <- ggplot(cleaned_expectancy, aes(x = Status, fill = Status)) +
+  geom_bar() +
+  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5) +
+  labs(
+    title = "Distribution of Count of Developed and Developing Countries",
+    x = "Status (Developed vs Developing)",
+    y = "Count"
+  ) +
+  theme_minimal() +
+  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "darkblue")) +
+  theme(legend.position = "none",
+  plot.title = element_text(size = 7))
+
+# Plot2: Create a bar plot to show the distribution of countries by Status
+numbercountry <- ggplot(country_counts, aes(x = Status, y = n, fill = Status)) +
+  geom_bar(stat = "identity") +  # Use 'identity' to directly use the count values
+  geom_text(aes(label = n), vjust = -0.5) +  # Add count labels on top of bars
+  labs(
+    title = "Distribution of Countries by Status (Developed vs Developing)",
+    x = "Status (Developed vs Developing)",
+    y = "Number of Countries"
+  ) +
+  theme_minimal() +
+  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "darkblue")) +
+  theme(
+    legend.position = "none", 
+  plot.title = element_text(size = 7))
+
+# Arrange the plots side by side
+grid.arrange(numberrows, numbercountry, ncol = 2)
+```
+
+```{r}
+#| label: fig-continent
+#| fig-cap: "Distribution of contient. Africa has the highest number of countries represented, followed by Asia among all 5 continents. "
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+#Calculate the number of unique countries per continent
+continent_count <- cleaned_expectancy %>%
+  group_by(Continent) %>%
+  summarise(num_countries = n_distinct(Country))
+
+#Plot1: Distribution of number of data per continent
+#Create the bar plot showing the number of data per continent
+continentrow <- ggplot(cleaned_expectancy, aes(x = Continent)) +
+  geom_bar(fill = "orange", color = "white") +
+  labs(
+    title = "Distribution of Count by Continent",
+    x = "Continent",
+    y = "Count"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(size = 12, face = "bold"),
+    axis.title = element_text(size = 12)
+  ) +
+  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
+
+# Plot2: The distribution of number of countries each continent
+#Create the bar plot showing the number of unique countries per continent
+continentnumber <-ggplot(continent_count, aes(x = Continent, y = num_countries)) +
+  geom_bar(stat = "identity", fill = "#FFA07A", color = "white") +
+  labs(
+    title = "Number of Countries by Continent",
+    x = "Continent",
+    y = "Number of Countries"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(size = 12, face = "bold"),
+    axis.title = element_text(size = 10)
+  ) +
+  geom_text(aes(label = num_countries), vjust = -0.5, size = 2.5)
+
+# Arrange the plots side by side
+grid.arrange(continentnumber, continentrow, ncol = 2)
 ```
@@
 # Model
+
 To predict the outcome of the life expectancy of people from different regions, we developed tow linear regression models: one for the developed country and one for developing country.
@@
 
-This paper utilizes linear regression models: 
-$$LifeExpecetancy_I = \beta_0 + \beta_1 $$
-$$LifeExpectancy_D = \beta_0 + \beta_1$$
+This paper utilizes linear regression models: $$LifeExpecetancy_I = \beta_0 + \beta_1 $$ $$LifeExpectancy_D = \beta_0 + \beta_1$$
 
@@
 Our results are summarized in @tbl-modelresults.
+
+1. check different continent has its different life expectancy. 
+2. compare the develop country with 
+3. check the shcooling year of develop countries to developing country, showing a relationship between shcooling with the life expenctancy. 
+4.
 

### 2024-11-30 paper/paper.qmd
inital

@@
 required_packages <- c(
-  "tidyverse", "sf", "dplyr", "here", "arrow", "ggplot2", "janitor", "purrr", "knitr", "kableExtra", "ggcorrplot", "modelsummary", "countrycode"
+  "tidyverse", "sf", "dplyr", "here", "arrow", "ggplot2", "janitor", "purrr", "knitr", "kableExtra", "ggcorrplot", "modelsummary", "countrycode", "gridExtra"
 )
@@
 library(countrycode)
+library(gridExtra)
 

### 2024-11-30 paper/paper.qmd
initial

@@
 
-2.  **Continent(`Continent`)**: This is the categorical variable showing the geographic information of each country. Continent usually
+2.
+**Continent(`Continent`)**: This is the categorical variable showing the geographic information of each country.
+Developed continents, for example Europe and North America, typically have well-established healthcare infrastructure, which are considered to contribute to higher life expectancy.
+Factors like clean water access, education resources, nutrition and lifestyle factors can significantly impact life expectancy and vary greatly across continents.
+@fig-continent reveals that Africa has the highest number of countries represented with the largest portion of the data.
+Other continents, America and Europe, have fewer countries included, with only 9 countries from Oceania.
 
-3.  **Percentage Expenditure on Health (`PercentageExpenditure`)**:
+3.  **Percentage Expenditure on Health (`PercentageExpenditure`)**: This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
 
-4.  **Total expenditure (`TotalExpenditure`)**:
+4.
+**Total expenditure (`TotalExpenditure`)**: This variable shows the general government expenditure on health as a percentage of total government expenditure.
+This is considered as a reflection of economic situation of a country.
+A higher percentage indicates that a country places significant emphasis on healthcare as a key area of public investment.
 
-5.  **Income composition of resource (`IncomeComposition`)**:
+5. **Income composition of resource (`IncomeComposition`)**: his is a numerical variable representing the income component of the Human Development Index (HDI).
 
-6.**Schooling (`Schooling`)**:
+6. **Schooling (`Schooling`)**: This is a numerical variable showing the number of education per person.
 
@@
   geom_bar() +
-  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5) +
+  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5,size = 2.5) +
   labs(
-    title = "Distribution of Count of Developed and Developing Countries",
+    title = "Distribution of Count of Country by Status",
     x = "Status (Developed vs Developing)",
@@
   theme(legend.position = "none",
-  plot.title = element_text(size = 7))
+  plot.title = element_text(size = 7,face = "bold"))
 
@@
   geom_bar(stat = "identity") +  # Use 'identity' to directly use the count values
-  geom_text(aes(label = n), vjust = -0.5) +  # Add count labels on top of bars
+  geom_text(aes(label = n), vjust = -0.5,size = 2.5) +  # Add count labels on top of bars
   labs(
-    title = "Distribution of Countries by Status (Developed vs Developing)",
+    title = "Distribution of Country by Status",
     x = "Status (Developed vs Developing)",
@@
     legend.position = "none", 
-  plot.title = element_text(size = 7))
+  plot.title = element_text(size = 7,face = "bold"))
 
@@
 #| label: fig-continent
-#| fig-cap: "Distribution of contient. Africa has the highest number of countries represented, followed by Asia among all 5 continents. "
+#| fig-cap: "Distribution of contient.
+Africa has the highest number of countries represented, followed by Asia among all 5 continents.
+The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
+"
 #| echo: false
@@
     axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 12, face = "bold"),
-    axis.title = element_text(size = 12)
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.title = element_text(size = 10)
   ) +
@@
   labs(
-    title = "Number of Countries by Continent",
+    title = "Distribution of Country by Continent",
     x = "Continent",
-    y = "Number of Countries"
+    y = "Number of Country"
   ) +
@@
     axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 12, face = "bold"),
+    plot.title = element_text(size = 10, face = "bold"),
     axis.title = element_text(size = 10)
@@
 
+```{r}
+#| label: fig-percentage
+#| fig-cap: "Distribution of expenditure allocated to health-related expenditures as a percentage of GDP per capita.
+Africa has the highest number of countries represented, followed by Asia among all 5 continents.
+The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
+"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+```
+
+```{r}
+#| label: fig-total
+#| fig-cap: "Distribution of contient.
+Africa has the highest number of countries represented, followed by Asia among all 5 continents.
+The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
+"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+```
+
+```{r}
+#| label: fig-income
+#| fig-cap: "Distribution of contient.
+Africa has the highest number of countries represented, followed by Asia among all 5 continents.
+The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
+"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+```
+
+```{r}
+#| label: fig-schooling
+#| fig-cap: "Distribution of contient.
+Africa has the highest number of countries represented, followed by Asia among all 5 continents.
+The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
+"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+```
+
 # Model
-
-To predict the outcome of the life expectancy of people from different regions, we developed tow linear regression models: one for the developed country and one for developing country.
-These models aim to estimate the life expectancy of people under different environment.
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-This paper utilizes linear regression models: $$LifeExpecetancy_I = \beta_0 + \beta_1 $$ $$LifeExpectancy_D = \beta_0 + \beta_1$$
+To predict the outcome of the life expectancy of people from different regions, we developed two linear regression models using R [@citeR]: one for the developed country and one for developing country.
+The outcome variable, `LifeExpectancy`, is a continuous and represents the average number of years a person is expected to live, assuming all related resources remain constant throughout their lifetime.
+These models aim to estimate the life expectancy of people under different environment.
+The GAM allows for capturing potential non-linear relationships between the predictors and the outcome.
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+The model is specified as follows:
 
+```{=tex}
 \begin{align} 
@@
 \end{align}
+```
 
+$$overall\_time\_seconds_i​=\beta_0​+s(age_i​)+\beta_1⋅gender_i​+s(race\_count_i​​)+ \beta_2⋅iaaf\_category​​ + ϵ_i​$$
+
+Where:
+
+-   $overall\_time\_seconds_i$ is the marathon finishing time in seconds for the i-th runner.
+
+-   $s(age_i)$ is a smooth function of the runner’s age at the time of the race.
+
+-   $gender_i$ is the runner's gender (treated as a categorical variable).
+
+-   $s(race\_count_i)$ is a smooth function of the total number of NYRR races the runner has participated in.
+
+-   $iaaf\_category_i$​ is the country the runner is from under IAAF standards.
+
+-   $\epsilon_i$ is the error term, assumed to be normally distributed with a mean of 0 and constant variance $ϵ_i​∼N(0,\sigma^2)$
+
+This GAM model allows for smooth, non-linear effects of continuous predictors (**`age`** and **`races_count`**) while keeping the categorical predictors (**`gender`** and **`iaaf_category`**) in a linear framework.
+
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+
+```{=tex}
+\begin{align} 
+y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_i + \gamma_i\\
+\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\beta &\sim \mbox{Normal}(0, 2.5) \\
+\gamma &\sim \mbox{Normal}(0, 2.5) \\
+\sigma &\sim \mbox{Exponential}(1)
+\end{align}
+```
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### 2024-12-01 paper/paper.qmd
initial

@@
 The primary goal of this paper is to determine which factors play a statistically significant role in driving lower life expectancy values and to offer actionable insights based on country status.
-Using Multiple Linear Regression model, this study focuses on understanding the relationship between country status(developed or developing), continent, personal average expenditure on health based on GDP, percentage of government expenditure on health, income composition of resources and year of schooling in predicting life expectancy across different countries.
+Using Multiple Linear Regression model, this study focuses on understanding the relationship between country status(developed or developing), personal average expenditure on health based on GDP, percentage of government expenditure on health, income composition of resources and year of schooling in predicting life expectancy across different countries.
 By identifying and analyzing these predictors, the study aims to highlight actionable aspects for policymakers to target in their efforts to improve population longevity effectively.
@@
 
-The measurement process refers to how real-world factors—such as the status of a country, average personal health care investment, average year of education, geographic location of a country and social determinants (country's healthcare investment, human development index of income) — are translated into numerical entries representing life expectancy in a dataset.
+The measurement process refers to how real-world factors—such as the status of a country, average personal health care investment, average year of education and social determinants (country's healthcare investment, human development index of income) — are translated into numerical entries representing life expectancy in a dataset.
 Each entry captures the average life expectancy of individuals in a specific country during a given year.
@@
 
-**Continent(`Continent`)**: This is a categorical variable that classifies the geographic location of the countries.
-It is detected by the name of the country using rpackage `countrycode`.
-The data is stored as the name of the continent(‘Africa’, ‘Oceania’, ‘Asia’, ‘Europe’, ‘North America’, ‘South America’)
-
 **Total expenditure (`TotalExpenditure`)**: This is a numerical variable that shows the general government expenditure on health as a percentage of total government expenditure.
@@
 The key variables of interest in our analysis include Country, Year, Status of the country, Life expectancy, Percentage expenditure, Total expenditure, Income composition of resources and the year of education.
-Additionally, we develop a new predictor named "Continent" to monitor each nation's geographic data.
 To make the subsequent analysis easier, we then convert variables to the proper data types and eliminate the rows that have missing data values.
@@
 2.
-**Continent(`Continent`)**: This is the categorical variable showing the geographic information of each country.
-Developed continents, for example Europe and North America, typically have well-established healthcare infrastructure, which are considered to contribute to higher life expectancy.
-Factors like clean water access, education resources, nutrition and lifestyle factors can significantly impact life expectancy and vary greatly across continents.
-@fig-continent reveals that Africa has the highest number of countries represented with the largest portion of the data.
-Other continents, America and Europe, have fewer countries included, with only 9 countries from Oceania.
+**Percentage Expenditure on Health (`PercentageExpenditure`)**: This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
+This percentage is generally expected to fall between 0% and 100%, where 100% would indicate that the total GDP per capita is allocated to healthcare.
+@fig-percentage shows that in most of the years from 2000 to 2015, most of the countries have the individual health expenditure higher than their GDP.
+It is noticeable that some developing countries have individual health expenditure less than 20% of the GDP.
 
-3.  **Percentage Expenditure on Health (`PercentageExpenditure`)**: This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
-
-4.
+3.
 **Total expenditure (`TotalExpenditure`)**: This variable shows the general government expenditure on health as a percentage of total government expenditure.
@@
 
-5. **Income composition of resource (`IncomeComposition`)**: his is a numerical variable representing the income component of the Human Development Index (HDI).
+4.  **Income composition of resource (`IncomeComposition`)**: his is a numerical variable representing the income component of the Human Development Index (HDI).
 
-6. **Schooling (`Schooling`)**: This is a numerical variable showing the number of education per person.
+5.
+**Schooling (`Schooling`)**: This is a numerical variable showing the year of receiving education.
+@fig-schooling is a combination of box plot and violin plot showing the year of schooling differs by the status.
+In development countries, the average number of years of schooling is approximately 16 years, with a narrow distribution suggesting that the educational attainment in these countries is more consistent.
+In contrast, in developing countries, the average number of years od schooling is around 11 years.
+With a much wider spread and significant more outlier, the education situation in developing countries is less stable.
 
@@
 country_counts <- cleaned_expectancy %>%
-  distinct(Country, Status) %>%  # Ensure each country is only counted once
-  count(Status)  # Count the number of countries in each Status category
+  # Ensure each country is only counted once
+  distinct(Country, Status) %>%  
+   # Count the number of countries in each Status category
+  count(Status)
 
@@
 numbercountry <- ggplot(country_counts, aes(x = Status, y = n, fill = Status)) +
-  geom_bar(stat = "identity") +  # Use 'identity' to directly use the count values
-  geom_text(aes(label = n), vjust = -0.5,size = 2.5) +  # Add count labels on top of bars
+   # Use 'identity' to directly use the count values
+  geom_bar(stat = "identity") + 
+   # Add count labels on top of bars
+  geom_text(aes(label = n), vjust = -0.5,size = 2.5) +  
   labs(
@@
 ```{r}
-#| label: fig-continent
-#| fig-cap: "Distribution of contient.
-Africa has the highest number of countries represented, followed by Asia among all 5 continents.
-The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
-"
+#| label: fig-percentage
+#| fig-cap: "Distribution of Health Expenditure ranges by country status.
+With the orange color showing the developing and blue showing developed, most of the country has more than 100% of their GDP per capita allocated to health-related expenditures."
 #| echo: false
@@
 
-#Calculate the number of unique countries per continent
-continent_count <- cleaned_expectancy %>%
-  group_by(Continent) %>%
-  summarise(num_countries = n_distinct(Country))
+# Define percentage ranges
+ranges <- c("0%-20%", "20%-30%", "30%-50%", "50%-100%", ">100%")
 
-#Plot1: Distribution of number of data per continent
-#Create the bar plot showing the number of data per continent
-continentrow <- ggplot(cleaned_expectancy, aes(x = Continent)) +
-  geom_bar(fill = "orange", color = "white") +
+# Create a new variable to classify the ranges
+expenditure_ranges <- cleaned_expectancy %>%
+  mutate(
+    ExpenditureRange = case_when(
+      PercentageExpenditure <= 20 ~ "0%-20%",
+      PercentageExpenditure > 20 & PercentageExpenditure <= 30 ~ "20%-30%",
+      PercentageExpenditure > 30 & PercentageExpenditure <= 50 ~ "30%-50%",
+      PercentageExpenditure > 50 & PercentageExpenditure <= 100 ~ "50%-100%",
+      PercentageExpenditure > 100 ~ ">100%"
+    )
+  ) %>%
+  # Ensure the right order
+  mutate(ExpenditureRange = factor(ExpenditureRange, levels = ranges))
+
+# Plot the histogram of expenditure ranges separated by status
+ggplot(expenditure_ranges, aes(x = ExpenditureRange, fill = Status)) +
+  geom_bar(stat = "count", position = "dodge", color = "white", alpha = 0.7) +
+  # Adds count on top of each bin
+  geom_text(stat='count', aes(label = ..count..), position = position_dodge(width = 0.8), vjust = - 0.5, size = 2.5) +
+  scale_fill_manual(values = c("Developed" = "blue", "Developing" = "orange")) +
   labs(
-    title = "Distribution of Count by Continent",
-    x = "Continent",
-    y = "Count"
+    title = "Distribution of Health Expenditure Ranges by Country Status",
+    x = "Health Expenditure Range (% of GDP per Capita)",
+    y = "Count",
+    fill = "Status"
   ) +
@@
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 10, face = "bold"),
-    axis.title = element_text(size = 10)
-  ) +
-  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
-
-# Plot2: The distribution of number of countries each continent
-#Create the bar plot showing the number of unique countries per continent
-continentnumber <-ggplot(continent_count, aes(x = Continent, y = num_countries)) +
-  geom_bar(stat = "identity", fill = "#FFA07A", color = "white") +
-  labs(
-    title = "Distribution of Country by Continent",
-    x = "Continent",
-    y = "Number of Country"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 10, face = "bold"),
-    axis.title = element_text(size = 10)
-  ) +
-  geom_text(aes(label = num_countries), vjust = -0.5, size = 2.5)
-
-# Arrange the plots side by side
-grid.arrange(continentnumber, continentrow, ncol = 2)
-```
-
-```{r}
-#| label: fig-percentage
-#| fig-cap: "Distribution of expenditure allocated to health-related expenditures as a percentage of GDP per capita.
-Africa has the highest number of countries represented, followed by Asia among all 5 continents.
-The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
-"
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
+    legend.position = "right",
+    axis.text.x = element_text(angle = 45, hjust = 1), # Adjusts the x-axis labels for clarity
+    plot.title = element_text(size = 10,face = "bold")) 
 ```
@@
 
+# Define percentage ranges
+ranges <- c("0%-2%", "2%-4%", "4%-6%", "6%-8%", "8%-10%", "10%-12%","12%-14%", ">14%")
+
+# Create a new variable to classify the ranges
+countryexpenditure <- cleaned_expectancy %>%
+  mutate(
+    TotalRange = case_when(
+      TotalExpenditure <= 2 ~ "0%-2%",
+      TotalExpenditure > 2 & TotalExpenditure <= 4 ~ "2%-4%",
+      TotalExpenditure > 4 & TotalExpenditure <= 6 ~ "4%-6%",
+      TotalExpenditure > 6 & TotalExpenditure <= 8 ~ "6%-8%",
+      TotalExpenditure > 8 & TotalExpenditure <= 10 ~ "8%-10%",
+      TotalExpenditure > 10 & TotalExpenditure <= 12 ~ "10%-12%",
+      TotalExpenditure > 12 & TotalExpenditure <= 14 ~ "12%-14%",
+      TotalExpenditure > 14 ~ ">14%"
+    )
+  ) %>%
+  # Ensure the right order
+  mutate(TotalRange = factor(TotalRange, levels = ranges))
+
+summary(countryexpenditure$TotalRange)
+table(countryexpenditure$TotalRange)
+
+# Plot the histogram of expenditure ranges separated by status
+ggplot(countryexpenditure, aes(x = TotalRange, fill = Status)) +
+  geom_bar(stat = "count", position = "dodge", color = "white", alpha = 0.7) +
+  # Adds count on top of each bin
+  geom_text(stat='count', aes(label = ..count..), position = position_dodge(width = 0.8), vjust = - 0.5, size = 2.5) +
+  scale_fill_manual(values = c("Developed" = "lightblue", "Developing" = "salmon")) +
+  labs(
+    title = "Distribution of Government Expenditure on Health as Percentage Range by Country Status",
+    x = "Government Expenditure Range (%)",
+    y = "Count",
+    fill = "Status"
+  ) +
+  theme_minimal() +
+  theme(
+    # Sidebar for the legend
+    legend.position = "right",
+    axis.text.x = element_text(angle = 45, hjust = 1), # Adjusts the x-axis labels for clarity
+    plot.title = element_text(size = 10,face = "bold"))
+
 ```
@@
 #| label: fig-income
-#| fig-cap: "Distribution of contient.
-Africa has the highest number of countries represented, followed by Asia among all 5 continents.
-The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
-"
+#| fig-cap: "Combined Box plot and Violin plot of income component of the Human Development Index (HDI) showing the variance and the average of the income component under status of different statuses."
 #| echo: false
@@
 
+# Create a combined boxplot and violin plot
+ggplot(cleaned_expectancy, aes(x = Status, y = IncomeComposition, fill = Status)) +
+  # Violin plot shows distribution
+  geom_violin(trim = FALSE, alpha = 0.5) + 
+  # Boxplot shows summary statistics
+  geom_boxplot(width = 0.2, alpha = 0.7, outlier.color = "red", outlier.shape = 16) + 
+  # Highlight mean
+  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkblue") + 
+  labs(
+    title = "Income Composition of Resources by Country Status",
+    x = "Country Status",
+    y = "Income Composition (HDI Contribution)"
+  ) +
+  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "salmon")) +
+  theme_minimal() +
+  theme(
+    # Remove legend as x-axis indicates status
+    legend.position = "none", 
+    axis.text.x = element_text(angle = 0, hjust = 0.5)
+  )
 ```
@@
 #| label: fig-schooling
-#| fig-cap: "Distribution of contient.
-Africa has the highest number of countries represented, followed by Asia among all 5 continents.
-The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
-"
+#| fig-cap: "Distribution of school separate by Status.
+In developed countries, the average number of years of schooling is approximately 16 years, typically following a bell-shaped distribution.
+In contrast, in developing countries, the average number of years of schooling is around 11 years.
+However, the variance in the years of schooling is significantly larger."
 #| echo: false
@@
 
+# Create a combined boxplot and violin plot
+ggplot(cleaned_expectancy, aes(x = Status, y = Schooling, fill = Status)) +
+  # Violin plot shows distribution
+  geom_violin(trim = FALSE, alpha = 0.5) + 
+  # Boxplot shows summary statistics
+  geom_boxplot(width = 0.2, alpha = 0.7, outlier.color = "red", outlier.shape = 16) + 
+  # Highlight mean
+  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkblue") + 
+  labs(
+    title = "Schooling by Country Status",
+    x = "Country Status",
+    y = "Year of Schooling"
+  ) +
+  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "pink")) +
+  theme_minimal() +
+  theme(
+    # Remove legend as x-axis indicates status
+    legend.position = "none", 
+    axis.text.x = element_text(angle = 0, hjust = 0.5)
+  )
 ```
@@
 
-```{=tex}
 \begin{align} 
@@
 \end{align}
-```
-
-$$overall\_time\_seconds_i​=\beta_0​+s(age_i​)+\beta_1⋅gender_i​+s(race\_count_i​​)+ \beta_2⋅iaaf\_category​​ + ϵ_i​$$
 
@@
 
--   $overall\_time\_seconds_i$ is the marathon finishing time in seconds for the i-th runner.
+-   $Lifeexpectancy\_developed$ is the life expectancy of developed country.
 
--   $s(age_i)$ is a smooth function of the runner’s age at the time of the race.
+-   $Lifeexpectancy\_developing$ is the life expectancy of developing country.
 
--   $gender_i$ is the runner's gender (treated as a categorical variable).
+-   $PercentageExpenditure$ is a smooth function of the runner’s age at the time of the race.
 
--   $s(race\_count_i)$ is a smooth function of the total number of NYRR races the runner has participated in.
+-   $Continent$ is
 
--   $iaaf\_category_i$​ is the country the runner is from under IAAF standards.
+-   $TotalExpenditure$ is the runner's gender (treated as a categorical variable).
+
+-   $IncomeComposition$ is a smooth function of the total number of NYRR races the runner has participated in.
+
+-   $Schooling$​ is the country the runner is from under IAAF standards.
 
@@
 
-```{=tex}
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-```
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
@@
 
+## Idealized Survey
+
+**Survey: Understanding Life Expectancy and Influencing Factor**
+
+Thank you for participating in this survey.
+This survey aims to gather insights into the factors influencing life expectancy, including health expenditure, education, ethnicity, government spending on healthcare, and income levels.
+Your responses will help us understand individual perspectives and experiences towards national policy.
+Participation is voluntary, and your answers will remain anonymous.
+
+**Contact Information:** If you have any questions about the survey or the data collection process, please contact
+
+**Survey Coordinator**: Yanfei Huang\
+**Email**: yanfei.huang\@mail.utoronto.ca
+
+**Section 1: Personal Health Expenditure**
+
+**1.What percentage of your monthly income do you spend on healthcare (e.g., insurance, medications, doctor visits)?**
+
+-   Less than 5%
+-   5%–10%
+-   10%–20%
+-   More than 20%
+
+**2.Do you or your household have health insurance coverage?**
+
+-   Yes
+-   No
+
+**3. How frequently do you visit a healthcare professional(eg.doctors, nurse) in a year?**
+
+-   0-1 times
+-   2-5 times
+-   6-10 times
+-   More than 10 times
+
+**Section 2: Education Background**
+
+**4.What is the highest level of education you have completed?**
+
+-   No formal education
+-   Primary school
+-   Secondary school
+-   College or university degree
+-   Postgraduate degree
+
+**5.How many years of formal schooling have you completed?**
+
+Please write the number: \_\_\_\_\_\_\_
+
+**Section 3: Ethnicity and Geographic Factors**
+
+**6.Which of the following best describes your ethnicity?**
+
+-   African
+-   Asian
+-   European
+-   Hispanic or Latino
+-   Middle Eastern
+-   Indigenous
+-   Other (please specify): \_\_\_\_\_\_\_
+
+**7.What's the distance to the nearest healthcare facility from your residence?**
+
+- Less than 1 km 
+- 1-5 km 
+- More than 5 km
+
+**Section 4: Government Expenditure on Healthcare**
+
+**8.Are health services in your country subsidized by the govenment?**
+
+-   Yes, fully subsidized
+-   Yes, partially subsidized
+-   No
+
+**9. What is the approximate cost of your most recent healthcare visit (in local currency)?**
+
+Please write the amount \_\_\_\_\_\_\_
+
+**10.Do public healthcare facilities in your area provide all the services you need?**
+
+-   Yes
+-   No
+-   Not applicable
+
+**Section 5: Income and Development Factor**
+
+**11.What is your approximate monthly household income after taxes?(in local currency)**
+
+-   Less than 1,000
+-   1,000 - 2,999
+-   3,000 - 4,999
+-   5,000 - 7,999
+-   8,000 - 10,999
+-   More than 11,000
+-   Prefer not to say
+
+**12.How would you describe your current financial situation?**
+
+-   Struggling to make ends meet
+-   Just getting by
+-   Comfortable, but not wealthy
+-   Financially secure
+-   Wealthy
+-   Prefer not to say
+
+**13.How often do you have difficulty affording basic healthcare (medical visits, medications, etc.)?**
+
+-   Never
+-   Rarely
+-   Sometimes
+-   Often
+-   Always
+-   Prefer not to say
+
+**Final Section**
+
+Thank you for completing this survey!
+Your responses will help capture information about economic conditions, access to healthcare and education, and basic living standards, which are critical for understanding life expectancy predictors and the impact of socioeconomic factors on health outcomes.
+
 # Additional data details
@@
 # Model details {#sec-model-details}
+
+## Additional graph for analysis
+
+```{r}
+#| label: fig-continent
+#| fig-cap: "Distribution of contient.
+Africa has the highest number of countries represented, followed by Asia among all 5 continents.
+The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
+"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+#Calculate the number of unique countries per continent
+continent_count <- cleaned_expectancy %>%
+  group_by(Continent) %>%
+  summarise(num_countries = n_distinct(Country))
+
+#Plot1: Distribution of number of data per continent
+#Create the bar plot showing the number of data per continent
+continentrow <- ggplot(cleaned_expectancy, aes(x = Continent)) +
+  geom_bar(fill = "orange", color = "white") +
+  labs(
+    title = "Distribution of Count by Continent",
+    x = "Continent",
+    y = "Count"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.title = element_text(size = 10)
+  ) +
+  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
+
+# Plot2: The distribution of number of countries each continent
+#Create the bar plot showing the number of unique countries per continent
+continentnumber <-ggplot(continent_count, aes(x = Continent, y = num_countries)) +
+  geom_bar(stat = "identity", fill = "#FFA07A", color = "white") +
+  labs(
+    title = "Distribution of Country by Continent",
+    x = "Continent",
+    y = "Number of Country"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.title = element_text(size = 10)
+  ) +
+  geom_text(aes(label = num_countries), vjust = -0.5, size = 2.5)
+
+# Arrange the plots side by side
+grid.arrange(continentnumber, continentrow, ncol = 2)
+```
 

### 2024-12-01 scripts/02-download_data.R

@@ -1,26 +1,22 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from 'https://www.kaggle.com/datasets/kumarajarshi/life-expectancy-who'
 # Author: Yanfei Huang
-# Date: 27 November 2024
+# Date: 01 December 2024
 # Contact: Yanfei Huang
 # License: University of Toronto
 # Pre-requisites: No
-# Any other information needed? Thanks to Kaggle opendataset
+# Any other information needed? N/A
 
 
 #### Workspace setup ####
 
 library(tidyverse)
 library(dplyr)
+library(readr)
 
 #### Download data ####
-raw_expectancy <- read.csv(
-  file = "https://storage.googleapis.com/kagglesdsdata/datasets/12603/17232/Life%20Expectancy%20Data.csv?X-Goog-Algorithm=GOOG4-RSA-SHA256&X-Goog-Credential=gcp-kaggle-com%40kaggle-161607.iam.gserviceaccount.com%2F20241116%2Fauto%2Fstorage%2Fgoog4_request&X-Goog-Date=20241116T194624Z&X-Goog-Expires=259200&X-Goog-SignedHeaders=host&X-Goog-Signature=3625aa8b39faeba57e2605fc4ede1027504871228e573a70f4f705cea9d74260f99d2a360e566d2fba1c03b80eeff5824a7a845caef69a9dca7dfbc22e7b1e34b8786b69fa2416697ca00b63f04e4f99f44a1aa11a1e74857c71ffbddd0653c4bd37759edb8b8515c4c4c0d8b7a0f77e46fb3d4718d7900704e030ed32fd4acf61a70dbefcaca71af63a829c9f84c2aefc832e26fe961de5b577dc39b8b340e77568aac54c5e1ef692ed842a48b77eaf6ce82c6e9bd36ffc0a21cf5657a21179063af495850f0c9a45f47f3eb2f82f102f6525837e51fd269221ef5711b04a4742428bd225098bed5de89a54971001f6ccc2c208eeaf1675a09cd60591bfb463"
-)
 
-
-#### Save data ####
-# change raw_data to whatever name you assigned when you downloaded it.
-write_csv(raw_expectancy, "data/01-raw_data/raw_data.csv") 
-
-         
+# go to link
+# select predictors
+#
+lfex_data <- read_csv("/Users/wendyhuang/lifeexpectancy/data/01-raw_data/WHOlifeexpectancy.csv")

### 2024-12-01 scripts/03-clean_data.R

@@ -17,12 +17,11 @@ library(countrycode)
 
 #### Clean data ####
 #Load the dataset
-raw_expectancy <- read_csv("data/01-raw_data/raw_data.csv")
+raw_expectancy <- read_csv("/Users/wendyhuang/lifeexpectancy/data/01-raw_data/WHOlifeexpectancy.csv")
 
 # Data cleaning by Filter and select relevant columns, renaming complex names, 
 # filtering invalid entries, round columns into specific decimals 
-cleaned_expectancy <- tryCatch(
-  {
+cleaned_expectancy <-
     raw_expectancy |> 
   select(Country, Year, Status, Life.expectancy, percentage.expenditure, Total.expenditure,
          Income.composition.of.resources, Schooling) |>
@@ -60,5 +59,211 @@ cleaned_expectancy <- tryCatch(
     NULL  # Return NULL if error occurs
     })
 
+head(cleaned_expectancy)  # Check the first few rows
+summary(cleaned_expectancy) 
+
+
+
 #### Save data ####
 write_csv(cleaned_expectancy, "data/02-analysis_data/analysis_data.parquet")
+write_csv(cleaned_expectancy, "data/02-analysis_data/analysis_data.csv")
+
+
+
+
+
+
+
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+library(arrow)
+
+#### Clean data ####
+# Read in the data
+lfex_data <- read_csv("/Users/wendyhuang/lifeexpectancy/data/01-raw_data/WHOlifeexpectancy.csv")
+
+
+# Function to extract the number before the opening square bracket
+extract_number <- function(x) {
+  gsub("\\[.*", "", x)
+}
+
+lecleaned_data <- lfex_data %>%
+  filter(!is.na(Location)) %>%       # Remove rows where 'Location' is NA
+  select(
+    Indicator,                       # Correct column name
+    Location,                        # Correct column name
+    Period,                          # Correct column name
+    Dim1,                            # Correct column name
+    Value                            # Correct column name
+  )|>
+  mutate(
+    `Value` = extract_number(`Value`))
+
+# Function to extract the number before the opening square bracket
+extract_number <- function(x) {
[…]

### 2024-12-01 scripts/06-model_data.R

@@ -25,7 +25,6 @@ cleaned_expectancy <- cleaned_expectancy %>%
     LifeExpectancy = as.numeric(LifeExpectancy),
     Status = as.factor(Status),
     PercentageExpenditure = as.numeric(PercentageExpenditure),
-    Continent = as.factor(Continent),
     TotalExpenditure = as.numeric(TotalExpenditure),
     IncomeComposition = as.numeric(IncomeComposition),
     Schooling = as.numeric(Schooling)
@@ -34,18 +33,18 @@ cleaned_expectancy <- cleaned_expectancy %>%
 
 ### Model for developing country based on various predictors ###
 lm_model_developing <-
-  lm(LifeExpectancy ~ PercentageExpenditure + Continent + TotalExpenditure + IncomeComposition + Schooling,
-     data = cleaned_expectancy %>% filter (Status == 'Developing') )
+  lm(LifeExpectancy ~ PercentageExpenditure + TotalExpenditure + IncomeComposition + Schooling,
+     data = cleaned_expectancy %>% filter (Status == 'Developing'))
 
 ### Model for developed country based on various predictors###
 lm_model_developed <-
-  lm(LifeExpectancy ~ PercentageExpenditure + Continent + TotalExpenditure + IncomeComposition + Schooling,
+  lm(LifeExpectancy ~ PercentageExpenditure + TotalExpenditure + IncomeComposition + Schooling,
      data = cleaned_expectancy %>% filter (Status == 'Developed') )
 
 
 #### Save modified data for model as a CSV + parquet and save model as RDS ####
-write_csv(cleaned_expectancy, here::here("data/02-analysis_data/analysis_data.csv"))
-write_parquet(cleaned_expectancy, here::here('data/02-analysis_data/analysis_data.parquet'))
+write_csv(cleaned_expectancy, "data/02-analysis_data/analysis_data.csv")
+write_parquet(cleaned_expectancy, 'data/02-analysis_data/analysis_data.parquet')
 saveRDS(lm_model_developing, file = "models/lm_model_developing.rds")
 saveRDS(lm_model_developed, file = "models/lm_model_developed.rds")
 

### 2024-12-01 scripts/02-download_data.R
initial

@@ -16,7 +16,13 @@ library(readr)
 
 #### Download data ####
 
-# go to link
-# select predictors
-#
+# To Access the WHO dataset: 
+# 1. Visit the [WHO website]
+# 2. Go to link: 'https://www.who.int/data/gho/data/indicators/indicator-details/GHO/life-expectancy-at-age-60-(years)'
+# 3. Select predictors: 
+# Year:2015 - 2020; Location Type: Country; by: Sex; Sex: Both Sex, Male, Female; 
+# Indicator: Life expectancy at birth(years), Life expectancy at age 60(years); Select all countries in WHO region 
+# 4. Download the `.csv` file with selected variables
+# 5. Upload, Save and read the csv file 
 lfex_data <- read_csv("/Users/wendyhuang/lifeexpectancy/data/01-raw_data/WHOlifeexpectancy.csv")
+

### 2024-12-01 paper/paper.qmd
initial

@@
 title: "Global Life Expectancy: Unraveling Health and Economic Determinants (2000-2015)"
-subtitle: "Analyzing Critical Factors Shaping Mortality and Well-Being Across 155 Nations"
+subtitle: "Multiple Linear Regression Analyzing Critical Factors Shaping Life Expectancy "
 author: 
@@
 thanks: "Code and data are available at: [https://github.com/wendyhuan/lifeexpectancy](https://github.com/wendyhuan/lifeexpectancy)."
-date: 30 November 2024
+date: 02 December 2024
 date-format: long

### 2024-12-01 scripts/03-clean_data.R

@@ -1,106 +1,36 @@
 #### Preamble ####
 # Purpose: Cleans the raw life expectancy data and recorded by 10 columns
 # Author:Yanfei Huang
-# Date: 25 November 2024
+# Date: 01 December 2024
 # Contact: yanfei.huang@mail.utoronto.ca
 # License: University of Toronto
-# Pre-requisites: raw data downloaded and saved from Kaggle
+# Pre-requisites: Raw data downloaded and saved 
 # Any other information needed? No
 
-#### Workspace setup ####
-install.packages("countrycode")
-library(tidyverse)
-library(dplyr)
-library(janitor)
-library(arrow)
-library(countrycode)
-
-#### Clean data ####
-#Load the dataset
-raw_expectancy <- read_csv("/Users/wendyhuang/lifeexpectancy/data/01-raw_data/WHOlifeexpectancy.csv")
-
-# Data cleaning by Filter and select relevant columns, renaming complex names, 
-# filtering invalid entries, round columns into specific decimals 
-cleaned_expectancy <-
-    raw_expectancy |> 
-  select(Country, Year, Status, Life.expectancy, percentage.expenditure, Total.expenditure,
-         Income.composition.of.resources, Schooling) |>
-  rename(LifeExpectancy = Life.expectancy,
-         PercentageExpenditure = percentage.expenditure,
-         TotalExpenditure = Total.expenditure,
-         IncomeComposition = Income.composition.of.resources) |>
-  filter (
-    # filtering invalid entries 
-    !is.na(Year),
-    !is.na(Status),
-    !is.na(LifeExpectancy),
-    !is.na(PercentageExpenditure),
-    !is.na(TotalExpenditure),
-    !is.na(IncomeComposition),
-    !is.na(Schooling) ) |>
-  mutate(
-    #Round specific columns to varying decimal places
-    LifeExpectancy = round(LifeExpectancy, 2),
-    PercentageExpenditure = round(PercentageExpenditure, 4),
-    TotalExpenditure = round(TotalExpenditure, 2),
-    IncomeComposition = round(IncomeComposition, 3),
-    Schooling = round(Schooling, 1)) |>
-  mutate(
-    #Change the name of South Korea avoiding misunderstanding
-    Country = ifelse(Country == "Republic of Korea",
-                           "South Korea", Country) )|>
-  mutate(
-    #create continent variable and check the continent of each country
[…]

### 2024-12-01 paper/paper.qmd
paper

@@
 ---
-title: "Global Life Expectancy: Unraveling Health and Economic Determinants (2000-2015)"
+title: "Global Life Expectancy: Unraveling Health and Economic Determinants (2015-2020)"
 subtitle: "Multiple Linear Regression Analyzing Critical Factors Shaping Life Expectancy "
@@
 date-format: long
-abstract: "This paper analyze life expectancy and its determinants through 155 countries and make the prediction of people from both developed and developing country.
-Multiple Linear regression is used to deploying the health and socio-economic factors.
-Predictions of life expectancy of people from developed or developing country is made according to the essential predictors.
-The finding indicates that the developed countries tend to live longer life as assumed.
-And we predict that the average age of persons in developed country is 80, while those in underdeveloped countries are 75.
+abstract: "This paper analyze life expectancy and its determinants through 155 countries and make the prediction of people from different Income Group.
+Multiple Linear regression is used to deploying the life expectanc with gender, income and region.
+Predictions of life expectancy of people from different income group is made according to these essential predictors.
+The finding indicates that the life expectancy is tend to get higher as the economic class grows.
+And we predict that the average age of person from low, lower-middle, upper-middle and high are 65,70, 75,80.
 The result of this paper will help in suggesting a country which area should be given importance in order to efficiently improve the life expectancy of its population."
@@
 # load data
-cleaned_expectancy <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
-
+lelecleaned_data<- read_parquet("data/02-analysis_data/lelecleaned.parquet")
+lea60 <- read_parquet("data/02-analysis_data/lea60.parquet")
+leab <- read_parquet("data/02-analysis_data/leab.parquet")
+male_table <- read_parquet("data/02-analysis_data/male_table.parquet")
+female_table <- read_parquet("data/02-analysis_data/female_table.parquet")
 ```
@@
 
-Life expectancy is a critical measure of a population's overall health and well-being, shaped by various factors such as personal expenditure on health, government healthcare access, economic stability, and social structures.
-The index of life expectancy is generally served as a benchmark for development, indicating the effectiveness of interventions in reducing mortality and improving well-being.
-Higher life expectancy is believed to linked to better living standards, access to education, and equitable healthcare.
-Conversely, low life expectancy often signals systemic challenges such as poverty, disease burden, and inadequate healthcare access [@socialdeterminantsofhealth].
+Life expectancy is a critical measure of a population's overall health and well-being, shaped by various factors such as gender, geographic location and economic group.
+The index of life expectancy is generally served as a benchmark for income group, indicating the effectiveness of interventions in reducing mortality and improving well-being.
+Higher life expectancy is believed to linked to stronger physical factor, better living standards, and geographic location.
+Conversely, low life expectancy often signals systemic challenges such as weaker health, lower economic situation, and inadequate healthcare access of different region.
+[@socialdeterminantsofhealth].
 

### 2024-12-01 scripts/03-clean_data.R
inital

@@ -205,17 +205,10 @@ leab <- lelecleaned_data %>%
 
 #Create a table of life expectancy at birth of Male
 male_table <- leab[leab$Gender == 'Male', ]
-male_table <- male_table |>
-  summarise(
-    "Gender" = "Male",
-    "Average life ex" = mean(`Life Expectancy`))
+
 
 # Create a table of life expectancy at birth of Female
 female_table <- leab[leab$Gender == 'Female', ]
-female_table <- female_table |>
-  summarise(
-    "Gender" = "Female",
-    "Average life ex" = mean(`Life Expectancy`))
 
 
 

### 2024-12-01 scripts/03-clean_data.R
iunital

@@ -219,9 +219,9 @@ write_csv(lea60, "data/02-analysis_data/lea60.csv")
 write_csv(male_table, "data/02-analysis_data/male_table.csv")
 write_csv(female_table, "data/02-analysis_data/female_table.csv")
 write_csv(leab, "data/02-analysis_data/leab.csv")
-write_csv(lelecleaned_data, "data/02-analysis_data/lelecleaned.parquet")
-write_csv(lea60, "data/02-analysis_data/lea60.parquet")
-write_csv(leab, "data/02-analysis_data/leab.parquet")
-write_csv(male_table, "data/02-analysis_data/male_table.parquet")
-write_csv(female_table, "data/02-analysis_data/female_table.parquet")
+write_parquet(lelecleaned_data, "data/02-analysis_data/lelecleaned.parquet")
+write_parquet(lea60, "data/02-analysis_data/lea60.parquet")
+write_parquet(leab, "data/02-analysis_data/leab.parquet")
+write_parquet(male_table, "data/02-analysis_data/male_table.parquet")
+write_parquet(female_table, "data/02-analysis_data/female_table.parquet")
 

### 2024-12-01 paper/paper.qmd
initial

@@
 # load data
-lelecleaned_data<- read_parquet("data/02-analysis_data/lelecleaned.parquet")
+lelecleaned_data <- read_parquet("data/02-analysis_data/lelecleaned.parquet")
 lea60 <- read_parquet("data/02-analysis_data/lea60.parquet")
@@
 
-The primary goal of this paper is to determine which factors play a statistically significant role in driving lower life expectancy values and to offer actionable insights based on country status.
-Using Multiple Linear Regression model, this study focuses on understanding the relationship between country status(developed or developing), personal average expenditure on health based on GDP, percentage of government expenditure on health, income composition of resources and year of schooling in predicting life expectancy across different countries.
+The primary goal of this paper is to determine which factors play a statistically significant role in driving lower life expectancy values and to offer actionable insights based on different income group.
+Using Multiple Linear Regression model and Bayesian model, this study focuses on understanding the relationship between Gender, Region and different income group in predicting life expectancy across different countries.
 By identifying and analyzing these predictors, the study aims to highlight actionable aspects for policymakers to target in their efforts to improve population longevity effectively.
 
-Related Research has shown that higher healthcare expenditure of government positively impact life expectancy [@valueofvaccination].
-Additionally, addressing social determinants such as education and income inequality has been identified as a vital pathway to improving longevity [@healthequity].
-Studies also highlight the role of global collaboration in tackling health crises, which can disproportionately affect lower-income nations, mostly developing countries under certain continents, further influencing life expectancy disparities [@World_Health_Organization].
+Related Research has shown that there exist difference between men and women related with biological, behavioral, and socioeconomic factors, highlighting that gender-specific health behaviors and societal roles influence longevity [@GenderandLifeExpectancy].
+Higher-income individuals tend to live longer due to better access to healthcare and healthier lifestyles, with notable regional disparities even within similar income groups [@IncomeGroupsandLongevity].
+Additionally, regional socioeconomic differences on health outcomes, especially life expectancy.
+It emphasizes that addressing regional inequities in wealth and resources is essential for improving population health globally.
+[@RegionalVariations].
 
-Findings from this paper reveal that countries with greater healthcare spending tend to achieve higher life expectancy, while factors like income inequality and absence of education emerge as significant obstacles.
+Findings from this paper reveal that countries of higher income group tend to achieve higher life expectancy, while factors like lower income and poverty region emerge as significant obstacles.
 The analysis underscores the importance of targeted interventions in key areas such as healthcare accessibility and economic equity to address disparities in life expectancy.

### 2024-12-02 scripts/00-simulate_data.R
initial

@@ -12,68 +12,52 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
-library(countrycode)
+
+# Set seed for reproducibility
 set.seed(853)
 
-
 #### Define data columns ####
-# Set numbers of rows in simulated data
-n<-50
 
-# Create a mapping of countries to status
-country_status_map <- tibble(
-  country = c(
-  "Canada", "Australia", "Argentina", "Brazil", "United States of America", "Portugal", "Qatar", "Republic of Korea"),
-  status = c(
-    'Developing', 'Developed', 'Developing', 'Developing', 'Developed', 'Developed', 'Developing', 'Developing')
-  )
+# Define the list of countries
+countries <- c("country_A", "country_B","country_C")
 
-# Define Year 
-year <- 2000:2015
+# Define number of rows
+n <- 100
 
+# Define gender
+genders <- c("Male", "Female")
 
-#### Simulate data
-simulated_expectancy <- tibble(
-  #randomly select countries from the 10 countries above
-  country = as.character(sample(country_status_map, n, replace = TRUE)) )%>%
-  
-  # Add the fixed status based on the country
-  left_join(country_status_map, by = "country") %>%  
-  
-  mutate(
-  #randomly select years from 2000 to 2015
-  year = sample(year, n, replace = TRUE),
-  
-  life_expectancy = ifelse(status == "Developed",
-                           #for developed countries, draw normal distribution with mean 80 and standard deviation of 5
-                           rnorm(n, mean = 80, sd = 5),
-                           #for developing countries, draw normal distribution with mean 65 and standard deviation of 10
-                           rnorm(n, mean = 65, sd = 10)),
-  
-  #random value between 1 to 100,000 of Expenditure on health as a percentage of Gross Domestic Product per capita(%)
-  percentage_expenditure = runif(n, min = 1, max = 100000),
-  
-  #uniform distribution of value of general government expenditure as a  between 1 and 20
-  total_expenditure = runif(n, min = 1, max = 20),
-  
-  #uniform distribution of random values of human development index of income composition between 0.3 and 0.9
-  income_composition_resources = runif(n, min = 0.3, max = 0.9),
-  
-  schooling = ifelse(status == "Developed",
-                     #for developed countries, draw normal distribution with mean 15 and standard deviation of 2
-                     rnorm(n, mean = 15, sd = 2),
[…]

### 2024-12-02 scripts/00-simulate_data.R
initial

@@ -21,9 +21,6 @@ set.seed(853)
 # Define the list of countries
 countries <- c("country_A", "country_B","country_C")
 
-# Define number of rows
-n <- 100
-
 # Define gender
 genders <- c("Male", "Female")
 
@@ -61,3 +58,4 @@ head(simulated_data)
 
 # Write the simulated data in the csv file
 write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")
+

### 2024-12-02 scripts/01-test_simulated_data.R

@@ -12,91 +12,69 @@
 
 #### Workspace setup ####
 library(tidyverse)
-library(countrycode)
+library(testthat)
+library(arrow)
 
-simulated_expectancy <- read_csv("data/00-simulated_data/simulated_data.csv")
+# load data 
+simulated_data <- read_csv("~/lifeexpectancy/data/00-simulated_data/simulated_data.csv")
+
+#### Test data ####
 
 # Test if the data was successfully loaded
-if (exists("simulated_expectancy")) {
+test_that("Simulated data has correct structure", {
+  if (exists("simulated_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
+# Test that the data has 4 columns
+expect_equal(ncol(simulated_data), 4)
 
-#### Test data ####
+# Test that the data has the correct column names
+expected_columns <- c(
+  "Country", "Gender", "Period", "Life Expectancy")
+expect_equal(colnames(simulated_data), expected_columns)
+})
 
-# Check if the dataset has 50 rows
-if (nrow(analysis_data) == 50) {
-  message("Test Passed: The dataset has 50 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 50 rows.")
+# Define a smaller test set of predictors for simplicity
+test_countries <- c("USA", "Canada")
+test_genders <- c("Male", "Female")
+test_periods <- 2020:2022
+
+# Initialize an empty list to store test simulated data
+test_simulated_data <- list()
+
+# Simulate test data for each combination of country, gender, and period
+for (country in test_countries) {
+  for (gender in test_genders) {
+    for (period in test_periods) {
+      # Create a small test dataset for the current combination
+      data <- tibble(
+        Country = country,
+        Gender = gender,
+        Period = period,
+        `Life Expectancy` = runif(3, 60, 80) # Random values between 60 and 90
+      )
+      
+      # Append the data to the list
+      test_simulated_data <- append(test_simulated_data, list(data))
+    }
+  }
 }
 
+# Combine the list into a single data frame
+test_final_data <- bind_rows(test_simulated_data)
 
+# Display a preview of the test data
+print(test_final_data)
 
-
-
-
-
-
-
-
-
-
-
-
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
-
[…]

### 2024-12-02 scripts/03-clean_data.R
initial

@@ -142,8 +142,8 @@ Europe <- c("Albania", "Andorra", "Armenia", "Austria", "Azerbaijan", "Belarus",
 North_America <- c("Antigua and Barbuda", "Bahamas", "Barbados", "Belize", "Canada", 
                    "Costa Rica", "Cuba", "Dominica", "Dominican Republic", "El Salvador", 
                    "Grenada", "Guatemala", "Haiti", "Honduras", "Jamaica", "Mexico", 
-                   "Nicaragua", "Panama", "Saint Kitts and Nevis", "Saint Lucia", 
-                   "Saint Vincent and the Grenadines", "Trinidad and Tobago", 
+                   "Nicaragua", "Panama","Puerto Rico", "Saint Kitts and Nevis", "Saint Lucia", 
+                   "Saint Vincent and the Grenadines", "Trinidad and Tobago",
                    "United States of America")
 
 # Make a mapping for countries in Oceania

### 2024-12-02 paper/paper.qmd
initial

@@
 date-format: long
-abstract: "This paper analyze life expectancy and its determinants through 155 countries and make the prediction of people from different Income Group.
+abstract: "This paper analyze life expectancy and its determinants through 184 countries and make the prediction of people from different Income Group.
 Multiple Linear regression is used to deploying the life expectanc with gender, income and region.
@@
 # load data
-lelecleaned_data <- read_parquet("data/02-analysis_data/lelecleaned.parquet")
-lea60 <- read_parquet("data/02-analysis_data/lea60.parquet")
-leab <- read_parquet("data/02-analysis_data/leab.parquet")
-male_table <- read_parquet("data/02-analysis_data/male_table.parquet")
-female_table <- read_parquet("data/02-analysis_data/female_table.parquet")
+lelecleaned_data <- read_parquet("~/lifeexpectancy/data/02-analysis_data/lelecleaned.parquet")
+lea60 <- read_parquet("~/lifeexpectancy/data/02-analysis_data/lea60.parquet")
+leab <- read_parquet("~/lifeexpectancy/data/02-analysis_data/leab.parquet")
+male_table <- read_parquet("~/lifeexpectancy/data/02-analysis_data/male_table.parquet")
+female_table <- read_parquet("~/lifeexpectancy/data/02-analysis_data/female_table.parquet")
 ```
@@
 The primary goal of this paper is to determine which factors play a statistically significant role in driving lower life expectancy values and to offer actionable insights based on different income group.
+According to the World Bank Income Group, the countries are classified into low, lower-middle, upper-middle, and high based on the country's Gross National Income.
 Using Multiple Linear Regression model and Bayesian model, this study focuses on understanding the relationship between Gender, Region and different income group in predicting life expectancy across different countries.
@@
 The data used in this analysis originates from The World Health Organization’s (WHO) and Global Health Observatory (GHO) [@lifeexpectancy].
-This data-set related to life expectancy, health factors for 155 countries has been collected from WHO data repository website and its corresponding economic data was collected from United Nation website.
+This data-set related to life expectancy, health factors for 184 countries has been collected from WHO data repository website and its corresponding economic data was collected from United Nation website.
 Among all categories of health-related factors only those socio-economic factors on the national level were chosen for global scale analysis.
@@
 
-The measurement process refers to how real-world factors—such as the status of a country, average personal health care investment, average year of education and social determinants (country's healthcare investment, human development index of income) — are translated into numerical entries representing life expectancy in a dataset.
+The measurement process refers to how real-world factors—such as the Gender, geographic location of a country and income group - are translated into numerical entries representing life expectancy in a dataset.
 Each entry captures the average life expectancy of individuals in a specific country during a given year.
 
-**Life Expectancy (`LifeExpectancy`)**: This variable represents the average number of years a person is expected to live, assuming current mortality conditions persist.
+**Life Expectancy (`Life Expectancy`)**: This variable, life expectancy at birth, represents the number of years a person is expected to live , assuming current mortality conditions persist.
 It is derived using data from national health records, the World Health Organization (WHO) and Global Health Observatory (GHO).
-The values are calculated and represented in age between 36.3 to 89.
+The data on the raw dataset is recorded as a range of age.
+For simple analysis, we drop the range and take the average of year with one decimal.
+The values are calculated and represented in age between 10.1 to 87.4.
 
-**Percentage Expenditure on Health (`PercentageExpenditure`)**: This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
-The data is typically collected from government reports, economic surveys, and global health databases.
-It indicates the level of personal financial investment in the health sector and is expressed as a percentage.
+**Income Group(`Income_Group`)**: This is a categorical variable that classifies countries into four groups by the country's Gross National Income according to the latest index from World Bank Income Group.
+The countries are classified into low, lower-middle, upper-middle, and high under the standard as follow.
+Low-income economies is defined as a country with a gross national income less than \$1135, lower-middle is between the range to \$1136 to \$4465, upper-middle in the range of \$4465 to \$13845 and high is more than \$13846.
 
-**Schooling (`Schooling`)**: This variable captures the average number of years of education received by individuals in a country.
-Data is obtained from educational surveys and censuses conducted by international and national organizations.
-The values are recorded in years and used to assess the link between education and health outcomes like life expectancy.
-The data range from 0 to 20.7
+**Gender(`Gender`)**: The gender of the population of each country is included as a categorical variable (Male/Female/Both Sex).
 
-**Status (`Status`)**: This is a categorical variable that classifies countries as "Developed" or "Developing," based on various socio-economic and health indicators accepted globally.
-It provides context for comparing life expectancy across different stages of national development.
-
-**Total expenditure (`TotalExpenditure`)**: This is a numerical variable that shows the general government expenditure on health as a percentage of total government expenditure.
-The number drop of the percentage and shows as the number between 0 to 100, where higher values indicate a greater share of government spending allocated to health.
-
-**Income composition of resource (`IncomeComposition`)**: This is a numerical variable representing the income component of the Human Development Index (HDI).
-It reflects the contribution of income to human development, with values ranging from 0 to 1, where higher values signify a greater income contribution to overall development.
+**Region(Region)**: This is a categorical variable that classifies the geographic location of the countries.
+It is mapped one by one by the name of the country.
+The data is stored as the name of the continent(‘Africa’, ‘Oceania’, ‘Asia’, ‘Europe’, ‘North America’, ‘South America’).
 
@@
 The raw life expectancy data underwent a several cleaning steps to ensure it was accurate, consistent and ready for analysis.
-We first select and rename key variables from raw data to focus on relevant information.
-The key variables of interest in our analysis include Country, Year, Status of the country, Life expectancy, Percentage expenditure, Total expenditure, Income composition of resources and the year of education.
+The goal of this cleaning process is to create a table including income group (high, upper middle, lower middle, low), gender (Male, Female, Both Sex), region (Asia, Europe, North America, South America, Africa, Oceania) as rows and life expectancy as column.
+
+To make such table, we first select and rename key variables from raw data to focus on relevant information.
 To make the subsequent analysis easier, we then convert variables to the proper data types and eliminate the rows that have missing data values.
-To keep things neat, we organize the decimal for every piece of numerical data.
-The cleaned dataset was then saved as a Parquet file for efficient storage and further analysis.
+To keep things neat, we organize the decimal for every piece of numerical data and drop the percentage symbol.
+The income group column and the region column was not given in the raw dataset.
+We created a mapping over country name to four income group according to the index given by World Bank Income Group and save the data under "Income_Group".
+We as well made a mapping to the countries according to its continent and saved as "Region".
+We again merge the table, removing repeated columns and rows.
+For easier visualization, we created four tables, which are grouped by life expectancy at age 60, life expectancy at birth, life expectancy at birth of Male and life expectancy at birth of Female.
+
+The cleaned dataset was then saved as both CSV and Parquet file for efficient storage and further analysis.
 
@@
 
-The outcome variable is **`LifeExpendency`**.
+The outcome variable is **`Life Expendency`**.
 This is the primary dependent variable that the model is designed to predict.
@@
 
-# create plot of historical 155 countries life expectancy dividing by country status. 
-ggplot(cleaned_expectancy, aes(x = LifeExpectancy)) +
+# create plot of historical 184 countries life expectancy dividing by country status. 
+ggplot(lelecleaned, aes(x = `Life Expectancy`)) +
   geom_histogram(aes(y = ..density..), 
@@
   labs(
-    title = "Distribution of Life Expectancy by Status",
+    title = "Distribution of Life Expectancy",
     x = "Life Expectancy", y = "Density"
@@
 1.
-**Status(`Status`)**: The status of a country is the key factor influencing the life expectancy.
-We divide the life expectancy by the status of a country as it is believed that developed country generally have higher life expectancy due to better healthcare access, sanitation, and living standards, while developing countries face greater health challenges.
-This variable provides context for comparing life expectancy between different levels of country development.
-@fig-statusdistribution includes 28 developed countries and 127 developing countries.
-The graph on left shows that we've got much greater representation of developing nations across the dataset.
-Comparing both graph, we still could tell that the dataset contains significantly more data for developing countries than for developed countries, even relative to the difference in the number of countries themselves.
+**Income Group(`Income_Group`)**: The income group of a country is the key factor influencing the life expectancy.
+This variable provides context for comparing life expectancy between different levels of country income group.
+The division of the life expectancy by the income group of a country because income levels often correlate strongly with various factors affecting health and longevity.
+Higher income countries typically have more resources to invest in robust healthcare systems, with better living conditions while lower income countries often face challenges such as inadequate healthcare infrastructure and malnutrition.
+
+Following by the four income group, we would like to see the distribution of the income group of 184 WHO member countries.
+@fid-income shows that there are 55 countries at the high income group, 26 countries at low income group, 54 countries at the lower-middle group while there are 49 countries at the upper-middle group.
+With significant less low income countries, we expect to see the life expectancy lie in a comparably higher range.
+On the other hand, there might exist sever outliers dropping the mean.
 
 2.
-**Percentage Expenditure on Health (`PercentageExpenditure`)**: This variable reflects the expenditure allocated to health-related expenditures as a percentage of GDP per capita.
-This percentage is generally expected to fall between 0% and 100%, where 100% would indicate that the total GDP per capita is allocated to healthcare.
-@fig-percentage shows that in most of the years from 2000 to 2015, most of the countries have the individual health expenditure higher than their GDP.
-It is noticeable that some developing countries have individual health expenditure less than 20% of the GDP.
+**Gender(`Gender`)**: The gender of the population of each country is included as a categorical variable (Male/Female/Both Sex).
+This is a key variable in the dataset because gender has been fully recognized connected with the biological physical factor which directly effect the life expectancy.
+@fig-gender shows that the with an stable average of 74, life expectancy of female is constantly higher than male's average of 70.
+The line plot reveals a steady increase until 2019, followed by a sharp decline in 2020, which is assumed to be associated with the impact of COVID-19.
 
 3.
-**Total expenditure (`TotalExpenditure`)**: This variable shows the general government expenditure on health as a percentage of total government expenditure.
-This is considered as a reflection of economic situation of a country.
-A higher percentage indicates that a country places significant emphasis on healthcare as a key area of public investment.
-
-4.  **Income composition of resource (`IncomeComposition`)**: his is a numerical variable representing the income component of the Human Development Index (HDI).
-
-5.
-**Schooling (`Schooling`)**: This is a numerical variable showing the year of receiving education.
-@fig-schooling is a combination of box plot and violin plot showing the year of schooling differs by the status.
-In development countries, the average number of years of schooling is approximately 16 years, with a narrow distribution suggesting that the educational attainment in these countries is more consistent.
-In contrast, in developing countries, the average number of years od schooling is around 11 years.
-With a much wider spread and significant more outlier, the education situation in developing countries is less stable.
+**Region(Region)**: This is a categorical variable that classifies the geographic location of the countries.
+It is mapped one by one by the name of the country.
+The data is stored as the name of the continent(‘Africa’, ‘Oceania’, ‘Asia’, ‘Europe’, ‘North America’, ‘South America’).
+@fig-region indicates that with the number of 54, Africa has the most WHO member countries.
+Both Asia and Europe has 43 countries,listing in the middle while the other three continent has the significant less number of countries.
+North America has 22 countries, South America has 12 countries and Oceania has the least, 10 countries.
 
 ```{r}
-#| label: fig-statusdistribution
-#| fig-cap: "Distribution of country status, showing 28 dveloped countries and 127 developing countries, with a substantial difference in the number of data points.
-From 2000 to 2015, notably, the number of data entries for developing countries far exceeds that of developed countries, reflecting the greater representation of developing nations across the dataset."
+#| label: fig-income
+#| fig-cap: "Distribution of country income group."
 #| echo: false
@@
 # Count the number of unique countries for each Status
-country_counts <- cleaned_expectancy %>%
+country_counts <- lelecleaned_data %>%
   # Ensure each country is only counted once
-  distinct(Country, Status) %>%  
+  distinct(Country, Income_Group) %>%  
    # Count the number of countries in each Status category
-  count(Status)
+  count(Income_Group)
 
-#Plot1: create bar plot of count of status
-numberrows <- ggplot(cleaned_expectancy, aes(x = Status, fill = Status)) +
-  geom_bar() +
-  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5,size = 2.5) +
-  labs(
-    title = "Distribution of Count of Country by Status",
-    x = "Status (Developed vs Developing)",
-    y = "Count"
-  ) +
-  theme_minimal() +
-  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "darkblue")) +
-  theme(legend.position = "none",
-  plot.title = element_text(size = 7,face = "bold"))
-
-# Plot2: Create a bar plot to show the distribution of countries by Status
-numbercountry <- ggplot(country_counts, aes(x = Status, y = n, fill = Status)) +
+# Create a bar plot to show the distribution of countries by Status
+ggplot(country_counts, aes(x = Income_Group, y = n, fill = Income_Group)) +
    # Use 'identity' to directly use the count values
@@
   labs(
-    title = "Distribution of Country by Status",
-    x = "Status (Developed vs Developing)",
+    title = "Distribution of Country by Income Group",
+    x = "Income Group",
     y = "Number of Countries"
@@
   theme_minimal() +
-  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "darkblue")) +
+  scale_fill_manual(values = c("lower_income" = "skyblue", "lower_middle" = "darkblue", "upper_middle" = "blue", "high_income" = "lightblue")) +
   theme(
     legend.position = "none", 
-  plot.title = element_text(size = 7,face = "bold"))
+  plot.title = element_text(size = 15,face = "bold"))
 
-# Arrange the plots side by side
-grid.arrange(numberrows, numbercountry, ncol = 2)
 ```
@@
 ```{r}
-#| label: fig-percentage
-#| fig-cap: "Distribution of Health Expenditure ranges by country status.
-With the orange color showing the developing and blue showing developed, most of the country has more than 100% of their GDP per capita allocated to health-related expenditures."
+#| label: fig-region
+#| fig-cap: "Distribution of different region of the 184 countries.
+Africa has the most countries with an number of 54.
+Asia and Europe has the same amount of 43, North America has 22 countries while the other two continent has almost the same amount of countries."
 #| echo: false
@@
 
-# Define percentage ranges
-ranges <- c("0%-20%", "20%-30%", "30%-50%", "50%-100%", ">100%")
+# Group by Region and count the number of countries
+region_counts <- lelecleaned_data %>%
+  distinct(Country, Region) %>%  # Ensure each country is only counted once
+  count(Region)  # Count the number of distinct countries in each Region
 
-# Create a new variable to classify the ranges
-expenditure_ranges <- cleaned_expectancy %>%
-  mutate(
-    ExpenditureRange = case_when(
-      PercentageExpenditure <= 20 ~ "0%-20%",
-      PercentageExpenditure > 20 & PercentageExpenditure <= 30 ~ "20%-30%",
-      PercentageExpenditure > 30 & PercentageExpenditure <= 50 ~ "30%-50%",
-      PercentageExpenditure > 50 & PercentageExpenditure <= 100 ~ "50%-100%",
-      PercentageExpenditure > 100 ~ ">100%"
-    )
-  ) %>%
-  # Ensure the right order
-  mutate(ExpenditureRange = factor(ExpenditureRange, levels = ranges))
-
-# Plot the histogram of expenditure ranges separated by status
-ggplot(expenditure_ranges, aes(x = ExpenditureRange, fill = Status)) +
-  geom_bar(stat = "count", position = "dodge", color = "white", alpha = 0.7) +
-  # Adds count on top of each bin
-  geom_text(stat='count', aes(label = ..count..), position = position_dodge(width = 0.8), vjust = - 0.5, size = 2.5) +
-  scale_fill_manual(values = c("Developed" = "blue", "Developing" = "orange")) +
+# Plot: Distribution of countries in different regions
+ggplot(region_counts, aes(x = Region, y = n, fill = Region)) +
+  geom_bar(stat = "identity") +  # Plot the count of countries
+  geom_text(aes(label = n), vjust = -0.3, size = 3) +  # Add count labels on top of bars
   labs(
-    title = "Distribution of Health Expenditure Ranges by Country Status",
-    x = "Health Expenditure Range (% of GDP per Capita)",
-    y = "Count",
-    fill = "Status"
+    title = "Distribution of Countries by Region",
+    x = "Region",
+    y = "Number of Countries"
   ) +
   theme_minimal() +
+  scale_fill_brewer(palette = "Set3") +  # Color palette for different regions
   theme(
-    legend.position = "right",
-    axis.text.x = element_text(angle = 45, hjust = 1), # Adjusts the x-axis labels for clarity
-    plot.title = element_text(size = 10,face = "bold")) 
+    legend.position = "none",
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate axis labels for clarity
+  )
+
 ```
@@
 ```{r}
-#| label: fig-total
-#| fig-cap: "Distribution of contient.
-Africa has the highest number of countries represented, followed by Asia among all 5 continents.
-The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
-"
+#| label: fig-gender
+#| fig-cap: "Distribution of gender each year.
+The average of female life expectancy is approximately 74 around years, constantly higher than male's average of 70.
+Compared to male, female's life expectancy is marginally more steady."
 #| echo: false
@@
 
-# Define percentage ranges
-ranges <- c("0%-2%", "2%-4%", "4%-6%", "6%-8%", "8%-10%", "10%-12%","12%-14%", ">14%")
+# Calculate the average life expectancy per year for males
+male_avg <- male_table %>%
+  group_by(Period) %>%
+  summarise(AverageLifeExpectancy = mean(`Life Expectancy`, na.rm = TRUE))
 
-# Create a new variable to classify the ranges
-countryexpenditure <- cleaned_expectancy %>%
-  mutate(
-    TotalRange = case_when(
-      TotalExpenditure <= 2 ~ "0%-2%",
-      TotalExpenditure > 2 & TotalExpenditure <= 4 ~ "2%-4%",
-      TotalExpenditure > 4 & TotalExpenditure <= 6 ~ "4%-6%",
-      TotalExpenditure > 6 & TotalExpenditure <= 8 ~ "6%-8%",
-      TotalExpenditure > 8 & TotalExpenditure <= 10 ~ "8%-10%",
-      TotalExpenditure > 10 & TotalExpenditure <= 12 ~ "10%-12%",
-      TotalExpenditure > 12 & TotalExpenditure <= 14 ~ "12%-14%",
-      TotalExpenditure > 14 ~ ">14%"
-    )
-  ) %>%
-  # Ensure the right order
-  mutate(TotalRange = factor(TotalRange, levels = ranges))
+# Calculate the average life expectancy per year for females
+female_avg <- female_table %>%
+  group_by(Period) %>%
+  summarise(AverageLifeExpectancy = mean(`Life Expectancy`, na.rm = TRUE))
 
-summary(countryexpenditure$TotalRange)
-table(countryexpenditure$TotalRange)
+#Combine the two tables into one
+combined_avg <- bind_rows(male_avg %>% mutate(Gender = "Male"), 
+                          female_avg %>% mutate(Gender = "Female"))
 
-# Plot the histogram of expenditure ranges separated by status
-ggplot(countryexpenditure, aes(x = TotalRange, fill = Status)) +
-  geom_bar(stat = "count", position = "dodge", color = "white", alpha = 0.7) +
-  # Adds count on top of each bin
-  geom_text(stat='count', aes(label = ..count..), position = position_dodge(width = 0.8), vjust = - 0.5, size = 2.5) +
-  scale_fill_manual(values = c("Developed" = "lightblue", "Developing" = "salmon")) +
+# Plot the combined data
+ggplot(combined_avg, aes(x = Period, y = AverageLifeExpectancy, color = Gender, group = Gender)) +
+  geom_line(size = 1) +
+  geom_point(size = 2) +
   labs(
-    title = "Distribution of Government Expenditure on Health as Percentage Range by Country Status",
-    x = "Government Expenditure Range (%)",
-    y = "Count",
-    fill = "Status"
+    title = "Life Expectancy Over Years by Gender",
+    x = "Period",
+    y = "Life Expectancy",
+    color = "Gender"
   ) +
@@
   theme(
-    # Sidebar for the legend
-    legend.position = "right",
-    axis.text.x = element_text(angle = 45, hjust = 1), # Adjusts the x-axis labels for clarity
-    plot.title = element_text(size = 10,face = "bold"))
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.position = "top",
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
 
@@
 
+## Basic Data Summary
+
+The table below shows the basic summary of the mean, median, max, standard deviation, variance and sample size of life expectancy.
+We could tell that the average of the life expectancy from the 6 years is 45.9, with a large standard deviation of 26.9.
+The max of the life expectancy is 87.4, among all 6624 rows of data.
+The standard deviation and variance are extremely high because of the range of data is large, in other words, because the mean and median are 45.9 and 37.7, compared to the max 87.4, there is likely some outliers in the data creating such a high standard deviation and variance.
+
 ```{r}
-#| label: fig-income
-#| fig-cap: "Combined Box plot and Violin plot of income component of the Human Development Index (HDI) showing the variance and the average of the income component under status of different statuses."
+#| label: fig-summary
+#| fig-cap: "Summary statistics of the number of life expectancy over countries and years. "
 #| echo: false
@@
 
-# Create a combined boxplot and violin plot
-ggplot(cleaned_expectancy, aes(x = Status, y = IncomeComposition, fill = Status)) +
-  # Violin plot shows distribution
-  geom_violin(trim = FALSE, alpha = 0.5) + 
-  # Boxplot shows summary statistics
-  geom_boxplot(width = 0.2, alpha = 0.7, outlier.color = "red", outlier.shape = 16) + 
-  # Highlight mean
-  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkblue") + 
-  labs(
-    title = "Income Composition of Resources by Country Status",
-    x = "Country Status",
-    y = "Income Composition (HDI Contribution)"
-  ) +
-  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "salmon")) +
-  theme_minimal() +
-  theme(
-    # Remove legend as x-axis indicates status
-    legend.position = "none", 
-    axis.text.x = element_text(angle = 0, hjust = 0.5)
+# Calculate summary statistics
+life_expectancy_stats <- lelecleaned_data %>%
+  summarise(
+    Mean = round(mean(`Life Expectancy`, na.rm = TRUE),1),
+    Median = median(`Life Expectancy`, na.rm = TRUE),
+    Max = max(`Life Expectancy`, na.rm = TRUE),
+    SD = round(sd(`Life Expectancy`, na.rm = TRUE),1),
+    Variance = round(var(`Life Expectancy`, na.rm = TRUE),1),
+    N = sum(!is.na(`Life Expectancy`)) # Count of non-missing values
   )
-```
 
-```{r}
-#| label: fig-schooling
-#| fig-cap: "Distribution of school separate by Status.
-In developed countries, the average number of years of schooling is approximately 16 years, typically following a bell-shaped distribution.
-In contrast, in developing countries, the average number of years of schooling is around 11 years.
-However, the variance in the years of schooling is significantly larger."
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+# Create and format the table
+life_expectancy_stats %>%
+  kbl(
+    caption = "Summary Statistics of Life Expectancy",
+    col.names = c("Mean", "Median","Max", "Standard Deviation", "Variance", "N"),
+    align = "c"
+  ) %>%
+  kable_styling(full_width = F, bootstrap_options = c("striped", "hover", "condensed"))
 
-# Create a combined boxplot and violin plot
-ggplot(cleaned_expectancy, aes(x = Status, y = Schooling, fill = Status)) +
-  # Violin plot shows distribution
-  geom_violin(trim = FALSE, alpha = 0.5) + 
-  # Boxplot shows summary statistics
-  geom_boxplot(width = 0.2, alpha = 0.7, outlier.color = "red", outlier.shape = 16) + 
-  # Highlight mean
-  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkblue") + 
-  labs(
-    title = "Schooling by Country Status",
-    x = "Country Status",
-    y = "Year of Schooling"
-  ) +
-  scale_fill_manual(values = c("Developed" = "skyblue", "Developing" = "pink")) +
-  theme_minimal() +
-  theme(
-    # Remove legend as x-axis indicates status
-    legend.position = "none", 
-    axis.text.x = element_text(angle = 0, hjust = 0.5)
-  )
 ```
@@
 
-To predict the outcome of the life expectancy of people from different regions, we developed two linear regression models using R [@citeR]: one for the developed country and one for developing country.
-The outcome variable, `LifeExpectancy`, is a continuous and represents the average number of years a person is expected to live, assuming all related resources remain constant throughout their lifetime.
-These models aim to estimate the life expectancy of people under different environment.
+The goal of the Bayesian model is to incorporate prior knowledge, such as insights from previous studies or analyses, into the selection of the model.
+To predict the outcome of the life expectancy of people from different regions, in this paper, we developed a linear regression models using R [@citeR].
+The outcome variable, **`Life Expectancy`**, is a continuous and represents the average number of years a person is expected to live, assuming all related resources remain constant throughout their lifetime.
+The model aim to estimate and predict the life expectancy of people under different gender, region and income group.
+The normal Gaussian distribution is effective when used for modeling scenarios where the residuals of the data aare assumed to be independent nd normally distributed around the regression line.
 The GAM allows for capturing potential non-linear relationships between the predictors and the outcome.
@@
 
--   $Lifeexpectancy\_developed$ is the life expectancy of developed country.
+-   $yi$ is the outcome variable (Life Expectancy)for the i-th country.
 
--   $Lifeexpectancy\_developing$ is the life expectancy of developing country.
+-   $_i$ represents the expected value of $yi$, modeled as a linear combination of the predictors: Gender, Region, and Income Group.
 
--   $PercentageExpenditure$ is a smooth function of the runner’s age at the time of the race.
+-   $Gender$ is the gender of the individual.
 
--   $Continent$ is
-
--   $TotalExpenditure$ is the runner's gender (treated as a categorical variable).
-
--   $IncomeComposition$ is a smooth function of the total number of NYRR races the runner has participated in.
-
--   $Schooling$​ is the country the runner is from under IAAF standards.
+-   $Income Group$ is the income group of the country.
 
@@
 
-This GAM model allows for smooth, non-linear effects of continuous predictors (**`age`** and **`races_count`**) while keeping the categorical predictors (**`gender`** and **`iaaf_category`**) in a linear framework.
+This GAM model allows for smooth, non-linear effects of continuous predictors (**`age`** and **`races_count`**) while keeping the categorical predictors (**`Income_Group`** and **`iaaf_category`**) in a linear framework.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+[Appendix -@sec-model-details].
 
@@
 We can use maths by including latex between dollar signs, for instance $\theta$.
+
+#### Model Validation
+
+RMSE
+
+Out-of- Sample testing
 
@@
 
-## Third discussion point
+## Life Expectancy at 60
+
+The life expectancy at 60 means that how long is a person expected to live at 60 instead of at birth.
 
@@
 
-## Idealized Survey
+## Data Cleaning Table
+
+### Idealized Survey
 

### 2024-12-02 paper/paper.qmd
paper data

@@
 
+@fig-cleaned shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
+
 The cleaned dataset was then saved as both CSV and Parquet file for efficient storage and further analysis.
 
+```{r}
+#| label: fig-cleaned
+#| fig-cap: ""
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+```
 More information on the data cleaning process can be found in @sec-appx.
@@
 The model seeks to identify the variables affecting this average.
-To examine the differences in life expectancy under the same variables, we separate the data into developed and developing countries, where developed country are generally believed to have higher life expectancy.
-@fig-expectancy displays density of the historical data of life expectancy across 195 countries from 2000 to 2015, comparing developing to developed countries.The average age of most developed country is approximately 80, while the majority developing countries typically have average life expectancy around mid-seventies.
+
+@fig-expectancy visualizes the distribution of life expectancy from 2015 to 2020 as percentages, combining a histogram and a density plot.
+A large concentration of observations is observed range of 0% to 25%, reflecting a significant proportion of countries with lower life expectancy relative to others in the dataset.
+Another visible concentration is around 75% to 100%, indicating a group of countries with relatively high life expectancy.
+The blue density curve overlays the histogram, providing a smoothed representation of the distribution.
+Peaks in the curve correspond to high frequency within the histogram.
+The density plot emphasized the bimodal nature of the distribution with two distinct peaks: one around 12 as low life expectancy percentages; another peak around 87as high life expectancy percentage.
 
@@
 #| label: fig-expectancy
-#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries.
-The graph of developed countries shows narrower spread with density curve located on the rightside of the x-axis.
-The graph of developing countries performs a wider spread while the highest density position at mid-seventies."
+#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy.
+With a huge gap between 25 and 50, we could indicate that most of the countries has a life expectancy of.
+There exist large data with low life expectancy less than 25 years.
+"
 #| echo: false
@@
 
-# create plot of historical 184 countries life expectancy dividing by country status. 
-ggplot(lelecleaned, aes(x = `Life Expectancy`)) +
-  geom_histogram(aes(y = ..density..), 
-                 bins = 70, fill = "salmon", color = "pink", alpha = 0.9) +
-  geom_density(color = "royalblue", fill = "lightblue", alpha = 0.6) +
+# Create 10-year bins for Life Expectancy
+lerange <- lelecleaned_data %>%
+  mutate(LifeExpectancyRange = cut(`Life Expectancy`, 
+                                   breaks = seq(floor(min(`Life Expectancy`, na.rm = TRUE)), 
+                                   ceiling(max(`Life Expectancy`, na.rm = TRUE)), by = 10), 
+                                   include.lowest = TRUE))
+
+# Calculate percentages for each bin
+life_expectancy_distribution <- lerange %>%
+  count(LifeExpectancyRange) %>%
+  mutate(Percentage = 100 * n / sum(n))
+
+# Plot the histogram with percentages
+ggplot(life_expectancy_distribution, aes(x = LifeExpectancyRange, y = Percentage, fill = LifeExpectancyRange)) +
+  geom_bar(stat = "identity", color = "white", alpha = 0.8) +
   labs(
-    title = "Distribution of Life Expectancy",
-    x = "Life Expectancy", y = "Density"
+    title = "Distribution of Life Expectancy by Age Range",
+    x = "Life Expectancy (10-Year Ranges)",
+    y = "Percentage"
   ) +
   theme_minimal() +
-  facet_wrap(~Status)
+  scale_fill_viridis_d(option = "C") +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = "none"
+  )
 
@@
 
-model_developed <-
-  readRDS(file = here::here("models/lm_model_developed.rds"))
+#model_developed <-
+  #readRDS(file = here::here("models/lm_model_developed.rds"))
 ```
@@
 We began by importing the raw dataset using the read_csv function from the tidyverse package.
-To focus our analysis on more relevant variables, we selected specific columns, such as percentage of expenditure of the country, total health expenditure by government .etc., omitting any unnecessary columns.
+To focus our analysis on more relevant variables, we selected specific columns, such as Indicator of life expectancy as birth and life expectancy at 60 years, Country, Period, Gender, and Life expectancy, omitting any unnecessary columns.
 
-We filter out the rows containing NA values in any of the selected columns for reducing the noise and simpler further analysis..
+We functioned to extract the number before opening the square bracket of life expectancy since the raw data gave both the range and the mean of life expectancy of each country under each year.
+
+We filter out the rows containing NA values in any of the selected columns for reducing the noise and simpler further analysis.
 
 We then renaming columns for clarity.
-For example, we changed ‘Income.composition.of.resources’ into ‘IncomeComposition’ , making it easier for anyone working with the data to read and understand what each variable represents.
+For example, we changed ‘Location’ into ‘Country’, "Dim1" for "Gender" and "Value" for "Life Expectancy", making it easier for anyone working with the data to read and understand what each variable represents.
 
@@
 Columns not mentioned in mutate remain unchanged.
-This ensures a flexible and precise cleaning process tailored to further compairation and graphing.
+This ensures a flexible and precise cleaning process tailored to further comparison and graphing.
+We dropped the potential percentage symbol to contain purely numerical data.
 
-We also modified the country name of ‘Republic of Korea’ under Country variable to ‘South Korea’ to avoid misunderstanding of North Korea.
+The income group column and the region column was not given in the raw dataset.
+We created a new variable called "Income_Group" by mapping over country name to four income group (lower_income, lower_middle, upper_middle, high_income) according to the index given by World Bank Income Group.
+This is a key variable in predicting life expectancy since it is believed that life expectancy is correlated to the income situation.
+We as well made a mapping to the countries according to its continent and saved as "Region".
+This is the variable indicates the geographic context to the analysis.
+Countries are mapped into six continents ("Africa", "Asia", "Europe", "North America", "South America", "Oceania") one by one.
 
-We also created a new variable called Continent, which indicates which continent does the country comes from in order to provide a geographical context to the analysis.
-Life expectancy may be higher in developed regions like Europe or North America compared to regions like Sub-Saharan Africa due to differences in healthcare, living standards, and economic development.
+We again merge the table, removing repeated columns and rows and mapping the region and the country income under different given names.
 
-We also wrapped the cleaning process in a tryCatch block in order to mitigate any errors that arose throughout the cleaning process.
+Lastly, we filter out NAs again as a further check. We continue filter out the Palestinian territory, which is not a country and was not mapped in neither Region nor Income Group.
+
+For easy reading format, we arrange the country into Alphabet order and mutate the variables again for converting columns into appropriate data types.
+
+For easier visualization, we created four tables, which are grouped by life expectancy at age 60, life expectancy at birth, life expectancy at birth of Male and life expectancy at birth of Female.
 
@@
 
-```{r}
-#| label: fig-continent
-#| fig-cap: "Distribution of contient.
-Africa has the highest number of countries represented, followed by Asia among all 5 continents.
-The distribution of count of data aslo shows that a significant portion of the data is focused on African and Asian nations.
-"
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-#Calculate the number of unique countries per continent
-continent_count <- cleaned_expectancy %>%
-  group_by(Continent) %>%
-  summarise(num_countries = n_distinct(Country))
-
-#Plot1: Distribution of number of data per continent
-#Create the bar plot showing the number of data per continent
-continentrow <- ggplot(cleaned_expectancy, aes(x = Continent)) +
-  geom_bar(fill = "orange", color = "white") +
-  labs(
-    title = "Distribution of Count by Continent",
-    x = "Continent",
-    y = "Count"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 10, face = "bold"),
-    axis.title = element_text(size = 10)
-  ) +
-  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
-
-# Plot2: The distribution of number of countries each continent
-#Create the bar plot showing the number of unique countries per continent
-continentnumber <-ggplot(continent_count, aes(x = Continent, y = num_countries)) +
-  geom_bar(stat = "identity", fill = "#FFA07A", color = "white") +
-  labs(
-    title = "Distribution of Country by Continent",
-    x = "Continent",
-    y = "Number of Country"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 10, face = "bold"),
-    axis.title = element_text(size = 10)
-  ) +
-  geom_text(aes(label = num_countries), vjust = -0.5, size = 2.5)
-
-# Arrange the plots side by side
-grid.arrange(continentnumber, continentrow, ncol = 2)
-```
-
 ## Posterior predictive check

### 2024-12-02 paper/paper.tex
paper data

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Global Life Expectancy: Unraveling Health and Economic Determinants (2015-2020)},
  pdfauthor={Yanfei Huang},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Global Life Expectancy: Unraveling Health and Economic
Determinants (2015-2020)\thanks{Code and data are available at:
\url{https://github.com/wendyhuan/lifeexpectancy}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Multiple Linear Regression Analyzing Critical Factors Shaping
Life Expectancy}
\author{Yanfei Huang}
\date{December 2, 2024}

\begin{document}
\maketitle
\begin{abstract}
This paper analyze life expectancy and its determinants through 184
countries and make the prediction of people from different Income Group.
Multiple Linear regression is used to deploying the life expectanc with
gender, income and region. Predictions of life expectancy of people from
different income group is made according to these essential predictors.
The finding indicates that the life expectancy is tend to get higher as
the economic class grows. And we predict that the average age of person
from low, lower-middle, upper-middle and high are 65,70, 75,80. The
result of this paper will help in suggesting a country which area should
be given importance in order to efficiently improve the life expectancy
of its population.
\end{abstract}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\section{Introduction}\label{introduction}

Life expectancy is a critical measure of a population's overall health
and well-being, shaped by various factors such as gender, geographic
location and economic group. The index of life expectancy is generally
served as a benchmark for income group, indicating the effectiveness of
interventions in reducing mortality and improving well-being. Higher
life expectancy is believed to linked to stronger physical factor,
better living standards, and geographic location. Conversely, low life
expectancy often signals systemic challenges such as weaker health,
lower economic situation, and inadequate healthcare access of different
region. (\textbf{socialdeterminantsofhealth?}).

The primary goal of this paper is to determine which factors play a
statistically significant role in driving lower life expectancy values
and to offer actionable insights based on different income group.
According to the World Bank Income Group, the countries are classified
into low, lower-middle, upper-middle, and high based on the country's
Gross National Income. Using Multiple Linear Regression model and
Bayesian model, this study focuses on understanding the relationship
between Gender, Region and different income group in predicting life
expectancy across different countries. By identifying and analyzing
these predictors, the study aims to highlight actionable aspects for
policymakers to target in their efforts to improve population longevity
effectively.

Related Research has shown that there exist difference between men and
women related with biological, behavioral, and socioeconomic factors,
highlighting that gender-specific health behaviors and societal roles
influence longevity (\textbf{GenderandLifeExpectancy?}). Higher-income
individuals tend to live longer due to better access to healthcare and
healthier lifestyles, with notable regional disparities even within
similar income groups (\textbf{IncomeGroupsandLongevity?}).
Additionally, regional socioeconomic differences on health outcomes,
especially life expectancy. It emphasizes that addressing regional
inequities in wealth and resources is essential for improving population
health globally. (\textbf{RegionalVariations?}).

Findings from this paper reveal that countries of higher income group
tend to achieve higher life expectancy, while factors like lower income
and poverty region emerge as significant obstacles. The analysis
underscores the importance of targeted interventions in key areas such
as healthcare accessibility and economic equity to address disparities
in life expectancy. This study further contributes to a deeper
understanding of how predictive modeling under different country status
can inform public health strategies and policy-making on a global scale.

The ultimate goal is to assist policymakers in developing evidence-based
strategies that can enhance population health outcomes. The approach of
this paper not only emphasizes the importance of equitable access to
healthcare but also contributes to a broader understanding of the
multifaceted factors shaping life expectancy globally. By highlighting
the interplay between various determinants, this study contributes to a
broader understanding of the challenges and opportunities in improving
life expectancy on a global scale.

The structure of the paper is as follows: Section~\ref{sec-data}
outlines the data sources and variables considered, followed by the
model setup in Section~\ref{sec-modset} and justification in
\textbf{?@sec-modjust}. The results in \textbf{?@sec-result} presents
the key findings of the analysis, with a discussion on the implications.
\textbf{?@sec-discussion} then discusses potential limitations and
suggestions for future research. \textbf{?@sec-appx} provides additional
detailed information about the data, model and methodology.

\section{Data}\label{sec-data}

\subsection{Overview}\label{overview}

The data used in this analysis originates from The World Health
Organization's (WHO) and Global Health Observatory (GHO)
(\textbf{lifeexpectancy?}). This data-set related to life expectancy,
health factors for 184 countries has been collected from WHO data
repository website and its corresponding economic data was collected
from United Nation website. Among all categories of health-related
factors only those socio-economic factors on the national level were
chosen for global scale analysis.

This analysis uses the statistical programming language R (R Core Team
2023) and several libraries, including \texttt{tidyverse}
(\textbf{tidyverse?}), \texttt{janitor} (\textbf{janitor?}),
\texttt{knitr} (\textbf{knitr?}), \texttt{dplyr} (\textbf{dplyr?}),
\texttt{arrow} (\textbf{arrow?}), \texttt{purrr} (\textbf{purrr?}),
\texttt{sf} (\textbf{sf?}), and \texttt{here} (\textbf{here?}) for data
manipulation. \texttt{ggplot2} (\textbf{ggplot?}), \texttt{ggcorrplot}
(\textbf{ggcorrplot?}) and \texttt{kableExtra} (\textbf{kableExtra?})
for visualization. The dataset covers various predictors conducted
across multiple countries, capturing the support for a country to
determine the predicting factor which is contributing to lower value of
life expectancy.

\subsection{Measurement}\label{measurement}

The measurement process refers to how real-world factors---such as the
Gender, geographic location of a country and income group - are
translated into numerical entries representing life expectancy in a
dataset. Each entry captures the average life expectancy of individuals
in a specific country during a given year.

\textbf{Life Expectancy (\texttt{Life\ Expectancy})}: This variable,
life expectancy at birth, represents the number of years a person is
expected to live , assuming current mortality conditions persist. It is
derived using data from national health records, the World Health
Organization (WHO) and Global Health Observatory (GHO). The data on the
raw dataset is recorded as a range of age. For simple analysis, we drop
the range and take the average of year with one decimal. The values are
calculated and represented in age between 10.1 to 87.4.

\textbf{Income Group(\texttt{Income\_Group})}: This is a categorical
variable that classifies countries into four groups by the country's
Gross National Income according to the latest index from World Bank
Income Group. The countries are classified into low, lower-middle,
upper-middle, and high under the standard as follow. Low-income
economies is defined as a country with a gross national income less than
\$1135, lower-middle is between the range to \$1136 to \$4465,
upper-middle in the range of \$4465 to \$13845 and high is more than
\$13846.

\textbf{Gender(\texttt{Gender})}: The gender of the population of each
country is included as a categorical variable (Male/Female/Both Sex).

\textbf{Region(Region)}: This is a categorical variable that classifies
the geographic location of the countries. It is mapped one by one by the
name of the country. The data is stored as the name of the
continent(`Africa', `Oceania', `Asia', `Europe', `North America', `South
America').

\subsection{Data Cleaning}\label{data-cleaning}

The raw life expectancy data underwent a several cleaning steps to
ensure it was accurate, consistent and ready for analysis. The goal of
this cleaning process is to create a table including income group (high,
upper middle, lower middle, low), gender (Male, Female, Both Sex),
region (Asia, Europe, North America, South America, Africa, Oceania) as
rows and life expectancy as column.

To make such table, we first select and rename key variables from raw
data to focus on relevant information. To make the subsequent analysis
easier, we then convert variables to the proper data types and eliminate
the rows that have missing data values. To keep things neat, we organize
the decimal for every piece of numerical data and drop the percentage
symbol. The income group column and the region column was not given in
the raw dataset. We created a mapping over country name to four income
group according to the index given by World Bank Income Group and save
the data under ``Income\_Group''. We as well made a mapping to the
countries according to its continent and saved as ``Region''. We again
merge the table, removing repeated columns and rows. For easier
visualization, we created four tables, which are grouped by life
expectancy at age 60, life expectancy at birth, life expectancy at birth
of Male and life expectancy at birth of Female.

The cleaned dataset was then saved as both CSV and Parquet file for
efficient storage and further analysis.

More information on the data cleaning process can be found in
\textbf{?@sec-appx}.

\subsection{Outcome Variables}\label{outcome-variables}

The outcome variable is \textbf{\texttt{Life\ Expendency}}. This is the
primary dependent variable that the model is designed to predict. It
represents the average number of years a person is expected to live,
under the condition that current mortality conditions persist. The model
seeks to identify the variables affecting this average.

To examine the differences in life expectancy under the same variables,
we separate the data into developed and developing countries, where
developed country are generally believed to have higher life expectancy.
Figure~\ref{fig-expectancy} displays density of the historical data of
life expectancy across 195 countries from 2000 to 2015, comparing
developing to developed countries.The average age of most developed
country is approximately 80, while the majority developing countries
typically have average life expectancy around mid-seventies.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-expectancy-1.pdf}

}

\caption{\label{fig-expectancy}This histogram shows the distribution of
the percentage of life expectancy.}

\end{figure}%

\subsection{Predictor Variables}\label{predictor-variables}

The \textbf{predictor variables} (or independent variables) are the
factors believed to influence the life expectancy:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Income Group(\texttt{Income\_Group})}: The income group of a
  country is the key factor influencing the life expectancy. This
  variable provides context for comparing life expectancy between
  different levels of country income group. The division of the life
  expectancy by the income group of a country because income levels
  often correlate strongly with various factors affecting health and
  longevity. Higher income countries typically have more resources to
  invest in robust healthcare systems, with better living conditions
  while lower income countries often face challenges such as inadequate
  healthcare infrastructure and malnutrition.
\end{enumerate}

Following by the four income group, we would like to see the
distribution of the income group of 184 WHO member countries.
(\textbf{fid-income?}) shows that there are 55 countries at the high
income group, 26 countries at low income group, 54 countries at the
lower-middle group while there are 49 countries at the upper-middle
group. With significant less low income countries, we expect to see the
life expectancy lie in a comparably higher range. On the other hand,
there might exist sever outliers dropping the mean.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
  \textbf{Gender(\texttt{Gender})}: The gender of the population of each
  country is included as a categorical variable (Male/Female/Both Sex).
  This is a key variable in the dataset because gender has been fully
  recognized connected with the biological physical factor which
  directly effect the life expectancy. Figure~\ref{fig-gender} shows
  that the with an stable average of 74, life expectancy of female is
  constantly higher than male's average of 70. The line plot reveals a
  steady increase until 2019, followed by a sharp decline in 2020, which
  is assumed to be associated with the impact of COVID-19.
\item
  \textbf{Region(Region)}: This is a categorical variable that
  classifies the geographic location of the countries. It is mapped one
  by one by the name of the country. The data is stored as the name of
  the continent(`Africa', `Oceania', `Asia', `Europe', `North America',
  `South America'). Figure~\ref{fig-region} indicates that with the
  number of 54, Africa has the most WHO member countries. Both Asia and
  Europe has 43 countries,listing in the middle while the other three
  continent has the significant less number of countries. North America
  has 22 countries, South America has 12 countries and Oceania has the
  least, 10 countries.
\end{enumerate}

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-income-1.pdf}

}

\caption{\label{fig-income}Distribution of country income group.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-region-1.pdf}

}

\caption{\label{fig-region}Distribution of different region of the 184
countries. Africa has the most countries with an number of 54. Asia and
Europe has the same amount of 43, North America has 22 countries while
the other two continent has almost the same amount of countries.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-gender-1.pdf}

}

\caption{\label{fig-gender}Distribution of gender each year. The average
of female life expectancy is approximately 74 around years, constantly
higher than male's average of 70. Compared to male, female's life
expectancy is marginally more steady.}

\end{figure}%

\subsection{Basic Data Summary}\label{basic-data-summary}

The table below shows the basic summary of the mean, median, max,
standard deviation, variance and sample size of life expectancy. We
could tell that the average of the life expectancy from the 6 years is
45.9, with a large standard deviation of 26.9. The max of the life
expectancy is 87.4, among all 6624 rows of data. The standard deviation
and variance are extremely high because of the range of data is large,
in other words, because the mean and median are 45.9 and 37.7, compared
to the max 87.4, there is likely some outliers in the data creating such
a high standard deviation and variance.

\begin{figure}

\centering{

\begin{table}
\centering
\caption{Summary Statistics of Life Expectancy}
\centering
\begin{tabular}[t]{c|c|c|c|c|c}
\hline
Mean & Median & Max & Standard Deviation & Variance & N\\
\hline
45.9 & 37.7 & 87.4 & 26.9 & 724.2 & 6624\\
\hline
\end{tabular}
\end{table}

}

\caption{\label{fig-summary}Summary statistics of the number of life
expectancy over countries and years.}

\end{figure}%

\section{Model}\label{model}

\subsection{Model set-up}\label{sec-modset}

The goal of the Bayesian model is to incorporate prior knowledge, such
as insights from previous studies or analyses, into the selection of the
model. To predict the outcome of the life expectancy of people from
different regions, in this paper, we developed a linear regression
models using R (R Core Team 2023). The outcome variable,
\textbf{\texttt{Life\ Expectancy}}, is a continuous and represents the
average number of years a person is expected to live, assuming all
related resources remain constant throughout their lifetime. The model
aim to estimate and predict the life expectancy of people under
different gender, region and income group. The normal Gaussian
distribution is effective when used for modeling scenarios where the
residuals of the data aare assumed to be independent nd normally
distributed around the regression line. The GAM allows for capturing
potential non-linear relationships between the predictors and the
outcome.

The model is specified as follows:

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

Where:

\begin{itemize}
\item
  \(yi\) is the outcome variable (Life Expectancy)for the i-th country.
\item
  \(_i\) represents the expected value of \(yi\), modeled as a linear
  combination of the predictors: Gender, Region, and Income Group.
\item
  \(Gender\) is the gender of the individual.
\item
  \(Income Group\) is the income group of the country.
\item
  \(\epsilon_i\) is the error term, assumed to be normally distributed
  with a mean of 0 and constant variance \(ϵ_i​∼N(0,\sigma^2)\)
\end{itemize}

This GAM model allows for smooth, non-linear effects of continuous
predictors (\textbf{\texttt{age}} and \textbf{\texttt{races\_count}})
while keeping the categorical predictors
(\textbf{\texttt{Income\_Group}} and \textbf{\texttt{iaaf\_category}})
in a linear framework.

Appendix~\ref{sec-model-details}.

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\subsubsection{Model justification}\label{model-justification}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\paragraph{Model Validation}\label{model-validation}

RMSE

Out-of- Sample testing

\section{Results}\label{results}

Our results are summarized in Table~\ref{tbl-modelresults}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  check different continent has its different life expectancy.
\item
  compare the develop country with
\item
  check the shcooling year of develop countries to developing country,
  showing a relationship between shcooling with the life expenctancy.
\item
\end{enumerate}

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

Please don't use these as sub-heading labels - change them to be what
your point actually is.

\subsection{Life Expectancy at 60}\label{life-expectancy-at-60}

The life expectancy at 60 means that how long is a person expected to
live at 60 instead of at birth.

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section{Appendix}\label{sec-appendix}

\subsection{Data Cleaning Notes}\label{data-cleaning-notes}

We began by importing the raw dataset using the read\_csv function from
the tidyverse package. To focus our analysis on more relevant variables,
we selected specific columns, such as percentage of expenditure of the
country, total health expenditure by government .etc., omitting any
unnecessary columns.

We filter out the rows containing NA values in any of the selected
columns for reducing the noise and simpler further analysis..

We then renaming columns for clarity. For example, we changed
`Income.composition.of.resources' into `IncomeComposition' , making it
easier for anyone working with the data to read and understand what each
variable represents.

Each column is rounded using the round function, specifying the desired
number of decimal places for each. Columns not mentioned in mutate
remain unchanged. This ensures a flexible and precise cleaning process
tailored to further compairation and graphing.

We also modified the country name of `Republic of Korea' under Country
variable to `South Korea' to avoid misunderstanding of North Korea.

We also created a new variable called Continent, which indicates which
continent does the country comes from in order to provide a geographical
context to the analysis. Life expectancy may be higher in developed
regions like Europe or North America compared to regions like
Sub-Saharan Africa due to differences in healthcare, living standards,
and economic development.

We also wrapped the cleaning process in a tryCatch block in order to
mitigate any errors that arose throughout the cleaning process.

After completing the cleaning, we saved the final dataset in both
Parquet and CSV formats for later analysis.

\subsection{Data Cleaning Table}\label{data-cleaning-table}

\subsubsection{Idealized Survey}\label{idealized-survey}

\textbf{Survey: Understanding Life Expectancy and Influencing Factor}

Thank you for participating in this survey. This survey aims to gather
insights into the factors influencing life expectancy, including health
expenditure, education, ethnicity, government spending on healthcare,
and income levels. Your responses will help us understand individual
perspectives and experiences towards national policy. Participation is
voluntary, and your answers will remain anonymous.

\textbf{Contact Information:} If you have any questions about the survey
or the data collection process, please contact

\textbf{Survey Coordinator}: Yanfei Huang\\
\textbf{Email}: yanfei.huang@mail.utoronto.ca

\textbf{Section 1: Personal Health Expenditure}

\textbf{1.What percentage of your monthly income do you spend on
healthcare (e.g., insurance, medications, doctor visits)?}

\begin{itemize}
\tightlist
\item
  Less than 5\%
\item
  5\%--10\%
\item
  10\%--20\%
\item
  More than 20\%
\end{itemize}

\textbf{2.Do you or your household have health insurance coverage?}

\begin{itemize}
\tightlist
\item
  Yes
\item
  No
\end{itemize}

\textbf{3. How frequently do you visit a healthcare
professional(eg.doctors, nurse) in a year?}

\begin{itemize}
\tightlist
\item
  0-1 times
\item
  2-5 times
\item
  6-10 times
\item
  More than 10 times
\end{itemize}

\textbf{Section 2: Education Background}

\textbf{4.What is the highest level of education you have completed?}

\begin{itemize}
\tightlist
\item
  No formal education
\item
  Primary school
\item
  Secondary school
\item
  College or university degree
\item
  Postgraduate degree
\end{itemize}

\textbf{5.How many years of formal schooling have you completed?}

Please write the number: \_\_\_\_\_\_\_

\textbf{Section 3: Ethnicity and Geographic Factors}

\textbf{6.Which of the following best describes your ethnicity?}

\begin{itemize}
\tightlist
\item
  African
\item
  Asian
\item
  European
\item
  Hispanic or Latino
\item
  Middle Eastern
\item
  Indigenous
\item
  Other (please specify): \_\_\_\_\_\_\_
\end{itemize}

\textbf{7.What's the distance to the nearest healthcare facility from
your residence?}

\begin{itemize}
\tightlist
\item
  Less than 1 km
\item
  1-5 km
\item
  More than 5 km
\end{itemize}

\textbf{Section 4: Government Expenditure on Healthcare}

\textbf{8.Are health services in your country subsidized by the
govenment?}

\begin{itemize}
\tightlist
\item
  Yes, fully subsidized
\item
  Yes, partially subsidized
\item
  No
\end{itemize}

\textbf{9. What is the approximate cost of your most recent healthcare
visit (in local currency)?}

Please write the amount \_\_\_\_\_\_\_

\textbf{10.Do public healthcare facilities in your area provide all the
services you need?}

\begin{itemize}
\tightlist
\item
  Yes
\item
  No
\item
  Not applicable
\end{itemize}

\textbf{Section 5: Income and Development Factor}

\textbf{11.What is your approximate monthly household income after
taxes?(in local currency)}

\begin{itemize}
\tightlist
\item
  Less than 1,000
\item
  1,000 - 2,999
\item
  3,000 - 4,999
\item
  5,000 - 7,999
\item
  8,000 - 10,999
\item
  More than 11,000
\item
  Prefer not to say
\end{itemize}

\textbf{12.How would you describe your current financial situation?}

\begin{itemize}
\tightlist
\item
  Struggling to make ends meet
\item
  Just getting by
\item
  Comfortable, but not wealthy
\item
  Financially secure
\item
  Wealthy
\item
  Prefer not to say
\end{itemize}

\textbf{13.How often do you have difficulty affording basic healthcare
(medical visits, medications, etc.)?}

\begin{itemize}
\tightlist
\item
  Never
\item
  Rarely
\item
  Sometimes
\item
  Often
\item
  Always
\item
  Prefer not to say
\end{itemize}

\textbf{Final Section}

Thank you for completing this survey! Your responses will help capture
information about economic conditions, access to healthcare and
education, and basic living standards, which are critical for
understanding life expectancy predictors and the impact of socioeconomic
factors on health outcomes.

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Additional graph for
analysis}\label{additional-graph-for-analysis}

\subsection{Posterior predictive
check}\label{posterior-predictive-check}

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}
Examining how the model fits, and is affected by, the
data\end{minipage}%

\end{figure}%

\subsection{Diagnostics}\label{diagnostics}

\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}
Checking the convergence of the MCMC algorithm\end{minipage}%

\end{figure}%

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\end{CSLReferences}

\end{document}

### 2024-12-02 paper/paper.tex
latex

@@
 
+\textbf{?@fig-cleaned} shows the average of life expectancy under male,
+female, 6 different regions and 4 income groups.
+
 The cleaned dataset was then saved as both CSV and Parquet file for
@@
 
-To examine the differences in life expectancy under the same variables,
-we separate the data into developed and developing countries, where
-developed country are generally believed to have higher life expectancy.
-Figure~\ref{fig-expectancy} displays density of the historical data of
-life expectancy across 195 countries from 2000 to 2015, comparing
-developing to developed countries.The average age of most developed
-country is approximately 80, while the majority developing countries
-typically have average life expectancy around mid-seventies.
+Figure~\ref{fig-expectancy} visualizes the distribution of life
+expectancy from 2015 to 2020 as percentages, combining a histogram and a
+density plot. A large concentration of observations is observed range of
+0\% to 25\%, reflecting a significant proportion of countries with lower
+life expectancy relative to others in the dataset. Another visible
+concentration is around 75\% to 100\%, indicating a group of countries
+with relatively high life expectancy. The blue density curve overlays
+the histogram, providing a smoothed representation of the distribution.
+Peaks in the curve correspond to high frequency within the histogram.
+The density plot emphasized the bimodal nature of the distribution with
+two distinct peaks: one around 12 as low life expectancy percentages;
+another peak around 87as high life expectancy percentage.
 
@@
 \caption{\label{fig-expectancy}This histogram shows the distribution of
-the percentage of life expectancy.}
+the percentage of life expectancy. With a huge gap between 25 and 50, we
+could indicate that most of the countries has a life expectancy of.
+There exist large data with low life expectancy less than 25 years.}
 
@@
 the tidyverse package. To focus our analysis on more relevant variables,
-we selected specific columns, such as percentage of expenditure of the
-country, total health expenditure by government .etc., omitting any
-unnecessary columns.
+we selected specific columns, such as Indicator of life expectancy as
+birth and life expectancy at 60 years, Country, Period, Gender, and Life
+expectancy, omitting any unnecessary columns.
+
+We functioned to extract the number before opening the square bracket of
+life expectancy since the raw data gave both the range and the mean of
+life expectancy of each country under each year.
 
 We filter out the rows containing NA values in any of the selected
-columns for reducing the noise and simpler further analysis..
-
-We then renaming columns for clarity. For example, we changed
-`Income.composition.of.resources' into `IncomeComposition' , making it
-easier for anyone working with the data to read and understand what each
-variable represents.
+columns for reducing the noise and simpler further analysis.
+
+We then renaming columns for clarity. For example, we changed `Location'
+into `Country', ``Dim1'' for ``Gender'' and ``Value'' for ``Life
+Expectancy'', making it easier for anyone working with the data to read
+and understand what each variable represents.
 
@@
 remain unchanged. This ensures a flexible and precise cleaning process
-tailored to further compairation and graphing.
-
-We also modified the country name of `Republic of Korea' under Country
-variable to `South Korea' to avoid misunderstanding of North Korea.
-
-We also created a new variable called Continent, which indicates which
-continent does the country comes from in order to provide a geographical
-context to the analysis. Life expectancy may be higher in developed
-regions like Europe or North America compared to regions like
-Sub-Saharan Africa due to differences in healthcare, living standards,
-and economic development.
-
-We also wrapped the cleaning process in a tryCatch block in order to
-mitigate any errors that arose throughout the cleaning process.
+tailored to further comparison and graphing. We dropped the potential
+percentage symbol to contain purely numerical data.
+
+The income group column and the region column was not given in the raw
+dataset. We created a new variable called ``Income\_Group'' by mapping
+over country name to four income group (lower\_income, lower\_middle,
+upper\_middle, high\_income) according to the index given by World Bank
+Income Group. This is a key variable in predicting life expectancy since
+it is believed that life expectancy is correlated to the income
+situation. We as well made a mapping to the countries according to its
+continent and saved as ``Region''. This is the variable indicates the
+geographic context to the analysis. Countries are mapped into six
+continents (``Africa'', ``Asia'', ``Europe'', ``North America'', ``South
+America'', ``Oceania'') one by one.
+
+We again merge the table, removing repeated columns and rows and mapping
+the region and the country income under different given names.
+
+Lastly, we filter out NAs again as a further check. We continue filter
+out the Palestinian territory, which is not a country and was not mapped
+in neither Region nor Income Group.
+
+For easy reading format, we arrange the country into Alphabet order and
+mutate the variables again for converting columns into appropriate data
+types.
+
+For easier visualization, we created four tables, which are grouped by
+life expectancy at age 60, life expectancy at birth, life expectancy at
+birth of Male and life expectancy at birth of Female.
 

### 2024-12-03 paper/paper.qmd
i

@@
 
-@fig-cleaned shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
+shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
 
@@
 
-```{r}
-#| label: fig-cleaned
-#| fig-cap: ""
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-```
 More information on the data cleaning process can be found in @sec-appx.
@@
 
-The outcome variable is **`Life Expendency`**.
+The outcome variable is **Life Expectancy**.
 This is the primary dependent variable that the model is designed to predict.
@@
 
-# Create 10-year bins for Life Expectancy
-lerange <- lelecleaned_data %>%
-  mutate(LifeExpectancyRange = cut(`Life Expectancy`, 
-                                   breaks = seq(floor(min(`Life Expectancy`, na.rm = TRUE)), 
-                                   ceiling(max(`Life Expectancy`, na.rm = TRUE)), by = 10), 
-                                   include.lowest = TRUE))
+# Normalize Life Expectancy to percentages
+life_expectancy_percentage <- lelecleaned_data %>%
+  mutate(
+    LifeExpectancyPercentage = 100 * (`Life Expectancy` - min(`Life Expectancy`, na.rm = TRUE)) / 
+                                  (max(`Life Expectancy`, na.rm = TRUE) - min(`Life Expectancy`, na.rm = TRUE))
+  )
 
-# Calculate percentages for each bin
-life_expectancy_distribution <- lerange %>%
-  count(LifeExpectancyRange) %>%
-  mutate(Percentage = 100 * n / sum(n))
-
-# Plot the histogram with percentages
-ggplot(life_expectancy_distribution, aes(x = LifeExpectancyRange, y = Percentage, fill = LifeExpectancyRange)) +
-  geom_bar(stat = "identity", color = "white", alpha = 0.8) +
+# Plot the distribution
+ggplot(life_expectancy_percentage, aes(x = LifeExpectancyPercentage)) +
+  geom_histogram(
+    bins = 20, 
+    fill = "skyblue", 
+    color = "white", 
+    alpha = 0.8
+  ) +
+  geom_density(
+    aes(y = ..scaled.. * max(..count..)),  # Align density with histogram
+    color = "blue", 
+    size = 1
+  ) +
   labs(
-    title = "Distribution of Life Expectancy by Age Range",
-    x = "Life Expectancy (10-Year Ranges)",
-    y = "Percentage"
+    title = "Distribution of Life Expectancy as Percentages",
+    x = "Life Expectancy (%)",
+    y = "Count"
   ) +
   theme_minimal() +
-  scale_fill_viridis_d(option = "C") +
   theme(
     plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    legend.position = "none"
+    axis.text.x = element_text(angle = 45, hjust = 1)
   )
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+The GAM was chosen for this analysis due to its ability to capture non-linear relationships between predictors and the outcome variable, which is essential when dealing with categorical predictors like income group and the
 
@@
 
-Our results are summarized in @tbl-modelresults.
-
-1.  check different continent has its different life expectancy.
-2.  compare the develop country with
-3.  check the shcooling year of develop countries to developing country, showing a relationship between shcooling with the life expenctancy.
-4.
+## Overview of model results
+Our results are summarized in @tbl-modelresults. We are primarily interest in the
 
@@
 
+## Multiple linear regression results
+
 # Discussion
 
-## First discussion point {#sec-first-point}
+## Insights into different gender
 
@@
 
+```{r}
+#| label: tbl-cleaned_leab
+#| tbl-cap: "Life expectancy over countries and years"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+#Show the whole graph of cleaned table leab
+kable(leab, 
+      col.names = names(leab), 
+      align = "l", 
+      caption = "Life Expectancy over countries and years")
+
+```
+
 ### Idealized Survey
 
-**Survey: Understanding Life Expectancy and Influencing Factor**
+**Survey: Life Expectancy and Lifestyle Survey**
 
 Thank you for participating in this survey.
-This survey aims to gather insights into the factors influencing life expectancy, including health expenditure, education, ethnicity, government spending on healthcare, and income levels.
-Your responses will help us understand individual perspectives and experiences towards national policy.
+This survey aims to gather insights into the factors influencing life expectancy, including gender, region and income group.
+Your responses will help us understand individual perspectives and experience towards national policy.
 Participation is voluntary, and your answers will remain anonymous.
@@
 
-**Section 1: Personal Health Expenditure**
+**Section 1: Demographics**
 
-**1.What percentage of your monthly income do you spend on healthcare (e.g., insurance, medications, doctor visits)?**
+**1. Gender**
 
--   Less than 5%
--   5%–10%
--   10%–20%
--   More than 20%
+-   Male
+-   Female
+-   Non-binary
+-   Prefer not to say
 
-**2.Do you or your household have health insurance coverage?**
+**2. Age (in years)**
 
+Please write the number: \_\_\_\_\_\_
+
+**3. Region of Residence**
+
+-   Africa
+-   Asia
+-   Europe
+-   North America
+-   South America
+-   Oceania
+
+**4. Income Level**
+
+Annual Income (Optional): \_\_\_\_\_\_ USD
+
+Income Group:
+-   Low Income (Less than $1,000/year)
+-   Lower-Middle Income (\$1,001 - \$10,000/year)
+-   Upper-Middle Income (\$10,001 - \$50,000/year)
+-   High Income (More than \$50,000/year)
+
+**Section 2: Health and Lifestyle**
+
+**5. Current Life Expectancy Perception**
+
+How many years do you expect to live?
+
+Please write the number: \_\_\_\_\_\_
+
+**6. Healthcare Access**
+
+How often do you visit healthcare professionals
+-   Regularly (e.g., annual checkups)
+-   Occasionally (e.g., only when unwell)
+-   Rarely or Never
+
+**7. Dietary Habits**
+
+How would you describe your diet?
+
+-   Balanced and healthy
+-   Somewhat balanced
+-   Unhealthy
+
+**8. Physical Activity**
+
+How many hours of physical activity do you engage in per week?
+-   Less than 1 hour
+-   1-3 hours
+-   More than 3 hours
+
+**9. Smoking Habits**
+
+Do you smoke?
 -   Yes
@@
 
-**3. How frequently do you visit a healthcare professional(eg.doctors, nurse) in a year?**
+**10. Alcohol Consumption**
 
--   0-1 times
--   2-5 times
--   6-10 times
--   More than 10 times
+How often do you consume alcoholic beverages?
+-   Never
+-   Occasionally (e.g., social drinking)
+-   Frequently
 
-**Section 2: Education Background**
+**Section 3: Environmental and Social Factors**
 
-**4.What is the highest level of education you have completed?**
+**11.Living Environment**
 
--   No formal education
--   Primary school
--   Secondary school
--   College or university degree
--   Postgraduate degree
-
-**5.How many years of formal schooling have you completed?**
-
-Please write the number: \_\_\_\_\_\_\_
-
-**Section 3: Ethnicity and Geographic Factors**
-
-**6.Which of the following best describes your ethnicity?**
-
--   African
--   Asian
--   European
--   Hispanic or Latino
--   Middle Eastern
--   Indigenous
--   Other (please specify): \_\_\_\_\_\_\_
-
-**7.What's the distance to the nearest healthcare facility from your residence?**
-
--   Less than 1 km
--   1-5 km
--   More than 5 km
-
-**Section 4: Government Expenditure on Healthcare**
-
-**8.Are health services in your country subsidized by the govenment?**
-
--   Yes, fully subsidized
--   Yes, partially subsidized
--   No
-
-**9. What is the approximate cost of your most recent healthcare visit (in local currency)?**
-
-Please write the amount \_\_\_\_\_\_\_
-
-**10.Do public healthcare facilities in your area provide all the services you need?**
-
--   Yes
--   No
--   Not applicable
-
-**Section 5: Income and Development Factor**
-
-**11.What is your approximate monthly household income after taxes?(in local currency)**
-
--   Less than 1,000
--   1,000 - 2,999
--   3,000 - 4,999
--   5,000 - 7,999
--   8,000 - 10,999
--   More than 11,000
--   Prefer not to say
-
-**12.How would you describe your current financial situation?**
-
--   Struggling to make ends meet
--   Just getting by
--   Comfortable, but not wealthy
--   Financially secure
--   Wealthy
--   Prefer not to say
-
-**13.How often do you have difficulty affording basic healthcare (medical visits, medications, etc.)?**
-
--   Never
--   Rarely
--   Sometimes
--   Often
--   Always
--   Prefer not to say
+How would you describe your living area?
+-   Urban
+-   Suburban
+-   Rural
 

### 2024-12-03 paper/paper.tex
initial

@@
 
-\textbf{?@fig-cleaned} shows the average of life expectancy under male,
-female, 6 different regions and 4 income groups.
+shows the average of life expectancy under male, female, 6 different
+regions and 4 income groups.
 
@@
 
-The outcome variable is \textbf{\texttt{Life\ Expendency}}. This is the
-primary dependent variable that the model is designed to predict. It
-represents the average number of years a person is expected to live,
-under the condition that current mortality conditions persist. The model
-seeks to identify the variables affecting this average.
+The outcome variable is \textbf{Life Expectancy}. This is the primary
+dependent variable that the model is designed to predict. It represents
+the average number of years a person is expected to live, under the
+condition that current mortality conditions persist. The model seeks to
+identify the variables affecting this average.
 
@@
 
-We expect a positive relationship between the size of the wings and time
-spent aloft. In particular\ldots{}
-
-We can use maths by including latex between dollar signs, for instance
-\(\theta\).
+The GAM was chosen for this analysis due to its ability to capture
+non-linear relationships between predictors and the outcome variable,
+which is essential when dealing with categorical predictors like income
+group and the
 
@@
 
-Our results are summarized in Table~\ref{tbl-modelresults}.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  check different continent has its different life expectancy.
-\item
-  compare the develop country with
-\item
-  check the shcooling year of develop countries to developing country,
-  showing a relationship between shcooling with the life expenctancy.
-\item
-\end{enumerate}
+\subsection{Overview of model results}\label{overview-of-model-results}
+
+Our results are summarized in Table~\ref{tbl-modelresults}. We are
+primarily interest in the
+
+\subsection{Multiple linear regression
+results}\label{multiple-linear-regression-results}
 
@@
 
-\subsection{First discussion point}\label{sec-first-point}
+\subsection{Insights into different
+gender}\label{insights-into-different-gender}
 
@@
 
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2245}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.3605}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0476}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0748}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1088}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0884}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0952}}@{}}
+
+\caption{\label{tbl-cleaned_leab}Life expectancy over countries and
+years}
+
+\tabularnewline
+
+\caption{Life Expectancy over countries and years}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Indicator
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Country
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Period
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Gender
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Life Expectancy
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Income\_Group
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Region
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Indicator
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Country
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Period
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Gender
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Life Expectancy
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Income\_Group
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Region
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Life expectancy at birth (years) & Afghanistan & 2020 & Male & 59.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2020 & Both sexes &
+60.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2020 & Female & 61.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2019 & Male & 60.0 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2019 & Both sexes &
+61.2 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2019 & Female & 62.5 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2018 & Male & 59.0 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2018 & Both sexes &
+60.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2018 & Female & 62.1 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2017 & Male & 59.8 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2017 & Both sexes &
+60.9 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2017 & Female & 62.1 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2016 & Male & 59.2 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2016 & Both sexes &
+60.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2016 & Female & 61.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2015 & Male & 59.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2015 & Both sexes &
+60.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2015 & Female & 61.5 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Albania & 2020 & Male & 74.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2020 & Both sexes & 76.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2020 & Female & 79.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2019 & Male & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2019 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2019 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2018 & Male & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2018 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2018 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2017 & Male & 76.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2017 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2017 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2016 & Male & 76.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2016 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2016 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2015 & Male & 76.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2015 & Both sexes & 77.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2015 & Female & 79.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Algeria & 2020 & Male & 73.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2020 & Both sexes & 74.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2020 & Female & 75.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2019 & Male & 76.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2019 & Both sexes & 76.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2019 & Female & 77.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2018 & Male & 76.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2018 & Both sexes & 76.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2018 & Female & 77.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2017 & Male & 76.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2017 & Both sexes & 76.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2017 & Female & 77.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2016 & Male & 75.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2016 & Both sexes & 76.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2016 & Female & 76.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2015 & Male & 75.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2015 & Both sexes & 76.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2015 & Female & 76.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2020 & Male & 60.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2020 & Both sexes & 62.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2020 & Female & 64.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2019 & Male & 60.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2019 & Both sexes & 62.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2019 & Female & 64.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2018 & Male & 60.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2018 & Both sexes & 62.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2018 & Female & 64.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2017 & Male & 59.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2017 & Both sexes & 62.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2017 & Female & 64.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2016 & Male & 59.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2016 & Both sexes & 61.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2016 & Female & 64.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2015 & Male & 59.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2015 & Both sexes & 61.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2015 & Female & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Male &
+75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Both
+sexes & 77.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Female &
+79.4 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Male &
+74.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Both
+sexes & 75.7 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Female &
+77.1 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Male &
+74.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Both
+sexes & 75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Female &
+77.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Male &
+73.9 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Both
+sexes & 75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Female &
+77.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Male &
+73.8 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Both
+sexes & 75.5 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Female &
+77.1 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Male &
+73.8 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Both
+sexes & 75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Female &
+77.2 & high\_income & North America \\
+Life expectancy at birth (years) & Argentina & 2020 & Male & 73.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2020 & Both sexes & 76.2
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2020 & Female & 79.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2019 & Male & 74.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2019 & Both sexes & 77.0
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2019 & Female & 79.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2018 & Male & 73.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2018 & Both sexes & 76.9
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2018 & Female & 79.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2017 & Male & 73.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2017 & Both sexes & 76.6
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2017 & Female & 79.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2016 & Male & 73.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2016 & Both sexes & 76.1
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2016 & Female & 79.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2015 & Male & 73.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2015 & Both sexes & 76.5
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2015 & Female & 79.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Armenia & 2020 & Male & 62.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2020 & Both sexes & 69.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2020 & Female & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2019 & Male & 70.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2019 & Both sexes & 75.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2019 & Female & 79.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2018 & Male & 71.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2018 & Both sexes & 75.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2018 & Female & 79.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2017 & Male & 70.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2017 & Both sexes & 75.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2017 & Female & 79.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2016 & Male & 69.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2016 & Both sexes & 74.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2016 & Female & 78.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2015 & Male & 69.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2015 & Both sexes & 74.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2015 & Female & 78.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Australia & 2020 & Male & 81.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2020 & Both sexes & 83.4
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2020 & Female & 85.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2019 & Male & 80.7 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2019 & Both sexes & 82.6
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2019 & Female & 84.6 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2018 & Male & 81.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2018 & Both sexes & 83.0
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2018 & Female & 84.9 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2017 & Male & 80.8 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2017 & Both sexes & 82.7
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2017 & Female & 84.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2016 & Male & 80.7 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2016 & Both sexes & 82.6
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2016 & Female & 84.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2015 & Male & 80.4 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2015 & Both sexes & 82.3
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2015 & Female & 84.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Austria & 2020 & Male & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2020 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2020 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2019 & Male & 79.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2019 & Both sexes & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2019 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2018 & Male & 79.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2018 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2018 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2017 & Male & 79.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2017 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2017 & Female & 83.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2016 & Male & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2016 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2016 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2015 & Male & 78.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2015 & Both sexes & 81.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2015 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2020 & Male & 67.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2020 & Both sexes & 71.4
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2020 & Female & 75.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2019 & Male & 73.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2019 & Both sexes & 75.8
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2019 & Female & 78.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2018 & Male & 72.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2018 & Both sexes & 75.1
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2018 & Female & 77.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2017 & Male & 72.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2017 & Both sexes & 74.6
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2017 & Female & 76.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2016 & Male & 71.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2016 & Both sexes & 74.0
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2016 & Female & 76.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2015 & Male & 71.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2015 & Both sexes & 73.6
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2015 & Female & 75.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bahamas & 2020 & Male & 69.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2020 & Both sexes & 72.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2020 & Female & 76.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2019 & Male & 68.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2019 & Both sexes & 70.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2019 & Female & 73.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2018 & Male & 70.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2018 & Both sexes & 73.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2018 & Female & 76.5 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2017 & Male & 70.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2017 & Both sexes & 73.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2017 & Female & 76.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2016 & Male & 69.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2016 & Both sexes & 72.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2016 & Female & 76.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2015 & Male & 69.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2015 & Both sexes & 72.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2015 & Female & 76.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahrain & 2020 & Male & 73.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2020 & Both sexes & 74.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2020 & Female & 76.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2019 & Male & 75.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2019 & Both sexes & 76.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2019 & Female & 76.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2018 & Male & 75.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2018 & Both sexes & 75.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2018 & Female & 77.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2017 & Male & 74.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2017 & Both sexes & 75.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2017 & Female & 76.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2016 & Male & 75.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2016 & Both sexes & 75.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2016 & Female & 76.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2015 & Male & 75.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2015 & Both sexes & 75.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2015 & Female & 76.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2020 & Male & 71.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2020 & Both sexes & 73.3
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2020 & Female & 75.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2019 & Male & 72.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2019 & Both sexes & 73.9
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2019 & Female & 75.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2018 & Male & 72.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2018 & Both sexes & 73.7
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2018 & Female & 75.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2017 & Male & 72.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2017 & Both sexes & 73.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2017 & Female & 74.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2016 & Male & 72.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2016 & Both sexes & 73.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2016 & Female & 74.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2015 & Male & 72.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2015 & Both sexes & 73.2
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Bangladesh & 2015 & Female & 74.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Barbados & 2020 & Male & 75.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2020 & Both sexes & 76.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2020 & Female & 78.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2019 & Male & 74.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2019 & Both sexes & 76.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2019 & Female & 77.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2018 & Male & 74.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2018 & Both sexes & 76.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2018 & Female & 77.5 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2017 & Male & 75.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2017 & Both sexes & 76.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2017 & Female & 77.5 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2016 & Male & 75.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2016 & Both sexes & 76.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2016 & Female & 77.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2015 & Male & 75.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2015 & Both sexes & 76.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Barbados & 2015 & Female & 77.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Belarus & 2020 & Male & 67.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2020 & Both sexes & 73.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2020 & Female & 78.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2019 & Male & 69.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2019 & Both sexes & 74.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2019 & Female & 79.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2018 & Male & 69.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2018 & Both sexes & 74.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2018 & Female & 79.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2017 & Male & 69.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2017 & Both sexes & 74.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2017 & Female & 79.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2016 & Male & 68.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2016 & Both sexes & 73.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2016 & Female & 78.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2015 & Male & 68.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2015 & Both sexes & 73.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belarus & 2015 & Female & 78.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Belgium & 2020 & Male & 78.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2020 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2020 & Female & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2019 & Male & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2019 & Both sexes & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2019 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2018 & Male & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2018 & Both sexes & 81.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2018 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2017 & Male & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2017 & Both sexes & 81.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2017 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2016 & Male & 78.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2016 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2016 & Female & 83.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2015 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2015 & Both sexes & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belgium & 2015 & Female & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Belize & 2020 & Male & 72.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2020 & Both sexes & 74.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2020 & Female & 76.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2019 & Male & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2019 & Both sexes & 74.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2019 & Female & 77.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2018 & Male & 72.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2018 & Both sexes & 74.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2018 & Female & 77.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2017 & Male & 71.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2017 & Both sexes & 74.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2017 & Female & 77.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2016 & Male & 71.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2016 & Both sexes & 74.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2016 & Female & 77.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2015 & Male & 71.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2015 & Both sexes & 74.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Belize & 2015 & Female & 77.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Benin & 2020 & Male & 61.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2020 & Both sexes & 64.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2020 & Female & 67.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2019 & Male & 61.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2019 & Both sexes & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2019 & Female & 66.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2018 & Male & 61.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2018 & Both sexes & 63.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2018 & Female & 66.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2017 & Male & 61.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2017 & Both sexes & 63.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2017 & Female & 65.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2016 & Male & 60.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2016 & Both sexes & 63.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2016 & Female & 65.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2015 & Male & 60.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2015 & Both sexes & 62.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Benin & 2015 & Female & 65.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Bhutan & 2020 & Male & 73.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2020 & Both sexes & 74.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2020 & Female & 75.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2019 & Male & 72.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2019 & Both sexes & 73.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2019 & Female & 75.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2018 & Male & 72.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2018 & Both sexes & 73.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2018 & Female & 74.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2017 & Male & 72.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2017 & Both sexes & 73.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2017 & Female & 74.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2016 & Male & 72.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2016 & Both sexes & 73.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2016 & Female & 74.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2015 & Male & 72.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2015 & Both sexes & 73.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bhutan & 2015 & Female & 74.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2020 & Male & 64.4 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2020 & Both sexes & 67.1 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2020 & Female & 70.4 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2019 & Male & 72.0 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2019 & Both sexes & 72.9 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2019 & Female & 73.8 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2018 & Male & 71.8 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2018 & Both sexes & 72.7 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2018 & Female & 73.6 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2017 & Male & 71.5 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2017 & Both sexes & 72.4 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2017 & Female & 73.3 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2016 & Male & 71.3 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2016 & Both sexes & 72.2 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2016 & Female & 73.1 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2015 & Male & 71.0 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2015 & Both sexes & 71.9 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bolivia (Plurinational State of) &
+2015 & Female & 72.8 & lower\_middle & South America \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2020 & Male
+& 73.0 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2020 & Both
+sexes & 75.7 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2020 &
+Female & 78.5 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2019 & Male
+& 74.6 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2019 & Both
+sexes & 77.1 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2019 &
+Female & 79.6 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2018 & Male
+& 74.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2018 & Both
+sexes & 77.3 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2018 &
+Female & 79.8 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2017 & Male
+& 74.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2017 & Both
+sexes & 77.2 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2017 &
+Female & 79.5 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2016 & Male
+& 74.6 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2016 & Both
+sexes & 77.1 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2016 &
+Female & 79.6 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2015 & Male
+& 74.5 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2015 & Both
+sexes & 77.0 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Bosnia and Herzegovina & 2015 &
+Female & 79.4 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Botswana & 2020 & Male & 62.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2020 & Both sexes & 65.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2020 & Female & 67.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2019 & Male & 62.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2019 & Both sexes & 64.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2019 & Female & 66.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2018 & Male & 62.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2018 & Both sexes & 64.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2018 & Female & 66.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2017 & Male & 61.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2017 & Both sexes & 64.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2017 & Female & 66.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2016 & Male & 60.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2016 & Both sexes & 63.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2016 & Female & 65.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2015 & Male & 60.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2015 & Both sexes & 62.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Botswana & 2015 & Female & 63.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Brazil & 2020 & Male & 70.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2020 & Both sexes & 74.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2020 & Female & 77.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2019 & Male & 72.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2019 & Both sexes & 75.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2019 & Female & 78.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2018 & Male & 71.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2018 & Both sexes & 75.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2018 & Female & 78.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2017 & Male & 71.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2017 & Both sexes & 75.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2017 & Female & 78.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2016 & Male & 71.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2016 & Both sexes & 74.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2016 & Female & 78.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2015 & Male & 71.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2015 & Both sexes & 74.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brazil & 2015 & Female & 78.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Brunei Darussalam & 2020 & Male &
+75.3 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2020 & Both sexes
+& 76.8 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2020 & Female &
+78.3 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2019 & Male &
+75.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2019 & Both sexes
+& 76.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2019 & Female &
+78.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2018 & Male &
+75.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2018 & Both sexes
+& 76.4 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2018 & Female &
+77.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2017 & Male &
+75.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2017 & Both sexes
+& 76.4 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2017 & Female &
+77.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2016 & Male &
+75.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2016 & Both sexes
+& 76.4 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2016 & Female &
+77.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2015 & Male &
+75.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2015 & Both sexes
+& 76.6 & high\_income & Asia \\
+Life expectancy at birth (years) & Brunei Darussalam & 2015 & Female &
+77.9 & high\_income & Asia \\
+Life expectancy at birth (years) & Bulgaria & 2020 & Male & 69.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2020 & Both sexes & 73.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2020 & Female & 77.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2019 & Male & 71.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2019 & Both sexes & 75.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2019 & Female & 78.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2018 & Male & 71.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2018 & Both sexes & 74.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2018 & Female & 78.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2017 & Male & 71.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2017 & Both sexes & 74.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2017 & Female & 78.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2016 & Male & 71.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2016 & Both sexes & 74.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2016 & Female & 78.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2015 & Male & 71.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2015 & Both sexes & 74.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bulgaria & 2015 & Female & 78.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Burkina Faso & 2020 & Male & 60.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2020 & Both sexes &
+62.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2020 & Female & 65.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2019 & Male & 60.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2019 & Both sexes &
+62.6 & lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2019 & Female & 65.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2018 & Male & 59.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2018 & Both sexes &
+62.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2018 & Female & 64.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2017 & Male & 59.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2017 & Both sexes &
+61.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2017 & Female & 64.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2016 & Male & 58.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2016 & Both sexes &
+61.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2016 & Female & 63.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2015 & Male & 58.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2015 & Both sexes &
+60.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Burkina Faso & 2015 & Female & 63.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2020 & Male & 62.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2020 & Both sexes & 64.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2020 & Female & 66.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2019 & Male & 62.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2019 & Both sexes & 64.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2019 & Female & 66.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2018 & Male & 62.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2018 & Both sexes & 64.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2018 & Female & 66.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2017 & Male & 61.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2017 & Both sexes & 63.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2017 & Female & 65.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2016 & Male & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2016 & Both sexes & 63.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2016 & Female & 65.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2015 & Male & 60.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2015 & Both sexes & 62.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Burundi & 2015 & Female & 64.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2020 & Male & 69.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2020 & Both sexes & 73.7
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2020 & Female & 78.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2019 & Male & 69.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2019 & Both sexes & 74.1
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2019 & Female & 78.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2018 & Male & 69.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2018 & Both sexes & 73.9
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2018 & Female & 78.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2017 & Male & 72.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2017 & Both sexes & 74.9
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2017 & Female & 77.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2016 & Male & 72.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2016 & Both sexes & 74.9
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2016 & Female & 77.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2015 & Male & 71.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2015 & Both sexes & 74.8
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cabo Verde & 2015 & Female & 77.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cambodia & 2020 & Male & 67.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2020 & Both sexes & 69.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2020 & Female & 72.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2019 & Male & 66.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2019 & Both sexes & 69.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2019 & Female & 72.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2018 & Male & 66.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2018 & Both sexes & 69.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2018 & Female & 72.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2017 & Male & 66.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2017 & Both sexes & 69.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2017 & Female & 71.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2016 & Male & 66.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2016 & Both sexes & 68.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2016 & Female & 71.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2015 & Male & 65.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2015 & Both sexes & 68.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cambodia & 2015 & Female & 71.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Cameroon & 2020 & Male & 60.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2020 & Both sexes & 62.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2020 & Female & 64.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2019 & Male & 60.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2019 & Both sexes & 62.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2019 & Female & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2018 & Male & 59.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2018 & Both sexes & 61.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2018 & Female & 63.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2017 & Male & 58.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2017 & Both sexes & 60.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2017 & Female & 62.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2016 & Male & 58.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2016 & Both sexes & 59.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2016 & Female & 61.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2015 & Male & 57.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2015 & Both sexes & 59.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cameroon & 2015 & Female & 60.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Canada & 2020 & Male & 79.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2020 & Both sexes & 81.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2020 & Female & 83.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2019 & Male & 80.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2019 & Both sexes & 82.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2019 & Female & 83.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2018 & Male & 79.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2018 & Both sexes & 81.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2018 & Female & 83.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2017 & Male & 79.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2017 & Both sexes & 81.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2017 & Female & 83.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2016 & Male & 79.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2016 & Both sexes & 81.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2016 & Female & 83.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2015 & Male & 79.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2015 & Both sexes & 81.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Canada & 2015 & Female & 83.5 &
+high\_income & North America \\
+Life expectancy at birth (years) & Central African Republic & 2020 &
+Male & 50.5 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2020 &
+Both sexes & 53.1 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2020 &
+Female & 56.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2019 &
+Male & 50.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2019 &
+Both sexes & 52.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2019 &
+Female & 55.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2018 &
+Male & 49.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2018 &
+Both sexes & 52.1 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2018 &
+Female & 55.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2017 &
+Male & 48.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2017 &
+Both sexes & 51.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2017 &
+Female & 54.7 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2016 &
+Male & 49.1 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2016 &
+Both sexes & 51.5 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2016 &
+Female & 54.2 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2015 &
+Male & 48.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2015 &
+Both sexes & 51.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Central African Republic & 2015 &
+Female & 53.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2020 & Male & 57.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2020 & Both sexes & 59.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2020 & Female & 60.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2019 & Male & 57.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2019 & Both sexes & 59.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2019 & Female & 60.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2018 & Male & 57.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2018 & Both sexes & 59.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2018 & Female & 60.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2017 & Male & 57.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2017 & Both sexes & 58.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2017 & Female & 60.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2016 & Male & 56.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2016 & Both sexes & 58.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2016 & Female & 59.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2015 & Male & 56.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2015 & Both sexes & 57.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chad & 2015 & Female & 59.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Chile & 2020 & Male & 77.3 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2020 & Both sexes & 79.9 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2020 & Female & 82.5 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2019 & Male & 78.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2019 & Both sexes & 81.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2019 & Female & 83.3 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2018 & Male & 78.6 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2018 & Both sexes & 81.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2018 & Female & 83.3 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2017 & Male & 78.2 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2017 & Both sexes & 80.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2017 & Female & 83.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2016 & Male & 78.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2016 & Both sexes & 80.5 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2016 & Female & 82.9 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2015 & Male & 77.5 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2015 & Both sexes & 80.1 &
+high\_income & South America \\
+Life expectancy at birth (years) & Chile & 2015 & Female & 82.6 &
+high\_income & South America \\
+Life expectancy at birth (years) & China & 2020 & Male & 74.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2020 & Both sexes & 77.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2020 & Female & 80.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2019 & Male & 74.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2019 & Both sexes & 77.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2019 & Female & 80.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2018 & Male & 74.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2018 & Both sexes & 77.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2018 & Female & 80.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2017 & Male & 74.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2017 & Both sexes & 76.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2017 & Female & 80.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2016 & Male & 73.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2016 & Both sexes & 76.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2016 & Female & 79.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2015 & Male & 73.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2015 & Both sexes & 76.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & China & 2015 & Female & 79.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Colombia & 2020 & Male & 73.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2020 & Both sexes & 76.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2020 & Female & 79.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2019 & Male & 75.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2019 & Both sexes & 78.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2019 & Female & 80.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2018 & Male & 75.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2018 & Both sexes & 77.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2018 & Female & 80.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2017 & Male & 75.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2017 & Both sexes & 77.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2017 & Female & 80.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2016 & Male & 74.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2016 & Both sexes & 77.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2016 & Female & 80.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2015 & Male & 74.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2015 & Both sexes & 77.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Colombia & 2015 & Female & 80.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Comoros & 2020 & Male & 67.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2020 & Both sexes & 68.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2020 & Female & 69.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2019 & Male & 66.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2019 & Both sexes & 68.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2019 & Female & 69.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2018 & Male & 67.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2018 & Both sexes & 68.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2018 & Female & 69.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2017 & Male & 66.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2017 & Both sexes & 67.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2017 & Female & 69.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2016 & Male & 66.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2016 & Both sexes & 67.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2016 & Female & 68.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2015 & Male & 66.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2015 & Both sexes & 67.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Comoros & 2015 & Female & 68.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2020 & Male & 62.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2020 & Both sexes & 63.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2020 & Female & 64.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2019 & Male & 62.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2019 & Both sexes & 62.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2019 & Female & 63.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2018 & Male & 62.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2018 & Both sexes & 63.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2018 & Female & 63.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2017 & Male & 62.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2017 & Both sexes & 62.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2017 & Female & 63.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2016 & Male & 62.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2016 & Both sexes & 62.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2016 & Female & 62.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2015 & Male & 61.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2015 & Both sexes & 62.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Congo & 2015 & Female & 62.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Costa Rica & 2020 & Male & 77.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2020 & Both sexes & 80.0
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2020 & Female & 82.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2019 & Male & 77.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2019 & Both sexes & 80.3
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2019 & Female & 82.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2018 & Male & 77.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2018 & Both sexes & 80.3
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2018 & Female & 83.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2017 & Male & 77.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2017 & Both sexes & 80.2
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2017 & Female & 82.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2016 & Male & 77.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2016 & Both sexes & 80.1
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2016 & Female & 82.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2015 & Male & 77.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2015 & Both sexes & 80.6
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Costa Rica & 2015 & Female & 83.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2020 & Male & 61.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2020 & Both sexes &
+63.3 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2020 & Female & 66.1
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2019 & Male & 61.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2019 & Both sexes &
+63.5 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2019 & Female & 66.2
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2018 & Male & 60.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2018 & Both sexes &
+62.9 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2018 & Female & 65.7
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2017 & Male & 60.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2017 & Both sexes &
+62.3 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2017 & Female & 65.0
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2016 & Male & 59.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2016 & Both sexes &
+61.6 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2016 & Female & 64.4
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2015 & Male & 58.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2015 & Both sexes &
+60.9 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Cote d'Ivoire & 2015 & Female & 63.7
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Croatia & 2020 & Male & 74.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2020 & Both sexes & 77.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2020 & Female & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2019 & Male & 75.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2019 & Both sexes & 78.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2019 & Female & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2018 & Male & 75.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2018 & Both sexes & 78.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2018 & Female & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2017 & Male & 75.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2017 & Both sexes & 78.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2017 & Female & 81.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2016 & Male & 75.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2016 & Both sexes & 78.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2016 & Female & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2015 & Male & 74.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2015 & Both sexes & 77.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Croatia & 2015 & Female & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cuba & 2020 & Male & 75.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2020 & Both sexes & 77.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2020 & Female & 80.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2019 & Male & 75.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2019 & Both sexes & 77.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2019 & Female & 80.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2018 & Male & 75.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2018 & Both sexes & 77.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2018 & Female & 80.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2017 & Male & 75.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2017 & Both sexes & 77.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2017 & Female & 80.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2016 & Male & 75.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2016 & Both sexes & 78.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2016 & Female & 80.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2015 & Male & 75.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2015 & Both sexes & 77.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cuba & 2015 & Female & 80.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Cyprus & 2020 & Male & 80.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2020 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2020 & Female & 84.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2019 & Male & 80.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2019 & Both sexes & 82.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2019 & Female & 84.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2018 & Male & 80.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2018 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2018 & Female & 84.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2017 & Male & 79.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2017 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2017 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2016 & Male & 79.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2016 & Both sexes & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2016 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2015 & Male & 79.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2015 & Both sexes & 81.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Cyprus & 2015 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2020 & Male & 75.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2020 & Both sexes & 78.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2020 & Female & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2019 & Male & 76.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2019 & Both sexes & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2019 & Female & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2018 & Male & 76.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2018 & Both sexes & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2018 & Female & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2017 & Male & 76.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2017 & Both sexes & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2017 & Female & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2016 & Male & 76.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2016 & Both sexes & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2016 & Female & 81.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2015 & Male & 75.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2015 & Both sexes & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Czechia & 2015 & Female & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2020 & Male & 69.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2020 & Both sexes & 72.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2020 & Female & 75.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2019 & Male & 69.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2019 & Both sexes & 72.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2019 & Female & 75.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2018 & Male & 69.1 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2018 & Both sexes & 72.1 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2018 & Female & 75.1 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2017 & Male & 68.9 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2017 & Both sexes & 71.9 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2017 & Female & 74.9 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2016 & Male & 68.6 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2016 & Both sexes & 71.6 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2016 & Female & 74.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2015 & Male & 68.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2015 & Both sexes & 71.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic People's Republic of Korea
+& 2015 & Female & 74.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2020 & Male & 59.7 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2020 & Both sexes & 62.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2020 & Female & 64.5 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2019 & Male & 59.7 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2019 & Both sexes & 61.8 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2019 & Female & 64.1 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2018 & Male & 59.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2018 & Both sexes & 61.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2018 & Female & 63.6 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2017 & Male & 58.8 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2017 & Both sexes & 60.8 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2017 & Female & 63.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2016 & Male & 58.5 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2016 & Both sexes & 60.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2016 & Female & 62.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2015 & Male & 58.1 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2015 & Both sexes & 60.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Democratic Republic of the Congo &
+2015 & Female & 61.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Denmark & 2020 & Male & 79.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2020 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2020 & Female & 83.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2019 & Male & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2019 & Both sexes & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2019 & Female & 83.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2018 & Male & 79.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2018 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2018 & Female & 82.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2017 & Male & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2017 & Both sexes & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2017 & Female & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2016 & Male & 79.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2016 & Both sexes & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2016 & Female & 82.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2015 & Male & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2015 & Both sexes & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Denmark & 2015 & Female & 82.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Djibouti & 2020 & Male & 63.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2020 & Both sexes & 65.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2020 & Female & 67.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2019 & Male & 63.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2019 & Both sexes & 65.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2019 & Female & 67.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2018 & Male & 63.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2018 & Both sexes & 65.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2018 & Female & 66.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2017 & Male & 63.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2017 & Both sexes & 64.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2017 & Female & 66.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2016 & Male & 62.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2016 & Both sexes & 64.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2016 & Female & 66.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2015 & Male & 62.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2015 & Both sexes & 63.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Djibouti & 2015 & Female & 65.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Dominican Republic & 2020 & Male &
+70.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2020 & Both
+sexes & 73.6 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2020 & Female &
+77.5 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2019 & Male &
+70.9 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2019 & Both
+sexes & 73.9 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2019 & Female &
+77.2 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2018 & Male &
+70.4 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2018 & Both
+sexes & 73.5 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2018 & Female &
+76.9 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2017 & Male &
+70.2 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2017 & Both
+sexes & 73.4 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2017 & Female &
+76.9 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2016 & Male &
+70.0 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2016 & Both
+sexes & 73.3 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2016 & Female &
+77.0 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2015 & Male &
+69.9 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2015 & Both
+sexes & 73.3 & upper\_middle & North America \\
+Life expectancy at birth (years) & Dominican Republic & 2015 & Female &
+77.0 & upper\_middle & North America \\
+Life expectancy at birth (years) & Ecuador & 2020 & Male & 69.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2020 & Both sexes & 72.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2020 & Female & 76.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2019 & Male & 75.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2019 & Both sexes & 77.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2019 & Female & 80.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2018 & Male & 75.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2018 & Both sexes & 77.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2018 & Female & 79.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2017 & Male & 74.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2017 & Both sexes & 77.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2017 & Female & 79.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2016 & Male & 74.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2016 & Both sexes & 77.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2016 & Female & 79.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2015 & Male & 74.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2015 & Both sexes & 77.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Ecuador & 2015 & Female & 79.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Egypt & 2020 & Male & 67.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2020 & Both sexes & 70.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2020 & Female & 72.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2019 & Male & 69.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2019 & Both sexes & 71.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2019 & Female & 74.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2018 & Male & 68.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2018 & Both sexes & 71.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2018 & Female & 74.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2017 & Male & 68.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2017 & Both sexes & 71.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2017 & Female & 74.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2016 & Male & 68.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2016 & Both sexes & 70.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2016 & Female & 73.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2015 & Male & 67.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2015 & Both sexes & 70.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Egypt & 2015 & Female & 72.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & El Salvador & 2020 & Male & 67.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2020 & Both sexes &
+72.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2020 & Female & 76.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2019 & Male & 69.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2019 & Both sexes &
+74.3 & upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2019 & Female & 78.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2018 & Male & 69.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2018 & Both sexes &
+74.7 & upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2018 & Female & 79.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2017 & Male & 69.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2017 & Both sexes &
+73.7 & upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2017 & Female & 78.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2016 & Male & 68.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2016 & Both sexes &
+73.6 & upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2016 & Female & 78.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2015 & Male & 67.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2015 & Both sexes &
+72.7 & upper\_middle & North America \\
+Life expectancy at birth (years) & El Salvador & 2015 & Female & 77.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Equatorial Guinea & 2020 & Male &
+59.6 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2020 & Both sexes
+& 61.2 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2020 & Female &
+62.9 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2019 & Male &
+59.9 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2019 & Both sexes
+& 61.4 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2019 & Female &
+63.0 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2018 & Male &
+59.9 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2018 & Both sexes
+& 61.4 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2018 & Female &
+63.1 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2017 & Male &
+59.7 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2017 & Both sexes
+& 61.2 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2017 & Female &
+62.8 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2016 & Male &
+59.6 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2016 & Both sexes
+& 60.9 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2016 & Female &
+62.1 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2015 & Male &
+60.0 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2015 & Both sexes
+& 61.1 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Equatorial Guinea & 2015 & Female &
+62.2 & upper\_middle & Africa \\
+Life expectancy at birth (years) & Eritrea & 2020 & Male & 61.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2020 & Both sexes & 63.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2020 & Female & 66.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2019 & Male & 61.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2019 & Both sexes & 63.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2019 & Female & 66.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2018 & Male & 60.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2018 & Both sexes & 63.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2018 & Female & 66.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2017 & Male & 60.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2017 & Both sexes & 63.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2017 & Female & 66.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2016 & Male & 60.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2016 & Both sexes & 62.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2016 & Female & 65.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2015 & Male & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2015 & Both sexes & 62.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Eritrea & 2015 & Female & 65.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Estonia & 2020 & Male & 74.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2020 & Both sexes & 78.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2020 & Female & 82.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2019 & Male & 74.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2019 & Both sexes & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2019 & Female & 82.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2018 & Male & 74.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2018 & Both sexes & 78.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2018 & Female & 82.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2017 & Male & 73.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2017 & Both sexes & 78.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2017 & Female & 82.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2016 & Male & 73.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2016 & Both sexes & 77.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2016 & Female & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2015 & Male & 73.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2015 & Both sexes & 77.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Estonia & 2015 & Female & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Eswatini & 2020 & Male & 52.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2020 & Both sexes & 56.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2020 & Female & 59.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2019 & Male & 52.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2019 & Both sexes & 55.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2019 & Female & 59.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2018 & Male & 51.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2018 & Both sexes & 54.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2018 & Female & 58.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2017 & Male & 50.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2017 & Both sexes & 53.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2017 & Female & 57.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2016 & Male & 50.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2016 & Both sexes & 53.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2016 & Female & 56.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2015 & Male & 49.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2015 & Both sexes & 52.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Eswatini & 2015 & Female & 55.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2020 & Male & 66.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2020 & Both sexes & 68.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2020 & Female & 70.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2019 & Male & 67.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2019 & Both sexes & 68.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2019 & Female & 70.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2018 & Male & 66.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2018 & Both sexes & 68.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2018 & Female & 70.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2017 & Male & 66.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2017 & Both sexes & 68.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2017 & Female & 69.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2016 & Male & 65.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2016 & Both sexes & 67.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2016 & Female & 69.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2015 & Male & 65.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2015 & Both sexes & 67.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ethiopia & 2015 & Female & 68.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Fiji & 2020 & Male & 65.4 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2020 & Both sexes & 67.7 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2020 & Female & 70.2 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2019 & Male & 65.8 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2019 & Both sexes & 67.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2019 & Female & 70.1 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2018 & Male & 65.8 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2018 & Both sexes & 67.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2018 & Female & 70.1 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2017 & Male & 65.8 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2017 & Both sexes & 67.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2017 & Female & 70.1 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2016 & Male & 65.7 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2016 & Both sexes & 67.7 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2016 & Female & 69.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2015 & Male & 65.8 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2015 & Both sexes & 67.8 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Fiji & 2015 & Female & 69.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Finland & 2020 & Male & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2020 & Both sexes & 81.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2020 & Female & 84.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2019 & Male & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2019 & Both sexes & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2019 & Female & 84.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2018 & Male & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2018 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2018 & Female & 84.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2017 & Male & 78.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2017 & Both sexes & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2017 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2016 & Male & 78.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2016 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2016 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2015 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2015 & Both sexes & 81.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Finland & 2015 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2020 & Male & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2020 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2020 & Female & 84.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2019 & Male & 79.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2019 & Both sexes & 82.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2019 & Female & 85.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2018 & Male & 79.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2018 & Both sexes & 82.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2018 & Female & 85.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2017 & Male & 79.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2017 & Both sexes & 82.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2017 & Female & 84.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2016 & Male & 79.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2016 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2016 & Female & 84.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2015 & Male & 79.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2015 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & France & 2015 & Female & 84.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Gabon & 2020 & Male & 62.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2020 & Both sexes & 65.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2020 & Female & 68.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2019 & Male & 62.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2019 & Both sexes & 65.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2019 & Female & 67.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2018 & Male & 62.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2018 & Both sexes & 64.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2018 & Female & 67.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2017 & Male & 62.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2017 & Both sexes & 64.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2017 & Female & 67.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2016 & Male & 61.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2016 & Both sexes & 64.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2016 & Female & 67.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2015 & Male & 61.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2015 & Both sexes & 64.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gabon & 2015 & Female & 66.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Gambia & 2020 & Male & 62.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2020 & Both sexes & 64.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2020 & Female & 67.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2019 & Male & 62.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2019 & Both sexes & 64.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2019 & Female & 67.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2018 & Male & 62.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2018 & Both sexes & 64.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2018 & Female & 66.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2017 & Male & 62.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2017 & Both sexes & 64.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2017 & Female & 66.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2016 & Male & 62.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2016 & Both sexes & 64.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2016 & Female & 66.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2015 & Male & 61.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2015 & Both sexes & 63.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Gambia & 2015 & Female & 65.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Georgia & 2020 & Male & 68.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2020 & Both sexes & 73.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2020 & Female & 77.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2019 & Male & 69.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2019 & Both sexes & 73.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2019 & Female & 78.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2018 & Male & 69.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2018 & Both sexes & 73.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2018 & Female & 78.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2017 & Male & 68.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2017 & Both sexes & 73.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2017 & Female & 78.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2016 & Male & 68.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2016 & Both sexes & 72.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2016 & Female & 77.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2015 & Male & 68.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2015 & Both sexes & 72.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Georgia & 2015 & Female & 77.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Germany & 2020 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2020 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2020 & Female & 83.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2019 & Male & 78.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2019 & Both sexes & 81.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2019 & Female & 83.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2018 & Male & 78.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2018 & Both sexes & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2018 & Female & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2017 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2017 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2017 & Female & 83.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2016 & Male & 78.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2016 & Both sexes & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2016 & Female & 83.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2015 & Male & 78.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2015 & Both sexes & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Germany & 2015 & Female & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ghana & 2020 & Male & 63.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2020 & Both sexes & 66.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2020 & Female & 68.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2019 & Male & 63.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2019 & Both sexes & 66.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2019 & Female & 68.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2018 & Male & 63.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2018 & Both sexes & 65.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2018 & Female & 68.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2017 & Male & 62.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2017 & Both sexes & 65.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2017 & Female & 67.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2016 & Male & 62.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2016 & Both sexes & 64.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2016 & Female & 67.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2015 & Male & 61.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2015 & Both sexes & 64.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Ghana & 2015 & Female & 67.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Greece & 2020 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2020 & Both sexes & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2020 & Female & 82.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2019 & Male & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2019 & Both sexes & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2019 & Female & 83.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2018 & Male & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2018 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2018 & Female & 83.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2017 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2017 & Both sexes & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2017 & Female & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2016 & Male & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2016 & Both sexes & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2016 & Female & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2015 & Male & 78.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2015 & Both sexes & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Greece & 2015 & Female & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Grenada & 2020 & Male & 72.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2020 & Both sexes & 75.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2020 & Female & 78.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2019 & Male & 70.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2019 & Both sexes & 72.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2019 & Female & 75.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2018 & Male & 70.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2018 & Both sexes & 72.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2018 & Female & 75.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2017 & Male & 70.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2017 & Both sexes & 72.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2017 & Female & 75.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2016 & Male & 70.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2016 & Both sexes & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2016 & Female & 75.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2015 & Male & 70.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2015 & Both sexes & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Grenada & 2015 & Female & 75.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2020 & Male & 67.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2020 & Both sexes & 71.0
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2020 & Female & 74.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2019 & Male & 70.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2019 & Both sexes & 72.7
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2019 & Female & 75.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2018 & Male & 70.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2018 & Both sexes & 72.7
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2018 & Female & 75.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2017 & Male & 70.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2017 & Both sexes & 72.7
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2017 & Female & 75.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2016 & Male & 69.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2016 & Both sexes & 72.2
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2016 & Female & 74.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2015 & Male & 69.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2015 & Both sexes & 72.0
+& upper\_middle & North America \\
+Life expectancy at birth (years) & Guatemala & 2015 & Female & 74.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Guinea & 2020 & Male & 59.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2020 & Both sexes & 61.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2020 & Female & 62.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2019 & Male & 59.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2019 & Both sexes & 61.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2019 & Female & 62.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2018 & Male & 59.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2018 & Both sexes & 60.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2018 & Female & 61.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2017 & Male & 59.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2017 & Both sexes & 60.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2017 & Female & 61.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2016 & Male & 58.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2016 & Both sexes & 59.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2016 & Female & 61.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2015 & Male & 57.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2015 & Both sexes & 59.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea & 2015 & Female & 60.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2020 & Male & 55.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2020 & Both sexes &
+58.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2020 & Female & 61.0
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2019 & Male & 56.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2019 & Both sexes &
+59.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2019 & Female & 61.4
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2018 & Male & 56.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2018 & Both sexes &
+58.6 & lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2018 & Female & 60.9
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2017 & Male & 56.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2017 & Both sexes &
+58.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2017 & Female & 60.6
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2016 & Male & 55.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2016 & Both sexes &
+58.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2016 & Female & 60.3
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2015 & Male & 55.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2015 & Both sexes &
+57.6 & lower\_income & Africa \\
+Life expectancy at birth (years) & Guinea-Bissau & 2015 & Female & 59.9
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Guyana & 2020 & Male & 63.8 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2020 & Both sexes & 66.9 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2020 & Female & 70.2 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2019 & Male & 65.6 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2019 & Both sexes & 68.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2019 & Female & 72.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2018 & Male & 65.6 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2018 & Both sexes & 68.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2018 & Female & 72.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2017 & Male & 65.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2017 & Both sexes & 68.2 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2017 & Female & 71.5 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2016 & Male & 64.3 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2016 & Both sexes & 67.6 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2016 & Female & 70.9 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2015 & Male & 63.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2015 & Both sexes & 67.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Guyana & 2015 & Female & 70.4 &
+high\_income & South America \\
+Life expectancy at birth (years) & Haiti & 2020 & Male & 62.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2020 & Both sexes & 63.4 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2020 & Female & 64.2 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2019 & Male & 63.2 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2019 & Both sexes & 63.7 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2019 & Female & 64.2 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2018 & Male & 63.0 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2018 & Both sexes & 63.5 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2018 & Female & 63.9 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2017 & Male & 62.9 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2017 & Both sexes & 63.2 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2017 & Female & 63.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2016 & Male & 62.5 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2016 & Both sexes & 62.8 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2016 & Female & 63.1 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2015 & Male & 62.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2015 & Both sexes & 62.5 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Haiti & 2015 & Female & 62.8 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2020 & Male & 68.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2020 & Both sexes & 70.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2020 & Female & 72.1 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2019 & Male & 70.0 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2019 & Both sexes & 71.4 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2019 & Female & 72.9 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2018 & Male & 69.9 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2018 & Both sexes & 71.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2018 & Female & 72.7 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2017 & Male & 70.0 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2017 & Both sexes & 71.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2017 & Female & 72.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2016 & Male & 69.8 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2016 & Both sexes & 71.1 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2016 & Female & 72.4 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2015 & Male & 67.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2015 & Both sexes & 69.5 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Honduras & 2015 & Female & 71.9 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Hungary & 2020 & Male & 72.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2020 & Both sexes & 75.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2020 & Female & 79.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2019 & Male & 73.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2019 & Both sexes & 76.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2019 & Female & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2018 & Male & 72.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2018 & Both sexes & 76.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2018 & Female & 79.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2017 & Male & 72.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2017 & Both sexes & 75.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2017 & Female & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2016 & Male & 72.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2016 & Both sexes & 76.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2016 & Female & 79.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2015 & Male & 72.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2015 & Both sexes & 75.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Hungary & 2015 & Female & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2020 & Male & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2020 & Both sexes & 82.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2020 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2019 & Male & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2019 & Both sexes & 82.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2019 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2018 & Male & 81.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2018 & Both sexes & 82.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2018 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2017 & Male & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2017 & Both sexes & 82.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2017 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2016 & Male & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2016 & Both sexes & 82.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2016 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2015 & Male & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2015 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Iceland & 2015 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & India & 2020 & Male & 68.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2020 & Both sexes & 70.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2020 & Female & 72.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2019 & Male & 69.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2019 & Both sexes & 70.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2019 & Female & 72.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2018 & Male & 68.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2018 & Both sexes & 70.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2018 & Female & 72.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2017 & Male & 68.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2017 & Both sexes & 70.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2017 & Female & 71.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2016 & Male & 68.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2016 & Both sexes & 69.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2016 & Female & 71.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2015 & Male & 67.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2015 & Both sexes & 69.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & India & 2015 & Female & 71.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2020 & Male & 67.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2020 & Both sexes & 69.7
+& upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2020 & Female & 71.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2019 & Male & 69.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2019 & Both sexes & 71.4
+& upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2019 & Female & 73.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2018 & Male & 69.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2018 & Both sexes & 71.2
+& upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2018 & Female & 73.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2017 & Male & 69.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2017 & Both sexes & 71.0
+& upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2017 & Female & 72.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2016 & Male & 69.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2016 & Both sexes & 70.8
+& upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2016 & Female & 72.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2015 & Male & 68.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2015 & Both sexes & 70.5
+& upper\_middle & Asia \\
+Life expectancy at birth (years) & Indonesia & 2015 & Female & 72.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2020 &
+Male & 73.3 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2020 &
+Both sexes & 75.2 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2020 &
+Female & 77.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2019 &
+Male & 76.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2019 &
+Both sexes & 77.8 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2019 &
+Female & 79.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2018 &
+Male & 76.3 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2018 &
+Both sexes & 77.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2018 &
+Female & 79.3 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2017 &
+Male & 76.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2017 &
+Both sexes & 77.5 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2017 &
+Female & 79.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2016 &
+Male & 75.9 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2016 &
+Both sexes & 77.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2016 &
+Female & 79.0 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2015 &
+Male & 75.8 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2015 &
+Both sexes & 77.3 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iran (Islamic Republic of) & 2015 &
+Female & 79.0 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2020 & Male & 67.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2020 & Both sexes & 70.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2020 & Female & 73.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2019 & Male & 70.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2019 & Both sexes & 72.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2019 & Female & 75.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2018 & Male & 70.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2018 & Both sexes & 73.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2018 & Female & 75.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2017 & Male & 68.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2017 & Both sexes & 71.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2017 & Female & 75.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2016 & Male & 67.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2016 & Both sexes & 71.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2016 & Female & 74.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2015 & Male & 67.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2015 & Both sexes & 71.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Iraq & 2015 & Female & 74.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Ireland & 2020 & Male & 79.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2020 & Both sexes & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2020 & Female & 83.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2019 & Male & 80.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2019 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2019 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2018 & Male & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2018 & Both sexes & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2018 & Female & 83.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2017 & Male & 79.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2017 & Both sexes & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2017 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2016 & Male & 79.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2016 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2016 & Female & 83.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2015 & Male & 79.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2015 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Ireland & 2015 & Female & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Israel & 2020 & Male & 80.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2020 & Both sexes & 82.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2020 & Female & 84.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2019 & Male & 80.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2019 & Both sexes & 82.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2019 & Female & 84.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2018 & Male & 80.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2018 & Both sexes & 82.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2018 & Female & 84.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2017 & Male & 80.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2017 & Both sexes & 82.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2017 & Female & 84.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2016 & Male & 80.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2016 & Both sexes & 82.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2016 & Female & 83.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2015 & Male & 79.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2015 & Both sexes & 81.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Israel & 2015 & Female & 83.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Italy & 2020 & Male & 79.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2020 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2020 & Female & 84.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2019 & Male & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2019 & Both sexes & 83.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2019 & Female & 84.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2018 & Male & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2018 & Both sexes & 82.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2018 & Female & 84.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2017 & Male & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2017 & Both sexes & 82.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2017 & Female & 84.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2016 & Male & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2016 & Both sexes & 82.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2016 & Female & 84.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2015 & Male & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2015 & Both sexes & 82.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Italy & 2015 & Female & 84.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Jamaica & 2020 & Male & 70.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2020 & Both sexes & 72.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2020 & Female & 75.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2019 & Male & 69.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2019 & Both sexes & 72.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2019 & Female & 75.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2018 & Male & 69.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2018 & Both sexes & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2018 & Female & 75.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2017 & Male & 69.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2017 & Both sexes & 72.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2017 & Female & 75.4 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2016 & Male & 69.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2016 & Both sexes & 72.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2016 & Female & 75.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2015 & Male & 69.7 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2015 & Both sexes & 72.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Jamaica & 2015 & Female & 75.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Japan & 2020 & Male & 81.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2020 & Both sexes & 84.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2020 & Female & 87.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2019 & Male & 81.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2019 & Both sexes & 84.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2019 & Female & 87.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2018 & Male & 81.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2018 & Both sexes & 84.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2018 & Female & 87.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2017 & Male & 81.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2017 & Both sexes & 84.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2017 & Female & 87.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2016 & Male & 81.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2016 & Both sexes & 84.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2016 & Female & 86.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2015 & Male & 81.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2015 & Both sexes & 84.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Japan & 2015 & Female & 86.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Jordan & 2020 & Male & 76.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2020 & Both sexes & 77.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2020 & Female & 78.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2019 & Male & 79.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2019 & Both sexes & 79.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2019 & Female & 80.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2018 & Both sexes & 79.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2018 & Male & 79.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2018 & Female & 80.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2017 & Both sexes & 79.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2017 & Male & 79.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2017 & Female & 79.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2016 & Both sexes & 78.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2016 & Male & 79.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2016 & Female & 79.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2015 & Both sexes & 78.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2015 & Male & 78.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Jordan & 2015 & Female & 79.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kazakhstan & 2020 & Male & 67.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2020 & Both sexes & 71.3
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2020 & Female & 75.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2019 & Male & 68.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2019 & Both sexes & 73.2
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2019 & Female & 77.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2018 & Male & 68.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2018 & Both sexes & 73.2
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2018 & Female & 77.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2017 & Male & 68.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2017 & Both sexes & 73.0
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2017 & Female & 76.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2016 & Male & 67.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2016 & Both sexes & 72.4
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2016 & Female & 76.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2015 & Male & 67.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2015 & Both sexes & 72.0
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Kazakhstan & 2015 & Female & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Kenya & 2020 & Male & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2020 & Both sexes & 66.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2020 & Female & 69.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2019 & Male & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2019 & Both sexes & 66.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2019 & Female & 69.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2018 & Male & 63.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2018 & Both sexes & 66.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2018 & Female & 68.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2017 & Male & 63.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2017 & Both sexes & 65.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2017 & Female & 68.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2016 & Male & 62.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2016 & Both sexes & 65.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2016 & Female & 67.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2015 & Male & 61.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2015 & Both sexes & 64.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kenya & 2015 & Female & 66.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Kiribati & 2020 & Male & 58.5 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2020 & Both sexes & 61.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2020 & Female & 65.3 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2019 & Male & 58.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2019 & Both sexes & 62.1 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2019 & Female & 65.3 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2018 & Male & 56.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2018 & Both sexes & 60.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2018 & Female & 64.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2017 & Male & 58.6 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2017 & Both sexes & 61.8 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2017 & Female & 65.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2016 & Male & 58.5 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2016 & Both sexes & 61.8 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2016 & Female & 65.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2015 & Male & 58.4 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2015 & Both sexes & 61.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kiribati & 2015 & Female & 64.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Kuwait & 2020 & Male & 76.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2020 & Both sexes & 78.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2020 & Female & 83.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2019 & Male & 80.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2019 & Both sexes & 82.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2019 & Female & 86.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2018 & Male & 80.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2018 & Both sexes & 82.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2018 & Female & 86.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2017 & Male & 80.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2017 & Both sexes & 82.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2017 & Female & 86.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2016 & Male & 80.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2016 & Both sexes & 82.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2016 & Female & 85.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2015 & Male & 79.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2015 & Both sexes & 81.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kuwait & 2015 & Female & 84.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2020 & Male & 67.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2020 & Both sexes & 71.5
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2020 & Female & 75.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2019 & Male & 69.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2019 & Both sexes & 73.6
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2019 & Female & 77.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2018 & Male & 69.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2018 & Both sexes & 73.3
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2018 & Female & 76.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2017 & Male & 69.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2017 & Both sexes & 72.8
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2017 & Female & 76.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2016 & Male & 69.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2016 & Both sexes & 72.7
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2016 & Female & 76.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2015 & Male & 67.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2015 & Both sexes & 71.5
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Kyrgyzstan & 2015 & Female & 75.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2020 & Male & 66.2 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2020 & Both sexes & 68.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2020 & Female & 71.6 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2019 & Male & 66.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2019 & Both sexes & 68.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2019 & Female & 70.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2018 & Male & 65.9 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2018 & Both sexes & 68.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2018 & Female & 70.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2017 & Male & 65.5 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2017 & Both sexes & 67.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2017 & Female & 70.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2016 & Male & 65.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2016 & Both sexes & 67.3 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2016 & Female & 69.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2015 & Male & 64.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2015 & Both sexes & 66.9 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Lao People's Democratic Republic &
+2015 & Female & 69.3 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Latvia & 2020 & Male & 70.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2020 & Both sexes & 75.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2020 & Female & 79.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2019 & Male & 71.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2019 & Both sexes & 75.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2019 & Female & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2018 & Male & 70.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2018 & Both sexes & 75.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2018 & Female & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2017 & Male & 70.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2017 & Both sexes & 75.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2017 & Female & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2016 & Male & 70.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2016 & Both sexes & 75.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2016 & Female & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2015 & Male & 70.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2015 & Both sexes & 74.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Latvia & 2015 & Female & 79.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lebanon & 2020 & Male & 74.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2020 & Both sexes & 77.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2020 & Female & 80.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2019 & Male & 76.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2019 & Both sexes & 79.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2019 & Female & 81.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2018 & Male & 77.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2018 & Both sexes & 79.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2018 & Female & 81.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2017 & Male & 76.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2017 & Both sexes & 79.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2017 & Female & 81.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2016 & Male & 76.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2016 & Both sexes & 78.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2016 & Female & 81.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2015 & Male & 75.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2015 & Both sexes & 78.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lebanon & 2015 & Female & 80.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Lesotho & 2020 & Male & 48.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2020 & Both sexes & 51.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2020 & Female & 55.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2019 & Male & 49.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2019 & Both sexes & 51.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2019 & Female & 54.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2018 & Male & 48.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2018 & Both sexes & 51.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2018 & Female & 54.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2017 & Male & 48.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2017 & Both sexes & 51.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2017 & Female & 54.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2016 & Male & 47.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2016 & Both sexes & 49.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2016 & Female & 52.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2015 & Male & 46.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2015 & Both sexes & 48.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Lesotho & 2015 & Female & 51.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Liberia & 2020 & Male & 62.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2020 & Both sexes & 63.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2020 & Female & 64.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2019 & Male & 62.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2019 & Both sexes & 63.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2019 & Female & 64.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2018 & Male & 62.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2018 & Both sexes & 63.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2018 & Female & 63.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2017 & Male & 61.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2017 & Both sexes & 62.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2017 & Female & 63.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2016 & Male & 61.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2016 & Both sexes & 62.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2016 & Female & 62.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2015 & Male & 60.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2015 & Both sexes & 60.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Liberia & 2015 & Female & 60.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Libya & 2020 & Male & 70.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2020 & Both sexes & 72.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2020 & Female & 75.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2019 & Male & 71.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2019 & Both sexes & 73.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2019 & Female & 75.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2018 & Male & 71.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2018 & Both sexes & 73.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2018 & Female & 75.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2017 & Male & 71.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2017 & Both sexes & 73.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2017 & Female & 75.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2016 & Male & 70.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2016 & Both sexes & 72.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2016 & Female & 75.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2015 & Male & 70.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2015 & Both sexes & 72.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Libya & 2015 & Female & 75.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Lithuania & 2020 & Male & 70.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2020 & Both sexes & 74.9
+& high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2020 & Female & 79.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2019 & Male & 71.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2019 & Both sexes & 76.2
+& high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2019 & Female & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2018 & Male & 70.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2018 & Both sexes & 75.8
+& high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2018 & Female & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2017 & Male & 70.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2017 & Both sexes & 75.5
+& high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2017 & Female & 80.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2016 & Male & 69.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2016 & Both sexes & 74.7
+& high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2016 & Female & 79.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2015 & Male & 69.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2015 & Both sexes & 74.4
+& high\_income & Europe \\
+Life expectancy at birth (years) & Lithuania & 2015 & Female & 79.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2020 & Male & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2020 & Both sexes & 82.8
+& high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2020 & Female & 84.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2019 & Male & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2019 & Both sexes & 82.8
+& high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2019 & Female & 84.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2018 & Male & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2018 & Both sexes & 82.8
+& high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2018 & Female & 84.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2017 & Male & 80.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2017 & Both sexes & 82.7
+& high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2017 & Female & 84.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2016 & Male & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2016 & Both sexes & 82.6
+& high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2016 & Female & 84.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2015 & Male & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2015 & Both sexes & 82.4
+& high\_income & Europe \\
+Life expectancy at birth (years) & Luxembourg & 2015 & Female & 84.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Madagascar & 2020 & Male & 61.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2020 & Both sexes & 63.1
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2020 & Female & 64.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2019 & Male & 62.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2019 & Both sexes & 63.8
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2019 & Female & 64.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2018 & Male & 62.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2018 & Both sexes & 63.7
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2018 & Female & 64.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2017 & Male & 62.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2017 & Both sexes & 63.6
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2017 & Female & 64.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2016 & Male & 62.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2016 & Both sexes & 63.5
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2016 & Female & 64.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2015 & Male & 62.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2015 & Both sexes & 63.4
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Madagascar & 2015 & Female & 64.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2020 & Male & 60.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2020 & Both sexes & 63.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2020 & Female & 66.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2019 & Male & 60.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2019 & Both sexes & 63.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2019 & Female & 66.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2018 & Male & 60.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2018 & Both sexes & 62.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2018 & Female & 65.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2017 & Male & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2017 & Both sexes & 62.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2017 & Female & 65.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2016 & Male & 59.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2016 & Both sexes & 62.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2016 & Female & 65.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2015 & Male & 58.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2015 & Both sexes & 61.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malawi & 2015 & Female & 64.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malaysia & 2020 & Male & 75.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2020 & Both sexes & 76.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2020 & Female & 78.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2019 & Male & 72.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2019 & Both sexes & 74.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2019 & Female & 77.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2018 & Male & 72.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2018 & Both sexes & 74.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2018 & Female & 76.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2017 & Male & 72.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2017 & Both sexes & 74.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2017 & Female & 76.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2016 & Male & 72.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2016 & Both sexes & 74.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2016 & Female & 76.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2015 & Male & 72.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2015 & Both sexes & 74.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Malaysia & 2015 & Female & 76.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2020 & Male & 74.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2020 & Both sexes & 76.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2020 & Female & 77.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2019 & Male & 74.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2019 & Both sexes & 75.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2019 & Female & 76.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2018 & Male & 77.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2018 & Both sexes & 78.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2018 & Female & 80.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2017 & Male & 76.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2017 & Both sexes & 78.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2017 & Female & 80.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2016 & Male & 76.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2016 & Both sexes & 77.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2016 & Female & 79.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2015 & Male & 75.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2015 & Both sexes & 77.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Maldives & 2015 & Female & 79.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Mali & 2020 & Male & 60.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2020 & Both sexes & 61.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2020 & Female & 62.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2019 & Male & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2019 & Both sexes & 61.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2019 & Female & 62.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2018 & Male & 60.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2018 & Both sexes & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2018 & Female & 61.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2017 & Male & 60.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2017 & Both sexes & 61.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2017 & Female & 61.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2016 & Male & 60.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2016 & Both sexes & 60.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2016 & Female & 61.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2015 & Male & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2015 & Both sexes & 60.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mali & 2015 & Female & 60.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Malta & 2020 & Male & 80.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2020 & Both sexes & 82.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2020 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2019 & Male & 80.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2019 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2019 & Female & 84.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2018 & Male & 80.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2018 & Both sexes & 82.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2018 & Female & 84.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2017 & Male & 80.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2017 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2017 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2016 & Male & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2016 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2016 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2015 & Male & 79.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2015 & Both sexes & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Malta & 2015 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Mauritania & 2020 & Male & 68.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2020 & Both sexes & 68.9
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2020 & Female & 69.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2019 & Male & 70.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2019 & Both sexes & 70.2
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2019 & Female & 70.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2018 & Male & 69.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2018 & Both sexes & 70.0
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2018 & Female & 70.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2017 & Male & 69.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2017 & Both sexes & 69.8
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2017 & Female & 69.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2016 & Male & 69.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2016 & Both sexes & 69.7
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2016 & Female & 69.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2015 & Both sexes & 69.5
+& lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2015 & Male & 69.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritania & 2015 & Female & 69.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2020 & Male & 70.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2020 & Both sexes & 73.6
+& upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2020 & Female & 77.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2019 & Male & 70.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2019 & Both sexes & 74.1
+& upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2019 & Female & 77.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2018 & Male & 70.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2018 & Both sexes & 74.0
+& upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2018 & Female & 77.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2017 & Male & 70.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2017 & Both sexes & 74.1
+& upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2017 & Female & 77.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2016 & Male & 71.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2016 & Both sexes & 74.2
+& upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2016 & Female & 77.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2015 & Male & 70.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2015 & Both sexes & 74.1
+& upper\_middle & Africa \\
+Life expectancy at birth (years) & Mauritius & 2015 & Female & 77.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Mexico & 2020 & Male & 67.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2020 & Both sexes & 70.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2020 & Female & 75.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2019 & Male & 72.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2019 & Both sexes & 75.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2019 & Female & 78.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2018 & Male & 72.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2018 & Both sexes & 75.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2018 & Female & 78.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2017 & Male & 73.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2017 & Both sexes & 75.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2017 & Female & 78.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2016 & Male & 73.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2016 & Both sexes & 75.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2016 & Female & 78.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2015 & Male & 73.3 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2015 & Both sexes & 75.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Mexico & 2015 & Female & 78.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2020 & Male & 62.8 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2020 & Both sexes & 65.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2020 & Female & 68.8 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2019 & Male & 63.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2019 & Both sexes & 65.9 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2019 & Female & 68.8 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2018 & Male & 63.2 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2018 & Both sexes & 65.8 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2018 & Female & 68.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2017 & Male & 63.0 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2017 & Both sexes & 65.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2017 & Female & 68.5 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2016 & Male & 62.9 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2016 & Both sexes & 65.5 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2016 & Female & 68.4 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2015 & Male & 62.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2015 & Both sexes & 65.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Micronesia (Federated States of) &
+2015 & Female & 68.2 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Mongolia & 2020 & Male & 68.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2020 & Both sexes & 72.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2020 & Female & 77.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2019 & Male & 66.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2019 & Both sexes & 70.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2019 & Female & 75.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2018 & Male & 66.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2018 & Both sexes & 70.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2018 & Female & 75.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2017 & Male & 65.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2017 & Both sexes & 70.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2017 & Female & 74.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2016 & Male & 65.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2016 & Both sexes & 69.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2016 & Female & 74.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2015 & Male & 65.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2015 & Both sexes & 69.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Mongolia & 2015 & Female & 73.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Montenegro & 2020 & Male & 72.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2020 & Both sexes & 75.5
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2020 & Female & 78.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2019 & Male & 73.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2019 & Both sexes & 76.8
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2019 & Female & 79.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2018 & Male & 74.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2018 & Both sexes & 77.2
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2018 & Female & 80.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2017 & Male & 74.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2017 & Both sexes & 77.1
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2017 & Female & 80.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2016 & Male & 74.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2016 & Both sexes & 77.1
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2016 & Female & 79.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2015 & Male & 74.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2015 & Both sexes & 76.9
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Montenegro & 2015 & Female & 79.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Morocco & 2020 & Male & 71.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2020 & Both sexes & 72.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2020 & Female & 73.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2019 & Male & 72.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2019 & Both sexes & 73.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2019 & Female & 74.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2018 & Male & 72.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2018 & Both sexes & 73.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2018 & Female & 74.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2017 & Male & 72.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2017 & Both sexes & 73.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2017 & Female & 74.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2016 & Male & 72.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2016 & Both sexes & 73.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2016 & Female & 74.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2015 & Male & 72.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2015 & Both sexes & 73.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Morocco & 2015 & Female & 74.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Mozambique & 2020 & Male & 55.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2020 & Both sexes & 58.6
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2020 & Female & 61.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2019 & Male & 55.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2019 & Both sexes & 58.5
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2019 & Female & 61.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2018 & Male & 54.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2018 & Both sexes & 57.9
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2018 & Female & 61.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2017 & Male & 54.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2017 & Both sexes & 57.3
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2017 & Female & 60.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2016 & Male & 53.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2016 & Both sexes & 56.6
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2016 & Female & 59.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2015 & Male & 53.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2015 & Both sexes & 55.9
+& lower\_income & Africa \\
+Life expectancy at birth (years) & Mozambique & 2015 & Female & 58.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Myanmar & 2020 & Male & 65.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2020 & Both sexes & 68.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2020 & Female & 72.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2019 & Male & 65.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2019 & Both sexes & 68.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2019 & Female & 72.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2018 & Male & 65.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2018 & Both sexes & 68.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2018 & Female & 71.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2017 & Male & 64.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2017 & Both sexes & 68.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2017 & Female & 71.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2016 & Male & 64.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2016 & Both sexes & 67.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2016 & Female & 71.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2015 & Male & 64.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2015 & Both sexes & 67.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Myanmar & 2015 & Female & 70.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Namibia & 2020 & Male & 60.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2020 & Both sexes & 63.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2020 & Female & 67.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2019 & Male & 60.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2019 & Both sexes & 63.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2019 & Female & 66.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2018 & Male & 59.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2018 & Both sexes & 62.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2018 & Female & 66.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2017 & Male & 59.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2017 & Both sexes & 62.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2017 & Female & 65.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2016 & Male & 59.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2016 & Both sexes & 62.1 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2016 & Female & 65.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2015 & Male & 58.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2015 & Both sexes & 61.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Namibia & 2015 & Female & 64.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & Nepal & 2020 & Male & 69.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2020 & Both sexes & 71.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2020 & Female & 73.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2019 & Male & 69.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2019 & Both sexes & 71.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2019 & Female & 73.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2018 & Male & 69.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2018 & Both sexes & 71.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2018 & Female & 72.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2017 & Male & 69.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2017 & Both sexes & 70.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2017 & Female & 72.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2016 & Male & 68.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2016 & Both sexes & 70.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2016 & Female & 72.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2015 & Male & 68.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2015 & Both sexes & 69.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Nepal & 2015 & Female & 71.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2020 &
+Male & 79.8 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2020 &
+Both sexes & 81.4 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2020 &
+Female & 82.9 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2019 &
+Male & 80.8 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2019 &
+Both sexes & 82.3 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2019 &
+Female & 83.8 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2018 &
+Male & 80.4 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2018 &
+Both sexes & 81.9 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2018 &
+Female & 83.3 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2017 &
+Male & 80.0 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2017 &
+Both sexes & 81.5 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2017 &
+Female & 83.0 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2016 &
+Male & 79.8 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2016 &
+Both sexes & 81.3 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2016 &
+Female & 82.8 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2015 &
+Male & 79.7 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2015 &
+Both sexes & 81.3 & high\_income & Europe \\
+Life expectancy at birth (years) & Netherlands (Kingdom of the) & 2015 &
+Female & 82.8 & high\_income & Europe \\
+Life expectancy at birth (years) & New Zealand & 2020 & Male & 80.7 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2020 & Both sexes &
+82.5 & high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2020 & Female & 84.3 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2019 & Male & 80.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2019 & Both sexes &
+81.8 & high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2019 & Female & 83.4 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2018 & Male & 80.1 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2018 & Both sexes &
+81.8 & high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2018 & Female & 83.4 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2017 & Male & 79.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2017 & Both sexes &
+81.2 & high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2017 & Female & 82.8 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2016 & Male & 80.1 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2016 & Both sexes &
+81.7 & high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2016 & Female & 83.3 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2015 & Male & 79.7 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2015 & Both sexes &
+81.3 & high\_income & Oceania \\
+Life expectancy at birth (years) & New Zealand & 2015 & Female & 82.9 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Nicaragua & 2020 & Male & 71.7 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2020 & Both sexes & 75.0
+& lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2020 & Female & 78.5 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2019 & Male & 76.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2019 & Both sexes & 78.9
+& lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2019 & Female & 81.3 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2018 & Male & 75.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2018 & Both sexes & 78.5
+& lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2018 & Female & 81.1 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2017 & Male & 76.0 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2017 & Both sexes & 78.5
+& lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2017 & Female & 80.9 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2016 & Male & 75.1 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2016 & Both sexes & 77.9
+& lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2016 & Female & 80.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2015 & Male & 75.6 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2015 & Both sexes & 78.3
+& lower\_middle & North America \\
+Life expectancy at birth (years) & Nicaragua & 2015 & Female & 80.7 &
+lower\_middle & North America \\
+Life expectancy at birth (years) & Niger & 2020 & Male & 59.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2020 & Both sexes & 60.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2020 & Female & 61.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2019 & Male & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2019 & Both sexes & 60.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2019 & Female & 61.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2018 & Male & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2018 & Both sexes & 60.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2018 & Female & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2017 & Male & 59.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2017 & Both sexes & 60.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2017 & Female & 61.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2016 & Male & 58.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2016 & Both sexes & 59.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2016 & Female & 60.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2015 & Male & 58.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2015 & Both sexes & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Niger & 2015 & Female & 60.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Nigeria & 2020 & Male & 61.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2020 & Both sexes & 62.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2020 & Female & 64.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2019 & Male & 61.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2019 & Both sexes & 63.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2019 & Female & 64.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2018 & Male & 61.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2018 & Both sexes & 62.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2018 & Female & 64.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2017 & Male & 60.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2017 & Both sexes & 62.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2017 & Female & 63.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2016 & Male & 60.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2016 & Both sexes & 62.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2016 & Female & 63.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2015 & Male & 60.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2015 & Both sexes & 61.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Nigeria & 2015 & Female & 63.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & North Macedonia & 2020 & Male & 72.1
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2020 & Both sexes &
+74.4 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2020 & Female &
+76.7 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2019 & Both sexes &
+76.1 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2019 & Male & 76.3
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2019 & Female &
+76.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2018 & Male & 74.4
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2018 & Both sexes &
+76.5 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2018 & Female &
+78.5 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2017 & Male & 74.0
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2017 & Both sexes &
+76.0 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2017 & Female &
+77.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2016 & Male & 73.5
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2016 & Both sexes &
+75.6 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2016 & Female &
+77.7 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2015 & Male & 73.4
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2015 & Both sexes &
+75.3 & upper\_middle & Europe \\
+Life expectancy at birth (years) & North Macedonia & 2015 & Female &
+77.3 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Norway & 2020 & Male & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2020 & Both sexes & 82.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2020 & Female & 84.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2019 & Male & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2019 & Both sexes & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2019 & Female & 84.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2018 & Male & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2018 & Both sexes & 82.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2018 & Female & 84.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2017 & Male & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2017 & Both sexes & 82.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2017 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2016 & Male & 80.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2016 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2016 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2015 & Male & 80.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2015 & Both sexes & 82.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Norway & 2015 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Oman & 2020 & Male & 72.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2020 & Both sexes & 73.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2020 & Female & 76.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2019 & Male & 73.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2019 & Both sexes & 75.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2019 & Female & 78.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2018 & Male & 72.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2018 & Both sexes & 75.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2018 & Female & 78.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2017 & Male & 72.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2017 & Both sexes & 74.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2017 & Female & 77.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2016 & Male & 71.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2016 & Both sexes & 73.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2016 & Female & 77.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2015 & Male & 71.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2015 & Both sexes & 73.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Oman & 2015 & Female & 77.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Pakistan & 2020 & Male & 64.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2020 & Both sexes & 65.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2020 & Female & 67.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2019 & Male & 66.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2019 & Both sexes & 67.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2019 & Female & 67.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2018 & Male & 66.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2018 & Both sexes & 66.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2018 & Female & 67.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2017 & Male & 65.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2017 & Both sexes & 66.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2017 & Female & 67.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2016 & Male & 65.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2016 & Both sexes & 66.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2016 & Female & 66.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2015 & Male & 64.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2015 & Both sexes & 65.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Pakistan & 2015 & Female & 66.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Panama & 2020 & Male & 74.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2020 & Both sexes & 77.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2020 & Female & 80.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2019 & Male & 76.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2019 & Both sexes & 79.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2019 & Female & 81.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2018 & Male & 75.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2018 & Both sexes & 78.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2018 & Female & 81.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2017 & Male & 75.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2017 & Both sexes & 78.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2017 & Female & 81.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2016 & Male & 75.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2016 & Both sexes & 78.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2016 & Female & 81.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2015 & Male & 75.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2015 & Both sexes & 78.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Panama & 2015 & Female & 81.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Papua New Guinea & 2020 & Male & 64.9
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2020 & Both sexes
+& 66.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2020 & Female &
+67.8 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2019 & Male & 65.6
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2019 & Both sexes
+& 66.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2019 & Female &
+67.9 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2018 & Male & 65.4
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2018 & Both sexes
+& 66.5 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2018 & Female &
+67.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2017 & Male & 65.4
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2017 & Both sexes
+& 66.4 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2017 & Female &
+67.6 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2016 & Male & 65.2
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2016 & Both sexes
+& 66.2 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2016 & Female &
+67.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2015 & Male & 65.0
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2015 & Both sexes
+& 66.0 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Papua New Guinea & 2015 & Female &
+67.1 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Paraguay & 2020 & Male & 72.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2020 & Both sexes & 75.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2020 & Female & 78.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2019 & Male & 72.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2019 & Both sexes & 75.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2019 & Female & 78.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2018 & Male & 72.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2018 & Both sexes & 75.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2018 & Female & 78.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2017 & Male & 72.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2017 & Both sexes & 75.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2017 & Female & 78.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2016 & Male & 72.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2016 & Both sexes & 74.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2016 & Female & 77.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2015 & Male & 72.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2015 & Both sexes & 75.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Paraguay & 2015 & Female & 78.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2020 & Male & 69.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2020 & Both sexes & 72.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2020 & Female & 76.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2019 & Male & 76.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2019 & Both sexes & 78.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2019 & Female & 79.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2018 & Male & 77.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2018 & Both sexes & 79.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2018 & Female & 80.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2017 & Male & 77.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2017 & Both sexes & 79.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2017 & Female & 80.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2016 & Male & 78.5 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2016 & Both sexes & 80.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2016 & Female & 81.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2015 & Male & 78.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2015 & Both sexes & 80.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Peru & 2015 & Female & 81.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Philippines & 2020 & Male & 66.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2020 & Both sexes &
+69.6 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2020 & Female & 73.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2019 & Male & 66.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2019 & Both sexes &
+69.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2019 & Female & 73.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2018 & Male & 66.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2018 & Both sexes &
+69.7 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2018 & Female & 73.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2017 & Male & 66.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2017 & Both sexes &
+69.6 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2017 & Female & 73.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2016 & Male & 65.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2016 & Both sexes &
+69.2 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2016 & Female & 73.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2015 & Male & 65.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2015 & Both sexes &
+69.5 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Philippines & 2015 & Female & 73.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Poland & 2020 & Male & 72.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2020 & Both sexes & 76.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2020 & Female & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2019 & Male & 73.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2019 & Both sexes & 77.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2019 & Female & 81.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2018 & Male & 73.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2018 & Both sexes & 77.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2018 & Female & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2017 & Male & 73.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2017 & Both sexes & 77.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2017 & Female & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2016 & Male & 73.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2016 & Both sexes & 77.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2016 & Female & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2015 & Male & 73.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2015 & Both sexes & 77.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Poland & 2015 & Female & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2020 & Male & 77.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2020 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2020 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2019 & Male & 78.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2019 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2019 & Female & 84.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2018 & Male & 78.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2018 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2018 & Female & 83.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2017 & Male & 78.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2017 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2017 & Female & 84.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2016 & Male & 77.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2016 & Both sexes & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2016 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2015 & Male & 77.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2015 & Both sexes & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Portugal & 2015 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Puerto Rico & 2020 & Male & 76.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2020 & Both sexes &
+79.9 & high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2020 & Female & 83.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2019 & Male & 76.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2019 & Both sexes &
+80.5 & high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2019 & Female & 84.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2018 & Male & 77.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2018 & Both sexes &
+80.7 & high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2018 & Female & 84.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2017 & Male & 75.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2017 & Both sexes &
+78.4 & high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2017 & Female & 81.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2016 & Male & 77.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2016 & Both sexes &
+80.2 & high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2016 & Female & 83.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2015 & Male & 77.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2015 & Both sexes &
+80.5 & high\_income & North America \\
+Life expectancy at birth (years) & Puerto Rico & 2015 & Female & 83.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Qatar & 2020 & Male & 76.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2020 & Both sexes & 77.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2020 & Female & 78.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2019 & Male & 78.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2019 & Both sexes & 78.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2019 & Female & 79.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2018 & Male & 78.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2018 & Both sexes & 78.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2018 & Female & 79.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2017 & Male & 78.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2017 & Both sexes & 78.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2017 & Female & 79.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2016 & Male & 77.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2016 & Both sexes & 78.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2016 & Female & 79.2 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2015 & Male & 77.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2015 & Both sexes & 77.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Qatar & 2015 & Female & 78.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2020 & Male &
+80.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2020 & Both sexes
+& 83.8 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2020 & Female &
+86.6 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2019 & Male &
+80.6 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2019 & Both sexes
+& 83.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2019 & Female &
+86.6 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2018 & Male &
+80.0 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2018 & Both sexes
+& 83.2 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2018 & Female &
+86.0 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2017 & Male &
+79.9 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2017 & Both sexes
+& 83.1 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2017 & Female &
+86.0 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2016 & Male &
+79.5 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2016 & Both sexes
+& 82.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2016 & Female &
+85.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2015 & Male &
+79.1 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2015 & Both sexes
+& 82.4 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Korea & 2015 & Female &
+85.4 & high\_income & Asia \\
+Life expectancy at birth (years) & Republic of Moldova & 2020 & Male &
+68.3 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2020 & Both
+sexes & 72.1 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2020 & Female &
+75.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2019 & Male &
+69.3 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2019 & Both
+sexes & 73.3 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2019 & Female &
+77.2 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2018 & Male &
+68.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2018 & Both
+sexes & 72.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2018 & Female &
+76.8 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2017 & Male &
+69.0 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2017 & Both
+sexes & 72.9 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2017 & Female &
+76.6 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2016 & Male &
+67.8 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2016 & Both
+sexes & 71.8 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2016 & Female &
+75.8 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2015 & Male &
+67.2 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2015 & Both
+sexes & 71.1 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Republic of Moldova & 2015 & Female &
+75.1 & upper\_middle & Europe \\
+Life expectancy at birth (years) & Romania & 2020 & Male & 70.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2020 & Both sexes & 74.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2020 & Female & 78.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2019 & Male & 71.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2019 & Both sexes & 75.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2019 & Female & 79.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2018 & Male & 71.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2018 & Both sexes & 75.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2018 & Female & 78.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2017 & Male & 71.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2017 & Both sexes & 75.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2017 & Female & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2016 & Male & 71.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2016 & Both sexes & 75.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2016 & Female & 78.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2015 & Male & 71.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2015 & Both sexes & 74.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Romania & 2015 & Female & 78.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Russian Federation & 2020 & Male &
+66.4 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2020 & Both
+sexes & 71.4 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2020 & Female &
+76.2 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2019 & Male &
+68.2 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2019 & Both
+sexes & 73.2 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2019 & Female &
+78.0 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2018 & Male &
+67.5 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2018 & Both
+sexes & 72.7 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2018 & Female &
+77.6 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2017 & Male &
+67.3 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2017 & Both
+sexes & 72.5 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2017 & Female &
+77.5 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2016 & Male &
+66.3 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2016 & Both
+sexes & 71.6 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2016 & Female &
+76.8 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2015 & Male &
+65.8 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2015 & Both
+sexes & 71.3 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Russian Federation & 2015 & Female &
+76.6 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Rwanda & 2020 & Male & 66.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2020 & Both sexes & 68.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2020 & Female & 70.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2019 & Male & 65.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2019 & Both sexes & 67.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2019 & Female & 69.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2018 & Male & 65.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2018 & Both sexes & 67.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2018 & Female & 69.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2017 & Male & 65.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2017 & Both sexes & 67.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2017 & Female & 69.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2016 & Male & 65.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2016 & Both sexes & 67.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2016 & Female & 69.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2015 & Male & 64.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2015 & Both sexes & 67.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Rwanda & 2015 & Female & 68.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Saint Lucia & 2020 & Male & 72.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2020 & Both sexes &
+75.6 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2020 & Female & 79.6 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2019 & Male & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2019 & Both sexes &
+76.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2019 & Female & 79.9 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2018 & Male & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2018 & Both sexes &
+76.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2018 & Female & 80.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2017 & Male & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2017 & Both sexes &
+76.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2017 & Female & 80.0 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2016 & Male & 72.5 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2016 & Both sexes &
+76.2 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2016 & Female & 80.2 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2015 & Male & 72.8 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2015 & Both sexes &
+76.4 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Lucia & 2015 & Female & 80.1 &
+upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2020 & Male & 70.3 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2020 & Both sexes & 72.7 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2020 & Female & 75.6 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2019 & Male & 70.8 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2019 & Both sexes & 73.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2019 & Female & 75.8 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2018 & Male & 71.0 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2018 & Both sexes & 73.2 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2018 & Female & 75.7 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2017 & Male & 71.0 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2017 & Both sexes & 73.1 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2017 & Female & 75.5 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2016 & Male & 70.8 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2016 & Both sexes & 73.0 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2016 & Female & 75.4 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2015 & Male & 70.6 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2015 & Both sexes & 72.8 & upper\_middle & North America \\
+Life expectancy at birth (years) & Saint Vincent and the Grenadines &
+2015 & Female & 75.3 & upper\_middle & North America \\
+Life expectancy at birth (years) & Samoa & 2020 & Male & 68.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2020 & Both sexes & 70.2 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2020 & Female & 71.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2019 & Male & 68.8 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2019 & Both sexes & 70.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2019 & Female & 71.3 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2018 & Male & 68.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2018 & Both sexes & 70.1 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2018 & Female & 71.4 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2017 & Male & 68.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2017 & Both sexes & 70.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2017 & Female & 71.3 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2016 & Male & 68.7 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2016 & Both sexes & 69.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2016 & Female & 71.3 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2015 & Male & 68.8 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2015 & Both sexes & 70.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Samoa & 2015 & Female & 71.4 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2020 & Male &
+69.5 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2020 & Both
+sexes & 71.3 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2020 & Female
+& 73.1 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2019 & Male &
+70.2 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2019 & Both
+sexes & 71.7 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2019 & Female
+& 73.2 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2018 & Male &
+70.0 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2018 & Both
+sexes & 71.4 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2018 & Female
+& 72.9 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2017 & Male &
+69.8 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2017 & Both
+sexes & 71.3 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2017 & Female
+& 72.7 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2016 & Male &
+69.5 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2016 & Both
+sexes & 70.9 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2016 & Female
+& 72.3 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2015 & Male &
+69.2 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2015 & Both
+sexes & 70.6 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Sao Tome and Principe & 2015 & Female
+& 72.0 & lower\_middle & Africa \\
+Life expectancy at birth (years) & Saudi Arabia & 2020 & Male & 74.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2020 & Both sexes &
+76.1 & high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2020 & Female & 77.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2019 & Male & 76.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2019 & Both sexes &
+76.9 & high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2019 & Female & 77.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2018 & Male & 76.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2018 & Both sexes &
+76.8 & high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2018 & Female & 77.5 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2017 & Male & 76.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2017 & Both sexes &
+76.7 & high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2017 & Female & 77.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2016 & Male & 76.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2016 & Both sexes &
+76.8 & high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2016 & Female & 77.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2015 & Male & 76.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2015 & Both sexes &
+76.9 & high\_income & Asia \\
+Life expectancy at birth (years) & Saudi Arabia & 2015 & Female & 77.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Senegal & 2020 & Male & 66.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2020 & Both sexes & 68.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2020 & Female & 70.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2019 & Male & 67.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2019 & Both sexes & 68.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2019 & Female & 70.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2018 & Male & 66.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2018 & Both sexes & 68.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2018 & Female & 69.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2017 & Male & 66.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2017 & Both sexes & 68.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2017 & Female & 69.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2016 & Male & 66.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2016 & Both sexes & 67.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2016 & Female & 69.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2015 & Male & 65.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2015 & Both sexes & 67.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Senegal & 2015 & Female & 68.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Serbia & 2020 & Male & 71.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2020 & Both sexes & 74.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2020 & Female & 77.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2019 & Male & 73.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2019 & Both sexes & 75.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2019 & Female & 78.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2018 & Male & 73.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2018 & Both sexes & 75.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2018 & Female & 78.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2017 & Male & 73.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2017 & Both sexes & 75.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2017 & Female & 78.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2016 & Male & 73.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2016 & Both sexes & 75.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2016 & Female & 78.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2015 & Male & 72.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2015 & Both sexes & 75.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Serbia & 2015 & Female & 77.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Seychelles & 2020 & Male & 75.3 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2020 & Both sexes & 77.3
+& high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2020 & Female & 80.5 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2019 & Male & 70.1 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2019 & Both sexes & 73.1
+& high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2019 & Female & 76.7 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2018 & Male & 70.0 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2018 & Both sexes & 73.1
+& high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2018 & Female & 76.6 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2017 & Male & 70.0 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2017 & Both sexes & 73.1
+& high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2017 & Female & 76.6 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2016 & Male & 70.0 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2016 & Both sexes & 73.1
+& high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2016 & Female & 76.6 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2015 & Male & 70.1 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2015 & Both sexes & 73.2
+& high\_income & Africa \\
+Life expectancy at birth (years) & Seychelles & 2015 & Female & 76.7 &
+high\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2020 & Male & 59.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2020 & Both sexes &
+60.5 & lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2020 & Female & 61.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2019 & Male & 59.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2019 & Both sexes &
+60.4 & lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2019 & Female & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2018 & Male & 59.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2018 & Both sexes &
+59.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2018 & Female & 60.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2017 & Male & 58.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2017 & Both sexes &
+59.2 & lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2017 & Female & 60.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2016 & Male & 57.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2016 & Both sexes &
+58.8 & lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2016 & Female & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2015 & Male & 56.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2015 & Both sexes &
+56.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & Sierra Leone & 2015 & Female & 57.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Singapore & 2020 & Male & 81.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2020 & Both sexes & 84.0
+& high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2020 & Female & 86.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2019 & Male & 81.8 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2019 & Both sexes & 83.9
+& high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2019 & Female & 86.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2018 & Male & 81.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2018 & Both sexes & 83.5
+& high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2018 & Female & 85.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2017 & Male & 81.1 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2017 & Both sexes & 83.2
+& high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2017 & Female & 85.3 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2016 & Male & 81.0 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2016 & Both sexes & 83.2
+& high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2016 & Female & 85.4 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2015 & Male & 80.7 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2015 & Both sexes & 82.8
+& high\_income & Asia \\
+Life expectancy at birth (years) & Singapore & 2015 & Female & 84.9 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Slovakia & 2020 & Male & 73.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2020 & Both sexes & 76.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2020 & Female & 80.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2019 & Male & 74.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2019 & Both sexes & 77.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2019 & Female & 80.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2018 & Male & 73.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2018 & Both sexes & 77.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2018 & Female & 80.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2017 & Male & 73.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2017 & Both sexes & 77.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2017 & Female & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2016 & Male & 73.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2016 & Both sexes & 77.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2016 & Female & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2015 & Male & 73.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2015 & Both sexes & 76.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovakia & 2015 & Female & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2020 & Male & 77.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2020 & Both sexes & 80.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2020 & Female & 83.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2019 & Male & 78.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2019 & Both sexes & 81.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2019 & Female & 84.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2018 & Male & 78.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2018 & Both sexes & 81.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2018 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2017 & Male & 78.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2017 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2017 & Female & 83.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2016 & Male & 77.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2016 & Both sexes & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2016 & Female & 83.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2015 & Male & 77.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2015 & Both sexes & 80.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Slovenia & 2015 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Solomon Islands & 2020 & Male & 62.9
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2020 & Both sexes &
+65.4 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2020 & Female &
+68.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2019 & Male & 63.4
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2019 & Both sexes &
+65.7 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2019 & Female &
+68.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2018 & Male & 63.2
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2018 & Both sexes &
+65.6 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2018 & Female &
+68.2 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2017 & Male & 63.1
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2017 & Both sexes &
+65.4 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2017 & Female &
+68.0 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2016 & Male & 63.0
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2016 & Both sexes &
+65.3 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2016 & Female &
+67.9 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2015 & Male & 62.9
+& lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2015 & Both sexes &
+65.2 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Solomon Islands & 2015 & Female &
+67.8 & lower\_middle & Oceania \\
+Life expectancy at birth (years) & Somalia & 2020 & Male & 52.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2020 & Both sexes & 55.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2020 & Female & 57.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2019 & Male & 52.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2019 & Both sexes & 55.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2019 & Female & 57.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2018 & Male & 52.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2018 & Both sexes & 54.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2018 & Female & 57.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2017 & Male & 51.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2017 & Both sexes & 54.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2017 & Female & 56.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2016 & Male & 51.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2016 & Both sexes & 53.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2016 & Female & 56.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2015 & Male & 51.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2015 & Both sexes & 53.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Somalia & 2015 & Female & 56.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Africa & 2020 & Male & 61.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2020 & Both sexes &
+64.3 & upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2020 & Female & 66.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2019 & Male & 62.5 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2019 & Both sexes &
+65.8 & upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2019 & Female & 68.8 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2018 & Male & 62.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2018 & Both sexes &
+65.3 & upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2018 & Female & 68.3 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2017 & Male & 61.4 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2017 & Both sexes &
+64.7 & upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2017 & Female & 67.7 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2016 & Male & 60.6 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2016 & Both sexes &
+63.9 & upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2016 & Female & 66.9 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2015 & Male & 60.0 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2015 & Both sexes &
+63.3 & upper\_middle & Africa \\
+Life expectancy at birth (years) & South Africa & 2015 & Female & 66.2 &
+upper\_middle & Africa \\
+Life expectancy at birth (years) & South Sudan & 2020 & Male & 56.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2020 & Both sexes &
+58.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2020 & Female & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2019 & Male & 56.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2019 & Both sexes &
+59.0 & lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2019 & Female & 61.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2018 & Male & 56.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2018 & Both sexes &
+58.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2018 & Female & 61.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2017 & Male & 56.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2017 & Both sexes &
+58.9 & lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2017 & Female & 61.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2016 & Male & 57.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2016 & Both sexes &
+59.2 & lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2016 & Female & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2015 & Male & 57.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2015 & Both sexes &
+59.3 & lower\_income & Africa \\
+Life expectancy at birth (years) & South Sudan & 2015 & Female & 61.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Spain & 2020 & Male & 79.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2020 & Both sexes & 81.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2020 & Female & 84.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2019 & Male & 80.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2019 & Both sexes & 83.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2019 & Female & 85.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2018 & Male & 80.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2018 & Both sexes & 82.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2018 & Female & 85.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2017 & Male & 80.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2017 & Both sexes & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2017 & Female & 85.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2016 & Male & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2016 & Both sexes & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2016 & Female & 85.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2015 & Male & 79.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2015 & Both sexes & 82.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Spain & 2015 & Female & 84.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sri Lanka & 2020 & Male & 77.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2020 & Both sexes & 80.7
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2020 & Female & 83.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2019 & Male & 74.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2019 & Both sexes & 77.5
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2019 & Female & 80.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2018 & Male & 74.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2018 & Both sexes & 77.2
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2018 & Female & 80.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2017 & Male & 73.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2017 & Both sexes & 76.9
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2017 & Female & 79.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2016 & Male & 73.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2016 & Both sexes & 76.8
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2016 & Female & 79.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2015 & Male & 73.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2015 & Both sexes & 76.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Sri Lanka & 2015 & Female & 79.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Sudan & 2020 & Male & 67.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2020 & Both sexes & 68.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2020 & Female & 69.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2019 & Male & 68.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2019 & Both sexes & 69.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2019 & Female & 70.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2018 & Male & 68.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2018 & Both sexes & 69.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2018 & Female & 70.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2017 & Male & 67.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2017 & Both sexes & 69.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2017 & Female & 70.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2016 & Male & 67.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2016 & Both sexes & 68.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2016 & Female & 69.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2015 & Male & 67.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2015 & Both sexes & 68.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Sudan & 2015 & Female & 69.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Suriname & 2020 & Male & 69.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2020 & Both sexes & 72.8 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2020 & Female & 76.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2019 & Male & 70.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2019 & Both sexes & 73.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2019 & Female & 76.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2018 & Male & 70.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2018 & Both sexes & 73.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2018 & Female & 76.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2017 & Male & 70.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2017 & Both sexes & 73.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2017 & Female & 76.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2016 & Male & 70.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2016 & Both sexes & 73.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2016 & Female & 76.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2015 & Male & 70.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2015 & Both sexes & 73.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Suriname & 2015 & Female & 76.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Sweden & 2020 & Male & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2020 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2020 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2019 & Male & 81.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2019 & Both sexes & 82.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2019 & Female & 84.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2018 & Male & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2018 & Both sexes & 82.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2018 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2017 & Male & 80.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2017 & Both sexes & 82.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2017 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2016 & Male & 80.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2016 & Both sexes & 82.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2016 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2015 & Male & 80.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2015 & Both sexes & 81.7 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Sweden & 2015 & Female & 83.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2020 & Male & 80.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2020 & Both sexes &
+82.7 & high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2020 & Female & 84.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2019 & Male & 81.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2019 & Both sexes &
+83.5 & high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2019 & Female & 85.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2018 & Male & 81.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2018 & Both sexes &
+83.3 & high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2018 & Female & 85.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2017 & Male & 81.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2017 & Both sexes &
+83.1 & high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2017 & Female & 84.9 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2016 & Male & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2016 & Both sexes &
+83.2 & high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2016 & Female & 84.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2015 & Male & 80.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2015 & Both sexes &
+82.6 & high\_income & Europe \\
+Life expectancy at birth (years) & Switzerland & 2015 & Female & 84.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2020 & Male &
+69.6 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2020 & Both
+sexes & 72.0 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2020 & Female
+& 74.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2019 & Male &
+65.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2019 & Both
+sexes & 69.2 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2019 & Female
+& 73.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2018 & Male &
+58.7 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2018 & Both
+sexes & 64.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2018 & Female
+& 71.1 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2017 & Male &
+51.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2017 & Both
+sexes & 59.2 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2017 & Female
+& 70.0 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2016 & Male &
+52.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2016 & Both
+sexes & 60.1 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2016 & Female
+& 70.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2015 & Male &
+52.8 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2015 & Both
+sexes & 60.0 & lower\_income & Asia \\
+Life expectancy at birth (years) & Syrian Arab Republic & 2015 & Female
+& 69.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2020 & Male & 68.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2020 & Both sexes & 70.6
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2020 & Female & 72.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2019 & Male & 72.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2019 & Both sexes & 73.8
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2019 & Female & 75.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2018 & Male & 71.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2018 & Both sexes & 73.5
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2018 & Female & 75.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2017 & Male & 71.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2017 & Both sexes & 73.2
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2017 & Female & 74.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2016 & Male & 71.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2016 & Both sexes & 72.7
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2016 & Female & 74.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2015 & Male & 70.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2015 & Both sexes & 72.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Tajikistan & 2015 & Female & 74.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2020 & Male & 73.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2020 & Both sexes & 76.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2020 & Female & 79.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2019 & Male & 73.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2019 & Both sexes & 76.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2019 & Female & 80.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2018 & Male & 73.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2018 & Both sexes & 77.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2018 & Female & 80.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2017 & Male & 73.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2017 & Both sexes & 77.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2017 & Female & 80.8 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2016 & Male & 73.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2016 & Both sexes & 77.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2016 & Female & 80.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2015 & Male & 73.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2015 & Both sexes & 77.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Thailand & 2015 & Female & 80.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2020 & Male & 67.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2020 & Both sexes &
+68.9 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2020 & Female & 70.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2019 & Male & 67.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2019 & Both sexes &
+68.5 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2019 & Female & 70.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2018 & Male & 66.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2018 & Both sexes &
+68.4 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2018 & Female & 70.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2017 & Male & 66.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2017 & Both sexes &
+68.2 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2017 & Female & 69.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2016 & Male & 66.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2016 & Both sexes &
+68.1 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2016 & Female & 69.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2015 & Male & 66.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2015 & Both sexes &
+67.8 & lower\_middle & Asia \\
+Life expectancy at birth (years) & Timor-Leste & 2015 & Female & 69.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Togo & 2020 & Male & 61.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2020 & Both sexes & 63.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2020 & Female & 66.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2019 & Male & 61.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2019 & Both sexes & 63.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2019 & Female & 66.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2018 & Male & 60.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2018 & Both sexes & 63.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2018 & Female & 65.9 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2017 & Male & 60.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2017 & Both sexes & 62.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2017 & Female & 65.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2016 & Male & 59.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2016 & Both sexes & 62.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2016 & Female & 64.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2015 & Male & 59.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2015 & Both sexes & 61.5 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Togo & 2015 & Female & 64.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Tonga & 2020 & Male & 70.4 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2020 & Both sexes & 73.2 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2020 & Female & 76.1 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2019 & Male & 70.4 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2019 & Both sexes & 72.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2019 & Female & 75.6 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2018 & Male & 70.3 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2018 & Both sexes & 72.8 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2018 & Female & 75.5 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2017 & Male & 70.1 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2017 & Both sexes & 72.7 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2017 & Female & 75.4 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2016 & Male & 70.0 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2016 & Both sexes & 72.6 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2016 & Female & 75.3 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2015 & Male & 69.9 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2015 & Both sexes & 72.5 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Tonga & 2015 & Female & 75.2 &
+upper\_middle & Oceania \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2020 & Male &
+70.1 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2020 & Both
+sexes & 73.6 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2020 & Female &
+77.3 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2019 & Male &
+70.7 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2019 & Both
+sexes & 74.1 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2019 & Female &
+77.5 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2018 & Male &
+70.6 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2018 & Both
+sexes & 74.0 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2018 & Female &
+77.5 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2017 & Male &
+70.7 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2017 & Both
+sexes & 74.0 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2017 & Female &
+77.3 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2016 & Male &
+70.7 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2016 & Both
+sexes & 73.8 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2016 & Female &
+76.9 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2015 & Male &
+71.4 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2015 & Both
+sexes & 74.4 & high\_income & North America \\
+Life expectancy at birth (years) & Trinidad and Tobago & 2015 & Female &
+77.3 & high\_income & North America \\
+Life expectancy at birth (years) & Tunisia & 2020 & Male & 74.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2020 & Both sexes & 77.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2020 & Female & 79.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2019 & Male & 75.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2019 & Both sexes & 77.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2019 & Female & 80.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2018 & Male & 74.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2018 & Both sexes & 77.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2018 & Female & 79.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2017 & Male & 74.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2017 & Both sexes & 77.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2017 & Female & 79.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2016 & Male & 74.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2016 & Both sexes & 76.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2016 & Female & 79.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2015 & Male & 74.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2015 & Both sexes & 76.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Tunisia & 2015 & Female & 79.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Turkmenistan & 2020 & Male & 64.9 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2020 & Both sexes &
+68.5 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2020 & Female & 72.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2019 & Male & 65.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2019 & Both sexes &
+69.1 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2019 & Female & 72.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2018 & Male & 65.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2018 & Both sexes &
+69.1 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2018 & Female & 72.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2017 & Male & 65.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2017 & Both sexes &
+69.0 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2017 & Female & 72.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2016 & Male & 65.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2016 & Both sexes &
+69.0 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2016 & Female & 72.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2015 & Male & 65.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2015 & Both sexes &
+68.8 & upper\_middle & Asia \\
+Life expectancy at birth (years) & Turkmenistan & 2015 & Female & 72.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2020 & Male & 73.4 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2020 & Both sexes & 76.2 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2020 & Female & 79.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2019 & Male & 75.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2019 & Both sexes & 77.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2019 & Female & 80.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2018 & Male & 75.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2018 & Both sexes & 77.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2018 & Female & 80.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2017 & Male & 74.5 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2017 & Both sexes & 77.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2017 & Female & 79.6 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2016 & Male & 74.1 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2016 & Both sexes & 76.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2016 & Female & 79.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2015 & Male & 74.0 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2015 & Both sexes & 76.7 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Türkiye & 2015 & Female & 79.3 &
+upper\_middle & Asia \\
+Life expectancy at birth (years) & Uganda & 2020 & Male & 63.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2020 & Both sexes & 66.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2020 & Female & 69.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2019 & Male & 62.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2019 & Both sexes & 66.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2019 & Female & 69.3 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2018 & Male & 62.4 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2018 & Both sexes & 65.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2018 & Female & 69.0 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2017 & Male & 61.8 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2017 & Both sexes & 65.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2017 & Female & 68.6 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2016 & Male & 61.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2016 & Both sexes & 64.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2016 & Female & 68.1 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2015 & Male & 60.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2015 & Both sexes & 64.2 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Uganda & 2015 & Female & 67.7 &
+lower\_income & Africa \\
+Life expectancy at birth (years) & Ukraine & 2020 & Male & 67.6 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2020 & Both sexes & 72.5 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2020 & Female & 77.2 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2019 & Male & 68.0 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2019 & Both sexes & 73.0 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2019 & Female & 77.8 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2018 & Male & 67.7 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2018 & Both sexes & 72.7 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2018 & Female & 77.6 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2017 & Male & 68.1 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2017 & Both sexes & 73.0 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2017 & Female & 77.7 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2016 & Male & 67.7 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2016 & Both sexes & 72.6 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2016 & Female & 77.3 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2015 & Male & 67.1 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2015 & Both sexes & 72.1 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & Ukraine & 2015 & Female & 77.0 &
+lower\_middle & Europe \\
+Life expectancy at birth (years) & United Arab Emirates & 2020 & Male &
+78.9 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2020 & Both
+sexes & 80.1 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2020 & Female
+& 82.2 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2019 & Male &
+81.0 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2019 & Both
+sexes & 81.4 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2019 & Female
+& 82.3 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2018 & Male &
+80.8 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2018 & Both
+sexes & 81.2 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2018 & Female
+& 82.1 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2017 & Male &
+80.5 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2017 & Both
+sexes & 80.9 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2017 & Female
+& 81.8 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2016 & Male &
+80.4 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2016 & Both
+sexes & 80.8 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2016 & Female
+& 81.6 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2015 & Male &
+80.4 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2015 & Both
+sexes & 80.7 & high\_income & Asia \\
+Life expectancy at birth (years) & United Arab Emirates & 2015 & Female
+& 81.5 & high\_income & Asia \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2020 & Male & 78.3 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2020 & Both sexes & 80.1 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2020 & Female & 82.0 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2019 & Male & 79.5 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2019 & Both sexes & 81.2 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2019 & Female & 82.9 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2018 & Male & 78.9 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2018 & Both sexes & 80.6 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2018 & Female & 82.3 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2017 & Male & 79.2 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2017 & Both sexes & 80.9 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2017 & Female & 82.6 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2016 & Male & 79.1 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2016 & Both sexes & 80.8 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2016 & Female & 82.5 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2015 & Male & 78.9 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2015 & Both sexes & 80.7 & high\_income & Europe \\
+Life expectancy at birth (years) & United Kingdom of Great Britain and
+Northern Ireland & 2015 & Female & 82.3 & high\_income & Europe \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2020 &
+Male & 65.7 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2020 &
+Both sexes & 67.4 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2020 &
+Female & 69.1 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2019 &
+Male & 65.2 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2019 &
+Both sexes & 66.8 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2019 &
+Female & 68.4 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2018 &
+Male & 64.8 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2018 &
+Both sexes & 66.4 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2018 &
+Female & 68.0 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2017 &
+Male & 64.4 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2017 &
+Both sexes & 66.0 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2017 &
+Female & 67.6 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2016 &
+Male & 64.0 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2016 &
+Both sexes & 65.6 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2016 &
+Female & 67.2 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2015 &
+Male & 63.5 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2015 &
+Both sexes & 65.2 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United Republic of Tanzania & 2015 &
+Female & 66.8 & lower\_middle & Africa \\
+Life expectancy at birth (years) & United States of America & 2020 &
+Male & 74.4 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2020 &
+Both sexes & 76.9 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2020 &
+Female & 79.5 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2019 &
+Male & 76.5 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2019 &
+Both sexes & 78.7 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2019 &
+Female & 81.0 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2018 &
+Male & 76.4 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2018 &
+Both sexes & 78.6 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2018 &
+Female & 80.9 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2017 &
+Male & 76.3 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2017 &
+Both sexes & 78.5 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2017 &
+Female & 80.7 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2016 &
+Male & 76.4 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2016 &
+Both sexes & 78.6 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2016 &
+Female & 80.8 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2015 &
+Male & 76.5 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2015 &
+Both sexes & 78.6 & high\_income & North America \\
+Life expectancy at birth (years) & United States of America & 2015 &
+Female & 80.8 & high\_income & North America \\
+Life expectancy at birth (years) & Uruguay & 2020 & Male & 74.2 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2020 & Both sexes & 77.8 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2020 & Female & 81.2 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2019 & Male & 73.4 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2019 & Both sexes & 77.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2019 & Female & 80.5 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2018 & Male & 73.2 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2018 & Both sexes & 77.0 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2018 & Female & 80.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2017 & Male & 73.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2017 & Both sexes & 77.3 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2017 & Female & 80.8 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2016 & Male & 73.1 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2016 & Both sexes & 76.8 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2016 & Female & 80.5 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2015 & Male & 73.3 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2015 & Both sexes & 77.1 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uruguay & 2015 & Female & 80.7 &
+high\_income & South America \\
+Life expectancy at birth (years) & Uzbekistan & 2020 & Male & 69.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2020 & Both sexes & 71.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2020 & Female & 73.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2019 & Male & 70.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2019 & Both sexes & 72.3
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2019 & Female & 74.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2018 & Male & 69.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2018 & Both sexes & 71.5
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2018 & Female & 73.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2017 & Male & 68.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2017 & Both sexes & 70.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2017 & Female & 72.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2016 & Male & 67.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2016 & Both sexes & 70.0
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2016 & Female & 72.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2015 & Male & 67.1 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2015 & Both sexes & 69.4
+& lower\_middle & Asia \\
+Life expectancy at birth (years) & Uzbekistan & 2015 & Female & 71.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Vanuatu & 2020 & Male & 63.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2020 & Both sexes & 67.1 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2020 & Female & 70.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2019 & Male & 64.1 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2019 & Both sexes & 67.1 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2019 & Female & 70.6 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2018 & Male & 64.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2018 & Both sexes & 67.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2018 & Female & 70.6 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2017 & Male & 64.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2017 & Both sexes & 67.0 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2017 & Female & 70.5 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2016 & Male & 63.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2016 & Both sexes & 66.9 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2016 & Female & 70.5 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2015 & Male & 63.8 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2015 & Both sexes & 66.8 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Vanuatu & 2015 & Female & 70.3 &
+lower\_middle & Oceania \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2020 & Male & 68.0 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2020 & Both sexes & 72.4 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2020 & Female & 77.2 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2019 & Male & 68.4 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2019 & Both sexes & 72.7 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2019 & Female & 77.3 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2018 & Male & 68.5 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2018 & Both sexes & 72.8 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2018 & Female & 77.4 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2017 & Male & 68.7 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2017 & Both sexes & 73.0 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2017 & Female & 77.6 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2016 & Male & 67.9 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2016 & Both sexes & 72.4 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2016 & Female & 77.2 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2015 & Male & 69.8 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2015 & Both sexes & 73.9 & upper\_middle & South America \\
+Life expectancy at birth (years) & Venezuela (Bolivarian Republic of) &
+2015 & Female & 78.3 & upper\_middle & South America \\
+Life expectancy at birth (years) & Viet Nam & 2020 & Male & 70.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2020 & Both sexes & 74.8 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2020 & Female & 79.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2019 & Male & 69.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2019 & Both sexes & 73.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2019 & Female & 78.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2018 & Male & 69.3 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2018 & Both sexes & 73.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2018 & Female & 77.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2017 & Male & 69.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2017 & Both sexes & 73.4 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2017 & Female & 77.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2016 & Male & 68.9 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2016 & Both sexes & 73.2 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2016 & Female & 77.6 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2015 & Male & 68.7 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2015 & Both sexes & 73.0 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Viet Nam & 2015 & Female & 77.5 &
+lower\_middle & Asia \\
+Life expectancy at birth (years) & Yemen & 2020 & Male & 63.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2020 & Both sexes & 66.5 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2020 & Female & 69.4 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2019 & Male & 63.9 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2019 & Both sexes & 66.9 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2019 & Female & 70.0 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2018 & Male & 63.2 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2018 & Both sexes & 66.4 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2018 & Female & 69.8 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2017 & Male & 65.1 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2017 & Both sexes & 67.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2017 & Female & 70.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2016 & Male & 65.2 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2016 & Both sexes & 67.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2016 & Female & 70.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2015 & Male & 66.1 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2015 & Both sexes & 68.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Yemen & 2015 & Female & 70.4 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Zambia & 2020 & Male & 59.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2020 & Both sexes & 61.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2020 & Female & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2019 & Male & 59.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2019 & Both sexes & 61.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2019 & Female & 63.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2018 & Male & 59.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2018 & Both sexes & 61.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2018 & Female & 63.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2017 & Male & 59.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2017 & Both sexes & 61.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2017 & Female & 63.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2016 & Male & 58.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2016 & Both sexes & 61.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2016 & Female & 63.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2015 & Male & 58.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2015 & Both sexes & 60.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zambia & 2015 & Female & 62.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2020 & Male & 57.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2020 & Both sexes & 59.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2020 & Female & 61.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2019 & Male & 56.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2019 & Both sexes & 59.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2019 & Female & 61.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2018 & Male & 56.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2018 & Both sexes & 58.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2018 & Female & 60.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2017 & Male & 56.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2017 & Both sexes & 58.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2017 & Female & 60.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2016 & Male & 55.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2016 & Both sexes & 57.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2016 & Female & 59.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2015 & Male & 55.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2015 & Both sexes & 57.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Zimbabwe & 2015 & Female & 59.4 &
+lower\_middle & Africa \\
+
+\end{longtable}
+
 \subsubsection{Idealized Survey}\label{idealized-survey}
 
-\textbf{Survey: Understanding Life Expectancy and Influencing Factor}
+\textbf{Survey: Life Expectancy and Lifestyle Survey}
 
 Thank you for participating in this survey. This survey aims to gather
-insights into the factors influencing life expectancy, including health
-expenditure, education, ethnicity, government spending on healthcare,
-and income levels. Your responses will help us understand individual
-perspectives and experiences towards national policy. Participation is
-voluntary, and your answers will remain anonymous.
+insights into the factors influencing life expectancy, including gender,
+region and income group. Your responses will help us understand
+individual perspectives and experience towards national policy.
+Participation is voluntary, and your answers will remain anonymous.
 
@@
 
-\textbf{Section 1: Personal Health Expenditure}
-
-\textbf{1.What percentage of your monthly income do you spend on
-healthcare (e.g., insurance, medications, doctor visits)?}
+\textbf{Section 1: Demographics}
+
+\textbf{1. Gender}
 
@@
 \item
-  Less than 5\%
+  Male
 \item
-  5\%--10\%
+  Female
 \item
-  10\%--20\%
+  Non-binary
 \item
-  More than 20\%
+  Prefer not to say
 \end{itemize}
 
-\textbf{2.Do you or your household have health insurance coverage?}
+\textbf{2. Age (in years)}
+
+Please write the number: \_\_\_\_\_\_
+
+\textbf{3. Region of Residence}
 
@@
 \item
-  Yes
+  Africa
 \item
-  No
+  Asia
+\item
+  Europe
+\item
+  North America
+\item
+  South America
+\item
+  Oceania
 \end{itemize}
 
-\textbf{3. How frequently do you visit a healthcare
-professional(eg.doctors, nurse) in a year?}
+\textbf{4. Income Level}
+
+Annual Income (Optional): \_\_\_\_\_\_ USD
+
+Income Group: - Low Income (Less than \$1,000/year) - Lower-Middle
+Income (\$1,001 - \$10,000/year) - Upper-Middle Income (\$10,001 -
+\$50,000/year) - High Income (More than \$50,000/year)
+
+\textbf{Section 2: Health and Lifestyle}
+
+\textbf{5. Current Life Expectancy Perception}
+
+How many years do you expect to live?
+
+Please write the number: \_\_\_\_\_\_
+
+\textbf{6. Healthcare Access}
+
+How often do you visit healthcare professionals - Regularly (e.g.,
+annual checkups) - Occasionally (e.g., only when unwell) - Rarely or
+Never
+
+\textbf{7. Dietary Habits}
+
+How would you describe your diet?
 
@@
 \item
-  0-1 times
+  Balanced and healthy
 \item
-  2-5 times
+  Somewhat balanced
 \item
-  6-10 times
-\item
-  More than 10 times
+  Unhealthy
 \end{itemize}
 
-\textbf{Section 2: Education Background}
-
-\textbf{4.What is the highest level of education you have completed?}
-
-\begin{itemize}
-\tightlist
-\item
-  No formal education
-\item
-  Primary school
-\item
-  Secondary school
-\item
-  College or university degree
-\item
-  Postgraduate degree
-\end{itemize}
-
-\textbf{5.How many years of formal schooling have you completed?}
-
-Please write the number: \_\_\_\_\_\_\_
-
-\textbf{Section 3: Ethnicity and Geographic Factors}
-
-\textbf{6.Which of the following best describes your ethnicity?}
-
-\begin{itemize}
-\tightlist
-\item
-  African
-\item
-  Asian
-\item
-  European
-\item
-  Hispanic or Latino
-\item
-  Middle Eastern
-\item
-  Indigenous
-\item
-  Other (please specify): \_\_\_\_\_\_\_
-\end{itemize}
-
-\textbf{7.What's the distance to the nearest healthcare facility from
-your residence?}
-
-\begin{itemize}
-\tightlist
-\item
-  Less than 1 km
-\item
-  1-5 km
-\item
-  More than 5 km
-\end{itemize}
-
-\textbf{Section 4: Government Expenditure on Healthcare}
-
-\textbf{8.Are health services in your country subsidized by the
-govenment?}
-
-\begin{itemize}
-\tightlist
-\item
-  Yes, fully subsidized
-\item
-  Yes, partially subsidized
-\item
-  No
-\end{itemize}
-
-\textbf{9. What is the approximate cost of your most recent healthcare
-visit (in local currency)?}
-
-Please write the amount \_\_\_\_\_\_\_
-
-\textbf{10.Do public healthcare facilities in your area provide all the
-services you need?}
-
-\begin{itemize}
-\tightlist
-\item
-  Yes
-\item
-  No
-\item
-  Not applicable
-\end{itemize}
-
-\textbf{Section 5: Income and Development Factor}
-
-\textbf{11.What is your approximate monthly household income after
-taxes?(in local currency)}
-
-\begin{itemize}
-\tightlist
-\item
-  Less than 1,000
-\item
-  1,000 - 2,999
-\item
-  3,000 - 4,999
-\item
-  5,000 - 7,999
-\item
-  8,000 - 10,999
-\item
-  More than 11,000
-\item
-  Prefer not to say
-\end{itemize}
-
-\textbf{12.How would you describe your current financial situation?}
-
-\begin{itemize}
-\tightlist
-\item
-  Struggling to make ends meet
-\item
-  Just getting by
-\item
-  Comfortable, but not wealthy
-\item
-  Financially secure
-\item
-  Wealthy
-\item
-  Prefer not to say
-\end{itemize}
-
-\textbf{13.How often do you have difficulty affording basic healthcare
-(medical visits, medications, etc.)?}
-
-\begin{itemize}
-\tightlist
-\item
-  Never
-\item
-  Rarely
-\item
-  Sometimes
-\item
-  Often
-\item
-  Always
-\item
-  Prefer not to say
-\end{itemize}
+\textbf{8. Physical Activity}
+
+How many hours of physical activity do you engage in per week? - Less
+than 1 hour - 1-3 hours - More than 3 hours
+
+\textbf{9. Smoking Habits}
+
+Do you smoke? - Yes - No
+
+\textbf{10. Alcohol Consumption}
+
+How often do you consume alcoholic beverages? - Never - Occasionally
+(e.g., social drinking) - Frequently
+
+\textbf{Section 3: Environmental and Social Factors}
+
+\textbf{11.Living Environment}
+
+How would you describe your living area? - Urban - Suburban - Rural
 

### 2024-12-03 scripts/05-model_data.R
initial

@@ -14,42 +14,31 @@ library(rstanarm)
 library(car)
 library(arrow)
 library(dplyr)
-library(countrycode)
+library(modelsummary) # for summarizing the model
 
 #### Read data ####
-cleaned_expectancy <- read_csv("data/02-analysis_data/analysis_data.parquet")
+lea60 <- read_parquet("data/02-analysis_data/lea60.parquet")
+leab <- read_parquet ("data/02-analysis_data/leab.parquet")
 
-#Convert the columns into appropriate data types
-cleaned_expectancy <- cleaned_expectancy %>%
-  mutate(
-    LifeExpectancy = as.numeric(LifeExpectancy),
-    Status = as.factor(Status),
-    PercentageExpenditure = as.numeric(PercentageExpenditure),
-    TotalExpenditure = as.numeric(TotalExpenditure),
-    IncomeComposition = as.numeric(IncomeComposition),
-    Schooling = as.numeric(Schooling)
-  )
+# Fit the Bayesian linear regression model using stan_glm
+ledata_normal_model <- stan_glm(
+  `Life Expectancy` ~ Region + Country + Income_Group + Gender, 
+  data = leab, 
+  family = gaussian(link = "identity"), 
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  seed = 123
+)
 
+# Create a model summary with median absolute deviation (mad) for statistics
+modelsummary(
+  list("Gaussian(Normal)" = ledata_normal_model),
+  statistic = "mad",  # Median absolute deviation
+  fmt = 2             # Format results to 2 decimal places
+)
 
-### Model for developing country based on various predictors ###
-lm_model_developing <-
-  lm(LifeExpectancy ~ PercentageExpenditure + TotalExpenditure + IncomeComposition + Schooling,
-     data = cleaned_expectancy %>% filter (Status == 'Developing'))
-
-### Model for developed country based on various predictors###
-lm_model_developed <-
-  lm(LifeExpectancy ~ PercentageExpenditure + TotalExpenditure + IncomeComposition + Schooling,
-     data = cleaned_expectancy %>% filter (Status == 'Developed') )
-
-
-#### Save modified data for model as a CSV + parquet and save model as RDS ####
-write_csv(cleaned_expectancy, "data/02-analysis_data/analysis_data.csv")
[…]

### 2024-12-03 paper/paper.qmd
initial

@@
 library(gridExtra)
+library(caret)
 
@@
 The model aim to estimate and predict the life expectancy of people under different gender, region and income group.
-The normal Gaussian distribution is effective when used for modeling scenarios where the residuals of the data aare assumed to be independent nd normally distributed around the regression line.
+The normal Gaussian distribution is effective when used for modeling scenarios where the residuals of the data are assumed to be independent nd normally distributed around the regression line.
 The GAM allows for capturing potential non-linear relationships between the predictors and the outcome.
@@
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\
+\alpha &\sim \text{Normal}(0, 2.5) \\
+\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\
+\sigma &\sim \text{Exponential}(1)
 \end{align}
@@
 
--   $yi$ is the outcome variable (Life Expectancy)for the i-th country.
+-   $yi$ is the outcome variable (Life Expectancy)for the i-th observation.
 
--   $_i$ represents the expected value of $yi$, modeled as a linear combination of the predictors: Gender, Region, and Income Group.
+-   $\mu_i$: the linear predictor for life expectancy, including the intercept ($\alpha$) and the coefficients for the predictors Region, Country, Income Group, and Gender.
 
--   $Gender$ is the gender of the individual.
+-   Priors for the intercept($\alpha$) and the coefficients($\beta_1, \beta_2, \beta_3$) are normal with mean 0 and standard deviation 2.5
 
--   $Income Group$ is the income group of the country.
-
--   $\epsilon_i$ is the error term, assumed to be normally distributed with a mean of 0 and constant variance $ϵ_i​∼N(0,\sigma^2)$
-
-This GAM model allows for smooth, non-linear effects of continuous predictors (**`age`** and **`races_count`**) while keeping the categorical predictors (**`Income_Group`** and **`iaaf_category`**) in a linear framework.
+-   $\sigma$: the residual standard deviation, modeled as an exponential distribution with rate 1.
 
@@
 
-The GAM was chosen for this analysis due to its ability to capture non-linear relationships between predictors and the outcome variable, which is essential when dealing with categorical predictors like income group and the
+The linear regression model with Gaussian likelihood was chosen for this analysis due to its simplicity and effectiveness in modeling continuous outcome variables, such as life expectancy.
+Life expectancy is influenced by multiple factors, including region, income group, and gender.
+The linear model allows us to examine the average effect of each predictor on the outcome, assuming that the relationships between these predictors and life expectancy are linear.
+
+The use of normal priors for the model coefficients $\alpha$ and $\beta$ reflects a belief in prior knowledge that the true values of these parameters are centered around zero, with some uncertainty, which is consistent with standard Bayesian modeling practices.
+The prior scale of 2.5 was chosen to reflect a reasonable level of uncertainty around the estimates without being overly restrictive.
+
+The Gaussian distribution was selected because life expectancy data, by nature, is continuous and expected to follow a normal distribution.
+The assumption of normal residuals is consistent with the idea that deviations from the regression line are random and normally distributed, allowing the model to make accurate inferences about the relationship between predictors and the outcome.
+
+Additionally, the exponential prior on the standard deviation $\alpha$ captures the residual variability in life expectancy across countries and regions.
+The exponential distribution was chosen because it provides a simple and interpretable way of modeling the variability, assuming that the data are not heavily skewed.
+
+This approach is appropriate given the data structure and the goal of the analysis, which is to estimate and predict life expectancy across different countries, regions, income groups, and genders.
+The model's assumptions about the data, along with its priors, allow for robust inference in the context of population health predictions.
 
@@
 
-RMSE
+To assess the performance of the life expectancy prediction model, two critical metrics were used: Root Mean Squared Error (RMSE) and Out-of-Sample Testing.
+These methods help ensure that the model generalizes well to unseen data and provides reliable predictions for life expectancy across different regions, income groups, and genders.
 
-Out-of- Sample testing
+RMSE measures the square root of the average squared differences between the predicted and observed values.
+In the context of this model, RMSE quantifies how closely the predicted life expectancy values align with the actual observed values.
+Lower RMSE values indicate better model performance, suggesting that the model’s predictions are close to the true values.
+
+By calculating RMSE, we can assess the goodness-of-fit of the model, with lower values indicating less error and higher precision in predicting life expectancy.
+It is particularly useful in comparing different models or iterations to select the best-performing one.
+
+Out-of-Sample testing is a critical component of model evaluation.
+In this approach, the data is split into a training set and a test set (or holdout set).
+The training set is used to fit the model, while the test set is used to evaluate how well the model performs on new, unseen data.
+For this analysis, the model was trained using a portion of the data (80% of the dataset) and then evaluated on the remaining data (20% of the dataset) that was not used during training.
+This method allows us to check whether the model overfits the training data or if it can generalize well to unseen observations.
+
+Together, RMSE and out-of-sample testing offer a robust framework for model validation, ensuring that the predictions made by the life expectancy model are both accurate and generalizable.
+
+```{r}
+
+model_developed <-
+  readRDS(file = "~/lifeexpectancy/models/ledata_normal_model.rds")
+
+# Split the dataset into training and testing sets (80% train, 20% test)
+set.seed(123)  # Setting seed for reproducibility
+train_index <- createDataPartition(leab$`Life Expectancy`, p = 0.8, list = FALSE)
+
+train_data <- leab[train_index, ]
+test_data <- leab[-train_index, ]
+
+# Predict life expectancy using the test data
+predictions <- predict(ledata_normal_model, newdata = test_data)
+```
+
+```{r}
+#| label: tbl-modelpredict
+#| tbl-cap: Summary of the life expectancy model, which includes gender, region and income group. The table presents the model RSME and out-of sample testing.
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+# Calculate RMSE
+actual_values <- test_data$`Life Expectancy`
+rmse <- sqrt(mean((predictions - actual_values)^2))
+print(paste("RMSE: ", round(rmse, 2)))
+
+# Calculate RMSE for the training set (in-sample testing)
+train_predictions <- predict(ledata_normal_model, newdata = train_data)
+train_rmse <- sqrt(mean((train_predictions - train_data$`Life Expectancy`)^2))
+print(paste("Training RMSE: ", round(train_rmse, 2)))
+
+# Compare RMSE results
+if (rmse < train_rmse) {
+  print("The model generalizes well to the test data (out-of-sample).")
+} else {
+  print("The model may be overfitting the training data (higher RMSE on test data).")
+}
+
+```
 
@@
 Our results are summarized in @tbl-modelresults. We are primarily interest in the
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-#model_developed <-
-  #readRDS(file = here::here("models/lm_model_developed.rds"))
-```
 
@@
   #list(
-    #"developed model" = #model_developed
+    #"developed model" = model_developed
   #),
@@
 
-#Show the whole graph of cleaned table leab
-kable(leab, 
+#Show the first 200 lines of the  graph of cleaned table leab
+leab_first_200 <- head(leab, 200)
+
+kable(leab_first_200, 
       col.names = names(leab), 
       align = "l", 
-      caption = "Life Expectancy over countries and years")
+      caption = "Life Expectancy over countries and years (first 200 rows)")
 
@@
 
-## Additional graph for analysis
+The model developed for predicting life expectancy is a linear regression model, where the goal is to estimate the outcome variable, Life Expectancy, based on multiple predictors: Region, Income Group, and Gender.
+Here's a more detailed breakdown of the components and structure of the model:
 
-## Posterior predictive check
+**1. Outcome variable (yi)**
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+The outcome variable $y_i$ represents the life expectancy of an country.
+This is a continuous variable representing the number of years a person is expected to live, assuming all conditions remain constant.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+**2. Linear Predictor (μi)**
+
+The linear predictor $μ_i$ is a linear combination of the predictors, which includes an intercept term $α$ and the coefficients $β_1$, $β_2$, $β_3$, corresponding to Region, Income Group, and Gender, respectively.
+This linear equation models the relationship between life expectancy and the predictors
+$\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)$
+The values for these coefficients (betas) represent the expected change in life expectancy for a one-unit change in each respective predictor.
+
+**3. Priors**
+
+The prior distribution for the intercept $α$ and the coefficients $β_1$, $β_2$, $β_3$ is assumed to be normal with a mean of 0 and a standard deviation of 2.5.
+This reflects our belief that, prior to seeing the data, the intercept and coefficients are most likely close to 0, with a reasonable range of variability (the scale of 2.5 is relatively broad, allowing flexibility in fitting the model).
+
+The prior for $σ$ (residual standard deviation) is assumed to follow an exponential distribution with a rate of 1.
+This prior reflects the assumption that the variance of the residuals (i.e., the deviation of the actual observations from the predicted values) is positive and that it could reasonably be spread across a wide range of values.
+
+**4. Residual Standard Deviation (σ)**
+The model also estimates $σ$, which represents the standard deviation of the residuals — the errors between the observed life expectancy values and those predicted by the model.
+The prior for $σ$ is assumed to follow an exponential distribution with a rate of 1, meaning that smaller values of $σ$ (indicating less variation) are somewhat more likely than larger ones.
+
+**5. Gaussian Likelihood**
+The outcome variable Life Expectancy is modeled using a normal distribution with mean μi (the linear predictor) and standard deviation σ.
+This means that the residuals (the differences between the observed and predicted values) are assumed to be normally distributed:
+$y_i| \mu_i, \sigma ~ Normal(\mu_i, \sigma)$
+This is a typical assumption in regression models when the data is continuous, and the relationship between the predictors and the outcome is linear.
+
+## RMSE table
 
 ```{r}
+#| label: tbl-testpredicted
+#| tbl-cap: "Life expectancy over countries and years"
+#| echo: false
 #| eval: true
-#| echo: false
+#| warning: false
 #| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 
-#pp_check(model_developed) +
-  #theme_classic() +
-  #theme(legend.position = "bottom")
+# Create a data frame for the predicted values and actual values in the test set
+results_df <- data.frame(
+  Country = test_data$Country,
+  Actual_Life_Expectancy = actual_values,
+  Predicted_Life_Expectancy = predictions,
+  RMSE_Test = rmse,
+  RMSE_Train = train_rmse
+)
 
-#posterior_vs_prior(model_developed) +
-  #theme_minimal() +
-  #scale_color_brewer(palette = "Set1") +
-  #theme(legend.position = "bottom") +
-  #coord_flip()
+# Create an indication column based on the RMSE comparison
+results_df$Indication <- ifelse(results_df$RMSE_Test < results_df$RMSE_Train, 
+                                 "Model generalizes well (out-of-sample)", 
+                                 "Model may be overfitting the training data")
+
+# Format the table using kable
+kable(
+  results_df,
+  col.names = c("Country", "Actual Life Expectancy", "Predicted Life Expectancy", "RMSE (Test)", "RMSE (Train)", "Indication"),
+  align = c("l", "r", "r", "r", "r", "l"),
+  digits = 2,
+  booktabs = TRUE
+)
+
 ```
 
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-#plot(model_developed, "trace")
-
-#plot(model_developed, "rhat")
-```
+### Additional graph for analysis
 

### 2024-12-03 paper/paper.qmd
initial

@@
 
-[Appendix -@sec-model-details].
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. More explanation of the model could be found [Appendix -@sec-model-details].
 
@@
 Lower RMSE values indicate better model performance, suggesting that the model’s predictions are close to the true values.
-
-By calculating RMSE, we can assess the goodness-of-fit of the model, with lower values indicating less error and higher precision in predicting life expectancy.
-It is particularly useful in comparing different models or iterations to select the best-performing one.
+The generalizability is checked by comparing rmse_test and rmse_train.
+Seeing the test RMSE is slightly lower than the training RMSE, the model generalizes well.
 
@@
 ## Overview of model results
+
 Our results are summarized in @tbl-modelresults. We are primarily interest in the
@@
 
-### Idealized Survey
+## Idealized Survey
 
@@
 
-Income Group:
--   Low Income (Less than $1,000/year)
--   Lower-Middle Income (\$1,001 - \$10,000/year)
--   Upper-Middle Income (\$10,001 - \$50,000/year)
--   High Income (More than \$50,000/year)
+Income Group: - Low Income (Less than \$1,000/year) - Lower-Middle Income (\$1,001 - \$10,000/year) - Upper-Middle Income (\$10,001 - \$50,000/year) - High Income (More than \$50,000/year)
 
@@
 
-How often do you visit healthcare professionals
--   Regularly (e.g., annual checkups)
--   Occasionally (e.g., only when unwell)
--   Rarely or Never
+How often do you visit healthcare professionals - Regularly (e.g., annual checkups) - Occasionally (e.g., only when unwell) - Rarely or Never
 
@@
 
-How many hours of physical activity do you engage in per week?
--   Less than 1 hour
--   1-3 hours
--   More than 3 hours
+How many hours of physical activity do you engage in per week? - Less than 1 hour - 1-3 hours - More than 3 hours
 
@@
 
-Do you smoke?
--   Yes
--   No
+Do you smoke? - Yes - No
 
@@
 
-How often do you consume alcoholic beverages?
--   Never
--   Occasionally (e.g., social drinking)
--   Frequently
+How often do you consume alcoholic beverages? - Never - Occasionally (e.g., social drinking) - Frequently
 
@@
 
-How would you describe your living area?
--   Urban
--   Suburban
--   Rural
+How would you describe your living area? - Urban - Suburban - Rural
 
@@
 
-# Model details {#sec-model-details}
+## Model details {#sec-model-details}
 
@@
 The linear predictor $μ_i$ is a linear combination of the predictors, which includes an intercept term $α$ and the coefficients $β_1$, $β_2$, $β_3$, corresponding to Region, Income Group, and Gender, respectively.
-This linear equation models the relationship between life expectancy and the predictors
-$\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)$
-The values for these coefficients (betas) represent the expected change in life expectancy for a one-unit change in each respective predictor.
+This linear equation models the relationship between life expectancy and the predictors $\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)$ The values for these coefficients (betas) represent the expected change in life expectancy for a one-unit change in each respective predictor.
 
@@
 
-**4. Residual Standard Deviation (σ)**
-The model also estimates $σ$, which represents the standard deviation of the residuals — the errors between the observed life expectancy values and those predicted by the model.
+**4.
+Residual Standard Deviation (σ)** The model also estimates $σ$, which represents the standard deviation of the residuals — the errors between the observed life expectancy values and those predicted by the model.
 The prior for $σ$ is assumed to follow an exponential distribution with a rate of 1, meaning that smaller values of $σ$ (indicating less variation) are somewhat more likely than larger ones.
 
-**5. Gaussian Likelihood**
-The outcome variable Life Expectancy is modeled using a normal distribution with mean μi (the linear predictor) and standard deviation σ.
-This means that the residuals (the differences between the observed and predicted values) are assumed to be normally distributed:
-$y_i| \mu_i, \sigma ~ Normal(\mu_i, \sigma)$
-This is a typical assumption in regression models when the data is continuous, and the relationship between the predictors and the outcome is linear.
+**5.
+Gaussian Likelihood** The outcome variable Life Expectancy is modeled using a normal distribution with mean μi (the linear predictor) and standard deviation σ.
+This means that the residuals (the differences between the observed and predicted values) are assumed to be normally distributed: $y_i| \mu_i, \sigma ~ Normal(\mu_i, \sigma)$ This is a typical assumption in regression models when the data is continuous, and the relationship between the predictors and the outcome is linear.
 
-## RMSE table
+## RMSE Full table
 
@@
 
-### Additional graph for analysis
+## Additional graph for analysis
 

### 2024-12-04 scripts/03-clean_data.R
commit

@@ -26,7 +26,7 @@ extract_number <- function(x) {
 
 lecleaned_data <- lfex_data %>%
   # Remove rows where 'Location' is NA
-  filter(!is.na(Location)) %>%    
+  filter(!is.na(Location)) %>% 
   # Select the useful predictor from raw data
   select(
     Indicator, Location, Period, Dim1, Value)|>
@@ -203,15 +203,156 @@ lea60 <- lelecleaned_data %>%
 leab <- lelecleaned_data %>%
   filter(Indicator == "Life expectancy at birth (years)")
 
-#Create a table of life expectancy at birth of Male
-male_table <- leab[leab$Gender == 'Male', ]
+#create average life expectancy table through the leab group by the country
+average_life_expectancy <- leab %>%
+  group_by(Country) %>%
+  summarise(
+    Average_Life_Expectancy = mean(`Life Expectancy`, na.rm = TRUE)
+  )
 
+
+# Summarize the table to find the average life expectancy for each country, keeping additional columns
+average_life_expectancy <- leab %>%
+  group_by(Country, Gender, Income_Group, Region) %>%
+  summarise(
+    Average_Life_Expectancy = mean(`Life Expectancy`, na.rm = TRUE),
+    .groups = "drop" # Ungroups after summarizing for a cleaner output
+  )
+
+# Create both gender average life expectancy table 
+bothg_average_life_expectancy <- average_life_expectancy[average_life_expectancy$Gender == "Both sexes", ]
+
+# clean the both gender average without the gender column
+bothg_average_life_expectancy <- bothg_average_life_expectancy|>
+  select(-c(Gender))
+
+#create the gender average table
+gavg_tbl <- bothg_average_life_expectancy|>
+  summarise(
+    "Income/Region/Gender" = "Global",
+    "Life expctancy" = mean(Average_Life_Expectancy)
+  )
+
+#Create a table of life expectancy at birth of Male
+male_table <- average_life_expectancy[average_life_expectancy$Gender == 'Male', ]
+male_table <- male_table|> 
+  summarise(
+    "Income/Region/Gender" = "Male",
+    "Life expctancy" = mean(Average_Life_Expectancy)
+  )
+
+
+# create a maletable of life expectancy
+matable <- leab[leab$Gender == 'Male', ]
+
+# create a femaletable of life expectancy
[…]

### 2024-12-04 paper/paper.tex
comi

--- 2024-12-02 paper/paper.tex
@@
 
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{241,243,245}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
+\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+
 \providecommand{\tightlist}{%
@@
 distribution is effective when used for modeling scenarios where the
-residuals of the data aare assumed to be independent nd normally
+residuals of the data are assumed to be independent nd normally
 distributed around the regression line. The GAM allows for capturing
@@
 \item
-  \(yi\) is the outcome variable (Life Expectancy)for the i-th country.
-\item
-  \(_i\) represents the expected value of \(yi\), modeled as a linear
-  combination of the predictors: Gender, Region, and Income Group.
-\item
-  \(Gender\) is the gender of the individual.
-\item
-  \(Income Group\) is the income group of the country.
-\item
-  \(\epsilon_i\) is the error term, assumed to be normally distributed
-  with a mean of 0 and constant variance \(ϵ_i​∼N(0,\sigma^2)\)
+  \(yi\) is the outcome variable (Life Expectancy)for the i-th
+  observation.
+\item
+  \(\mu_i\): the linear predictor for life expectancy, including the
+  intercept (\(\alpha\)) and the coefficients for the predictors Region,
+  Country, Income Group, and Gender.
+\item
+  Priors for the intercept(\(\alpha\)) and the
+  coefficients(\(\beta_1, \beta_2, \beta_3\)) are normal with mean 0 and
+  standard deviation 2.5
+\item
+  \(\sigma\): the residual standard deviation, modeled as an exponential
+  distribution with rate 1.
 \end{itemize}
-
-This GAM model allows for smooth, non-linear effects of continuous
-predictors (\textbf{\texttt{age}} and \textbf{\texttt{races\_count}})
-while keeping the categorical predictors
-(\textbf{\texttt{Income\_Group}} and \textbf{\texttt{iaaf\_category}})
-in a linear framework.
-
-Appendix~\ref{sec-model-details}.
 
@@
 package of Goodrich et al. (2022). We use the default priors from
-\texttt{rstanarm}.
+\texttt{rstanarm}. More explanation of the model could be found
+Appendix~\ref{sec-model-details}.
 
@@
 
-We expect a positive relationship between the size of the wings and time
-spent aloft. In particular\ldots{}
-
-We can use maths by including latex between dollar signs, for instance
-\(\theta\).
+The linear regression model with Gaussian likelihood was chosen for this
+analysis due to its simplicity and effectiveness in modeling continuous
+outcome variables, such as life expectancy. Life expectancy is
+influenced by multiple factors, including region, income group, and
+gender. The linear model allows us to examine the average effect of each
+predictor on the outcome, assuming that the relationships between these
+predictors and life expectancy are linear.
+
+The use of normal priors for the model coefficients \(\alpha\) and
+\(\beta\) reflects a belief in prior knowledge that the true values of
+these parameters are centered around zero, with some uncertainty, which
+is consistent with standard Bayesian modeling practices. The prior scale
+of 2.5 was chosen to reflect a reasonable level of uncertainty around
+the estimates without being overly restrictive.
+
+The Gaussian distribution was selected because life expectancy data, by
+nature, is continuous and expected to follow a normal distribution. The
+assumption of normal residuals is consistent with the idea that
+deviations from the regression line are random and normally distributed,
+allowing the model to make accurate inferences about the relationship
+between predictors and the outcome.
+
+Additionally, the exponential prior on the standard deviation \(\alpha\)
+captures the residual variability in life expectancy across countries
+and regions. The exponential distribution was chosen because it provides
+a simple and interpretable way of modeling the variability, assuming
+that the data are not heavily skewed.
+
+This approach is appropriate given the data structure and the goal of
+the analysis, which is to estimate and predict life expectancy across
+different countries, regions, income groups, and genders. The model's
+assumptions about the data, along with its priors, allow for robust
+inference in the context of population health predictions.
 
@@
 
-RMSE
-
-Out-of- Sample testing
+To assess the performance of the life expectancy prediction model, two
+critical metrics were used: Root Mean Squared Error (RMSE) and
+Out-of-Sample Testing. These methods help ensure that the model
+generalizes well to unseen data and provides reliable predictions for
+life expectancy across different regions, income groups, and genders.
+
+RMSE measures the square root of the average squared differences between
+the predicted and observed values. In the context of this model, RMSE
+quantifies how closely the predicted life expectancy values align with
+the actual observed values. Lower RMSE values indicate better model
+performance, suggesting that the model's predictions are close to the
+true values. The generalizability is checked by comparing rmse\_test and
+rmse\_train. Seeing the test RMSE is slightly lower than the training
+RMSE, the model generalizes well.
+
+Out-of-Sample testing is a critical component of model evaluation. In
+this approach, the data is split into a training set and a test set (or
+holdout set). The training set is used to fit the model, while the test
+set is used to evaluate how well the model performs on new, unseen data.
+For this analysis, the model was trained using a portion of the data
+(80\% of the dataset) and then evaluated on the remaining data (20\% of
+the dataset) that was not used during training. This method allows us to
+check whether the model overfits the training data or if it can
+generalize well to unseen observations.
+
+Together, RMSE and out-of-sample testing offer a robust framework for
+model validation, ensuring that the predictions made by the life
+expectancy model are both accurate and generalizable.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#model\_developed \textless{}{-}}
+  \CommentTok{\#readRDS(file = "\textasciitilde{}/lifeexpectancy/models/ledata\_normal\_model.rds")}
+
+\CommentTok{\# Split the dataset into training and testing sets (80\% train, 20\% test)}
+\CommentTok{\#set.seed(123)  \# Setting seed for reproducibility}
+\CommentTok{\#train\_index \textless{}{-} createDataPartition(leab$\textasciigrave{}Life Expectancy\textasciigrave{}, p = 0.8, list = FALSE)}
+
+\CommentTok{\#train\_data \textless{}{-} leab[train\_index, ]}
+\CommentTok{\#test\_data \textless{}{-} leab[{-}train\_index, ]}
+
+\CommentTok{\# Predict life expectancy using the test data}
+\CommentTok{\#predictions \textless{}{-} predict(ledata\_normal\_model, newdata = test\_data)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\subsubsection{Idealized Survey}\label{idealized-survey}
-
-\textbf{Survey: Understanding Life Expectancy and Influencing Factor}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2895}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1754}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0614}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0965}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1404}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1140}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1228}}@{}}
+
+\caption{\label{tbl-cleaned_leab}Life expectancy over countries and
+years}
+
+\tabularnewline
+
+\caption{Life Expectancy over countries and years (first 200
+rows)}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Indicator
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Country
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Period
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Gender
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Life Expectancy
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Income\_Group
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Region
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Indicator
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Country
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Period
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Gender
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Life Expectancy
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Income\_Group
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Region
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Life expectancy at birth (years) & Afghanistan & 2020 & Male & 59.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2020 & Both sexes &
+60.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2020 & Female & 61.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2019 & Male & 60.0 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2019 & Both sexes &
+61.2 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2019 & Female & 62.5 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2018 & Male & 59.0 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2018 & Both sexes &
+60.5 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2018 & Female & 62.1 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2017 & Male & 59.8 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2017 & Both sexes &
+60.9 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2017 & Female & 62.1 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2016 & Male & 59.2 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2016 & Both sexes &
+60.4 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2016 & Female & 61.7 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2015 & Male & 59.3 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2015 & Both sexes &
+60.3 & lower\_income & Asia \\
+Life expectancy at birth (years) & Afghanistan & 2015 & Female & 61.5 &
+lower\_income & Asia \\
+Life expectancy at birth (years) & Albania & 2020 & Male & 74.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2020 & Both sexes & 76.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2020 & Female & 79.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2019 & Male & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2019 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2019 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2018 & Male & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2018 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2018 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2017 & Male & 76.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2017 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2017 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2016 & Male & 76.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2016 & Both sexes & 77.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2016 & Female & 79.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2015 & Male & 76.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2015 & Both sexes & 77.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Albania & 2015 & Female & 79.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Algeria & 2020 & Male & 73.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2020 & Both sexes & 74.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2020 & Female & 75.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2019 & Male & 76.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2019 & Both sexes & 76.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2019 & Female & 77.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2018 & Male & 76.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2018 & Both sexes & 76.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2018 & Female & 77.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2017 & Male & 76.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2017 & Both sexes & 76.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2017 & Female & 77.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2016 & Male & 75.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2016 & Both sexes & 76.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2016 & Female & 76.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2015 & Male & 75.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2015 & Both sexes & 76.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Algeria & 2015 & Female & 76.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2020 & Male & 60.4 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2020 & Both sexes & 62.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2020 & Female & 64.9 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2019 & Male & 60.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2019 & Both sexes & 62.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2019 & Female & 64.7 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2018 & Male & 60.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2018 & Both sexes & 62.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2018 & Female & 64.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2017 & Male & 59.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2017 & Both sexes & 62.0 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2017 & Female & 64.3 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2016 & Male & 59.5 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2016 & Both sexes & 61.8 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2016 & Female & 64.2 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2015 & Male & 59.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2015 & Both sexes & 61.6 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Angola & 2015 & Female & 64.1 &
+lower\_middle & Africa \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Male &
+75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Both
+sexes & 77.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Female &
+79.4 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Male &
+74.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Both
+sexes & 75.7 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Female &
+77.1 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Male &
+74.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Both
+sexes & 75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Female &
+77.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Male &
+73.9 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Both
+sexes & 75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Female &
+77.0 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Male &
+73.8 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Both
+sexes & 75.5 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Female &
+77.1 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Male &
+73.8 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Both
+sexes & 75.6 & high\_income & North America \\
+Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Female &
+77.2 & high\_income & North America \\
+Life expectancy at birth (years) & Argentina & 2020 & Male & 73.1 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2020 & Both sexes & 76.2
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2020 & Female & 79.4 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2019 & Male & 74.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2019 & Both sexes & 77.0
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2019 & Female & 79.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2018 & Male & 73.7 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2018 & Both sexes & 76.9
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2018 & Female & 79.9 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2017 & Male & 73.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2017 & Both sexes & 76.6
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2017 & Female & 79.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2016 & Male & 73.0 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2016 & Both sexes & 76.1
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2016 & Female & 79.2 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2015 & Male & 73.3 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2015 & Both sexes & 76.5
+& upper\_middle & South America \\
+Life expectancy at birth (years) & Argentina & 2015 & Female & 79.6 &
+upper\_middle & South America \\
+Life expectancy at birth (years) & Armenia & 2020 & Male & 62.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2020 & Both sexes & 69.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2020 & Female & 76.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2019 & Male & 70.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2019 & Both sexes & 75.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2019 & Female & 79.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2018 & Male & 71.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2018 & Both sexes & 75.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2018 & Female & 79.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2017 & Male & 70.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2017 & Both sexes & 75.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2017 & Female & 79.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2016 & Male & 69.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2016 & Both sexes & 74.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2016 & Female & 78.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2015 & Male & 69.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2015 & Both sexes & 74.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Armenia & 2015 & Female & 78.3 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Australia & 2020 & Male & 81.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2020 & Both sexes & 83.4
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2020 & Female & 85.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2019 & Male & 80.7 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2019 & Both sexes & 82.6
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2019 & Female & 84.6 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2018 & Male & 81.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2018 & Both sexes & 83.0
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2018 & Female & 84.9 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2017 & Male & 80.8 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2017 & Both sexes & 82.7
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2017 & Female & 84.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2016 & Male & 80.7 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2016 & Both sexes & 82.6
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2016 & Female & 84.5 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2015 & Male & 80.4 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2015 & Both sexes & 82.3
+& high\_income & Oceania \\
+Life expectancy at birth (years) & Australia & 2015 & Female & 84.2 &
+high\_income & Oceania \\
+Life expectancy at birth (years) & Austria & 2020 & Male & 78.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2020 & Both sexes & 81.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2020 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2019 & Male & 79.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2019 & Both sexes & 81.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2019 & Female & 83.8 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2018 & Male & 79.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2018 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2018 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2017 & Male & 79.2 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2017 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2017 & Female & 83.5 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2016 & Male & 79.1 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2016 & Both sexes & 81.4 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2016 & Female & 83.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2015 & Male & 78.6 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2015 & Both sexes & 81.0 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Austria & 2015 & Female & 83.3 &
+high\_income & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2020 & Male & 67.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2020 & Both sexes & 71.4
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2020 & Female & 75.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2019 & Male & 73.4 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2019 & Both sexes & 75.8
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2019 & Female & 78.1 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2018 & Male & 72.6 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2018 & Both sexes & 75.1
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2018 & Female & 77.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2017 & Male & 72.2 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2017 & Both sexes & 74.6
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2017 & Female & 76.9 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2016 & Male & 71.8 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2016 & Both sexes & 74.0
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2016 & Female & 76.0 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2015 & Male & 71.7 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2015 & Both sexes & 73.6
+& upper\_middle & Europe \\
+Life expectancy at birth (years) & Azerbaijan & 2015 & Female & 75.5 &
+upper\_middle & Europe \\
+Life expectancy at birth (years) & Bahamas & 2020 & Male & 69.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2020 & Both sexes & 72.6 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2020 & Female & 76.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2019 & Male & 68.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2019 & Both sexes & 70.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2019 & Female & 73.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2018 & Male & 70.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2018 & Both sexes & 73.4 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2018 & Female & 76.5 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2017 & Male & 70.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2017 & Both sexes & 73.2 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2017 & Female & 76.3 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2016 & Male & 69.7 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2016 & Both sexes & 72.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2016 & Female & 76.1 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2015 & Male & 69.8 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2015 & Both sexes & 72.9 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahamas & 2015 & Female & 76.0 &
+high\_income & North America \\
+Life expectancy at birth (years) & Bahrain & 2020 & Male & 73.6 &
+high\_income & Asia \\
+Life expectancy at birth (years) & Bahrain & 2020 & Both sexes & 74.9 &
+high\_income & Asia \\
+
+\end{longtable}
+
+\subsection{Idealized Survey}\label{idealized-survey}
+
+\textbf{Survey: Life Expectancy and Lifestyle Survey}
 
 Thank you for participating in this survey. This survey aims to gather
-insights into the factors influencing life expectancy, including health
-expenditure, education, ethnicity, government spending on healthcare,
-and income levels. Your responses will help us understand individual
-perspectives and experiences towards national policy. Participation is
-voluntary, and your answers will remain anonymous.
+insights into the factors influencing life expectancy, including gender,
+region and income group. Your responses will help us understand
+individual perspectives and experience towards national policy.
+Participation is voluntary, and your answers will remain anonymous.
 
@@
 \item
-  Less than 5\%
-\item
-  5\%--10\%
-\item
-  10\%--20\%
-\item
-  More than 20\%
+  Male
+\item
+  Female
+\item
+  Non-binary
+\item
+  Prefer not to say
 \end{itemize}
 
-\textbf{2.Do you or your household have health insurance coverage?}
+\textbf{2. Age (in years)}
+
+Please write the number: \_\_\_\_\_\_
+
+\textbf{3. Region of Residence}
 
@@
 \item
-  Yes
-\item
-  No
+  Africa
+\item
+  Asia
+\item
+  Europe
+\item
+  North America
+\item
+  South America
+\item
+  Oceania
 \end{itemize}
 
-\textbf{3. How frequently do you visit a healthcare
-professional(eg.doctors, nurse) in a year?}
+\textbf{4. Income Level}
+
+Annual Income (Optional): \_\_\_\_\_\_ USD
+
+Income Group: - Low Income (Less than \$1,000/year) - Lower-Middle
+Income (\$1,001 - \$10,000/year) - Upper-Middle Income (\$10,001 -
+\$50,000/year) - High Income (More than \$50,000/year)
+
+\textbf{Section 2: Health and Lifestyle}
+
+\textbf{5. Current Life Expectancy Perception}
+
+How many years do you expect to live?
+
+Please write the number: \_\_\_\_\_\_
+
+\textbf{6. Healthcare Access}
+
+How often do you visit healthcare professionals - Regularly (e.g.,
+annual checkups) - Occasionally (e.g., only when unwell) - Rarely or
+Never
+
+\textbf{7. Dietary Habits}
+
+How would you describe your diet?
 
@@
 \item
-  0-1 times
-\item
-  2-5 times
-\item
-  6-10 times
-\item
-  More than 10 times
+  Balanced and healthy
+\item
+  Somewhat balanced
+\item
+  Unhealthy
 \end{itemize}
 
-\textbf{Section 2: Education Background}
-
-\textbf{4.What is the highest level of education you have completed?}
-
-\begin{itemize}
-\tightlist
-\item
-  No formal education
-\item
-  Primary school
-\item
-  Secondary school
-\item
-  College or university degree
-\item
-  Postgraduate degree
-\end{itemize}
-
-\textbf{5.How many years of formal schooling have you completed?}
-
-Please write the number: \_\_\_\_\_\_\_
-
-\textbf{Section 3: Ethnicity and Geographic Factors}
-
-\textbf{6.Which of the following best describes your ethnicity?}
-
-\begin{itemize}
-\tightlist
-\item
-  African
-\item
-  Asian
-\item
-  European
-\item
-  Hispanic or Latino
-\item
-  Middle Eastern
-\item
-  Indigenous
-\item
-  Other (please specify): \_\_\_\_\_\_\_
-\end{itemize}
-
-\textbf{7.What's the distance to the nearest healthcare facility from
-your residence?}
-
-\begin{itemize}
-\tightlist
-\item
-  Less than 1 km
-\item
-  1-5 km
-\item
-  More than 5 km
-\end{itemize}
-
-\textbf{Section 4: Government Expenditure on Healthcare}
-
-\textbf{8.Are health services in your country subsidized by the
-govenment?}
-
-\begin{itemize}
-\tightlist
-\item
-  Yes, fully subsidized
-\item
-  Yes, partially subsidized
-\item
-  No
-\end{itemize}
-
-\textbf{9. What is the approximate cost of your most recent healthcare
-visit (in local currency)?}
-
-Please write the amount \_\_\_\_\_\_\_
-
-\textbf{10.Do public healthcare facilities in your area provide all the
-services you need?}
-
-\begin{itemize}
-\tightlist
-\item
-  Yes
-\item
-  No
-\item
-  Not applicable
-\end{itemize}
-
-\textbf{Section 5: Income and Development Factor}
-
-\textbf{11.What is your approximate monthly household income after
-taxes?(in local currency)}
-
-\begin{itemize}
-\tightlist
-\item
-  Less than 1,000
-\item
-  1,000 - 2,999
-\item
-  3,000 - 4,999
-\item
-  5,000 - 7,999
-\item
-  8,000 - 10,999
-\item
-  More than 11,000
-\item
-  Prefer not to say
-\end{itemize}
-
-\textbf{12.How would you describe your current financial situation?}
-
-\begin{itemize}
-\tightlist
-\item
-  Struggling to make ends meet
-\item
-  Just getting by
-\item
-  Comfortable, but not wealthy
-\item
-  Financially secure
-\item
-  Wealthy
-\item
-  Prefer not to say
-\end{itemize}
-
-\textbf{13.How often do you have difficulty affording basic healthcare
-(medical visits, medications, etc.)?}
-
-\begin{itemize}
-\tightlist
-\item
-  Never
-\item
-  Rarely
-\item
-  Sometimes
-\item
-  Often
-\item
-  Always
-\item
-  Prefer not to say
-\end{itemize}
+\textbf{8. Physical Activity}
+
+How many hours of physical activity do you engage in per week? - Less
+than 1 hour - 1-3 hours - More than 3 hours
+
+\textbf{9. Smoking Habits}
+
+Do you smoke? - Yes - No
+
+\textbf{10. Alcohol Consumption}
+
+How often do you consume alcoholic beverages? - Never - Occasionally
+(e.g., social drinking) - Frequently
+
+\textbf{Section 3: Environmental and Social Factors}
+
+\textbf{11.Living Environment}
+
+How would you describe your living area? - Urban - Suburban - Rural
 
@@
 
-\section{Model details}\label{sec-model-details}
+\subsection{Model details}\label{sec-model-details}
+
+The model developed for predicting life expectancy is a linear
+regression model, where the goal is to estimate the outcome variable,
+Life Expectancy, based on multiple predictors: Region, Income Group, and
+Gender. Here's a more detailed breakdown of the components and structure
+of the model:
+
+\textbf{1. Outcome variable (yi)}
+
+The outcome variable \(y_i\) represents the life expectancy of an
+country. This is a continuous variable representing the number of years
+a person is expected to live, assuming all conditions remain constant.
+
+\textbf{2. Linear Predictor (μi)}
+
+The linear predictor \(μ_i\) is a linear combination of the predictors,
+which includes an intercept term \(α\) and the coefficients \(β_1\),
+\(β_2\), \(β_3\), corresponding to Region, Income Group, and Gender,
+respectively. This linear equation models the relationship between life
+expectancy and the predictors
+\(\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)\)
+The values for these coefficients (betas) represent the expected change
+in life expectancy for a one-unit change in each respective predictor.
+
+\textbf{3. Priors}
+
+The prior distribution for the intercept \(α\) and the coefficients
+\(β_1\), \(β_2\), \(β_3\) is assumed to be normal with a mean of 0 and a
+standard deviation of 2.5. This reflects our belief that, prior to
+seeing the data, the intercept and coefficients are most likely close to
+0, with a reasonable range of variability (the scale of 2.5 is
+relatively broad, allowing flexibility in fitting the model).
+
+The prior for \(σ\) (residual standard deviation) is assumed to follow
+an exponential distribution with a rate of 1. This prior reflects the
+assumption that the variance of the residuals (i.e., the deviation of
+the actual observations from the predicted values) is positive and that
+it could reasonably be spread across a wide range of values.
+
+\textbf{4. Residual Standard Deviation (σ)} The model also estimates
+\(σ\), which represents the standard deviation of the residuals --- the
+errors between the observed life expectancy values and those predicted
+by the model. The prior for \(σ\) is assumed to follow an exponential
+distribution with a rate of 1, meaning that smaller values of \(σ\)
+(indicating less variation) are somewhat more likely than larger ones.
+
+\textbf{5. Gaussian Likelihood} The outcome variable Life Expectancy is
+modeled using a normal distribution with mean μi (the linear predictor)
+and standard deviation σ. This means that the residuals (the differences
+between the observed and predicted values) are assumed to be normally
+distributed: \(y_i| \mu_i, \sigma ~ Normal(\mu_i, \sigma)\) This is a
+typical assumption in regression models when the data is continuous, and
+the relationship between the predictors and the outcome is linear.
+
+\subsection{RMSE Full table}\label{rmse-full-table}
 
@@
 analysis}\label{additional-graph-for-analysis}
-
-\subsection{Posterior predictive
-check}\label{posterior-predictive-check}
-
-In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
-predictive check. This shows\ldots{}
-
-In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
-with the prior. This shows\ldots{}
-
-\begin{figure}
-
-\begin{minipage}{0.50\linewidth}
-Examining how the model fits, and is affected by, the
-data\end{minipage}%
-
-\end{figure}%
-
-\subsection{Diagnostics}\label{diagnostics}
-
-\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
-suggests\ldots{}
-
-\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
-suggests\ldots{}
-
-\begin{figure}
-
-\begin{minipage}{0.50\linewidth}
-Checking the convergence of the MCMC algorithm\end{minipage}%
-
-\end{figure}%
 

### 2024-12-04 paper/paper.qmd
commit

@@
 library(kableExtra)
+library(xtable)
 library(ggcorrplot)
@@
 library(caret)
+library(tinytex)
 
@@
 
-shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
+@fig-sum_sta shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
 
@@
 
+```{r}
+#| label: tbl-sum_sta
+#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy.
+With a huge gap between 25 and 50, we could indicate that most of the countries has a life expectancy of.
+There exist large data with low life expectancy less than 25 years.
+"
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+# find average life expectancy for both sex
+bothsexavg <- leab |>
+  filter(Gender == "Both sexes") |>
+  summarise(
+    "Gender" = "Both sexes",
+    "Average life ex" = mean(`Life Expectancy`))
+
+#find average life expectancy of female
+female_tableavg <- female_table |>
+  summarise(
+    "Gender" = "Female",
+    "Average life ex" = mean(`Life Expectancy`))
+
+#find average life expectancy of male
+male_tableavg <- male_table |>
+  summarise(
+    "Gender" = "Male",
+    "Average life ex" = mean(`Life Expectancy`))
+
+#find average life expectancy of Africa
+africaavg <- leab |>
+  filter(Region == "Africa") |>
+  summarise(
+    "Group" = "Africa",
+    "Average life ex" = mean(`Life Expectancy`, na.rm = TRUE)
+  )
+
+##find average life expectancy of Asia
+asiaavg <- leab |>
+  filter(Region == "Asia") |>
+  summarise(
+    "Region" = "Asia",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of North America
+naavg <- leab |>
+  filter(Region == "North America") |>
+  summarise(
+    "Region" = "North America",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of South America
+saavg <- leab |>
+  filter(Region == "South America") |>
+  summarise(
+    "Region" = "South Amereica",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of Oceania
+oceaniaavg <- leab |>
+  filter(Region == "Oceania") |>
+  summarise(
+    "Region" = "Oceania",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of Europe
+europeavg <- leab |>
+  filter(Region == "Europe") |>
+  summarise(
+    "Region" = "Europe",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of lower_income
+lowavg <- leab |>
+  filter(Income_Group == "lower_income") |>
+  summarise(
+    "Income_Group" = "lower_income",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of lower_middle
+middleavg <- leab |>
+  filter(Income_Group == "lower_middle") |>
+  summarise(
+    "Income_Group" = "lower_middle",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of upper_middle
+upperavg <- leab |>
+  filter(Income_Group == "upper_middle") |>
+  summarise(
+    "Income_Group" = "upper_middle",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+#find average life expectancy of high_income
+highavg <- leab |>
+  filter(Income_Group == "high_income") |>
+  summarise(
+    "Income_Group" = "high_income",
+    "Average life ex" = mean(`Life Expectancy`)
+  )
+
+# create a summary statistic by binding all the subtables into one
+sum_sta <- bind_rows(
+  bothsexavg,
+  male_tableavg,
+  female_tableavg,
+  africaavg,
+  asiaavg,
+  naavg,
+  saavg,
+  oceaniaavg,
+  europeavg,
+  lowavg,
+  middleavg,
+  upperavg,
+  highavg
+)
+
+# View the combined summary table
+sum_sta
+
+```
 ## Outcome Variables
@@
 
-# Normalize Life Expectancy to percentages
-life_expectancy_percentage <- lelecleaned_data %>%
-  mutate(
-    LifeExpectancyPercentage = 100 * (`Life Expectancy` - min(`Life Expectancy`, na.rm = TRUE)) / 
-                                  (max(`Life Expectancy`, na.rm = TRUE) - min(`Life Expectancy`, na.rm = TRUE))
-  )
+# Assuming lelecleaned_data is the data frame containing life expectancy
+# Bin Life Expectancy into 5-year ranges
+life_expectancy_bins <- leab %>%
 
-# Plot the distribution
-ggplot(life_expectancy_percentage, aes(x = LifeExpectancyPercentage)) +
-  geom_histogram(
-    bins = 20, 
-    fill = "skyblue", 
-    color = "white", 
-    alpha = 0.8
-  ) +
-  geom_density(
-    aes(y = ..scaled.. * max(..count..)),  # Align density with histogram
-    color = "blue", 
-    size = 1
-  ) +
+  mutate(AgeRange = cut(`Life Expectancy`, 
+                        breaks = seq(floor(min(`Life Expectancy`, na.rm = TRUE)), 
+                                     ceiling(max(`Life Expectancy`, na.rm = TRUE)), 
+                                     by = 5), 
+                        include.lowest = TRUE)) %>%
+  # Calculate the percentage in each age range
+  group_by(AgeRange) %>%
+  summarise(Count = n()) %>%
+  mutate(Percentage = 100 * Count / sum(Count))
+
+# Print the table showing age ranges and percentages
+print(life_expectancy_bins)
+
+# Plot the percentage distribution
+ggplot(life_expectancy_bins, aes(x = AgeRange, y = Percentage, fill = AgeRange)) +
+  geom_bar(stat = "identity", color = "white", alpha = 0.8) +
+  geom_text(aes(label = paste0(round(Percentage, 2), "%")), vjust = -0.5, size = 3.5) +
   labs(
-    title = "Distribution of Life Expectancy as Percentages",
-    x = "Life Expectancy (%)",
-    y = "Count"
+    title = "Distribution of Life Expectancy by Age Range",
+    x = "Life Expectancy (5-Year Ranges)",
+    y = "Percentage"
   ) +
@@
     plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
-    axis.text.x = element_text(angle = 45, hjust = 1)
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = "none"
   )
@@
 # Calculate the average life expectancy per year for males
-male_avg <- male_table %>%
+male_avg <- matable %>%
   group_by(Period) %>%
@@
 # Calculate the average life expectancy per year for females
-female_avg <- female_table %>%
+female_avg <- femaletable %>%
   group_by(Period) %>%
@@
 The table below shows the basic summary of the mean, median, max, standard deviation, variance and sample size of life expectancy.
-We could tell that the average of the life expectancy from the 6 years is 45.9, with a large standard deviation of 26.9.
-The max of the life expectancy is 87.4, among all 6624 rows of data.
-The standard deviation and variance are extremely high because of the range of data is large, in other words, because the mean and median are 45.9 and 37.7, compared to the max 87.4, there is likely some outliers in the data creating such a high standard deviation and variance.
+We could tell that the average of the life expectancy from the 6 years is 72.2, with a relatively small standard deviation of 7.8.
+The max of the life expectancy is 87.4, among all 3312 rows of data.
+The variance is high because of the range of data is large, in other words, because the mean and median are 72.2 and 73.1, compared to the max 87.4, there is likely some outliers in the data creating such a slightly high variance of 60.1.
 
@@
 # Calculate summary statistics
-life_expectancy_stats <- lelecleaned_data %>%
+life_expectancy_stats <- leab %>%
   summarise(
@@
 
-# Create and format the table
+#Create and format the table using kableExtra
 life_expectancy_stats %>%
@@
     caption = "Summary Statistics of Life Expectancy",
-    col.names = c("Mean", "Median","Max", "Standard Deviation", "Variance", "N"),
-    align = "c"
+    col.names = c("Mean", "Median", "Max", "Standard Deviation", "Variance", "N"),
+    align = "c",
+    digits = 2 # Ensure numeric values are rounded to 2 decimal places
   ) %>%
-  kable_styling(full_width = F, bootstrap_options = c("striped", "hover", "condensed"))
+  kable_styling(
+    full_width = FALSE, 
+    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
+    font_size = 14
+  ) %>%
+  column_spec(1, bold = TRUE, color = "white", background = "darkblue") %>% # Highlight the first column
+  column_spec(2:ncol(life_expectancy_stats), color = "black") %>% # Style the data columns
+  row_spec(0, bold = TRUE, background = "lightgray") %>% # Add a header row styling
+  add_header_above(c(" " = 6)) %>% # Add optional grouping header
+  footnote(
+    general = "This table summarizes the key statistics of life expectancy data.",
+    footnote_as_chunk = TRUE, 
+    general_title = "Note:"
+  )
 
@@
 
+```{=tex}
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\
-\alpha &\sim \text{Normal}(0, 2.5) \\
-\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\
-\sigma &\sim \text{Exponential}(1)
+y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \text{(1)} \\
+\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\text{(2)} \\
+\alpha &\sim \text{Normal}(0, 2.5) \text{(3)}\\
+\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \text{(4)}\\
+\sigma &\sim \text{Exponential}(1) \text{(5)} \\
 \end{align}
+```
 
@@
 Lower RMSE values indicate better model performance, suggesting that the model’s predictions are close to the true values.
+@tbl-modelpredict gives out the RMSE of both testing data and training data.
 The generalizability is checked by comparing rmse_test and rmse_train.
@@
 
+Extended versions of the table can be found in @tbl-testpredicted.
+
 ```{r}
 
+#read the model developed
 model_developed <-
@@
 rmse <- sqrt(mean((predictions - actual_values)^2))
-print(paste("RMSE: ", round(rmse, 2)))
 
@@
 train_rmse <- sqrt(mean((train_predictions - train_data$`Life Expectancy`)^2))
-print(paste("Training RMSE: ", round(train_rmse, 2)))
 
-# Compare RMSE results
-if (rmse < train_rmse) {
-  print("The model generalizes well to the test data (out-of-sample).")
-} else {
-  print("The model may be overfitting the training data (higher RMSE on test data).")
-}
+# Create the RMSE table
+rmse_table <- data.frame(
+  Dataset = c("Test Data", "Training Data"),
+  RMSE = c(round(rmse, 2), round(train_rmse, 2))
+)
+
+# Create a styled table with kableExtra
+rmse_table %>%
+  kbl(
+    col.names = c("Dataset", "RMSE"), 
+    caption = "RMSE Comparison for Test and Training Data",
+    align = "c", # Center alignment for columns
+    digits = 2   # Display RMSE values with two decimal places
+  ) %>%
+  kable_styling(
+    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
+    full_width = FALSE,
+    font_size = 14
+  ) %>%
+  column_spec(1, bold = TRUE, color = "white", background = "steelblue") %>%
+  column_spec(2, color = "black") %>%
+  add_header_above(c(" " = 1, "Root Mean Squared Error (RMSE)" = 1))
 
@@
 
-Our results are summarized in @tbl-modelresults. We are primarily interest in the
+Our results are summarized in @tbl-model. We are primarily interest in the
+
+```{r}
+#| label: tbl-model
+#| tbl-cap: Summary of the life expectancy model, which includes gender, region and income group. The table presents the model RSME and out-of sample testing.
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+# Create a model summary with median absolute deviation (mad) for statistics
+modelsummary(
+  list("Gaussian(Normal)" = ledata_normal_model),
+  statistic = "mad",  # Median absolute deviation
+  fmt = 2             # Format results to 2 decimal places
+)
+
+```
+
+## Multiple linear regression results
+
+The
 
@@
 #| eval: true
-#| label: tbl-modelresults
+#| label: tbl-regresult
 #| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
 #| warning: false
-
-#modelsummary::modelsummary(
-  #list(
-    #"developed model" = model_developed
-  #),
-  #statistic = "mad",
-  #fmt = 2
-#)
 ```
-
-## Multiple linear regression results
 
@@
 
-## Insights into different gender
+## Insights into Life Expectancy Differences by Gender
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+Thought the result part we have noticed that female constantly have higher life expectancy than male.
+@fig-gender shows that female has around 4 years higher average age than male.
+Even during the sudden drop of 2020, female kept a more stable trend than male.
+Through literature research, we found that historically women tend to have longer life than men across most regions and cultures.
+[@whymandieyounger]These difference can be attributed to a variety of interconnected reasons.
+Women generally have stronger immune systems and are less prone to certain life-threatening diseases like cardiovascular diseases in early adulthood.
+Estrogen, a hormone prevalent in women, provides some protection against heart disease by improving cholesterol levels.
+On the other hand, men are more prone to risk factors such as hypertension and higher levels of LDL cholesterol, which contribute to shorter life spansehavioral patterns [@behaviouralfactor].
+What's more, male are more likely to engage in behaviours such as smoking, excessive alcohol consumption and hazardous occupations.
+These behaviors increase the risk of accidents, chronic diseases, and early mortality.
+Last but not least, globally, women tend to use healthcare services more frequently than men, which allows for earlier detection and treatment of illnesses.
+Men often delay seeking medical care, worsening outcomes for preventable or manageable diseases.[@womenhigherhealthcare]
 
-## Second discussion point
+## Insights into Life Expectancy Differences by Income Group
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+From the summary and analysis of @tbl-regresult, we have seen that high income group has the significant high life expectancy compared to the lower income group, which indicates that life expectancy is significantly influenced by income groups.
+It is known that income determines access to resources, healthcare and living conditions.
+Difference in life expectancy across income groups reflect broader inequalities in socioeconomic factors and highlight disparities in global health outcomes.
+
+High-income groups have greater access to quality healthcare services, including preventive care, advanced medical treatments, and regular health checkups.Conversely, lower-income groups often face barriers such as cost, lack of infrastructure, and insufficient health insurance coverage, leading to untreated or poorly managed health conditions [@inequalworld].
+Other living conditions like access to nutritious food, safe drinking water and sanitary living environments are also linked with high economics.
+Low-income populations are more likely to experience malnutrition, exposure to environmental toxins, and overcrowded living conditions, all of which negatively impact health and life expectancy.
+
+What's more, lower-income individuals are often exposed to higher levels of chronic stress due to financial instability and job insecurity.
+Stress is linked to adverse health outcomes such as hypertension, cardiovascular diseases, and mental health issues [@incomeinequality].
+Moreover, low-income workers frequently engage in physically demanding or hazardous jobs, increasing their risk of injury and illness.
+All these factors together makes the lower income countries disadvantage in life expectancy.
 
@@
 The life expectancy at 60 means that how long is a person expected to live at 60 instead of at birth.
+From the box plot @fig-lea60, we could tell the high-income group tends to have an average life expectancy of approximately 23 years at age 60, whereas the lower-income group averages around 16 years.
+Notably, the lower-middle-income group exhibits the largest variance, with the most outliers, indicating a wide disparity in life expectancy within this category.
+
+The data also reveal a clear trend: as income levels increase, so does the average life expectancy at age 60.
+This aligns with findings from analyses of life expectancy at birth, emphasizing the significant correlation between income and life expectancy.
+Higher-income groups likely benefit from better access to healthcare, nutrition, and living conditions, which collectively contribute to improved longevity.
+
+Life expectancy at 60 provides insights into the additional years a person can expect to live after reaching 60, reflecting the health and living conditions of older populations.
+Unlike life expectancy at birth, which captures the average years a newborn is expected to live based on current mortality rates across all ages, life expectancy at 60 excludes the impact of child and early-adult mortality.
+This makes it particularly useful for assessing health outcomes, chronic disease management, and the effectiveness of healthcare systems for aging populations.
+It highlights longevity and quality of life in later years, crucial for designing age-focused policies and support systems.
+
+```{r}
+#| label: fig-lea60
+#| fig-cap: "Box plot of life expectancy at 60 by different income group.
+The high income group tend to have 23 years of life expectancy at 60 while the lower income group has an average of 16 years at 60.
+It is noticable that lower middle has the most outlier showing the largest varaiance."
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+# Create a boxplot to show life expectancy by income group
+ggplot(lea60, aes(x = Income_Group, y = `Life Expectancy`, fill = Income_Group)) +
+  geom_boxplot(outlier.color = "red", outlier.shape = 16, outlier.size = 2) +
+  labs(
+    title = "Life Expectancy by Income Group",
+    x = "Income Group",
+    y = "Life Expectancy"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = "none"
+  ) +
+  scale_fill_brewer(palette = "Set3")
+
+```
 
@@
 
-Weaknesses and next steps should also be included.
+### Other factors related to income group and region
+
+Income groups, often categorized as low, middle, or high-income, play a significant role in determining access to resources and opportunities that directly and indirectly affect life expectancy.
+However, income group classifications themselves are shaped by a variety of factors that this analysis may not have accounted for, which introduces limitations to the model.
+Region would be one key factor that influence the income group.
+Regions with limited access to stable employment opportunities may fall into lower-income groups, leading to reduced access to healthcare, education, and nutritious food, all of which affect life expectancy.
+It is reckon that trade imbalances, resource exploitation, and historical colonization have left some countries with weak economies and infrastructure, directly influencing their classification as low or middle-income.
+Since these factors influence the income groups, their absence in the model creates a gap in understanding how income ultimately impacts life expectancy.
+A comprehensive model should explore these underlying determinants of income groups alongside traditional predictors of life expectancy.
+
+### Dataset limitation
+
+Weakness may arise from the generalization of the data.
+When working with data provided by authoritative sources like the World Health Organization (WHO), it’s important to recognize the methodological nuances underlying the calculations.
+In this case, the dataset includes average life expectancy values, which are themselves estimates derived from sophisticated statistical and demographic models.
+The accuracy of the derived averages depends heavily on the statistical methods used by WHO.
+Since the initial dataset offers the average of the life expectancy of each country which are calculated after several factor, these assumptions cascade into our analysis.
+The "average of averages" cannot rectify inaccuracies or gaps in the original model.
+
+By acknowledging these limitations and incorporating appropriate statistical techniques, for further studies, it would be suggested to use a more variety of models such as the multilevel modeling to increase the accuracy of the model by cross validation or comparing the results from other models as well.
+Study deeper into the correlations with more factors we discussed above would let us notice which factors influences life expectancy.
+Like mentioned in the introduction, this analysis aims to empower policymakers by providing critical insights into factors affecting life expectancy across various regions, genders, and income groups.
+By addressing identified limitations and leveraging data-driven strategies, analyses can better capture the complexities of life expectancy data and provide insights that align more closely with real-world dynamics while policymakers can implement targeted interventions to improve healthcare access, reduce disparities, and enhance the overall quality of life for their populations.
 
@@
 
-## Data Cleaning Table
+## Data Cleaning Full Table
 
 ```{r}
-#| label: tbl-cleaned_leab
-#| tbl-cap: "Life expectancy over countries and years"
+#| label: tbl-cleaned_average
+#| tbl-cap: "Full cleaned Average life expectancy"
 #| echo: false
@@
 
-#Show the first 200 lines of the  graph of cleaned table leab
-leab_first_200 <- head(leab, 200)
-
-kable(leab_first_200, 
-      col.names = names(leab), 
-      align = "l", 
-      caption = "Life Expectancy over countries and years (first 200 rows)")
+# Create a nicely formatted kable table
+average_life_expectancy %>%
+  kable(
+    col.names = c("Country", "Gender", "Income Group", "Region", "Average Life Expectancy"),
+    align = c("l", "l", "l", "l", "r"),
+    digits = 2
+  ) %>%
+  kable_styling(
+    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
+    full_width = FALSE,
+    position = "center"
+  ) %>%
+  row_spec(0, bold = TRUE, color = "white", background = "#0073C2") %>% # Style the header row
+  column_spec(5, bold = TRUE, background = "#F7F7F7")
 
@@
 
-Do you smoke? - Yes - No
+Do you smoke?
+
+-   Yes 
+-   No
 
@@
 
-How often do you consume alcoholic beverages? - Never - Occasionally (e.g., social drinking) - Frequently
+How often do you consume alcoholic beverages?
+
+-   Never 
+-   Occasionally (e.g., social drinking) 
+-   Frequently
 
@@
 
-How would you describe your living area? - Urban - Suburban - Rural
+How would you describe your living area?
+
+-   Urban 
+-   Suburban 
+-   Rural
 
@@
 
-## Additional graph for analysis
-
 \newpage

### 2024-12-04 scripts/03-clean_data.R
initial

@@ -361,6 +361,8 @@ write_csv(male_table, "data/02-analysis_data/male_table.csv")
 write_csv(female_table, "data/02-analysis_data/female_table.csv")
 write_csv(leab, "data/02-analysis_data/leab.csv")
 write_csv(sum_sta, "data/02-analysis_data/sum_sta.csv")
+write_csv(matable, "data/02-analysis_data/matable.csv")
+write_csv(femaletable, "data/02-analysis_data/femaletable.csv")
 write_csv(average_life_expectancy, "data/02-analysis_data/average_life_expectancy.csv")
 write_parquet(lelecleaned_data, "data/02-analysis_data/lelecleaned.parquet")
 write_parquet(lea60, "data/02-analysis_data/lea60.parquet")
@@ -368,5 +370,7 @@ write_parquet(leab, "data/02-analysis_data/leab.parquet")
 write_parquet(sum_sta, "data/02-analysis_data/sum_sta.parquet")
 write_parquet(male_table, "data/02-analysis_data/male_table.parquet")
 write_parquet(female_table, "data/02-analysis_data/female_table.parquet")
+write_parquet(matable, "data/02-analysis_data/matable.parquet")
+write_parquet(femaletable, "data/02-analysis_data/femaletable.parquet")
 write_parquet(average_life_expectancy, "data/02-analysis_data/average_life_expectancy.parquet")
 

### 2024-12-04 paper/paper.tex
initial

@@
 \usepackage{xcolor}
+\usepackage{tabularray}
+\usepackage[normalem]{ulem}
+\usepackage{graphicx}
+\UseTblrLibrary{booktabs}
+\UseTblrLibrary{rotating}
+\UseTblrLibrary{siunitx}
+\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
+\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
+\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
 \KOMAoption{captions}{tableheading}
@@
 expectancy at age 60, life expectancy at birth, life expectancy at birth
-of Male and life expectancy at birth of Female.
-
-shows the average of life expectancy under male, female, 6 different
-regions and 4 income groups.
+of Male and life expectancy at birth of Female. For easier summary and
+convenience for graph drawing, we calculate the average of life
+expectancy of each country under 6 years. Also, we calculate the average
+of 6 years life expectancy according to the other 4 income groups and
+different gender by mutate according to the different factors. We then
+merge the columns of each table into a summary table for easy looking.
+
+\textbf{?@fig-sum\_sta} shows the average of life expectancy under male,
+female, 6 different regions and 4 income groups. Life expectancy
+according to different countries have attached and be found in data
+cleaning full data in Section~\ref{sec-appendix}.
 
@@
 \textbf{?@sec-appx}.
+
+\begin{table}
+
+\caption{\label{tbl-sum_sta}}
+
+\centering{
+
+[!h]
+\centering\begingroup\fontsize{10}{12}\selectfont
+
+\begin{tabular}[t]{lc}
+\toprule
+\multicolumn{2}{c}{\textbf{ }} \\
+
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{1}{c}{\textbf{Life Expectancy Summary}} \\
+\cmidrule(l{3pt}r{3pt}){2-2}
+Region/Income/Gender & Life Expectancy\\
+\midrule
+\cellcolor{gray!10}{Global} & \cellcolor{gray!10}{72.13}\\
+Male & 69.71\\
+\cellcolor{gray!10}{Female} & \cellcolor{gray!10}{74.62}\\
+Africa & 64.17\\
+\cellcolor{gray!10}{Asia} & \cellcolor{gray!10}{73.97}\\
+\addlinespace
+North America & 75.04\\
+\cellcolor{gray!10}{South America} & \cellcolor{gray!10}{75.18}\\
+Oceania & 70.17\\
+\cellcolor{gray!10}{Europe} & \cellcolor{gray!10}{78.50}\\
+lower\_income & 62.35\\
+\addlinespace
+\cellcolor{gray!10}{lower\_middle} & \cellcolor{gray!10}{68.40}\\
+upper\_middle & 73.38\\
+\cellcolor{gray!10}{high\_income} & \cellcolor{gray!10}{79.38}\\
+\bottomrule
+\end{tabular}
+\endgroup{}
+
+This table shows the cleaned data of life expectancy at different
+predictor. We could visual that high income has the highest life
+expectancy of 79.8, compared to lower income has the least life
+expectancy of 62.35. Among all the region, it's clear that Africa has
+the least 64.17, while Europe has the highest 78.50 years old. Female
+has slightly higher life expectancy than male.
+
+}
+
+\end{table}%
 
@@
 Figure~\ref{fig-expectancy} visualizes the distribution of life
-expectancy from 2015 to 2020 as percentages, combining a histogram and a
-density plot. A large concentration of observations is observed range of
-0\% to 25\%, reflecting a significant proportion of countries with lower
-life expectancy relative to others in the dataset. Another visible
-concentration is around 75\% to 100\%, indicating a group of countries
-with relatively high life expectancy. The blue density curve overlays
-the histogram, providing a smoothed representation of the distribution.
-Peaks in the curve correspond to high frequency within the histogram.
-The density plot emphasized the bimodal nature of the distribution with
-two distinct peaks: one around 12 as low life expectancy percentages;
-another peak around 87as high life expectancy percentage.
+expectancy from 2015 to 2020 as percentages. The histogram visualizes
+the distribution of life expectancy grouped into 5-year ranges,
+expressed as percentages. Most of the data lies between the ranges of
+66--81 years, with the largest percentage (24.7\%) in the 76--81 range.
+This suggests that a significant portion of individuals have life
+expectancy within this range. The data also shows smaller percentages at
+the lower (46--56 years) and higher ends (81--86 years). Additionally, a
+small percentage of missing (NA) values may highlight areas for data
+quality. Even we remove the NA while cleaning, the data of NA still
+exists for not belongs to any of these ranges.
 
@@
 \caption{\label{fig-expectancy}This histogram shows the distribution of
-the percentage of life expectancy. With a huge gap between 25 and 50, we
-could indicate that most of the countries has a life expectancy of.
-There exist large data with low life expectancy less than 25 years.}
+the percentage of life expectancy for all years. Among all the life
+expectancy ranges, 76-81 has the largest percenage of 24.7\%, while the
+46-51 has the 0.54\%. Life expectancy shows a growing trend with the
+increasing of age and drop sharply comes to the 81-86 range.}
 
@@
 could tell that the average of the life expectancy from the 6 years is
-45.9, with a large standard deviation of 26.9. The max of the life
-expectancy is 87.4, among all 6624 rows of data. The standard deviation
-and variance are extremely high because of the range of data is large,
-in other words, because the mean and median are 45.9 and 37.7, compared
-to the max 87.4, there is likely some outliers in the data creating such
-a high standard deviation and variance.
+72.2, with a relatively small standard deviation of 7.8. The max of the
+life expectancy is 87.4, among all 3312 rows of data. The variance is
+high because of the range of data is large, in other words, because the
+mean and median are 72.2 and 73.1, compared to the max 87.4, there is
+likely some outliers in the data creating such a slightly high variance
+of 60.1.
 
@@
 \centering
-\begin{tabular}[t]{c|c|c|c|c|c}
+\fontsize{14}{16}\selectfont
+\begin{tabular}[t]{>{}c|>{}c|>{}c|>{}c|>{}c|>{}c}
 \hline
-Mean & Median & Max & Standard Deviation & Variance & N\\
+\multicolumn{6}{c}{ } \\
+
+\cellcolor{lightgray}{\textbf{Mean}} & \cellcolor{lightgray}{\textbf{Median}} & \cellcolor{lightgray}{\textbf{Max}} & \cellcolor{lightgray}{\textbf{Standard Deviation}} & \cellcolor{lightgray}{\textbf{Variance}} & \cellcolor{lightgray}{\textbf{N}}\\
 \hline
-45.9 & 37.7 & 87.4 & 26.9 & 724.2 & 6624\\
+\cellcolor{darkblue}{\textcolor{white}{\textbf{72.2}}} & \textcolor{black}{73.1} & \textcolor{black}{87.4} & \textcolor{black}{7.8} & \textcolor{black}{60.1} & \textcolor{black}{3312}\\
 \hline
+\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note:} This table summarizes the key statistics of life expectancy data.}\\
 \end{tabular}
@@
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\
-\alpha &\sim \text{Normal}(0, 2.5) \\
-\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\
-\sigma &\sim \text{Exponential}(1)
+y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \text{(1)} \\
+\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\text{(2)} \\
+\alpha &\sim \text{Normal}(0, 2.5) \text{(3)}\\
+\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \text{(4)}\\
+\sigma &\sim \text{Exponential}(1) \text{(5)} \\
 \end{align}
@@
 performance, suggesting that the model's predictions are close to the
-true values. The generalizability is checked by comparing rmse\_test and
-rmse\_train. Seeing the test RMSE is slightly lower than the training
-RMSE, the model generalizes well.
+true values. Table~\ref{tbl-modelpredict} gives out the RMSE of both
+testing data and training data. The generalizability is checked by
+comparing rmse\_test and rmse\_train. Seeing the test RMSE is slightly
+lower than the training RMSE, the model generalizes well.
 
@@
 
+Extended versions of the table can be found in
+Table~\ref{tbl-testpredicted}.
+
 \begin{Shaded}
 \begin{Highlighting}[]
-\CommentTok{\#model\_developed \textless{}{-}}
-  \CommentTok{\#readRDS(file = "\textasciitilde{}/lifeexpectancy/models/ledata\_normal\_model.rds")}
-
 \CommentTok{\# Split the dataset into training and testing sets (80\% train, 20\% test)}
-\CommentTok{\#set.seed(123)  \# Setting seed for reproducibility}
-\CommentTok{\#train\_index \textless{}{-} createDataPartition(leab$\textasciigrave{}Life Expectancy\textasciigrave{}, p = 0.8, list = FALSE)}
-
-\CommentTok{\#train\_data \textless{}{-} leab[train\_index, ]}
-\CommentTok{\#test\_data \textless{}{-} leab[{-}train\_index, ]}
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)  }\CommentTok{\# Setting seed for reproducibility}
+\NormalTok{train\_index }\OtherTok{\textless{}{-}} \FunctionTok{createDataPartition}\NormalTok{(leab}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Life Expectancy}\StringTok{\textasciigrave{}}\NormalTok{, }\AttributeTok{p =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{list =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{train\_data }\OtherTok{\textless{}{-}}\NormalTok{ leab[train\_index, ]}
+\NormalTok{test\_data }\OtherTok{\textless{}{-}}\NormalTok{ leab[}\SpecialCharTok{{-}}\NormalTok{train\_index, ]}
 
 \CommentTok{\# Predict life expectancy using the test data}
-\CommentTok{\#predictions \textless{}{-} predict(ledata\_normal\_model, newdata = test\_data)}
+\NormalTok{predictions }\OtherTok{\textless{}{-}} \FunctionTok{predict}\NormalTok{(model\_developed, }\AttributeTok{newdata =}\NormalTok{ test\_data)}
 \end{Highlighting}
@@
 
+\begin{table}
+
+\caption{\label{tbl-modelpredict}Summary of the life expectancy model,
+which includes gender, region and income group. The table presents the
+model RSME and out-of sample testing.}
+
+\centering{
+
+\centering
+\caption{RMSE Comparison for Test and Training Data}
+\centering
+\fontsize{14}{16}\selectfont
+\begin{tabular}[t]{>{}c|>{}c}
+\hline
+\multicolumn{1}{c|}{ } & \multicolumn{1}{c}{Root Mean Squared Error (RMSE)} \\
+\cline{2-2}
+Dataset & RMSE\\
+\hline
+\cellcolor{steelblue}{\textcolor{white}{\textbf{Test Data}}} & \textcolor{black}{1.15}\\
+\hline
+\cellcolor{steelblue}{\textcolor{white}{\textbf{Training Data}}} & \textcolor{black}{1.17}\\
+\hline
+\end{tabular}
+
+}
+
+\end{table}%
+
 \section{Results}\label{results}
 
+\subsection{Data results analysis}\label{data-results-analysis}
+
+According to the Table~\ref{tbl-sum_sta}, we could tell that
+
 \subsection{Overview of model results}\label{overview-of-model-results}
 
-Our results are summarized in Table~\ref{tbl-modelresults}. We are
-primarily interest in the
+Our results are summarized in Table~\ref{tbl-model}. We are primarily
+interest in the general life expectancy regarding to the related
+predictors. The multiple linear model provides us with the estimates for
+the intercept and coefficients for the predictors which are male,
+female, both genders, lower income, lower-middle, upper-middle, high
+income, Asia, Europe, Africa, Oceania, North America and South America.
+The intercept represents the estimate of region-standard life expectancy
+when all the predictors are zero. The coefficients represent the
+additional life expectancy associated with each predictor. The model
+results will display the estimates- posterior means or medians for each
+coefficient including the intercept, uncertainty measures- credible
+intervals. The output values of each predictor is the regression
+coefficient, meaning how much the outcome is expected to increase or
+decrease with one unit increase in the life expectancy (per year) of
+that predictor, holding all else constant. The value in the brackets
+represent the Median Absolute Deviation of the posterior distributions
+of the coefficients. It conveys the dispersion around the median of each
+coefficients' posterior distribution, exhibiting how spread the
+distributions are.
+
+Num.Obs represents the number of observations made in the model. R2 is
+the R-squared value which is the proportion of variance in the dependent
+variable that can be explained bu the independent variable. The R2 adj
+is the adjusted R squared which accounts for the number of predictors
+used. Log.lik is the log-likelihood which gives us an idea of the
+likelihood of the data, higher is the better, but this is typically used
+for comparison between the models. ELPD and ELPD s.e. explains the log
+predictive density and its standard error. The ELPD measures the sum of
+the log predictive densities for each observation, used for model
+comparison. LOOIC is an acronym for leave-one-out information criterion
+in which a lower value indicates a model with better out-of-sample
+predictive performance. WAIC stands for Watanabe-Akaike information
+criterion which is another measure of good fit; lower values are better
+fit. RMSE is the room mean squared error measuring the models's
+predictive performance where lower values means more accurate predicts.
+
+\begin{table}
+
+\caption{\label{tbl-model}Summary of the life expectancy model, which
+includes gender, region and income group. The table presents the model
+RSME and out-of sample testing.}
+
+\centering{
+
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]},
+column{1}={halign=l,},
+column{2}={halign=c,},
+hline{390}={1,2}{solid, 0.05em, black},
+}                     %% tabularray inner close
+\toprule
+& Gaussian(Normal) \\ \midrule %% TinyTableHeader
+(Intercept)                                                 & \num{79.53}     \\
+& (\num{43.50})   \\
+RegionAsia                                                  & \num{-6.22}     \\
+& (\num{21.20})   \\
+RegionEurope                                                & \num{-8.39}     \\
+& (\num{45.65})   \\
+RegionNorth America                                         & \num{-5.48}     \\
+& (\num{50.68})   \\
+RegionOceania                                               & \num{-8.43}     \\
+& (\num{80.66})   \\
+RegionSouth America                                         & \num{21.91}     \\
+& (\num{55.21})   \\
+CountryAlbania                                              & \num{0.68}      \\
+& (\num{28.99})   \\
+CountryAlgeria                                              & \num{9.41}      \\
+& (\num{47.74})   \\
+CountryAngola                                               & \num{-4.60}     \\
+& (\num{47.88})   \\
+CountryAntigua and Barbuda                                  & \num{2.12}      \\
+& (\num{31.15})   \\
+CountryArgentina                                            & \num{-28.26}    \\
+& (\num{65.45})   \\
+CountryArmenia                                              & \num{-3.20}     \\
+& (\num{29.08})   \\
+CountryAustralia                                            & \num{17.28}     \\
+& (\num{64.59})   \\
+CountryAustria                                              & \num{7.63}      \\
+& (\num{26.97})   \\
+CountryAzerbaijan                                           & \num{-2.97}     \\
+& (\num{29.29})   \\
+CountryBahamas                                              & \num{-1.15}     \\
+& (\num{31.29})   \\
+CountryBahrain                                              & \num{3.35}      \\
+& (\num{36.83})   \\
+CountryBangladesh                                           & \num{4.23}      \\
+& (\num{54.21})   \\
+CountryBarbados                                             & \num{2.55}      \\
+& (\num{30.97})   \\
+CountryBelarus                                              & \num{-3.11}     \\
+& (\num{29.12})   \\
+CountryBelgium                                              & \num{7.36}      \\
+& (\num{26.87})   \\
+CountryBelize                                               & \num{0.25}      \\
+& (\num{30.40})   \\
+CountryBenin                                                & \num{-3.17}     \\
+& (\num{48.20})   \\
+CountryBhutan                                               & \num{4.36}      \\
+& (\num{54.23})   \\
+CountryBolivia (Plurinational State of)                     & \num{-24.08}    \\
+& (\num{76.01})   \\
+CountryBosnia and Herzegovina                               & \num{-0.20}     \\
+& (\num{29.18})   \\
+CountryBotswana                                             & \num{-19.85}    \\
+& (\num{51.26})   \\
+CountryBrazil                                               & \num{-30.04}    \\
+& (\num{65.42})   \\
+CountryBrunei Darussalam                                    & \num{4.00}      \\
+& (\num{36.91})   \\
+CountryBulgaria                                             & \num{-2.45}     \\
+& (\num{29.09})   \\
+CountryBurkina Faso                                         & \num{-5.08}     \\
+& (\num{21.33})   \\
+CountryBurundi                                              & \num{-3.23}     \\
+& (\num{21.40})   \\
+CountryCabo Verde                                           & \num{7.65}      \\
+& (\num{47.94})   \\
+CountryCambodia                                             & \num{-0.02}     \\
+& (\num{54.13})   \\
+CountryCameroon                                             & \num{-5.86}     \\
+& (\num{48.02})   \\
+CountryCanada                                               & \num{7.86}      \\
+& (\num{30.96})   \\
+CountryCentral African Republic                             & \num{-14.92}    \\
+& (\num{21.25})   \\
+CountryChad                                                 & \num{-8.32}     \\
+& (\num{21.18})   \\
+CountryChile                                                & \num{-24.65}    \\
+& (\num{56.84})   \\
+CountryChina                                                & \num{-4.35}     \\
+& (\num{51.31})   \\
+CountryColombia                                             & \num{-27.30}    \\
+& (\num{65.38})   \\
+CountryComoros                                              & \num{1.26}      \\
+& (\num{48.11})   \\
+CountryCongo                                                & \num{-3.93}     \\
+& (\num{48.00})   \\
+CountryCosta Rica                                           & \num{5.85}      \\
+& (\num{30.49})   \\
+CountryCote d'Ivoire                                        & \num{-4.15}     \\
+& (\num{48.20})   \\
+CountryCroatia                                              & \num{4.47}      \\
+& (\num{26.98})   \\
+CountryCuba                                                 & \num{3.41}      \\
+& (\num{30.53})   \\
+CountryCyprus                                               & \num{8.31}      \\
+& (\num{26.83})   \\
+CountryCzechia                                              & \num{5.01}      \\
+& (\num{27.04})   \\
+CountryDemocratic People's Republic of Korea                & \num{11.23}     \\
+& (\num{0.48})    \\
+CountryDemocratic Republic of the Congo                     & \num{-5.91}     \\
+& (\num{21.28})   \\
+CountryDenmark                                              & \num{7.40}      \\
+& (\num{26.95})   \\
+CountryDjibouti                                             & \num{-1.98}     \\
+& (\num{47.97})   \\
+CountryDominican Republic                                   & \num{-0.78}     \\
+& (\num{30.48})   \\
+CountryEcuador                                              & \num{-28.26}    \\
+& (\num{65.51})   \\
+CountryEgypt                                                & \num{4.21}      \\
+& (\num{47.84})   \\
+CountryEl Salvador                                          & \num{-0.99}     \\
+& (\num{30.48})   \\
+CountryEquatorial Guinea                                    & \num{-22.60}    \\
+& (\num{51.41})   \\
+CountryEritrea                                              & \num{-3.74}     \\
+& (\num{21.28})   \\
+CountryEstonia                                              & \num{4.46}      \\
+& (\num{26.91})   \\
+CountryEswatini                                             & \num{-12.28}    \\
+& (\num{48.03})   \\
+CountryEthiopia                                             & \num{1.13}      \\
+& (\num{21.26})   \\
+CountryFiji                                                 & \num{-0.68}     \\
+& (\num{71.02})   \\
+CountryFinland                                              & \num{7.61}      \\
+& (\num{27.08})   \\
+CountryFrance                                               & \num{8.48}      \\
+& (\num{26.98})   \\
+CountryGabon                                                & \num{-19.19}    \\
+& (\num{51.46})   \\
+CountryGambia                                               & \num{-2.56}     \\
+& (\num{21.32})   \\
+CountryGeorgia                                              & \num{-3.87}     \\
+& (\num{29.20})   \\
+CountryGermany                                              & \num{7.02}      \\
+& (\num{27.00})   \\
+CountryGhana                                                & \num{-1.35}     \\
+& (\num{47.86})   \\
+CountryGreece                                               & \num{7.16}      \\
+& (\num{26.98})   \\
+CountryGrenada                                              & \num{-1.25}     \\
+& (\num{30.43})   \\
+CountryGuatemala                                            & \num{-2.17}     \\
+& (\num{30.39})   \\
+CountryGuinea                                               & \num{-6.20}     \\
+& (\num{47.88})   \\
+CountryGuinea-Bissau                                        & \num{-8.80}     \\
+& (\num{21.23})   \\
+CountryGuyana                                               & \num{-37.07}    \\
+& (\num{56.78})   \\
+CountryHaiti                                                & \num{-1.41}     \\
+& (\num{33.25})   \\
+CountryHonduras                                             & \num{6.26}      \\
+& (\num{33.17})   \\
+CountryHungary                                              & \num{2.27}      \\
+& (\num{27.02})   \\
+CountryIceland                                              & \num{8.69}      \\
+& (\num{26.93})   \\
+CountryIndia                                                & \num{1.11}      \\
+& (\num{54.41})   \\
+CountryIndonesia                                            & \num{-10.63}    \\
+& (\num{51.36})   \\
+CountryIran (Islamic Republic of)                           & \num{7.86}      \\
+& (\num{54.06})   \\
+CountryIraq                                                 & \num{-9.81}     \\
+& (\num{51.25})   \\
+CountryIreland                                              & \num{8.03}      \\
+& (\num{26.93})   \\
+CountryIsrael                                               & \num{9.91}      \\
+& (\num{36.89})   \\
+CountryItaly                                                & \num{8.81}      \\
+& (\num{26.91})   \\
+CountryJamaica                                              & \num{-1.99}     \\
+& (\num{30.43})   \\
+CountryJapan                                                & \num{11.94}     \\
+& (\num{36.88})   \\
+CountryJordan                                               & \num{9.67}      \\
+& (\num{54.24})   \\
+CountryKazakhstan                                           & \num{-4.71}     \\
+& (\num{29.26})   \\
+CountryKenya                                                & \num{-0.86}     \\
+& (\num{47.87})   \\
+CountryKiribati                                             & \num{4.08}      \\
+& (\num{61.70})   \\
+CountryKuwait                                               & \num{9.87}      \\
+& (\num{36.84})   \\
+CountryKyrgyzstan                                           & \num{3.47}      \\
+& (\num{54.41})   \\
+CountryLao People's Democratic Republic                     & \num{-1.48}     \\
+& (\num{54.13})   \\
+CountryLatvia                                               & \num{1.45}      \\
+& (\num{26.95})   \\
+CountryLebanon                                              & \num{9.14}      \\
+& (\num{54.11})   \\
+CountryLesotho                                              & \num{-15.82}    \\
+& (\num{48.08})   \\
+CountryLiberia                                              & \num{-4.50}     \\
+& (\num{21.35})   \\
+CountryLibya                                                & \num{-10.87}    \\
+& (\num{51.31})   \\
+CountryLithuania                                            & \num{1.52}      \\
+& (\num{27.02})   \\
+CountryLuxembourg                                           & \num{9.05}      \\
+& (\num{26.98})   \\
+CountryMadagascar                                           & \num{-3.54}     \\
+& (\num{21.21})   \\
+CountryMalawi                                               & \num{-4.38}     \\
+& (\num{21.25})   \\
+CountryMalaysia                                             & \num{-6.51}     \\
+& (\num{51.20})   \\
+CountryMaldives                                             & \num{-4.14}     \\
+& (\num{51.20})   \\
+CountryMali                                                 & \num{-6.00}     \\
+& (\num{21.21})   \\
+CountryMalta                                                & \num{8.28}      \\
+& (\num{26.88})   \\
+CountryMauritania                                           & \num{2.98}      \\
+& (\num{47.95})   \\
+CountryMauritius                                            & \num{-9.94}     \\
+& (\num{51.30})   \\
+CountryMexico                                               & \num{0.67}      \\
+& (\num{30.33})   \\
+CountryMicronesia (Federated States of)                     & \num{8.09}      \\
+& (\num{61.64})   \\
+CountryMongolia                                             & \num{1.06}      \\
+& (\num{54.16})   \\
+CountryMontenegro                                           & \num{-0.28}     \\
+& (\num{29.22})   \\
+CountryMorocco                                              & \num{6.69}      \\
+& (\num{48.03})   \\
+CountryMozambique                                           & \num{-9.56}     \\
+& (\num{21.26})   \\
+CountryMyanmar                                              & \num{-0.94}     \\
+& (\num{54.36})   \\
+CountryNamibia                                              & \num{-21.00}    \\
+& (\num{51.42})   \\
+CountryNepal                                                & \num{1.41}      \\
+& (\num{54.14})   \\
+CountryNetherlands (Kingdom of the)                         & \num{8.02}      \\
+& (\num{27.04})   \\
+CountryNew Zealand                                          & \num{16.32}     \\
+& (\num{64.57})   \\
+CountryNicaragua                                            & \num{13.32}     \\
+& (\num{33.40})   \\
+CountryNiger                                                & \num{-6.88}     \\
+& (\num{21.20})   \\
+CountryNigeria                                              & \num{-4.28}     \\
+& (\num{48.05})   \\
+CountryNorth Macedonia                                      & \num{-1.40}     \\
+& (\num{29.34})   \\
+CountryNorway                                               & \num{8.78}      \\
+& (\num{26.93})   \\
+CountryOman                                                 & \num{2.38}      \\
+& (\num{36.87})   \\
+CountryPakistan                                             & \num{-3.13}     \\
+& (\num{54.28})   \\
+CountryPanama                                               & \num{4.48}      \\
+& (\num{31.13})   \\
+CountryPapua New Guinea                                     & \num{8.94}      \\
+& (\num{61.59})   \\
+CountryParaguay                                             & \num{-29.48}    \\
+& (\num{65.36})   \\
+CountryPeru                                                 & \num{-26.42}    \\
+& (\num{65.46})   \\
+CountryPhilippines                                          & \num{0.30}      \\
+& (\num{54.15})   \\
+CountryPoland                                               & \num{3.67}      \\
+& (\num{27.01})   \\
+CountryPortugal                                             & \num{7.36}      \\
+& (\num{27.07})   \\
+CountryPuerto Rico                                          & \num{6.28}      \\
+& (\num{31.19})   \\
+CountryQatar                                                & \num{5.93}      \\
+& (\num{36.80})   \\
+CountryRepublic of Korea                                    & \num{10.61}     \\
+& (\num{36.81})   \\
+CountryRepublic of Moldova                                  & \num{-4.72}     \\
+& (\num{29.13})   \\
+CountryRomania                                              & \num{1.39}      \\
+& (\num{26.96})   \\
+CountryRussian Federation                                   & \num{-9.31}     \\
+& (\num{51.36})   \\
+CountryRwanda                                               & \num{0.44}      \\
+& (\num{21.29})   \\
+CountrySaint Lucia                                          & \num{1.72}      \\
+& (\num{30.45})   \\
+CountrySaint Vincent and the Grenadines                     & \num{-1.25}     \\
+& (\num{30.38})   \\
+CountrySamoa                                                & \num{12.64}     \\
+& (\num{61.59})   \\
+CountrySao Tome and Principe                                & \num{4.58}      \\
+& (\num{47.96})   \\
+CountrySaudi Arabia                                         & \num{4.35}      \\
+& (\num{36.87})   \\
+CountrySenegal                                              & \num{1.47}      \\
+& (\num{48.01})   \\
+CountrySerbia                                               & \num{-1.59}     \\
+& (\num{29.20})   \\
+CountrySeychelles                                           & \num{-5.53}     \\
+& (\num{43.56})   \\
+CountrySierra Leone                                         & \num{-7.75}     \\
+& (\num{21.34})   \\
+CountrySingapore                                            & \num{10.98}     \\
+& (\num{36.89})   \\
+CountrySlovakia                                             & \num{3.40}      \\
+& (\num{27.00})   \\
+CountrySlovenia                                             & \num{7.13}      \\
+& (\num{27.00})   \\
+CountrySolomon Islands                                      & \num{7.87}      \\
+& (\num{61.68})   \\
+CountrySomalia                                              & \num{-12.52}    \\
+& (\num{21.30})   \\
+CountrySouth Africa                                         & \num{-19.37}    \\
+& (\num{51.43})   \\
+CountrySouth Sudan                                          & \num{-8.01}     \\
+& (\num{21.29})   \\
+CountrySpain                                                & \num{8.85}      \\
+& (\num{27.13})   \\
+CountrySri Lanka                                            & \num{7.99}      \\
+& (\num{54.25})   \\
+CountrySudan                                                & \num{1.81}      \\
+& (\num{21.31})   \\
+CountrySuriname                                             & \num{-31.76}    \\
+& (\num{65.41})   \\
+CountrySweden                                               & \num{8.42}      \\
+& (\num{26.97})   \\
+CountrySwitzerland                                          & \num{9.33}      \\
+& (\num{27.01})   \\
+CountrySyrian Arab Republic                                 & \num{3.97}      \\
+& (\num{0.40})    \\
+CountryTajikistan                                           & \num{3.09}      \\
+& (\num{53.97})   \\
+CountryThailand                                             & \num{-4.50}     \\
+& (\num{51.28})   \\
+CountryTimor-Leste                                          & \num{-0.90}     \\
+& (\num{54.22})   \\
+CountryTogo                                                 & \num{-4.19}     \\
+& (\num{21.21})   \\
+CountryTonga                                                & \num{4.42}      \\
+& (\num{71.06})   \\
+CountryTrinidad and Tobago                                  & \num{0.20}      \\
+& (\num{31.16})   \\
+CountryTunisia                                              & \num{10.40}     \\
+& (\num{47.95})   \\
+CountryTürkiye                                              & \num{-4.47}     \\
+& (\num{51.31})   \\
+CountryTurkmenistan                                         & \num{-12.58}    \\
+& (\num{51.24})   \\
+CountryUganda                                               & \num{-1.74}     \\
+& (\num{21.23})   \\
+CountryUkraine                                              & \num{6.68}      \\
+& (\num{36.36})   \\
+CountryUnited Arab Emirates                                 & \num{8.68}      \\
+& (\num{36.79})   \\
+CountryUnited Kingdom of Great Britain and Northern Ireland & \num{7.08}      \\
+& (\num{27.10})   \\
+CountryUnited Republic of Tanzania                          & \num{-0.45}     \\
+& (\num{47.88})   \\
+CountryUnited States of America                             & \num{4.57}      \\
+& (\num{31.22})   \\
+CountryUruguay                                              & \num{-27.80}    \\
+& (\num{56.83})   \\
+CountryUzbekistan                                           & \num{1.65}      \\
+& (\num{54.36})   \\
+CountryVanuatu                                              & \num{9.66}      \\
+& (\num{61.72})   \\
+CountryVenezuela (Bolivarian Republic of)                   & \num{-31.90}    \\
+& (\num{65.65})   \\
+CountryViet Nam                                             & \num{3.94}      \\
+& (\num{53.92})   \\
+CountryYemen                                                & \num{6.61}      \\
+& (\num{0.40})    \\
+CountryZambia                                               & \num{-5.46}     \\
+& (\num{47.98})   \\
+CountryZimbabwe                                             & \num{-8.25}     \\
+& (\num{48.08})   \\
+Income\_Grouplower\_income                                & \num{-12.06}    \\
+& (\num{36.90})   \\
+Income\_Grouplower\_middle                                & \num{-4.04}     \\
+& (\num{23.94})   \\
+Income\_Groupupper\_middle                                & \num{3.40}      \\
+& (\num{20.47})   \\
+GenderFemale                                                & \num{2.50}      \\
+& (\num{0.05})    \\
+GenderMale                                                  & \num{-2.42}     \\
+& (\num{0.05})    \\
+Num.Obs.                                                    & \num{3312}      \\
+R2                                                          & \num{0.976}     \\
+R2 Adj.                                                     & \num{0.975}     \\
+Log.Lik.                                                    & \num{-5231.038} \\
+ELPD                                                        & \num{-5409.7}   \\
+ELPD s.e.                                                   & \num{94.5}      \\
+LOOIC                                                       & \num{10819.4}   \\
+LOOIC s.e.                                                  & \num{189.0}     \\
+WAIC                                                        & \num{10816.6}   \\
+RMSE                                                        & \num{4.37}      \\
+\bottomrule
+\end{tblr}
+
+}
+
+\end{table}%
 
@@
 
+Table~\ref{tbl-model} is thye table of the results from out model.
+
 \section{Discussion}\label{discussion}
 
-\subsection{Insights into different
-gender}\label{insights-into-different-gender}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The
-discussion is a chance to show off what you know and what you learnt
-from all this.
-
-\subsection{Second discussion point}\label{second-discussion-point}
-
-Please don't use these as sub-heading labels - change them to be what
-your point actually is.
+\subsection{Insights into Life Expectancy Differences by
+Gender}\label{insights-into-life-expectancy-differences-by-gender}
+
+Thought the result part we have noticed that female constantly have
+higher life expectancy than male. Figure~\ref{fig-gender} shows that
+female has around 4 years higher average age than male. Even during the
+sudden drop of 2020, female kept a more stable trend than male. Through
+literature research, we found that historically women tend to have
+longer life than men across most regions and cultures.
+(\textbf{whymandieyounger?})These difference can be attributed to a
+variety of interconnected reasons. Women generally have stronger immune
+systems and are less prone to certain life-threatening diseases like
+cardiovascular diseases in early adulthood. Estrogen, a hormone
+prevalent in women, provides some protection against heart disease by
+improving cholesterol levels. On the other hand, men are more prone to
+risk factors such as hypertension and higher levels of LDL cholesterol,
+which contribute to shorter life spansehavioral patterns
+(\textbf{behaviouralfactor?}). What's more, male are more likely to
+engage in behaviours such as smoking, excessive alcohol consumption and
+hazardous occupations. These behaviors increase the risk of accidents,
+chronic diseases, and early mortality. Last but not least, globally,
+women tend to use healthcare services more frequently than men, which
+allows for earlier detection and treatment of illnesses. Men often delay
+seeking medical care, worsening outcomes for preventable or manageable
+diseases.(\textbf{womenhigherhealthcare?})
+
+\subsection{Insights into Life Expectancy Differences by Income
+Group}\label{insights-into-life-expectancy-differences-by-income-group}
+
+From the summary and analysis of \textbf{?@tbl-regresult}, we have seen
+that high income group has the significant high life expectancy compared
+to the lower income group, which indicates that life expectancy is
+significantly influenced by income groups. It is known that income
+determines access to resources, healthcare and living conditions.
+Difference in life expectancy across income groups reflect broader
+inequalities in socioeconomic factors and highlight disparities in
+global health outcomes.
+
+High-income groups have greater access to quality healthcare services,
+including preventive care, advanced medical treatments, and regular
+health checkups.Conversely, lower-income groups often face barriers such
+as cost, lack of infrastructure, and insufficient health insurance
+coverage, leading to untreated or poorly managed health conditions
+(\textbf{inequalworld?}). Other living conditions like access to
+nutritious food, safe drinking water and sanitary living environments
+are also linked with high economics. Low-income populations are more
+likely to experience malnutrition, exposure to environmental toxins, and
+overcrowded living conditions, all of which negatively impact health and
+life expectancy.
+
+What's more, lower-income individuals are often exposed to higher levels
+of chronic stress due to financial instability and job insecurity.
+Stress is linked to adverse health outcomes such as hypertension,
+cardiovascular diseases, and mental health issues
+(\textbf{incomeinequality?}). Moreover, low-income workers frequently
+engage in physically demanding or hazardous jobs, increasing their risk
+of injury and illness. All these factors together makes the lower income
+countries disadvantage in life expectancy.
 
@@
 The life expectancy at 60 means that how long is a person expected to
-live at 60 instead of at birth.
+live at 60 instead of at birth. From the box plot
+Figure~\ref{fig-lea60}, we could tell the high-income group tends to
+have an average life expectancy of approximately 23 years at age 60,
+whereas the lower-income group averages around 16 years. Notably, the
+lower-middle-income group exhibits the largest variance, with the most
+outliers, indicating a wide disparity in life expectancy within this
+category.
+
+The data also reveal a clear trend: as income levels increase, so does
+the average life expectancy at age 60. This aligns with findings from
+analyses of life expectancy at birth, emphasizing the significant
+correlation between income and life expectancy. Higher-income groups
+likely benefit from better access to healthcare, nutrition, and living
+conditions, which collectively contribute to improved longevity.
+
+Life expectancy at 60 provides insights into the additional years a
+person can expect to live after reaching 60, reflecting the health and
+living conditions of older populations. Unlike life expectancy at birth,
+which captures the average years a newborn is expected to live based on
+current mortality rates across all ages, life expectancy at 60 excludes
+the impact of child and early-adult mortality. This makes it
+particularly useful for assessing health outcomes, chronic disease
+management, and the effectiveness of healthcare systems for aging
+populations. It highlights longevity and quality of life in later years,
+crucial for designing age-focused policies and support systems.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-lea60-1.pdf}
+
+}
+
+\caption{\label{fig-lea60}Box plot of life expectancy at 60 by different
+income group. The high income group tend to have 23 years of life
+expectancy at 60 while the lower income group has an average of 16 years
+at 60. It is noticable that lower middle has the most outlier showing
+the largest varaiance.}
+
+\end{figure}%
 
@@
 
-Weaknesses and next steps should also be included.
+\subsubsection{Other factors related to income group and
+region}\label{other-factors-related-to-income-group-and-region}
+
+Income groups, often categorized as low, middle, or high-income, play a
+significant role in determining access to resources and opportunities
+that directly and indirectly affect life expectancy. However, income
+group classifications themselves are shaped by a variety of factors that
+this analysis may not have accounted for, which introduces limitations
+to the model. Region would be one key factor that influence the income
+group. Regions with limited access to stable employment opportunities
+may fall into lower-income groups, leading to reduced access to
+healthcare, education, and nutritious food, all of which affect life
+expectancy. It is reckon that trade imbalances, resource exploitation,
+and historical colonization have left some countries with weak economies
+and infrastructure, directly influencing their classification as low or
+middle-income. Since these factors influence the income groups, their
+absence in the model creates a gap in understanding how income
+ultimately impacts life expectancy. A comprehensive model should explore
+these underlying determinants of income groups alongside traditional
+predictors of life expectancy.
+
+\subsubsection{Dataset limitation}\label{dataset-limitation}
+
+Weakness may arise from the generalization of the data. When working
+with data provided by authoritative sources like the World Health
+Organization (WHO), it's important to recognize the methodological
+nuances underlying the calculations. In this case, the dataset includes
+average life expectancy values, which are themselves estimates derived
+from sophisticated statistical and demographic models. The accuracy of
+the derived averages depends heavily on the statistical methods used by
+WHO. Since the initial dataset offers the average of the life expectancy
+of each country which are calculated after several factor, these
+assumptions cascade into our analysis. The ``average of averages''
+cannot rectify inaccuracies or gaps in the original model.
+
+By acknowledging these limitations and incorporating appropriate
+statistical techniques, for further studies, it would be suggested to
+use a more variety of models such as the multilevel modeling to increase
+the accuracy of the model by cross validation or comparing the results
+from other models as well. Study deeper into the correlations with more
+factors we discussed above would let us notice which factors influences
+life expectancy. Like mentioned in the introduction, this analysis aims
+to empower policymakers by providing critical insights into factors
+affecting life expectancy across various regions, genders, and income
+groups. By addressing identified limitations and leveraging data-driven
+strategies, analyses can better capture the complexities of life
+expectancy data and provide insights that align more closely with
+real-world dynamics while policymakers can implement targeted
+interventions to improve healthcare access, reduce disparities, and
+enhance the overall quality of life for their populations.
 
@@
 
-\subsection{Data Cleaning Table}\label{data-cleaning-table}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2895}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1754}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0614}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0965}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1404}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1140}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1228}}@{}}
-
-\caption{\label{tbl-cleaned_leab}Life expectancy over countries and
-years}
+\subsection{Data Cleaning Full Table}\label{data-cleaning-full-table}
+
+\begin{longtable}[t]{llll>{}r}
+
+\caption{\label{tbl-cleaned_average}Full cleaned Average life
+expectancy}
 
@@
 
-\caption{Life Expectancy over countries and years (first 200
-rows)}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Indicator
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Country
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Period
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Gender
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Life Expectancy
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Income\_Group
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Region
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Indicator
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Country
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Period
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Gender
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Life Expectancy
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Income\_Group
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Region
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Life expectancy at birth (years) & Afghanistan & 2020 & Male & 59.3 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2020 & Both sexes &
-60.5 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2020 & Female & 61.7 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2019 & Male & 60.0 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2019 & Both sexes &
-61.2 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2019 & Female & 62.5 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2018 & Male & 59.0 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2018 & Both sexes &
-60.5 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2018 & Female & 62.1 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2017 & Male & 59.8 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2017 & Both sexes &
-60.9 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2017 & Female & 62.1 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2016 & Male & 59.2 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2016 & Both sexes &
-60.4 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2016 & Female & 61.7 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2015 & Male & 59.3 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2015 & Both sexes &
-60.3 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2015 & Female & 61.5 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Albania & 2020 & Male & 74.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2020 & Both sexes & 76.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2020 & Female & 79.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2019 & Male & 76.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2019 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2019 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2018 & Male & 76.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2018 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2018 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2017 & Male & 76.1 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2017 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2017 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2016 & Male & 76.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2016 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2016 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2015 & Male & 76.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2015 & Both sexes & 77.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2015 & Female & 79.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Algeria & 2020 & Male & 73.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2020 & Both sexes & 74.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2020 & Female & 75.2 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2019 & Male & 76.2 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2019 & Both sexes & 76.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2019 & Female & 77.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2018 & Male & 76.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2018 & Both sexes & 76.4 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2018 & Female & 77.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2017 & Male & 76.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2017 & Both sexes & 76.4 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2017 & Female & 77.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2016 & Male & 75.9 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2016 & Both sexes & 76.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2016 & Female & 76.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2015 & Male & 75.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2015 & Both sexes & 76.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2015 & Female & 76.6 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2020 & Male & 60.4 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2020 & Both sexes & 62.6 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2020 & Female & 64.9 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2019 & Male & 60.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2019 & Both sexes & 62.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2019 & Female & 64.7 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2018 & Male & 60.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2018 & Both sexes & 62.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2018 & Female & 64.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2017 & Male & 59.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2017 & Both sexes & 62.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2017 & Female & 64.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2016 & Male & 59.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2016 & Both sexes & 61.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2016 & Female & 64.2 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2015 & Male & 59.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2015 & Both sexes & 61.6 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2015 & Female & 64.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Male &
-75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Both
-sexes & 77.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Female &
-79.4 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Male &
-74.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Both
-sexes & 75.7 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Female &
-77.1 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Male &
-74.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Both
-sexes & 75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Female &
-77.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Male &
-73.9 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Both
-sexes & 75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Female &
-77.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Male &
-73.8 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Both
-sexes & 75.5 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Female &
-77.1 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Male &
-73.8 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Both
-sexes & 75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Female &
-77.2 & high\_income & North America \\
-Life expectancy at birth (years) & Argentina & 2020 & Male & 73.1 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2020 & Both sexes & 76.2
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2020 & Female & 79.4 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2019 & Male & 74.0 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2019 & Both sexes & 77.0
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2019 & Female & 79.9 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2018 & Male & 73.7 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2018 & Both sexes & 76.9
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2018 & Female & 79.9 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2017 & Male & 73.6 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2017 & Both sexes & 76.6
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2017 & Female & 79.6 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2016 & Male & 73.0 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2016 & Both sexes & 76.1
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2016 & Female & 79.2 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2015 & Male & 73.3 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2015 & Both sexes & 76.5
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2015 & Female & 79.6 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Armenia & 2020 & Male & 62.7 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2020 & Both sexes & 69.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2020 & Female & 76.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2019 & Male & 70.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2019 & Both sexes & 75.7 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2019 & Female & 79.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2018 & Male & 71.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2018 & Both sexes & 75.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2018 & Female & 79.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2017 & Male & 70.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2017 & Both sexes & 75.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2017 & Female & 79.1 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2016 & Male & 69.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2016 & Both sexes & 74.4 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2016 & Female & 78.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2015 & Male & 69.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2015 & Both sexes & 74.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2015 & Female & 78.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Australia & 2020 & Male & 81.5 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2020 & Both sexes & 83.4
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2020 & Female & 85.2 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2019 & Male & 80.7 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2019 & Both sexes & 82.6
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2019 & Female & 84.6 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2018 & Male & 81.2 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2018 & Both sexes & 83.0
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2018 & Female & 84.9 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2017 & Male & 80.8 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2017 & Both sexes & 82.7
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2017 & Female & 84.5 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2016 & Male & 80.7 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2016 & Both sexes & 82.6
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2016 & Female & 84.5 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2015 & Male & 80.4 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2015 & Both sexes & 82.3
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2015 & Female & 84.2 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Austria & 2020 & Male & 78.8 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2020 & Both sexes & 81.1 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2020 & Female & 83.3 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2019 & Male & 79.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2019 & Both sexes & 81.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2019 & Female & 83.8 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2018 & Male & 79.2 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2018 & Both sexes & 81.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2018 & Female & 83.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2017 & Male & 79.2 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2017 & Both sexes & 81.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2017 & Female & 83.5 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2016 & Male & 79.1 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2016 & Both sexes & 81.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2016 & Female & 83.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2015 & Male & 78.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2015 & Both sexes & 81.0 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2015 & Female & 83.3 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2020 & Male & 67.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2020 & Both sexes & 71.4
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2020 & Female & 75.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2019 & Male & 73.4 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2019 & Both sexes & 75.8
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2019 & Female & 78.1 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2018 & Male & 72.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2018 & Both sexes & 75.1
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2018 & Female & 77.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2017 & Male & 72.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2017 & Both sexes & 74.6
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2017 & Female & 76.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2016 & Male & 71.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2016 & Both sexes & 74.0
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2016 & Female & 76.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2015 & Male & 71.7 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2015 & Both sexes & 73.6
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2015 & Female & 75.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Bahamas & 2020 & Male & 69.2 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2020 & Both sexes & 72.6 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2020 & Female & 76.0 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2019 & Male & 68.1 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2019 & Both sexes & 70.7 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2019 & Female & 73.3 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2018 & Male & 70.2 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2018 & Both sexes & 73.4 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2018 & Female & 76.5 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2017 & Male & 70.0 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2017 & Both sexes & 73.2 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2017 & Female & 76.3 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2016 & Male & 69.7 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2016 & Both sexes & 72.9 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2016 & Female & 76.1 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2015 & Male & 69.8 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2015 & Both sexes & 72.9 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2015 & Female & 76.0 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahrain & 2020 & Male & 73.6 &
-high\_income & Asia \\
-Life expectancy at birth (years) & Bahrain & 2020 & Both sexes & 74.9 &
-high\_income & Asia \\
+\toprule
+\cellcolor[HTML]{0073C2}{\textcolor{white}{\textbf{Country}}} & \cellcolor[HTML]{0073C2}{\textcolor{white}{\textbf{Gender}}} & \cellcolor[HTML]{0073C2}{\textcolor{white}{\textbf{Income Group}}} & \cellcolor[HTML]{0073C2}{\textcolor{white}{\textbf{Region}}} & \cellcolor[HTML]{0073C2}{\textcolor{white}{\textbf{Average Life Expectancy}}}\\
+\midrule
+Afghanistan & Both sexes & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{60.63}}\\
+Afghanistan & Female & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{61.93}}\\
+Afghanistan & Male & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{59.43}}\\
+Albania & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{77.65}}\\
+Albania & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.70}}\\
+\addlinespace
+Albania & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.80}}\\
+Algeria & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{75.95}}\\
+Algeria & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{76.62}}\\
+Algeria & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{75.50}}\\
+Angola & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.13}}\\
+\addlinespace
+Angola & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.45}}\\
+Angola & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.87}}\\
+Antigua and Barbuda & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.93}}\\
+Antigua and Barbuda & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.47}}\\
+Antigua and Barbuda & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{74.18}}\\
+\addlinespace
+Argentina & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{76.55}}\\
+Argentina & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{79.60}}\\
+Argentina & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{73.45}}\\
+Armenia & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{74.08}}\\
+Armenia & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.57}}\\
+\addlinespace
+Armenia & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{69.12}}\\
+Australia & Both sexes & high\_income & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{82.77}}\\
+Australia & Female & high\_income & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{84.65}}\\
+Australia & Male & high\_income & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{80.88}}\\
+Austria & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.32}}\\
+\addlinespace
+Austria & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.52}}\\
+Austria & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.05}}\\
+Azerbaijan & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{74.08}}\\
+Azerbaijan & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{76.58}}\\
+Azerbaijan & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{71.53}}\\
+\addlinespace
+Bahamas & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.62}}\\
+Bahamas & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.70}}\\
+Bahamas & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{69.50}}\\
+Bahrain & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{75.67}}\\
+Bahrain & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.75}}\\
+\addlinespace
+Bahrain & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.87}}\\
+Bangladesh & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{73.48}}\\
+Bangladesh & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.82}}\\
+Bangladesh & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.20}}\\
+Barbados & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{76.35}}\\
+\addlinespace
+Barbados & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.67}}\\
+Barbados & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{74.93}}\\
+Belarus & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.98}}\\
+Belarus & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.03}}\\
+Belarus & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{68.83}}\\
+\addlinespace
+Belgium & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.10}}\\
+Belgium & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.25}}\\
+Belgium & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.90}}\\
+Belize & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{74.58}}\\
+Belize & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.30}}\\
+\addlinespace
+Belize & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.08}}\\
+Benin & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.52}}\\
+Benin & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.00}}\\
+Benin & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.17}}\\
+Bhutan & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{73.68}}\\
+\addlinespace
+Bhutan & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.87}}\\
+Bhutan & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.62}}\\
+Bolivia (Plurinational State of) & Both sexes & lower\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{71.53}}\\
+Bolivia (Plurinational State of) & Female & lower\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{72.83}}\\
+Bolivia (Plurinational State of) & Male & lower\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{70.33}}\\
+\addlinespace
+Bosnia and Herzegovina & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{76.90}}\\
+Bosnia and Herzegovina & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.40}}\\
+Bosnia and Herzegovina & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{74.42}}\\
+Botswana & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.93}}\\
+Botswana & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.02}}\\
+\addlinespace
+Botswana & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.75}}\\
+Brazil & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{74.87}}\\
+Brazil & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{78.28}}\\
+Brazil & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{71.45}}\\
+Brunei Darussalam & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.55}}\\
+\addlinespace
+Brunei Darussalam & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.92}}\\
+Brunei Darussalam & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{75.22}}\\
+Bulgaria & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{74.58}}\\
+Bulgaria & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.17}}\\
+Bulgaria & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{71.10}}\\
+\addlinespace
+Burkina Faso & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.02}}\\
+Burkina Faso & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.43}}\\
+Burkina Faso & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.50}}\\
+Burundi & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.75}}\\
+Burundi & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.70}}\\
+\addlinespace
+Burundi & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.80}}\\
+Cabo Verde & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{74.38}}\\
+Cabo Verde & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{77.92}}\\
+Cabo Verde & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{70.73}}\\
+Cambodia & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{69.25}}\\
+\addlinespace
+Cambodia & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.92}}\\
+Cambodia & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{66.48}}\\
+Cameroon & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.83}}\\
+Cameroon & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.80}}\\
+Cameroon & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{58.95}}\\
+\addlinespace
+Canada & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{81.67}}\\
+Canada & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{83.58}}\\
+Canada & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{79.78}}\\
+Central African Republic & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{51.98}}\\
+Central African Republic & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{54.90}}\\
+\addlinespace
+Central African Republic & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{49.42}}\\
+Chad & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{58.72}}\\
+Chad & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.25}}\\
+Chad & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{57.23}}\\
+Chile & Both sexes & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{80.53}}\\
+\addlinespace
+Chile & Female & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{82.93}}\\
+Chile & Male & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{78.05}}\\
+China & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.00}}\\
+China & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{80.18}}\\
+China & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.23}}\\
+\addlinespace
+Colombia & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{77.45}}\\
+Colombia & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{80.17}}\\
+Colombia & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{74.75}}\\
+Comoros & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.92}}\\
+Comoros & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.12}}\\
+\addlinespace
+Comoros & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.77}}\\
+Congo & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.80}}\\
+Congo & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.13}}\\
+Congo & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.40}}\\
+Costa Rica & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{80.25}}\\
+\addlinespace
+Costa Rica & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{82.87}}\\
+Costa Rica & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.70}}\\
+Cote d'Ivoire & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.42}}\\
+Cote d'Ivoire & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.18}}\\
+Cote d'Ivoire & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.15}}\\
+\addlinespace
+Croatia & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.13}}\\
+Croatia & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.13}}\\
+Croatia & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.08}}\\
+Cuba & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.82}}\\
+Cuba & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{80.15}}\\
+\addlinespace
+Cuba & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.55}}\\
+Cyprus & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.97}}\\
+Cyprus & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{84.00}}\\
+Cyprus & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.93}}\\
+Czechia & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.73}}\\
+\addlinespace
+Czechia & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.58}}\\
+Czechia & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.85}}\\
+Democratic People's Republic of Korea & Both sexes & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.95}}\\
+Democratic People's Republic of Korea & Female & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.93}}\\
+Democratic People's Republic of Korea & Male & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.93}}\\
+\addlinespace
+Democratic Republic of the Congo & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.07}}\\
+Democratic Republic of the Congo & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.25}}\\
+Democratic Republic of the Congo & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.02}}\\
+Denmark & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.95}}\\
+Denmark & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.73}}\\
+\addlinespace
+Denmark & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.17}}\\
+Djibouti & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.78}}\\
+Djibouti & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.57}}\\
+Djibouti & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.05}}\\
+Dominican Republic & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{73.50}}\\
+\addlinespace
+Dominican Republic & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.08}}\\
+Dominican Republic & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{70.25}}\\
+Ecuador & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{76.62}}\\
+Ecuador & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{79.27}}\\
+Ecuador & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{74.03}}\\
+\addlinespace
+Egypt & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{70.87}}\\
+Egypt & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{73.52}}\\
+Egypt & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{68.27}}\\
+El Salvador & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{73.52}}\\
+El Salvador & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{78.05}}\\
+\addlinespace
+El Salvador & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{68.63}}\\
+Equatorial Guinea & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.20}}\\
+Equatorial Guinea & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.68}}\\
+Equatorial Guinea & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.78}}\\
+Eritrea & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.28}}\\
+\addlinespace
+Eritrea & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.13}}\\
+Eritrea & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.45}}\\
+Estonia & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.22}}\\
+Estonia & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.18}}\\
+Estonia & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.83}}\\
+\addlinespace
+Eswatini & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{54.23}}\\
+Eswatini & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{57.83}}\\
+Eswatini & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{51.08}}\\
+Ethiopia & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{68.15}}\\
+Ethiopia & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.88}}\\
+\addlinespace
+Ethiopia & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.43}}\\
+Fiji & Both sexes & upper\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{67.82}}\\
+Fiji & Female & upper\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{70.05}}\\
+Fiji & Male & upper\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{65.72}}\\
+Finland & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.35}}\\
+\addlinespace
+Finland & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{84.00}}\\
+Finland & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.73}}\\
+France & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.17}}\\
+France & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{84.87}}\\
+France & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.35}}\\
+\addlinespace
+Gabon & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.60}}\\
+Gabon & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.47}}\\
+Gabon & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.18}}\\
+Gambia & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.42}}\\
+Gambia & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.48}}\\
+\addlinespace
+Gambia & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.42}}\\
+Georgia & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.30}}\\
+Georgia & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{77.82}}\\
+Georgia & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{68.62}}\\
+Germany & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.72}}\\
+\addlinespace
+Germany & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.98}}\\
+Germany & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.43}}\\
+Ghana & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.30}}\\
+Ghana & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.98}}\\
+Ghana & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.78}}\\
+\addlinespace
+Greece & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.73}}\\
+Greece & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.92}}\\
+Greece & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.57}}\\
+Grenada & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{73.08}}\\
+Grenada & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.88}}\\
+\addlinespace
+Grenada & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{70.70}}\\
+Guatemala & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.22}}\\
+Guatemala & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{74.95}}\\
+Guatemala & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{69.50}}\\
+Guinea & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.38}}\\
+\addlinespace
+Guinea & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.62}}\\
+Guinea & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.03}}\\
+Guinea-Bissau & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{58.33}}\\
+Guinea-Bissau & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.68}}\\
+Guinea-Bissau & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{55.83}}\\
+\addlinespace
+Guyana & Both sexes & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{67.85}}\\
+Guyana & Female & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{71.17}}\\
+Guyana & Male & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{64.67}}\\
+Haiti & Both sexes & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{63.18}}\\
+Haiti & Female & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{63.63}}\\
+\addlinespace
+Haiti & Male & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{62.75}}\\
+Honduras & Both sexes & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{70.82}}\\
+Honduras & Female & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.43}}\\
+Honduras & Male & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{69.27}}\\
+Hungary & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.97}}\\
+\addlinespace
+Hungary & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.20}}\\
+Hungary & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{72.53}}\\
+Iceland & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.35}}\\
+Iceland & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.77}}\\
+Iceland & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.93}}\\
+\addlinespace
+India & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.10}}\\
+India & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.75}}\\
+India & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.58}}\\
+Indonesia & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.77}}\\
+Indonesia & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.65}}\\
+\addlinespace
+Indonesia & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.92}}\\
+Iran (Islamic Republic of) & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.15}}\\
+Iran (Islamic Republic of) & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{78.82}}\\
+Iran (Islamic Republic of) & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{75.63}}\\
+Iraq & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.68}}\\
+\addlinespace
+Iraq & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.82}}\\
+Iraq & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.50}}\\
+Ireland & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.57}}\\
+Ireland & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.32}}\\
+Ireland & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.82}}\\
+\addlinespace
+Israel & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{82.35}}\\
+Israel & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{84.15}}\\
+Israel & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{80.42}}\\
+Italy & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.55}}\\
+Italy & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{84.58}}\\
+\addlinespace
+Italy & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.42}}\\
+Jamaica & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.37}}\\
+Jamaica & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.27}}\\
+Jamaica & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{69.65}}\\
+Japan & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{84.35}}\\
+\addlinespace
+Japan & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{87.07}}\\
+Japan & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{81.50}}\\
+Jordan & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{78.90}}\\
+Jordan & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{79.50}}\\
+Jordan & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{78.83}}\\
+\addlinespace
+Kazakhstan & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{72.52}}\\
+Kazakhstan & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{76.53}}\\
+Kazakhstan & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{68.12}}\\
+Kenya & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.72}}\\
+Kenya & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{68.28}}\\
+\addlinespace
+Kenya & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.23}}\\
+Kiribati & Both sexes & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{61.67}}\\
+Kiribati & Female & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{65.03}}\\
+Kiribati & Male & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{58.30}}\\
+Kuwait & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{81.78}}\\
+\addlinespace
+Kuwait & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{85.47}}\\
+Kuwait & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{79.63}}\\
+Kyrgyzstan & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.57}}\\
+Kyrgyzstan & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.12}}\\
+Kyrgyzstan & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.90}}\\
+\addlinespace
+Lao People's Democratic Republic & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{67.85}}\\
+Lao People's Democratic Republic & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.30}}\\
+Lao People's Democratic Republic & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{65.58}}\\
+Latvia & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.18}}\\
+Latvia & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.62}}\\
+\addlinespace
+Latvia & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{70.40}}\\
+Lebanon & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{78.77}}\\
+Lebanon & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{81.10}}\\
+Lebanon & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.27}}\\
+Lesotho & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{50.85}}\\
+\addlinespace
+Lesotho & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{53.88}}\\
+Lesotho & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{48.13}}\\
+Liberia & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.53}}\\
+Liberia & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.22}}\\
+Liberia & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.87}}\\
+\addlinespace
+Libya & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{73.02}}\\
+Libya & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{75.37}}\\
+Libya & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{70.80}}\\
+Lithuania & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.25}}\\
+Lithuania & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.08}}\\
+\addlinespace
+Lithuania & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{70.25}}\\
+Luxembourg & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.68}}\\
+Luxembourg & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{84.60}}\\
+Luxembourg & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.72}}\\
+Madagascar & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.52}}\\
+\addlinespace
+Madagascar & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.55}}\\
+Madagascar & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.45}}\\
+Malawi & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.70}}\\
+Malawi & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.62}}\\
+Malawi & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.82}}\\
+\addlinespace
+Malaysia & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.85}}\\
+Malaysia & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.00}}\\
+Malaysia & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{73.10}}\\
+Maldives & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.25}}\\
+Maldives & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{79.13}}\\
+\addlinespace
+Maldives & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{75.82}}\\
+Mali & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.05}}\\
+Mali & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.63}}\\
+Mali & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.53}}\\
+Malta & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.02}}\\
+\addlinespace
+Malta & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.85}}\\
+Malta & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.15}}\\
+Mauritania & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.68}}\\
+Mauritania & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.88}}\\
+Mauritania & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.48}}\\
+\addlinespace
+Mauritius & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{74.02}}\\
+Mauritius & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{77.35}}\\
+Mauritius & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{70.80}}\\
+Mexico & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.03}}\\
+Mexico & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{78.12}}\\
+\addlinespace
+Mexico & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.02}}\\
+Micronesia (Federated States of) & Both sexes & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{65.65}}\\
+Micronesia (Federated States of) & Female & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{68.57}}\\
+Micronesia (Federated States of) & Male & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{62.98}}\\
+Mongolia & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.48}}\\
+\addlinespace
+Mongolia & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.97}}\\
+Mongolia & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{66.25}}\\
+Montenegro & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{76.77}}\\
+Montenegro & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.58}}\\
+Montenegro & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.87}}\\
+\addlinespace
+Morocco & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{73.33}}\\
+Morocco & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{74.30}}\\
+Morocco & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{72.40}}\\
+Mozambique & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{57.47}}\\
+Mozambique & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.62}}\\
+\addlinespace
+Mozambique & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{54.42}}\\
+Myanmar & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.27}}\\
+Myanmar & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.53}}\\
+Myanmar & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{65.13}}\\
+Namibia & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.75}}\\
+\addlinespace
+Namibia & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.92}}\\
+Namibia & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.43}}\\
+Nepal & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.78}}\\
+Nepal & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.57}}\\
+Nepal & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.97}}\\
+\addlinespace
+Netherlands (Kingdom of the) & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.62}}\\
+Netherlands (Kingdom of the) & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.10}}\\
+Netherlands (Kingdom of the) & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.08}}\\
+New Zealand & Both sexes & high\_income & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{81.72}}\\
+New Zealand & Female & high\_income & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{83.35}}\\
+\addlinespace
+New Zealand & Male & high\_income & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{80.05}}\\
+Nicaragua & Both sexes & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.85}}\\
+Nicaragua & Female & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{80.52}}\\
+Nicaragua & Male & lower\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.05}}\\
+Niger & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.17}}\\
+\addlinespace
+Niger & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.15}}\\
+Niger & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.22}}\\
+Nigeria & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.45}}\\
+Nigeria & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.98}}\\
+Nigeria & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.00}}\\
+\addlinespace
+North Macedonia & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.65}}\\
+North Macedonia & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{77.50}}\\
+North Macedonia & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.95}}\\
+Norway & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.38}}\\
+Norway & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.97}}\\
+\addlinespace
+Norway & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.82}}\\
+Oman & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.30}}\\
+Oman & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.82}}\\
+Oman & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.20}}\\
+Pakistan & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{66.28}}\\
+\addlinespace
+Pakistan & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{67.15}}\\
+Pakistan & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{65.47}}\\
+Panama & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{78.27}}\\
+Panama & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{81.25}}\\
+Panama & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.47}}\\
+\addlinespace
+Papua New Guinea & Both sexes & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{66.35}}\\
+Papua New Guinea & Female & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{67.57}}\\
+Papua New Guinea & Male & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{65.25}}\\
+Paraguay & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{75.15}}\\
+Paraguay & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{78.12}}\\
+\addlinespace
+Paraguay & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{72.37}}\\
+Peru & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{78.33}}\\
+Peru & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{80.27}}\\
+Peru & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{76.47}}\\
+Philippines & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{69.50}}\\
+\addlinespace
+Philippines & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{73.53}}\\
+Philippines & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{65.95}}\\
+Poland & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{77.38}}\\
+Poland & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.23}}\\
+Poland & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.47}}\\
+\addlinespace
+Portugal & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.03}}\\
+Portugal & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.85}}\\
+Portugal & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.02}}\\
+Puerto Rico & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{80.03}}\\
+Puerto Rico & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{83.50}}\\
+\addlinespace
+Puerto Rico & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{76.52}}\\
+Qatar & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{78.22}}\\
+Qatar & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{79.27}}\\
+Qatar & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.80}}\\
+Republic of Korea & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{83.15}}\\
+\addlinespace
+Republic of Korea & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{86.05}}\\
+Republic of Korea & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{79.97}}\\
+Republic of Moldova & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{72.35}}\\
+Republic of Moldova & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{76.23}}\\
+Republic of Moldova & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{68.42}}\\
+\addlinespace
+Romania & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{74.97}}\\
+Romania & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.70}}\\
+Romania & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{71.33}}\\
+Russian Federation & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.12}}\\
+Russian Federation & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.12}}\\
+\addlinespace
+Russian Federation & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{66.92}}\\
+Rwanda & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.55}}\\
+Rwanda & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.42}}\\
+Rwanda & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.45}}\\
+Saint Lucia & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{76.08}}\\
+\addlinespace
+Saint Lucia & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{79.97}}\\
+Saint Lucia & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.47}}\\
+Saint Vincent and the Grenadines & Both sexes & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{72.98}}\\
+Saint Vincent and the Grenadines & Female & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{75.55}}\\
+Saint Vincent and the Grenadines & Male & upper\_middle & North America & \cellcolor[HTML]{F7F7F7}{\textbf{70.75}}\\
+\addlinespace
+Samoa & Both sexes & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{70.03}}\\
+Samoa & Female & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{71.40}}\\
+Samoa & Male & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{68.77}}\\
+Sao Tome and Principe & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{71.20}}\\
+Sao Tome and Principe & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{72.70}}\\
+\addlinespace
+Sao Tome and Principe & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.70}}\\
+Saudi Arabia & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.70}}\\
+Saudi Arabia & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.60}}\\
+Saudi Arabia & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.17}}\\
+Senegal & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{68.18}}\\
+\addlinespace
+Senegal & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{69.70}}\\
+Senegal & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.47}}\\
+Serbia & Both sexes & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{75.47}}\\
+Serbia & Female & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.00}}\\
+Serbia & Male & upper\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{72.83}}\\
+\addlinespace
+Seychelles & Both sexes & high\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{73.82}}\\
+Seychelles & Female & high\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{77.28}}\\
+Seychelles & Male & high\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{70.92}}\\
+Sierra Leone & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.28}}\\
+Sierra Leone & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.17}}\\
+\addlinespace
+Sierra Leone & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{58.37}}\\
+Singapore & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{83.43}}\\
+Singapore & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{85.58}}\\
+Singapore & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{81.28}}\\
+Slovakia & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{77.10}}\\
+\addlinespace
+Slovakia & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.40}}\\
+Slovakia & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{73.67}}\\
+Slovenia & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.78}}\\
+Slovenia & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.53}}\\
+Slovenia & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.00}}\\
+\addlinespace
+Solomon Islands & Both sexes & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{65.43}}\\
+Solomon Islands & Female & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{68.08}}\\
+Solomon Islands & Male & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{63.08}}\\
+Somalia & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{54.43}}\\
+Somalia & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{56.97}}\\
+\addlinespace
+Somalia & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{52.08}}\\
+South Africa & Both sexes & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.55}}\\
+South Africa & Female & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.42}}\\
+South Africa & Male & upper\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.40}}\\
+South Sudan & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{59.03}}\\
+\addlinespace
+South Sudan & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.20}}\\
+South Sudan & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{56.83}}\\
+Spain & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.58}}\\
+Spain & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{85.17}}\\
+Spain & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{79.97}}\\
+\addlinespace
+Sri Lanka & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.58}}\\
+Sri Lanka & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{80.43}}\\
+Sri Lanka & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.45}}\\
+Sudan & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{68.85}}\\
+Sudan & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{70.00}}\\
+\addlinespace
+Sudan & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.67}}\\
+Suriname & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{73.03}}\\
+Suriname & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{76.12}}\\
+Suriname & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{69.98}}\\
+Sweden & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.13}}\\
+\addlinespace
+Sweden & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.75}}\\
+Sweden & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.52}}\\
+Switzerland & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{83.07}}\\
+Switzerland & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{84.82}}\\
+Switzerland & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{81.22}}\\
+\addlinespace
+Syrian Arab Republic & Both sexes & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{64.13}}\\
+Syrian Arab Republic & Female & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.45}}\\
+Syrian Arab Republic & Male & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{58.37}}\\
+Tajikistan & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.70}}\\
+Tajikistan & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.43}}\\
+\addlinespace
+Tajikistan & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{71.02}}\\
+Thailand & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.95}}\\
+Thailand & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{80.48}}\\
+Thailand & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{73.52}}\\
+Timor-Leste & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.32}}\\
+\addlinespace
+Timor-Leste & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{69.93}}\\
+Timor-Leste & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{66.82}}\\
+Togo & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{62.77}}\\
+Togo & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.48}}\\
+Togo & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.33}}\\
+\addlinespace
+Tonga & Both sexes & upper\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{72.78}}\\
+Tonga & Female & upper\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{75.52}}\\
+Tonga & Male & upper\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{70.18}}\\
+Trinidad and Tobago & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{73.98}}\\
+Trinidad and Tobago & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{77.30}}\\
+\addlinespace
+Trinidad and Tobago & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{70.70}}\\
+Tunisia & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{77.08}}\\
+Tunisia & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{79.62}}\\
+Tunisia & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{74.68}}\\
+Türkiye & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{76.98}}\\
+\addlinespace
+Türkiye & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{79.57}}\\
+Türkiye & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{74.35}}\\
+Turkmenistan & Both sexes & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.92}}\\
+Turkmenistan & Female & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.33}}\\
+Turkmenistan & Male & upper\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{65.45}}\\
+\addlinespace
+Uganda & Both sexes & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{65.37}}\\
+Uganda & Female & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{68.72}}\\
+Uganda & Male & lower\_income & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.98}}\\
+Ukraine & Both sexes & lower\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{72.65}}\\
+Ukraine & Female & lower\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{77.43}}\\
+\addlinespace
+Ukraine & Male & lower\_middle & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{67.70}}\\
+United Arab Emirates & Both sexes & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{80.85}}\\
+United Arab Emirates & Female & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{81.92}}\\
+United Arab Emirates & Male & high\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{80.33}}\\
+United Kingdom of Great Britain and Northern Ireland & Both sexes & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{80.72}}\\
+\addlinespace
+United Kingdom of Great Britain and Northern Ireland & Female & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{82.43}}\\
+United Kingdom of Great Britain and Northern Ireland & Male & high\_income & Europe & \cellcolor[HTML]{F7F7F7}{\textbf{78.98}}\\
+United Republic of Tanzania & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{66.23}}\\
+United Republic of Tanzania & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{67.85}}\\
+United Republic of Tanzania & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{64.60}}\\
+\addlinespace
+United States of America & Both sexes & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{78.32}}\\
+United States of America & Female & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{80.62}}\\
+United States of America & Male & high\_income & North America & \cellcolor[HTML]{F7F7F7}{\textbf{76.08}}\\
+Uruguay & Both sexes & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{77.17}}\\
+Uruguay & Female & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{80.73}}\\
+\addlinespace
+Uruguay & Male & high\_income & South America & \cellcolor[HTML]{F7F7F7}{\textbf{73.48}}\\
+Uzbekistan & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.83}}\\
+Uzbekistan & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{72.97}}\\
+Uzbekistan & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{68.60}}\\
+Vanuatu & Both sexes & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{66.98}}\\
+\addlinespace
+Vanuatu & Female & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{70.57}}\\
+Vanuatu & Male & lower\_middle & Oceania & \cellcolor[HTML]{F7F7F7}{\textbf{63.95}}\\
+Venezuela (Bolivarian Republic of) & Both sexes & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{72.87}}\\
+Venezuela (Bolivarian Republic of) & Female & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{77.50}}\\
+Venezuela (Bolivarian Republic of) & Male & upper\_middle & South America & \cellcolor[HTML]{F7F7F7}{\textbf{68.55}}\\
+\addlinespace
+Viet Nam & Both sexes & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{73.62}}\\
+Viet Nam & Female & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{77.98}}\\
+Viet Nam & Male & lower\_middle & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{69.33}}\\
+Yemen & Both sexes & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{67.25}}\\
+Yemen & Female & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{70.03}}\\
+\addlinespace
+Yemen & Male & lower\_income & Asia & \cellcolor[HTML]{F7F7F7}{\textbf{64.53}}\\
+Zambia & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{61.28}}\\
+Zambia & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{63.42}}\\
+Zambia & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{58.98}}\\
+Zimbabwe & Both sexes & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{58.47}}\\
+\addlinespace
+Zimbabwe & Female & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{60.43}}\\
+Zimbabwe & Male & lower\_middle & Africa & \cellcolor[HTML]{F7F7F7}{\textbf{56.32}}\\
+\bottomrule
 
@@
 
-Do you smoke? - Yes - No
+Do you smoke?
+
+\begin{itemize}
+\tightlist
+\item
+  Yes
+\item
+  No
+\end{itemize}
 
@@
 
-How often do you consume alcoholic beverages? - Never - Occasionally
-(e.g., social drinking) - Frequently
+How often do you consume alcoholic beverages?
+
+\begin{itemize}
+\tightlist
+\item
+  Never
+\item
+  Occasionally (e.g., social drinking)
+\item
+  Frequently
+\end{itemize}
 
@@
 
-How would you describe your living area? - Urban - Suburban - Rural
+How would you describe your living area?
+
+\begin{itemize}
+\tightlist
+\item
+  Urban
+\item
+  Suburban
+\item
+  Rural
+\end{itemize}
 
@@
 
-\subsection{Additional graph for
-analysis}\label{additional-graph-for-analysis}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.3193}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1386}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1566}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0723}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0783}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2349}}@{}}
+
+\caption{\label{tbl-testpredicted}Life expectancy over countries and
+years}
+
+\tabularnewline
+
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Country
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Actual Life Expectancy
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Predicted Life Expectancy
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+RMSE (Test)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+RMSE (Train)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Indication
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Afghanistan & 59.3 & 58.23 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Afghanistan & 61.7 & 63.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Afghanistan & 62.1 & 63.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Afghanistan & 62.1 & 63.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Albania & 74.3 & 75.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Albania & 76.2 & 75.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Albania & 79.9 & 80.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Albania & 79.9 & 80.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Albania & 79.9 & 80.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Algeria & 76.1 & 73.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Algeria & 76.0 & 73.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Algeria & 75.9 & 73.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Angola & 60.3 & 59.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Angola & 60.1 & 59.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Angola & 64.5 & 64.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Angola & 59.8 & 59.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Angola & 61.8 & 62.12 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Antigua and Barbuda & 73.8 & 73.42 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Antigua and Barbuda & 75.5 & 75.84 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Antigua and Barbuda & 77.1 & 78.33 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Antigua and Barbuda & 73.8 & 73.42 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Argentina & 79.9 & 79.01 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Argentina & 76.6 & 76.51 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Argentina & 73.0 & 74.09 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Argentina & 76.1 & 76.51 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Armenia & 75.7 & 73.90 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Armenia & 79.8 & 76.39 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Armenia & 79.1 & 76.39 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Australia & 82.6 & 82.74 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Australia & 84.2 & 85.24 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Austria & 81.4 & 81.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Austria & 83.6 & 83.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Austria & 81.4 & 81.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Austria & 83.3 & 83.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Azerbaijan & 67.5 & 71.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Azerbaijan & 75.8 & 74.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Azerbaijan & 72.2 & 71.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Azerbaijan & 71.7 & 71.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 76.0 & 75.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 76.5 & 75.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 73.2 & 72.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 69.7 & 70.16 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 72.9 & 72.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 76.1 & 75.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahamas & 69.8 & 70.16 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahrain & 74.9 & 75.74 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahrain & 75.9 & 75.74 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahrain & 75.7 & 75.74 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bahrain & 75.8 & 75.74 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bangladesh & 72.6 & 71.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bangladesh & 75.0 & 75.97 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bangladesh & 73.4 & 73.48 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bangladesh & 73.2 & 73.48 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Barbados & 74.9 & 73.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Barbados & 76.3 & 76.30 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Barbados & 77.4 & 78.79 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Barbados & 76.3 & 76.30 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Belarus & 79.7 & 76.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Belarus & 79.2 & 76.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Belarus & 78.9 & 76.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Belgium & 81.6 & 81.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Belize & 74.4 & 74.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Benin & 63.7 & 63.54 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Benin & 66.2 & 66.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Benin & 65.4 & 66.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bhutan & 74.5 & 73.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bhutan & 72.3 & 71.28 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bhutan & 73.3 & 73.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bhutan & 74.2 & 76.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bolivia (Plurinational State of) & 73.8 & 74.04 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Bolivia (Plurinational State of) & 71.8 & 69.13 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Bolivia (Plurinational State of) & 71.3 & 69.13 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Bolivia (Plurinational State of) & 71.0 & 69.13 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Bolivia (Plurinational State of) & 72.8 & 74.04 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Bosnia and Herzegovina & 74.9 & 74.46 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Bosnia and Herzegovina & 74.6 & 74.46 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Botswana & 64.9 & 63.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Botswana & 64.5 & 63.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Botswana & 64.0 & 63.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Botswana & 66.1 & 66.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Botswana & 65.0 & 66.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Brazil & 75.3 & 74.84 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Brazil & 74.6 & 74.84 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Brunei Darussalam & 78.3 & 79.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Brunei Darussalam & 76.4 & 76.54 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Brunei Darussalam & 77.9 & 79.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bulgaria & 71.4 & 72.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Bulgaria & 78.4 & 77.09 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burkina Faso & 60.3 & 59.54 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burkina Faso & 62.4 & 61.97 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burkina Faso & 58.9 & 59.54 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burkina Faso & 60.9 & 61.97 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burundi & 66.2 & 66.23 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burundi & 63.7 & 63.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burundi & 61.3 & 61.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Burundi & 60.8 & 61.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cabo Verde & 78.2 & 76.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cabo Verde & 69.7 & 71.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cabo Verde & 72.0 & 71.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cabo Verde & 72.2 & 71.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cabo Verde & 77.7 & 76.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cambodia & 69.4 & 69.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cambodia & 68.9 & 69.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cambodia & 65.8 & 66.77 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cameroon & 57.2 & 58.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Canada & 81.3 & 81.66 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Canada & 82.0 & 81.66 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Canada & 81.6 & 81.66 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Central African Republic & 50.5 & 49.66 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Central African Republic & 54.2 & 54.57 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Central African Republic & 51.0 & 52.08 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Chad & 57.6 & 56.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 59.2 & 58.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 60.9 & 61.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 57.8 & 56.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 60.9 & 61.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 57.5 & 56.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 58.6 & 58.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chad & 58.3 & 58.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chile & 82.5 & 82.98 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Chile & 82.9 & 82.98 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+China & 77.5 & 77.12 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+China & 74.6 & 74.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+China & 76.5 & 77.12 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Colombia & 77.8 & 77.43 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Colombia & 77.3 & 77.43 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Comoros & 68.3 & 67.92 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Comoros & 67.1 & 65.49 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Comoros & 69.3 & 70.41 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Comoros & 66.6 & 65.49 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Comoros & 68.8 & 70.41 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Congo & 62.6 & 62.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Costa Rica & 82.7 & 82.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Costa Rica & 82.7 & 82.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cote d'Ivoire & 63.3 & 62.56 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cote d'Ivoire & 66.1 & 65.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cote d'Ivoire & 65.0 & 65.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Croatia & 74.8 & 75.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Croatia & 78.3 & 78.10 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Croatia & 81.3 & 80.59 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Croatia & 80.6 & 80.59 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cuba & 75.3 & 75.40 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cuba & 75.3 & 75.40 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cuba & 77.9 & 77.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cuba & 77.9 & 77.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cyprus & 82.1 & 81.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Cyprus & 79.7 & 79.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Democratic People's Republic of Korea & 69.3 & 69.50 & 1.15 & 1.17 &
+Model generalizes well (out-of-sample) \\
+Democratic People's Republic of Korea & 72.4 & 71.92 & 1.15 & 1.17 &
+Model generalizes well (out-of-sample) \\
+Democratic People's Republic of Korea & 69.3 & 69.50 & 1.15 & 1.17 &
+Model generalizes well (out-of-sample) \\
+Democratic People's Republic of Korea & 72.3 & 71.92 & 1.15 & 1.17 &
+Model generalizes well (out-of-sample) \\
+Democratic People's Republic of Korea & 75.3 & 74.41 & 1.15 & 1.17 &
+Model generalizes well (out-of-sample) \\
+Democratic People's Republic of Korea & 74.5 & 74.41 & 1.15 & 1.17 &
+Model generalizes well (out-of-sample) \\
+Democratic Republic of the Congo & 58.8 & 58.67 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Democratic Republic of the Congo & 62.4 & 63.59 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Democratic Republic of the Congo & 58.1 & 58.67 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Denmark & 80.9 & 80.93 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Djibouti & 67.2 & 67.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Djibouti & 67.3 & 67.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Djibouti & 63.9 & 64.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Dominican Republic & 70.2 & 71.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Dominican Republic & 77.0 & 76.08 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Dominican Republic & 73.3 & 73.59 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ecuador & 76.4 & 79.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ecuador & 80.2 & 79.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ecuador & 77.3 & 76.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ecuador & 79.6 & 79.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ecuador & 77.2 & 76.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Egypt & 70.1 & 70.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+El Salvador & 72.1 & 73.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+El Salvador & 79.1 & 75.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+El Salvador & 78.0 & 75.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Equatorial Guinea & 61.2 & 61.20 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Equatorial Guinea & 62.2 & 63.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eritrea & 63.8 & 63.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eritrea & 66.3 & 65.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eritrea & 60.4 & 60.85 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Estonia & 74.0 & 75.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Estonia & 82.3 & 80.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Estonia & 73.2 & 75.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Estonia & 77.7 & 78.05 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Estonia & 81.7 & 80.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eswatini & 52.8 & 51.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eswatini & 52.5 & 51.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eswatini & 58.4 & 56.86 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Eswatini & 55.5 & 56.86 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 66.9 & 65.72 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 70.7 & 70.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 66.8 & 65.72 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 70.2 & 70.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 65.9 & 65.72 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 67.6 & 68.14 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 69.3 & 70.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ethiopia & 67.1 & 68.14 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Fiji & 70.1 & 70.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Fiji & 70.1 & 70.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Finland & 78.9 & 78.92 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Finland & 81.5 & 81.34 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Finland & 78.8 & 78.92 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+France & 79.1 & 79.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+France & 82.5 & 82.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+France & 79.2 & 79.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gabon & 62.7 & 62.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gabon & 65.0 & 64.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gabon & 64.5 & 64.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gambia & 62.9 & 62.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gambia & 66.4 & 66.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gambia & 62.1 & 62.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Gambia & 63.8 & 64.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Georgia & 77.8 & 75.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Georgia & 78.4 & 75.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Georgia & 72.6 & 73.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Georgia & 72.9 & 73.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Georgia & 77.2 & 75.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Germany & 78.5 & 78.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Germany & 78.7 & 78.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Germany & 81.0 & 80.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Germany & 83.2 & 83.18 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Germany & 80.7 & 80.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Germany & 78.1 & 78.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ghana & 66.2 & 65.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ghana & 63.0 & 62.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ghana & 65.5 & 65.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ghana & 62.2 & 62.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ghana & 67.4 & 67.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ghana & 67.0 & 67.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Greece & 83.0 & 83.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Greece & 78.9 & 78.30 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Greece & 82.9 & 83.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Greece & 82.9 & 83.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Grenada & 70.5 & 70.79 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guatemala & 71.0 & 72.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guatemala & 72.7 & 72.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guatemala & 75.2 & 74.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guatemala & 75.2 & 74.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guinea & 59.0 & 57.90 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guinea & 60.3 & 60.32 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guinea-Bissau & 58.4 & 58.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guyana & 70.2 & 70.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guyana & 68.7 & 67.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guyana & 65.6 & 65.46 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Guyana & 64.3 & 65.46 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Haiti & 63.0 & 60.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Haiti & 62.9 & 60.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Haiti & 62.8 & 63.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Honduras & 70.3 & 70.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Honduras & 71.4 & 70.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Honduras & 71.3 & 70.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Honduras & 72.4 & 73.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Honduras & 71.9 & 73.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Hungary & 75.8 & 75.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Hungary & 72.6 & 73.46 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Hungary & 75.6 & 75.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iceland & 82.6 & 82.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iceland & 81.1 & 79.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iceland & 82.4 & 82.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+India & 70.7 & 70.12 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+India & 72.0 & 72.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+India & 71.0 & 72.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Indonesia & 67.6 & 68.34 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Indonesia & 71.9 & 73.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Indonesia & 69.0 & 68.34 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Indonesia & 70.5 & 70.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Indonesia & 72.3 & 73.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iran (Islamic Republic of) & 73.3 & 74.76 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Iran (Islamic Republic of) & 76.4 & 74.76 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Iran (Islamic Republic of) & 76.3 & 74.76 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Iran (Islamic Republic of) & 77.5 & 77.18 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Iran (Islamic Republic of) & 79.1 & 79.67 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Iran (Islamic Republic of) & 77.4 & 77.18 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Iraq & 71.1 & 71.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iraq & 74.7 & 74.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iraq & 67.5 & 69.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Iraq & 74.5 & 74.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ireland & 82.9 & 84.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Israel & 80.4 & 79.86 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Israel & 82.6 & 82.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Israel & 79.9 & 79.86 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Italy & 80.9 & 80.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Italy & 80.4 & 80.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Italy & 84.9 & 84.99 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jamaica & 75.6 & 74.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jamaica & 69.4 & 69.99 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jamaica & 75.0 & 74.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Japan & 86.9 & 86.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 76.6 & 76.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 79.7 & 76.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 79.1 & 79.05 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 79.3 & 76.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 79.6 & 81.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 79.0 & 76.63 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Jordan & 79.0 & 81.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kazakhstan & 71.3 & 72.36 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kazakhstan & 68.8 & 69.94 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kazakhstan & 68.9 & 69.94 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kenya & 66.5 & 65.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kenya & 68.1 & 68.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 58.9 & 59.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 62.1 & 61.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 65.3 & 64.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 56.9 & 59.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 64.7 & 64.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 58.5 & 59.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kiribati & 64.9 & 64.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 78.8 & 82.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 82.5 & 82.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 86.4 & 84.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 80.4 & 79.85 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 82.6 & 82.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 86.3 & 84.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 79.2 & 79.85 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kuwait & 84.9 & 84.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kyrgyzstan & 77.1 & 75.01 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kyrgyzstan & 73.3 & 72.51 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kyrgyzstan & 69.1 & 70.09 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kyrgyzstan & 76.1 & 75.01 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Kyrgyzstan & 75.2 & 75.01 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lao People's Democratic Republic & 68.4 & 67.89 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Lao People's Democratic Republic & 65.5 & 65.47 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Lao People's Democratic Republic & 64.7 & 65.47 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Lao People's Democratic Republic & 66.9 & 67.89 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Latvia & 75.0 & 75.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Latvia & 75.0 & 75.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lebanon & 81.1 & 81.18 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lesotho & 48.4 & 48.51 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lesotho & 52.8 & 53.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Liberia & 62.5 & 60.09 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Liberia & 64.4 & 65.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Liberia & 64.2 & 65.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Liberia & 61.9 & 60.09 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Liberia & 60.4 & 62.51 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Libya & 72.6 & 73.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Libya & 71.5 & 70.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Libya & 73.5 & 73.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Libya & 73.2 & 73.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Libya & 75.2 & 75.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 74.9 & 75.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 80.8 & 77.67 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 75.5 & 75.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 80.1 & 77.67 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 79.9 & 77.67 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 69.1 & 72.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Lithuania & 74.4 & 75.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Luxembourg & 80.9 & 80.23 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Luxembourg & 84.8 & 85.14 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Luxembourg & 82.7 & 82.65 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Luxembourg & 84.5 & 85.14 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Luxembourg & 82.4 & 82.65 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Madagascar & 61.9 & 61.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Madagascar & 63.7 & 63.49 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Madagascar & 62.6 & 61.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Madagascar & 62.4 & 61.07 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Madagascar & 63.4 & 63.49 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malawi & 63.5 & 62.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malawi & 65.8 & 65.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malawi & 59.2 & 60.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malawi & 62.2 & 62.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malaysia & 78.6 & 77.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malaysia & 74.7 & 74.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malaysia & 77.0 & 77.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malaysia & 76.8 & 77.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malaysia & 76.5 & 77.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Maldives & 78.7 & 77.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Maldives & 80.7 & 79.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Maldives & 76.6 & 74.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Maldives & 78.2 & 77.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Maldives & 80.2 & 79.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mali & 61.8 & 61.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mali & 60.8 & 58.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mali & 60.6 & 61.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mali & 60.1 & 61.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malta & 80.3 & 79.57 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malta & 84.0 & 84.48 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Malta & 80.2 & 79.57 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mauritania & 70.0 & 67.24 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mauritania & 70.2 & 72.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mauritius & 77.4 & 76.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mauritius & 70.9 & 71.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mauritius & 74.1 & 74.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mauritius & 71.0 & 71.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mexico & 72.8 & 72.60 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mexico & 75.8 & 75.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mexico & 75.9 & 75.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Micronesia (Federated States of) & 65.7 & 65.71 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Micronesia (Federated States of) & 68.8 & 68.21 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Micronesia (Federated States of) & 63.2 & 63.29 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Micronesia (Federated States of) & 68.4 & 68.21 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Micronesia (Federated States of) & 68.2 & 68.21 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Mongolia & 77.0 & 73.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mongolia & 75.5 & 73.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mongolia & 65.9 & 68.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mongolia & 69.6 & 70.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 72.4 & 74.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 78.5 & 79.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 73.9 & 74.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 80.0 & 79.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 74.2 & 74.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 76.9 & 76.71 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Montenegro & 79.4 & 79.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 72.5 & 73.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 73.9 & 75.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 72.7 & 70.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 72.7 & 70.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 72.5 & 70.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 72.4 & 70.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 73.3 & 73.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Morocco & 74.1 & 75.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mozambique & 57.9 & 57.48 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mozambique & 54.2 & 55.06 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Mozambique & 55.9 & 57.48 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Myanmar & 72.3 & 70.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Myanmar & 65.7 & 65.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Myanmar & 64.3 & 65.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Namibia & 62.8 & 62.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Namibia & 66.2 & 65.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Namibia & 65.5 & 65.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Namibia & 58.8 & 60.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Netherlands (Kingdom of the) & 82.9 & 84.08 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Netherlands (Kingdom of the) & 83.3 & 84.08 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Netherlands (Kingdom of the) & 81.5 & 81.59 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Netherlands (Kingdom of the) & 81.3 & 81.59 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+New Zealand & 80.2 & 79.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+New Zealand & 83.4 & 84.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+New Zealand & 81.2 & 81.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+New Zealand & 82.9 & 84.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nicaragua & 78.5 & 80.28 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nicaragua & 81.3 & 80.28 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nicaragua & 75.6 & 75.36 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nicaragua & 78.5 & 77.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nicaragua & 78.3 & 77.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nicaragua & 80.7 & 80.28 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Niger & 60.4 & 60.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Niger & 59.6 & 57.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Niger & 60.2 & 60.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Niger & 61.1 & 62.65 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nigeria & 64.2 & 64.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nigeria & 62.0 & 62.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Nigeria & 63.3 & 64.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+North Macedonia & 74.4 & 75.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+North Macedonia & 77.7 & 78.17 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+North Macedonia & 73.4 & 73.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+North Macedonia & 75.3 & 75.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Norway & 81.3 & 79.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Norway & 80.8 & 79.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Norway & 83.9 & 84.86 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Norway & 80.3 & 79.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Norway & 82.0 & 82.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Oman & 73.1 & 72.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Oman & 74.1 & 74.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Oman & 77.8 & 77.24 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Oman & 71.7 & 72.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Pakistan & 64.7 & 63.85 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Pakistan & 66.3 & 63.85 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Pakistan & 66.7 & 66.27 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Pakistan & 65.3 & 63.85 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Pakistan & 66.9 & 68.77 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Panama & 77.3 & 78.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Panama & 76.2 & 75.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Panama & 81.9 & 80.80 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Panama & 81.6 & 80.80 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Panama & 78.3 & 78.31 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Panama & 75.4 & 75.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Papua New Guinea & 66.4 & 66.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Papua New Guinea & 67.6 & 68.86 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Papua New Guinea & 65.2 & 63.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Paraguay & 72.4 & 72.77 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Peru & 69.5 & 75.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Peru & 79.9 & 80.82 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Peru & 79.4 & 78.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Peru & 80.2 & 78.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Philippines & 66.0 & 67.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Philippines & 69.4 & 69.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Philippines & 73.2 & 72.13 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Philippines & 66.3 & 67.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Philippines & 66.0 & 67.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Philippines & 65.8 & 67.22 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Poland & 73.9 & 74.92 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Poland & 81.6 & 79.84 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Portugal & 84.0 & 83.44 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Portugal & 80.9 & 80.94 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Portugal & 83.7 & 83.44 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Puerto Rico & 83.6 & 82.49 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Puerto Rico & 80.5 & 80.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Puerto Rico & 80.5 & 80.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Qatar & 79.8 & 80.89 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Qatar & 78.6 & 78.40 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Qatar & 77.9 & 75.98 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Qatar & 77.4 & 75.98 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Qatar & 78.8 & 80.89 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Republic of Korea & 80.6 & 80.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Republic of Korea & 80.0 & 80.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Republic of Korea & 86.0 & 85.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Republic of Korea & 82.4 & 83.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Republic of Moldova & 73.3 & 72.32 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Republic of Moldova & 69.0 & 69.90 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Romania & 75.1 & 74.98 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Russian Federation & 76.2 & 74.52 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Russian Federation & 77.6 & 74.52 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Russian Federation & 67.3 & 69.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 70.3 & 69.94 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 65.7 & 65.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 69.6 & 69.94 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 67.6 & 67.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 65.4 & 65.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 67.4 & 67.45 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Rwanda & 65.1 & 65.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 72.0 & 73.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 75.6 & 76.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 76.1 & 76.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 76.1 & 76.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 72.5 & 73.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 80.2 & 78.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Lucia & 80.1 & 78.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saint Vincent and the Grenadines & 73.1 & 73.07 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Saint Vincent and the Grenadines & 71.0 & 70.65 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Saint Vincent and the Grenadines & 71.0 & 70.65 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Saint Vincent and the Grenadines & 73.0 & 73.07 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Samoa & 70.2 & 70.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Samoa & 71.7 & 72.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Samoa & 71.3 & 72.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Samoa & 68.7 & 67.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Samoa & 71.3 & 72.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sao Tome and Principe & 71.3 & 71.17 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Sao Tome and Principe & 73.1 & 73.67 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Sao Tome and Principe & 70.2 & 68.75 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Saudi Arabia & 74.9 & 74.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Saudi Arabia & 77.3 & 79.29 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Senegal & 68.6 & 68.10 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Senegal & 68.8 & 68.10 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Senegal & 66.5 & 65.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Senegal & 69.6 & 70.59 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Senegal & 66.1 & 65.68 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Senegal & 67.8 & 68.10 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Serbia & 75.6 & 75.41 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Serbia & 75.3 & 75.41 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Seychelles & 73.2 & 73.99 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sierra Leone & 58.3 & 56.84 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sierra Leone & 59.2 & 59.26 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sierra Leone & 59.6 & 61.76 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sierra Leone & 56.1 & 56.84 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Singapore & 84.0 & 83.41 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Singapore & 83.5 & 83.41 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Singapore & 81.0 & 80.99 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Singapore & 84.9 & 85.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Slovakia & 73.1 & 74.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Slovenia & 77.7 & 78.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Slovenia & 78.2 & 78.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Slovenia & 83.5 & 83.24 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Solomon Islands & 67.9 & 68.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Africa & 61.9 & 62.02 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Africa & 64.3 & 64.44 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Africa & 68.8 & 66.93 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Africa & 62.0 & 62.02 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Africa & 63.3 & 64.44 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Sudan & 56.8 & 56.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Sudan & 56.7 & 56.58 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Sudan & 59.2 & 59.00 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+South Sudan & 61.4 & 61.49 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Spain & 83.1 & 82.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Spain & 82.8 & 82.55 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sri Lanka & 77.2 & 77.46 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sri Lanka & 80.1 & 79.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sri Lanka & 79.9 & 79.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sri Lanka & 73.6 & 75.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sri Lanka & 73.2 & 75.04 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sudan & 69.0 & 68.81 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sudan & 67.5 & 66.39 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Suriname & 72.8 & 73.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Suriname & 70.0 & 70.60 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Suriname & 76.1 & 75.52 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Suriname & 76.1 & 75.52 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Suriname & 70.3 & 70.60 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Suriname & 73.0 & 73.03 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sweden & 80.4 & 79.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sweden & 82.1 & 82.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sweden & 83.8 & 84.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sweden & 84.2 & 84.61 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sweden & 80.4 & 79.69 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Sweden & 82.0 & 82.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Switzerland & 82.7 & 83.02 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Switzerland & 81.8 & 80.60 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Switzerland & 83.5 & 83.02 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Switzerland & 85.1 & 85.51 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Switzerland & 83.3 & 83.02 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Syrian Arab Republic & 52.8 & 62.19 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Tajikistan & 70.6 & 72.70 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tajikistan & 75.4 & 75.19 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Thailand & 76.5 & 76.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Thailand & 73.6 & 74.54 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Timor-Leste & 67.2 & 65.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Timor-Leste & 66.8 & 65.91 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Timor-Leste & 68.1 & 68.33 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Timor-Leste & 69.6 & 70.83 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Timor-Leste & 69.4 & 70.83 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Togo & 66.3 & 65.34 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Togo & 65.3 & 65.34 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Togo & 59.6 & 60.42 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tonga & 70.4 & 70.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tonga & 70.4 & 70.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tonga & 75.6 & 75.30 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tonga & 70.3 & 70.38 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tonga & 72.8 & 72.80 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Trinidad and Tobago & 77.3 & 76.46 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Trinidad and Tobago & 77.5 & 76.46 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Trinidad and Tobago & 74.0 & 73.97 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Trinidad and Tobago & 77.5 & 76.46 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Trinidad and Tobago & 74.0 & 73.97 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+Tunisia & 77.0 & 77.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tunisia & 79.4 & 79.60 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Tunisia & 76.8 & 77.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Turkmenistan & 68.5 & 68.88 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Turkmenistan & 72.4 & 71.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Turkmenistan & 72.3 & 71.37 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Turkmenistan & 65.3 & 66.46 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Türkiye & 75.1 & 74.53 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Türkiye & 80.1 & 79.44 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Türkiye & 79.6 & 79.44 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Türkiye & 76.7 & 76.95 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Uganda & 66.3 & 65.35 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Uganda & 68.1 & 67.84 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ukraine & 67.6 & 70.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ukraine & 72.5 & 72.57 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ukraine & 68.1 & 70.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ukraine & 67.7 & 70.15 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Ukraine & 72.1 & 72.57 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+United Arab Emirates & 82.3 & 83.50 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+United Arab Emirates & 80.4 & 78.59 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+United Arab Emirates & 80.4 & 78.59 & 1.15 & 1.17 & Model generalizes
+well (out-of-sample) \\
+United Kingdom of Great Britain and Northern Ireland & 78.3 & 78.26 &
+1.15 & 1.17 & Model generalizes well (out-of-sample) \\
+United Kingdom of Great Britain and Northern Ireland & 78.9 & 78.26 &
+1.15 & 1.17 & Model generalizes well (out-of-sample) \\
+United Kingdom of Great Britain and Northern Ireland & 79.2 & 78.26 &
+1.15 & 1.17 & Model generalizes well (out-of-sample) \\
+United Kingdom of Great Britain and Northern Ireland & 80.9 & 80.69 &
+1.15 & 1.17 & Model generalizes well (out-of-sample) \\
+United Kingdom of Great Britain and Northern Ireland & 82.6 & 83.18 &
+1.15 & 1.17 & Model generalizes well (out-of-sample) \\
+United Republic of Tanzania & 67.4 & 66.21 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+United Republic of Tanzania & 65.2 & 63.79 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+United Republic of Tanzania & 64.4 & 63.79 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+United Republic of Tanzania & 63.5 & 63.79 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+United States of America & 79.5 & 80.81 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+United States of America & 76.5 & 75.89 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+United States of America & 78.6 & 78.31 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Uruguay & 77.8 & 77.11 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Uzbekistan & 72.3 & 70.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Uzbekistan & 70.4 & 70.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Uzbekistan & 70.0 & 70.78 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Vanuatu & 70.6 & 69.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Vanuatu & 64.0 & 64.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Vanuatu & 70.5 & 69.64 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Vanuatu & 63.8 & 64.73 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Venezuela (Bolivarian Republic of) & 72.4 & 72.95 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Venezuela (Bolivarian Republic of) & 72.4 & 72.95 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Venezuela (Bolivarian Republic of) & 73.9 & 72.95 & 1.15 & 1.17 & Model
+generalizes well (out-of-sample) \\
+Viet Nam & 68.9 & 71.20 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Viet Nam & 73.2 & 73.62 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Viet Nam & 77.5 & 76.12 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Yemen & 63.7 & 64.83 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Yemen & 69.4 & 69.75 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Zambia & 59.4 & 58.79 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Zambia & 61.8 & 61.21 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Zimbabwe & 61.0 & 60.87 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Zimbabwe & 55.8 & 55.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+Zimbabwe & 55.5 & 55.96 & 1.15 & 1.17 & Model generalizes well
+(out-of-sample) \\
+
+\end{longtable}
 

### 2024-12-04 paper/paper.qmd
initila

@@
 female_table <- read_parquet("~/lifeexpectancy/data/02-analysis_data/female_table.parquet")
+average_life_expectancy <- read_parquet("~/lifeexpectancy/data/02-analysis_data/average_life_expectancy.parquet")
+sum_sta <- read_parquet("~/lifeexpectancy/data/02-analysis_data/sum_sta.parquet")
+matable <- read_parquet("~/lifeexpectancy/data/02-analysis_data/matable.parquet")
+femaletable <- read_parquet("~/lifeexpectancy/data/02-analysis_data/femaletable.parquet")
+model_developed <- readRDS(file = "~/lifeexpectancy/models/ledata_normal_model.rds")
 ```
@@
 For easier visualization, we created four tables, which are grouped by life expectancy at age 60, life expectancy at birth, life expectancy at birth of Male and life expectancy at birth of Female.
+For easier summary and convenience for graph drawing, we calculate the average of life expectancy of each country under 6 years.
+Also, we calculate the average of 6 years life expectancy according to the other 4 income groups and different gender by mutate according to the different factors.
+We then merge the columns of each table into a summary table for easy looking.
 
 @fig-sum_sta shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
+Life expectancy according to different countries have attached and be found in data cleaning full data in @sec-appendix.
 
@@
 #| label: tbl-sum_sta
-#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy.
-With a huge gap between 25 and 50, we could indicate that most of the countries has a life expectancy of.
-There exist large data with low life expectancy less than 25 years.
+#| fig-cap: "This table shows the cleaned data of life expectancy at different predictor.
+We could visual that high income has the highest life expectancy of 79.8, compared to lower income has the least life expectancy of 62.35.
+Among all the region, it's clear that Africa has the least 64.17, while Europe has the highest 78.50 years old.
+Female has slightly higher life expectancy than male.
 "
@@
 
-# find average life expectancy for both sex
-bothsexavg <- leab |>
-  filter(Gender == "Both sexes") |>
-  summarise(
-    "Gender" = "Both sexes",
-    "Average life ex" = mean(`Life Expectancy`))
-
-#find average life expectancy of female
-female_tableavg <- female_table |>
-  summarise(
-    "Gender" = "Female",
-    "Average life ex" = mean(`Life Expectancy`))
-
-#find average life expectancy of male
-male_tableavg <- male_table |>
-  summarise(
-    "Gender" = "Male",
-    "Average life ex" = mean(`Life Expectancy`))
-
-#find average life expectancy of Africa
-africaavg <- leab |>
-  filter(Region == "Africa") |>
-  summarise(
-    "Group" = "Africa",
-    "Average life ex" = mean(`Life Expectancy`, na.rm = TRUE)
-  )
-
-##find average life expectancy of Asia
-asiaavg <- leab |>
-  filter(Region == "Asia") |>
-  summarise(
-    "Region" = "Asia",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of North America
-naavg <- leab |>
-  filter(Region == "North America") |>
-  summarise(
-    "Region" = "North America",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of South America
-saavg <- leab |>
-  filter(Region == "South America") |>
-  summarise(
-    "Region" = "South Amereica",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of Oceania
-oceaniaavg <- leab |>
-  filter(Region == "Oceania") |>
-  summarise(
-    "Region" = "Oceania",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of Europe
-europeavg <- leab |>
-  filter(Region == "Europe") |>
-  summarise(
-    "Region" = "Europe",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of lower_income
-lowavg <- leab |>
-  filter(Income_Group == "lower_income") |>
-  summarise(
-    "Income_Group" = "lower_income",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of lower_middle
-middleavg <- leab |>
-  filter(Income_Group == "lower_middle") |>
-  summarise(
-    "Income_Group" = "lower_middle",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of upper_middle
-upperavg <- leab |>
-  filter(Income_Group == "upper_middle") |>
-  summarise(
-    "Income_Group" = "upper_middle",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-#find average life expectancy of high_income
-highavg <- leab |>
-  filter(Income_Group == "high_income") |>
-  summarise(
-    "Income_Group" = "high_income",
-    "Average life ex" = mean(`Life Expectancy`)
-  )
-
-# create a summary statistic by binding all the subtables into one
-sum_sta <- bind_rows(
-  bothsexavg,
-  male_tableavg,
-  female_tableavg,
-  africaavg,
-  asiaavg,
-  naavg,
-  saavg,
-  oceaniaavg,
-  europeavg,
-  lowavg,
-  middleavg,
-  upperavg,
-  highavg
-)
-
-# View the combined summary table
-sum_sta
+# Format and display the sum_sta table
+# Load necessary libraries
+library(knitr)
+library(kableExtra)
+
+# Format and style the sum_sta table using kableExtra
+sum_sta %>%
+  kbl(
+    col.names = c("Region/Income/Gender", "Life Expectancy"),  # Column names
+    align = c("l", "c"),                                       # Left-align column 1, center-align column 2
+    digits = 2,                                                # Round values to 2 decimal places
+    booktabs = TRUE,                                           # LaTeX-style table rule
+  ) %>%
+  kable_styling(
+    latex_options = c("striped", "hold_position"),             # Add striped rows and prevent table floating
+    full_width = FALSE,                                        # Prevent table from stretching to full width
+    font_size = 10                                             # Adjust font size
+  ) %>%
+  add_header_above(c(" " = 1, "Life Expectancy Summary" = 1),bold = TRUE) %>%
+  add_header_above(c(" " = 2), bold = TRUE) # Add a header row
 
@@
 
-@fig-expectancy visualizes the distribution of life expectancy from 2015 to 2020 as percentages, combining a histogram and a density plot.
-A large concentration of observations is observed range of 0% to 25%, reflecting a significant proportion of countries with lower life expectancy relative to others in the dataset.
-Another visible concentration is around 75% to 100%, indicating a group of countries with relatively high life expectancy.
-The blue density curve overlays the histogram, providing a smoothed representation of the distribution.
-Peaks in the curve correspond to high frequency within the histogram.
-The density plot emphasized the bimodal nature of the distribution with two distinct peaks: one around 12 as low life expectancy percentages; another peak around 87as high life expectancy percentage.
+@fig-expectancy visualizes the distribution of life expectancy from 2015 to 2020 as percentages.
+The histogram visualizes the distribution of life expectancy grouped into 5-year ranges, expressed as percentages.
+Most of the data lies between the ranges of 66–81 years, with the largest percentage (24.7%) in the 76–81 range.
+This suggests that a significant portion of individuals have life expectancy within this range.
+The data also shows smaller percentages at the lower (46–56 years) and higher ends (81–86 years).
+Additionally, a small percentage of missing (NA) values may highlight areas for data quality.
+Even we remove the NA while cleaning, the data of NA still exists for not belongs to any of these ranges.
 
@@
 #| label: fig-expectancy
-#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy.
-With a huge gap between 25 and 50, we could indicate that most of the countries has a life expectancy of.
-There exist large data with low life expectancy less than 25 years.
+#| fig-cap: "This histogram shows the distribution of the percentage of life expectancy for all years.
+Among all the life expectancy ranges, 76-81 has the largest percenage of 24.7%, while the 46-51 has the 0.54%.
+Life expectancy shows a growing trend with the increasing of age and drop sharply comes to the 81-86 range.
 "
@@
 
-# Assuming lelecleaned_data is the data frame containing life expectancy
+# leab is the data frame containing life expectancy of life expectancy at birth of all 3312 data
 # Bin Life Expectancy into 5-year ranges
@@
   mutate(Percentage = 100 * Count / sum(Count))
-
-# Print the table showing age ranges and percentages
-print(life_expectancy_bins)
 
@@
 ```{r}
-
-#read the model developed
-model_developed <-
-  readRDS(file = "~/lifeexpectancy/models/ledata_normal_model.rds")
-
 # Split the dataset into training and testing sets (80% train, 20% test)
@@
 # Predict life expectancy using the test data
-predictions <- predict(ledata_normal_model, newdata = test_data)
+predictions <- predict(model_developed, newdata = test_data)
 ```
@@
 # Calculate RMSE for the training set (in-sample testing)
-train_predictions <- predict(ledata_normal_model, newdata = train_data)
+train_predictions <- predict(model_developed, newdata = train_data)
 train_rmse <- sqrt(mean((train_predictions - train_data$`Life Expectancy`)^2))
@@
 
+## Data results analysis
+
+According to the @tbl-sum_sta, we could tell that
+
 ## Overview of model results
 
-Our results are summarized in @tbl-model. We are primarily interest in the
+Our results are summarized in @tbl-model.
+We are primarily interest in the general life expectancy regarding to the related predictors.
+The multiple linear model provides us with the estimates for the intercept and coefficients for the predictors which are male, female, both genders, lower income, lower-middle, upper-middle, high income, Asia, Europe, Africa, Oceania, North America and South America.
+The intercept represents the estimate of region-standard life expectancy when all the predictors are zero.
+The coefficients represent the additional life expectancy associated with each predictor.
+The model results will display the estimates- posterior means or medians for each coefficient including the intercept, uncertainty measures- credible intervals.
+The output values of each predictor is the regression coefficient, meaning how much the outcome is expected to increase or decrease with one unit increase in the life expectancy (per year) of that predictor, holding all else constant.
+The value in the brackets represent the Median Absolute Deviation of the posterior distributions of the coefficients.
+It conveys the dispersion around the median of each coefficients' posterior distribution, exhibiting how spread the distributions are.
+
+Num.Obs represents the number of observations made in the model.
+R2 is the R-squared value which is the proportion of variance in the dependent variable that can be explained bu the independent variable.
+The R2 adj is the adjusted R squared which accounts for the number of predictors used.
+Log.lik is the log-likelihood which gives us an idea of the likelihood of the data, higher is the better, but this is typically used for comparison between the models.
+ELPD and ELPD s.e.
+explains the log predictive density and its standard error.
+The ELPD measures the sum of the log predictive densities for each observation, used for model comparison.
+LOOIC is an acronym for leave-one-out information criterion in which a lower value indicates a model with better out-of-sample predictive performance.
+WAIC stands for Watanabe-Akaike information criterion which is another measure of good fit; lower values are better fit.
+RMSE is the room mean squared error measuring the models's predictive performance where lower values means more accurate predicts.
 
@@
 modelsummary(
-  list("Gaussian(Normal)" = ledata_normal_model),
+  list("Gaussian(Normal)" = model_developed),
   statistic = "mad",  # Median absolute deviation
@@
 
-The
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-regresult
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-```
+@tbl-model is the table of the results from out model.
+The intercept serves as the baseline, which in this case is 79.53.
+Asia shows a negative coefficient of -6.22, indicating lower values compared to the baseline, with a relatively large standard error of 21.20.
+This suggests that as the predictor increases, the outcome tends to increase.
+In contrast, a negative coefficient implies a decrease in the outcome.
+Europe exhibits a negligible negative effect of -8.39, though it also has a large standard error of 45.65.
+The effect for females is more substantial, with a positive coefficient of 2.50 and a standard error of 0.05, indicating considerable variability in the estimate.
+The male and lower-middle-income groups show minimal negative coefficients, suggesting slight decreases from the baseline.
+The upper-middle-income group, however, shows a positive effect of 3.40 relative to the baseline.
+Regions like North America, Oceania, Asia, and Europe all have notable negative coefficients, highlighting significant regional variations.
+In general, there is a downward trend in coefficients across countries.
+Most countries exhibit large standard errors, with European countries such as Ireland, Israel, and Italy showing slightly positive trends.
+
+With an R-squared value of 0.976, the model demonstrates a strong level of explanatory power, supporting the accuracy of the results.
+The adjusted R-squared value is 0.975, which is nearly identical to the R-squared value, indicating the model's robustness with 3,312 observations.
+The RMSE of 4.37 reflects the average magnitude of the model's prediction errors, suggesting good predictive accuracy.
+Although values like LOOIC and WAIC are excluded due to the lack of alternative models for comparison, the overall results indicate that the model performs well on the cleaned dataset.Further evaluation of the model results will be done in @sec-model_details.
 

### 2024-12-04 paper/paper.qmd
commint

@@
 
-According to the @tbl-sum_sta, we could tell that
+According to @fig-summary, we could tell that the mean life expectancy over the 6 years is 72.2, with a relatively low standard deviation of 7.8.
+This suggests that, on average, life expectancy across the dataset is fairly consistent, with only moderate variation from the mean.
+However, the maximum life expectancy of 87.4 stands out significantly, indicating that some countries or regions are achieving substantially higher life expectancy.With the mean at 72.2 and the median at 73.1, it’s apparent that the data is fairly symmetric, with the median being slightly higher than the mean, suggesting a mild left skew.
+This shift, combined with the large maximum value, hints at the presence of outliers—countries with exceptionally high life expectancy that pull the maximum up.
+The variance of 60.1 is relatively large, further supporting the idea that the data spans a wide range, with some observations considerably deviating from the central tendency.
+
+Given this, the high variance can be attributed to the diversity in life expectancy values across different regions, particularly when countries at the higher end of the spectrum (e.g., those with life expectancy around 87 years) are compared with those at the lower end.
+This variability suggests that while most countries have life expectancy near 72 years, the outliers significantly influence the spread of the data, leading to a higher variance than what would be expected in a more homogenous dataset.
+Therefore, while the standard deviation is relatively small, the data is far from uniform, and a deeper analysis of the outliers could provide further insights into the factors contributing to the high life expectancy in certain regions.
+
+@tbl-sum_sta summarizes global life expectancy across various categories such as gender, geographic regions, and income levels.
+We could tell that the global life expectancy is 72.13 years, providing a benchmark against which other categories can be compared.
+Women have a significantly higher life expectancy (74.62 years) than men (69.71 years), which reflects a common global trend due to biological and social factors.
+Region variation does happens to influence the life expectncy.
+Europe has the highest life expectancy (78.50 years), which is likely due to better healthcare and living conditions, with having the most amount of high income countries.
+Africa has the lowest (64.17 years), potentially reflecting challenges like limited healthcare infrastructure, poverty, and infectious diseases.
+Income level, as one of the most essential factor, significantly affect the life expectancy.
+High-income countries have the highest life expectancy (79.38 years), illustrating the correlation between economic wealth and longevity.
+High income level are believed to enable better living standard compared to other income groups.
+Upper middle income countries has an average of 73.38 years, where we could observe that the difference is significant lower than high income group.
+Lower middle income group has the life expectancy drop to 68.40.
+While these countries usually face challenges such as infrastructure and limit access to health resources, economic growth may need to be taken seriously be policy makers.
+Lower-income countries have a significantly lower life expectancy of 62.35 years, which can be attributed to limited access to healthcare, education, and basic services.
+@tbl-sum_sta highlights global inequalities and emphasizes the importance of improving living standards, especially in lower-income and underdeveloped regions.
 

### 2024-12-04 paper/paper.qmd
ini
jk

@@
 The finding indicates that the life expectancy is tend to get higher as the economic class grows.
-And we predict that the average age of person from low, lower-middle, upper-middle and high are 65,70, 75,80.
+And we predict that the average age of person from low, lower-middle, upper-middle and high are 62.35, 68.40, 73.38, 79.38.
 The result of this paper will help in suggesting a country which area should be given importance in order to efficiently improve the life expectancy of its population."
@@
 model_developed <- readRDS(file = "~/lifeexpectancy/models/ledata_normal_model.rds")
+bothg_average_life_expectancy <- read_parquet("~/lifeexpectancy/data/02-analysis_data/bothg_average_life_expectancy.parquet")
 ```
@@
 This analysis uses the statistical programming language R [@citeR] and several libraries, including `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `dplyr` [@dplyr], `arrow` [@arrow], `purrr` [@purrr], `sf` [@sf], and `here` [@here] for data manipulation.
-`ggplot2` [@ggplot], `ggcorrplot` [@ggcorrplot] and `kableExtra` [@kableExtra] for visualization.
+`ggplot2` [@ggplot2], `ggcorrplot` [@ggcorrplot] and `kableExtra` [@kableExtra] for visualization.
 The dataset covers various predictors conducted across multiple countries, capturing the support for a country to determine the predicting factor which is contributing to lower value of life expectancy.
@@
 
-**Region(Region)**: This is a categorical variable that classifies the geographic location of the countries.
+**Region(`Region`)**: This is a categorical variable that classifies the geographic location of the countries.
 It is mapped one by one by the name of the country.
@@
 
-@fig-sum_sta shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
-Life expectancy according to different countries have attached and be found in data cleaning full data in @sec-appendix.
+@tbl-sum_sta shows the average of life expectancy under male, female, 6 different regions and 4 income groups.
+Life expectancy according to different countries have attached and be found in data cleaning full data in @sec-appx.
 
@@
 #| label: tbl-sum_sta
-#| fig-cap: "This table shows the cleaned data of life expectancy at different predictor.
+#| tbl-cap: "This table shows the cleaned data of life expectancy at different predictor.
 We could visual that high income has the highest life expectancy of 79.8, compared to lower income has the least life expectancy of 62.35.
@@
 
-# Format and display the sum_sta table
-# Load necessary libraries
-library(knitr)
-library(kableExtra)
-
 # Format and style the sum_sta table using kableExtra
 sum_sta %>%
-  kbl(
+  kable(
     col.names = c("Region/Income/Gender", "Life Expectancy"),  # Column names
     align = c("l", "c"),                                       # Left-align column 1, center-align column 2
-    digits = 2,                                                # Round values to 2 decimal places
-    booktabs = TRUE,                                           # LaTeX-style table rule
-  ) %>%
-  kable_styling(
-    latex_options = c("striped", "hold_position"),             # Add striped rows and prevent table floating
+    digits = 2 ) %>%
+  kable_styling(          # Add striped rows and prevent table floating
     full_width = FALSE,                                        # Prevent table from stretching to full width
     font_size = 10                                             # Adjust font size
-  ) %>%
-  add_header_above(c(" " = 1, "Life Expectancy Summary" = 1),bold = TRUE) %>%
-  add_header_above(c(" " = 2), bold = TRUE) # Add a header row
+  )
 
 ```
+
 ## Outcome Variables
@@
 Higher income countries typically have more resources to invest in robust healthcare systems, with better living conditions while lower income countries often face challenges such as inadequate healthcare infrastructure and malnutrition.
-
 Following by the four income group, we would like to see the distribution of the income group of 184 WHO member countries.
-@fid-income shows that there are 55 countries at the high income group, 26 countries at low income group, 54 countries at the lower-middle group while there are 49 countries at the upper-middle group.
+@fig-income shows that there are 55 countries at the high income group, 26 countries at low income group, 54 countries at the lower-middle group while there are 49 countries at the upper-middle group.
 With significant less low income countries, we expect to see the life expectancy lie in a comparably higher range.
@@
 #| label: fig-income
-#| fig-cap: "Distribution of country income group."
+#| fig-cap: "Distribution of country income group.
+Among 184 WHO member countries, there are 55 high income countries, 54 lower middle income countries and 49 upper middle income countries.
+There are significant less lower income countries, which we could assume there might exist less outliers in life experctanncy."
 #| echo: false
@@
 #| label: fig-summary
-#| fig-cap: "Summary statistics of the number of life expectancy over countries and years. "
+#| fig-cap: "Summary statistics of the number of life expectancy over countries and years.
+Less difference between mean and median, showing that the life expectancy distribution might shows a naturally bell curve.However, variance is slightly high indicates that the tails on both sides might be long.
+"
 #| echo: false
@@
   summarise(
-    Mean = round(mean(`Life Expectancy`, na.rm = TRUE),1),
+    Mean = round(mean(`Life Expectancy`, na.rm = TRUE), 1),
     Median = median(`Life Expectancy`, na.rm = TRUE),
     Max = max(`Life Expectancy`, na.rm = TRUE),
-    SD = round(sd(`Life Expectancy`, na.rm = TRUE),1),
-    Variance = round(var(`Life Expectancy`, na.rm = TRUE),1),
+    SD = round(sd(`Life Expectancy`, na.rm = TRUE), 1),
+    Variance = round(var(`Life Expectancy`, na.rm = TRUE), 1),
     N = sum(!is.na(`Life Expectancy`)) # Count of non-missing values
@@
 life_expectancy_stats %>%
-  kbl(
-    caption = "Summary Statistics of Life Expectancy",
+  kable(
     col.names = c("Mean", "Median", "Max", "Standard Deviation", "Variance", "N"),
@@
     full_width = FALSE, 
-    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
     font_size = 14
-  ) %>%
-  column_spec(1, bold = TRUE, color = "white", background = "darkblue") %>% # Highlight the first column
-  column_spec(2:ncol(life_expectancy_stats), color = "black") %>% # Style the data columns
-  row_spec(0, bold = TRUE, background = "lightgray") %>% # Add a header row styling
-  add_header_above(c(" " = 6)) %>% # Add optional grouping header
-  footnote(
-    general = "This table summarizes the key statistics of life expectancy data.",
-    footnote_as_chunk = TRUE, 
-    general_title = "Note:"
   )
@@
 ```{=tex}
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \text{(1)} \\
-\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\text{(2)} \\
-\alpha &\sim \text{Normal}(0, 2.5) \text{(3)}\\
-\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \text{(4)}\\
-\sigma &\sim \text{Exponential}(1) \text{(5)} \\
-\end{align}
+
+\begin{align*} 
+y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income\_Group}_i \\
+\alpha &\sim \text{Normal}(0, 2.5) \\
+\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\
+\sigma &\sim \text{Exponential}
+\end{align*}
+
 ```
-
 Where:
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. More explanation of the model could be found [Appendix -@sec-model-details].
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. More explanation of the model could be found [Appendix @sec-model-details].
 
-### Model justification
+## Model justification {#sec-modjust}
 
@@
 
-#### Model Validation
+## Model Validation
 
@@
 ```{r}
+#| label: tbl-modelpredict
+#| tbl-cap: "Summary of the life expectancy model, which includes gender, region and income group.
+The table presents the model RSME and out-of sample testing.
+Seeing the testing data slightly less than the training data, our model is under good generalization."
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
 # Split the dataset into training and testing sets (80% train, 20% test)
@@
 predictions <- predict(model_developed, newdata = test_data)
-```
-
-```{r}
-#| label: tbl-modelpredict
-#| tbl-cap: Summary of the life expectancy model, which includes gender, region and income group. The table presents the model RSME and out-of sample testing.
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
 
@@
 rmse_table %>%
-  kbl(
+  kable(
     col.names = c("Dataset", "RMSE"), 
-    caption = "RMSE Comparison for Test and Training Data",
     align = "c", # Center alignment for columns
@@
   kable_styling(
-    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
     full_width = FALSE,
     font_size = 14
-  ) %>%
-  column_spec(1, bold = TRUE, color = "white", background = "steelblue") %>%
-  column_spec(2, color = "black") %>%
-  add_header_above(c(" " = 1, "Root Mean Squared Error (RMSE)" = 1))
+  )
 
@@
 
-# Results
+# Results {#sec-result}
 
@@
   statistic = "mad",  # Median absolute deviation
-  fmt = 2             # Format results to 2 decimal places
+  fmt = 2,     # Format results to 2 decimal places
+  output = "kableExtra"
+) %>%
+  kable_styling(font_size = 8.5,
+                full_width = FALSE,  # Keeps the table from spanning the full width
+    position = "center", # Centers the table
+    bootstrap_options = c("striped", "condensed") # Makes rows tighter
   )
@@
 The RMSE of 4.37 reflects the average magnitude of the model's prediction errors, suggesting good predictive accuracy.
-Although values like LOOIC and WAIC are excluded due to the lack of alternative models for comparison, the overall results indicate that the model performs well on the cleaned dataset.Further evaluation of the model results will be done in @sec-model_details.
+Although values like LOOIC and WAIC are excluded due to the lack of alternative models for comparison, the overall results indicate that the model performs well on the cleaned dataset.Further evaluation of the model results will be done in @sec-model-details.
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-From the summary and analysis of @tbl-regresult, we have seen that high income group has the significant high life expectancy compared to the lower income group, which indicates that life expectancy is significantly influenced by income groups.
+From the summary and analysis of @tbl-sum_sta, we have seen that high income group has the significant high life expectancy compared to the lower income group, which indicates that life expectancy is significantly influenced by income groups.
 It is known that income determines access to resources, healthcare and living conditions.
@@
 
-# Appendix {#sec-appendix}
+# Appendix {#sec-appx}
 
@@
 
-## Data Cleaning Full Table
+## Data Cleaning Table
 
@@
 #| label: tbl-cleaned_average
-#| tbl-cap: "Full cleaned Average life expectancy"
+#| tbl-cap: "Cleaned data of average life expectancy of 6 years by different countries.
+Full cleaned Average life expectancy by country by gender could be find in https://github.com/wendyhuan/lifeexpectancy/blob/main/data/02-analysis_data/average_life_expectancy.csv"
 #| echo: false
@@
 # Create a nicely formatted kable table
-average_life_expectancy %>%
+bothg_average_life_expectancy %>%
   kable(
-    col.names = c("Country", "Gender", "Income Group", "Region", "Average Life Expectancy"),
+    col.names = c("Country", "Income Group", "Region", "Average Life Expectancy"),
     align = c("l", "l", "l", "l", "r"),
-    digits = 2
+    digits = 2,
+    output = "kableExtra"
 ) %>%
-  kable_styling(
-    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
+  kable_styling(font_size = 8.5,
     full_width = FALSE,
-    position = "center"
-  ) %>%
-  row_spec(0, bold = TRUE, color = "white", background = "#0073C2") %>% # Style the header row
-  column_spec(5, bold = TRUE, background = "#F7F7F7")
-
+    position = "center",
+    bootstrap_options = c("striped", "condensed")
+  ) 
 ```
@@
 
-**1. Outcome variable (yi)**
+**1. Outcome variable (**$y_i$)
 
@@
 
-**2. Linear Predictor (μi)**
+**2. Linear Predictor (**$μ_i$)
 
 The linear predictor $μ_i$ is a linear combination of the predictors, which includes an intercept term $α$ and the coefficients $β_1$, $β_2$, $β_3$, corresponding to Region, Income Group, and Gender, respectively.
-This linear equation models the relationship between life expectancy and the predictors $\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)$ The values for these coefficients (betas) represent the expected change in life expectancy for a one-unit change in each respective predictor.
+This linear equation models the relationship between life expectancy and the predictors $\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)$.
+The values for these coefficients (betas) represent the expected change in life expectancy for a one-unit change in each respective predictor.
 
@@
 **4.
-Residual Standard Deviation (σ)** The model also estimates $σ$, which represents the standard deviation of the residuals — the errors between the observed life expectancy values and those predicted by the model.
+Residual Standard Deviation (**$σ$) The model also estimates $σ$, which represents the standard deviation of the residuals — the errors between the observed life expectancy values and those predicted by the model.
 The prior for $σ$ is assumed to follow an exponential distribution with a rate of 1, meaning that smaller values of $σ$ (indicating less variation) are somewhat more likely than larger ones.
@@
 #| label: tbl-testpredicted
-#| tbl-cap: "Life expectancy over countries and years"
+#| tbl-cap: "Partical table of the test and training RMSE of Life expectancy over countries and gender of average of 6 years (First 100 rows).
+Through the model part we could tell that with comparing the training and testing data, the model is well generated without doubt."
 #| echo: false
@@
 # Format the table using kable
-kable(
-  results_df,
-  col.names = c("Country", "Actual Life Expectancy", "Predicted Life Expectancy", "RMSE (Test)", "RMSE (Train)", "Indication"),
+results_df %>%
+  head(100) %>%
+  kable(col.names = c("Country", "Actual Life Expectancy", "Predicted Life Expectancy", "RMSE (Test)", "RMSE (Train)", "Indication"),
   align = c("l", "r", "r", "r", "r", "l"),
   digits = 2,
-  booktabs = TRUE
-)
+  output = "kableExtra"
+) |>
+  kable_styling(font_size = 7.5,
+                full_width = FALSE,  # Keeps the table from spanning the full width
+    position = "center", # Centers the table
+    bootstrap_options = c("striped", "condensed"))
 

### 2024-12-04 scripts/03-clean_data.R
i

@@ -364,6 +364,7 @@ write_csv(sum_sta, "data/02-analysis_data/sum_sta.csv")
 write_csv(matable, "data/02-analysis_data/matable.csv")
 write_csv(femaletable, "data/02-analysis_data/femaletable.csv")
 write_csv(average_life_expectancy, "data/02-analysis_data/average_life_expectancy.csv")
+write_csv(bothg_average_life_expectancy, "data/02-analysis_data/bothg_average_life_expectancy.csv")
 write_parquet(lelecleaned_data, "data/02-analysis_data/lelecleaned.parquet")
 write_parquet(lea60, "data/02-analysis_data/lea60.parquet")
 write_parquet(leab, "data/02-analysis_data/leab.parquet")
@@ -373,4 +374,5 @@ write_parquet(female_table, "data/02-analysis_data/female_table.parquet")
 write_parquet(matable, "data/02-analysis_data/matable.parquet")
 write_parquet(femaletable, "data/02-analysis_data/femaletable.parquet")
 write_parquet(average_life_expectancy, "data/02-analysis_data/average_life_expectancy.parquet")
+write_parquet(bothg_average_life_expectancy, "data/02-analysis_data/bothg_average_life_expectancy.parquet")
 

### 2024-12-04 scripts/05-model_data.R

@@ -19,11 +19,12 @@ library(modelsummary) # for summarizing the model
 #### Read data ####
 lea60 <- read_parquet("data/02-analysis_data/lea60.parquet")
 leab <- read_parquet ("data/02-analysis_data/leab.parquet")
+average_life_expectancy <- read_parquet("data/02-analysis_data/average_life_expectancy.parquet")
 
 # Fit the Bayesian linear regression model using stan_glm
 ledata_normal_model <- stan_glm(
   `Life Expectancy` ~ Region + Country + Income_Group + Gender, 
-  data = leab, 
+  data = average_life_expectancy, 
   family = gaussian(link = "identity"), 
   prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
   prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-12-04 paper/paper.qmd
momo

@@
 toc: true
+pdf-engine: xelatex
+geometry: landscape
 toc-depth: 3
+keep-tex: true
+output:
+  pdf_document:
+    extra_dependencies: ["longtable"]
 number-sections: true
@@
   geom_bar(stat = "identity", color = "white", alpha = 0.8) +
-  geom_text(aes(label = paste0(round(Percentage, 2), "%")), vjust = -0.5, size = 3.5) +
+  geom_text(aes(label = paste0(round(Percentage, 2), "%")), vjust = -0.5, size = 2.5) +
   labs(
@@
 ) %>%
-  kable_styling(font_size = 8.5,
+  kable_styling(
+    font_size = 7.5,
                 full_width = FALSE,  # Keeps the table from spanning the full width
                 position = "center", # Centers the table
-    bootstrap_options = c("striped", "condensed") # Makes rows tighter
-  )
+                bootstrap_options = c("striped", "condensed"))
 
@@
 The income group column and the region column was not given in the raw dataset.
-We created a new variable called "Income_Group" by mapping over country name to four income group (lower_income, lower_middle, upper_middle, high_income) according to the index given by World Bank Income Group.
+We created a new variable called "Income_Group" by mapping over country name to four income group ("lower_income", "lower_middle", "upper_middle", "high_income") according to the index given by World Bank Income Group.
 This is a key variable in predicting life expectancy since it is believed that life expectancy is correlated to the income situation.
@@
 #| label: tbl-cleaned_average
-#| tbl-cap: "Cleaned data of average life expectancy of 6 years by different countries.
-Full cleaned Average life expectancy by country by gender could be find in https://github.com/wendyhuan/lifeexpectancy/blob/main/data/02-analysis_data/average_life_expectancy.csv"
+#| tbl-cap: "Cleaned data of average life expectancy of 6 years by different countries."
 #| echo: false
@@
 ) %>%
-  kable_styling(font_size = 8.5,
+  kable_styling(font_size = 5.5,
     full_width = FALSE,
@@
 ) |>
-  kable_styling(font_size = 7.5,
+  kable_styling(font_size = 8.5,
                 full_width = FALSE,  # Keeps the table from spanning the full width
-    position = "center", # Centers the table
-    bootstrap_options = c("striped", "condensed"))
+    bootstrap_options = c("striped", "condensed")) %>%
+  column_spec(1, width = "0.35in") %>%
+  column_spec(3:6, width = "1in")
 

### 2024-12-04 paper/paper.tex
momo

--- 2024-12-04 paper/paper.tex
@@
 \usepackage{xcolor}
+\usepackage[landscape]{geometry}
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \makeatother
-
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{241,243,245}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
 
@@
 \usepackage{xcolor}
+\usepackage{siunitx}
+
+    \newcolumntype{d}{S[
+      table-align-text-before=false,
+      table-align-text-after=false,
+      input-symbols={-,\*+()}
+    ]}
+
 \KOMAoption{captions}{tableheading}
@@
 the economic class grows. And we predict that the average age of person
-from low, lower-middle, upper-middle and high are 65,70, 75,80. The
-result of this paper will help in suggesting a country which area should
-be given importance in order to efficiently improve the life expectancy
-of its population.
+from low, lower-middle, upper-middle and high are 62.35, 68.40, 73.38,
+79.38. The result of this paper will help in suggesting a country which
+area should be given importance in order to efficiently improve the life
+expectancy of its population.
 \end{abstract}
@@
 lower economic situation, and inadequate healthcare access of different
-region. (\textbf{socialdeterminantsofhealth?}).
+region. (Wilkinson 2003).
 
@@
 highlighting that gender-specific health behaviors and societal roles
-influence longevity (\textbf{GenderandLifeExpectancy?}). Higher-income
-individuals tend to live longer due to better access to healthcare and
-healthier lifestyles, with notable regional disparities even within
-similar income groups (\textbf{IncomeGroupsandLongevity?}).
-Additionally, regional socioeconomic differences on health outcomes,
-especially life expectancy. It emphasizes that addressing regional
-inequities in wealth and resources is essential for improving population
-health globally. (\textbf{RegionalVariations?}).
+influence longevity (Oksuzyan 2008b). Higher-income individuals tend to
+live longer due to better access to healthcare and healthier lifestyles,
+with notable regional disparities even within similar income groups
+(Chetty 2016). Additionally, regional socioeconomic differences on
+health outcomes, especially life expectancy. It emphasizes that
+addressing regional inequities in wealth and resources is essential for
+improving population health globally. (F. Marmot M. 2008).
 
@@
 model setup in Section~\ref{sec-modset} and justification in
-\textbf{?@sec-modjust}. The results in \textbf{?@sec-result} presents
-the key findings of the analysis, with a discussion on the implications.
-\textbf{?@sec-discussion} then discusses potential limitations and
-suggestions for future research. \textbf{?@sec-appx} provides additional
-detailed information about the data, model and methodology.
+Section~\ref{sec-modjust}. The results in Section~\ref{sec-result}
+presents the key findings of the analysis, with a discussion on the
+implications. Section~\ref{sec-discussion} then discusses potential
+limitations and suggestions for future research. Section~\ref{sec-appx}
+provides additional detailed information about the data, model and
+methodology.
 
@@
 The data used in this analysis originates from The World Health
-Organization's (WHO) and Global Health Observatory (GHO)
-(\textbf{lifeexpectancy?}). This data-set related to life expectancy,
-health factors for 184 countries has been collected from WHO data
-repository website and its corresponding economic data was collected
-from United Nation website. Among all categories of health-related
-factors only those socio-economic factors on the national level were
-chosen for global scale analysis.
+Organization's (WHO) and Global Health Observatory (GHO) (WHO 2020).
+This data-set related to life expectancy, health factors for 184
+countries has been collected from WHO data repository website and its
+corresponding economic data was collected from United Nation website.
+Among all categories of health-related factors only those socio-economic
+factors on the national level were chosen for global scale analysis.
 
 This analysis uses the statistical programming language R (R Core Team
-2023) and several libraries, including \texttt{tidyverse}
-(\textbf{tidyverse?}), \texttt{janitor} (\textbf{janitor?}),
-\texttt{knitr} (\textbf{knitr?}), \texttt{dplyr} (\textbf{dplyr?}),
-\texttt{arrow} (\textbf{arrow?}), \texttt{purrr} (\textbf{purrr?}),
-\texttt{sf} (\textbf{sf?}), and \texttt{here} (\textbf{here?}) for data
-manipulation. \texttt{ggplot2} (\textbf{ggplot?}), \texttt{ggcorrplot}
-(\textbf{ggcorrplot?}) and \texttt{kableExtra} (\textbf{kableExtra?})
+2023) and several libraries, including \texttt{tidyverse} (Wickham et
+al. 2019), \texttt{janitor} (Firke 2024), \texttt{knitr} (Xie 2024),
+\texttt{dplyr} (Wickham, François, et al. 2023), \texttt{arrow}
+(Richardson et al. 2023), \texttt{purrr} (Wickham and Henry 2023),
+\texttt{sf} (Pebesma and Bivand 2023), and \texttt{here} (Müller 2023)
+for data manipulation. \texttt{ggplot2} (Wickham, Chang, et al. 2023),
+\texttt{ggcorrplot} (Kassambara 2029) and \texttt{kableExtra} (Zhu 2023)
 for visualization. The dataset covers various predictors conducted
@@
 
-\textbf{Region(Region)}: This is a categorical variable that classifies
-the geographic location of the countries. It is mapped one by one by the
-name of the country. The data is stored as the name of the
+\textbf{Region(\texttt{Region})}: This is a categorical variable that
+classifies the geographic location of the countries. It is mapped one by
+one by the name of the country. The data is stored as the name of the
 continent(`Africa', `Oceania', `Asia', `Europe', `North America', `South
@@
 expectancy at age 60, life expectancy at birth, life expectancy at birth
-of Male and life expectancy at birth of Female.
-
-shows the average of life expectancy under male, female, 6 different
-regions and 4 income groups.
+of Male and life expectancy at birth of Female. For easier summary and
+convenience for graph drawing, we calculate the average of life
+expectancy of each country under 6 years. Also, we calculate the average
+of 6 years life expectancy according to the other 4 income groups and
+different gender by mutate according to the different factors. We then
+merge the columns of each table into a summary table for easy looking.
+
+Table~\ref{tbl-sum_sta} shows the average of life expectancy under male,
+female, 6 different regions and 4 income groups. Life expectancy
+according to different countries have attached and be found in data
+cleaning full data in Section~\ref{sec-appx}.
 
@@
 More information on the data cleaning process can be found in
-\textbf{?@sec-appx}.
+Section~\ref{sec-appx}.
+
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtable}[t]{lc}
+
+\caption{\label{tbl-sum_sta}This table shows the cleaned data of life
+expectancy at different predictor. We could visual that high income has
+the highest life expectancy of 79.8, compared to lower income has the
+least life expectancy of 62.35. Among all the region, it's clear that
+Africa has the least 64.17, while Europe has the highest 78.50 years
+old. Female has slightly higher life expectancy than male.}
+
+\tabularnewline
+
+\toprule
+Region/Income/Gender & Life Expectancy\\
+\midrule
+Global & 72.13\\
+Male & 69.71\\
+Female & 74.62\\
+Africa & 64.17\\
+Asia & 73.97\\
+\addlinespace
+North America & 75.04\\
+South America & 75.18\\
+Oceania & 70.17\\
+Europe & 78.50\\
+lower\_income & 62.35\\
+\addlinespace
+lower\_middle & 68.40\\
+upper\_middle & 73.38\\
+high\_income & 79.38\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
 
@@
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
 \item
@@
   while lower income countries often face challenges such as inadequate
-  healthcare infrastructure and malnutrition.
-\end{enumerate}
-
-Following by the four income group, we would like to see the
-distribution of the income group of 184 WHO member countries.
-(\textbf{fid-income?}) shows that there are 55 countries at the high
-income group, 26 countries at low income group, 54 countries at the
-lower-middle group while there are 49 countries at the upper-middle
-group. With significant less low income countries, we expect to see the
-life expectancy lie in a comparably higher range. On the other hand,
-there might exist sever outliers dropping the mean.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
+  healthcare infrastructure and malnutrition. Following by the four
+  income group, we would like to see the distribution of the income
+  group of 184 WHO member countries. Figure~\ref{fig-income} shows that
+  there are 55 countries at the high income group, 26 countries at low
+  income group, 54 countries at the lower-middle group while there are
+  49 countries at the upper-middle group. With significant less low
+  income countries, we expect to see the life expectancy lie in a
+  comparably higher range. On the other hand, there might exist sever
+  outliers dropping the mean.
 \item
@@
 
-\caption{\label{fig-income}Distribution of country income group.}
+\caption{\label{fig-income}Distribution of country income group. Among
+184 WHO member countries, there are 55 high income countries, 54 lower
+middle income countries and 49 upper middle income countries. There are
+significant less lower income countries, which we could assume there
+might exist less outliers in life experctanncy.}
 
@@
 
-\begin{table}
-\centering
-\caption{Summary Statistics of Life Expectancy}
-\centering
-\begin{tabular}[t]{c|c|c|c|c|c}
-\hline
+\begingroup\fontsize{14}{16}\selectfont
+
+\begin{longtable*}[t]{cccccc}
+\toprule
 Mean & Median & Max & Standard Deviation & Variance & N\\
-\hline
-45.9 & 37.7 & 87.4 & 26.9 & 724.2 & 6624\\
-\hline
-\end{tabular}
-\end{table}
+\midrule
+72.2 & 73.1 & 87.4 & 7.8 & 60.1 & 3312\\
+\bottomrule
+\end{longtable*}
+\endgroup{}
 
@@
 \caption{\label{fig-summary}Summary statistics of the number of life
-expectancy over countries and years.}
+expectancy over countries and years. Less difference between mean and
+median, showing that the life expectancy distribution might shows a
+naturally bell curve.However, variance is slightly high indicates that
+the tails on both sides might be long.}
 
@@
 
-\begin{align} 
+\begin{align*} 
 y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\
+\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income\_Group}_i \\
 \alpha &\sim \text{Normal}(0, 2.5) \\
 \beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\
-\sigma &\sim \text{Exponential}(1)
-\end{align}
+\sigma &\sim \text{Exponential}
+\end{align*}
 
@@
 We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
-package of Goodrich et al. (2022). We use the default priors from
+package of Goodrich et al. (2020). We use the default priors from
 \texttt{rstanarm}. More explanation of the model could be found
@@
 
-\subsubsection{Model justification}\label{model-justification}
+\subsection{Model justification}\label{sec-modjust}
 
@@
 
-\paragraph{Model Validation}\label{model-validation}
+\subsection{Model Validation}\label{model-validation}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\#model\_developed \textless{}{-}}
-  \CommentTok{\#readRDS(file = "\textasciitilde{}/lifeexpectancy/models/ledata\_normal\_model.rds")}
-
-\CommentTok{\# Split the dataset into training and testing sets (80\% train, 20\% test)}
-\CommentTok{\#set.seed(123)  \# Setting seed for reproducibility}
-\CommentTok{\#train\_index \textless{}{-} createDataPartition(leab$\textasciigrave{}Life Expectancy\textasciigrave{}, p = 0.8, list = FALSE)}
-
-\CommentTok{\#train\_data \textless{}{-} leab[train\_index, ]}
-\CommentTok{\#test\_data \textless{}{-} leab[{-}train\_index, ]}
-
-\CommentTok{\# Predict life expectancy using the test data}
-\CommentTok{\#predictions \textless{}{-} predict(ledata\_normal\_model, newdata = test\_data)}
-\end{Highlighting}
-\end{Shaded}
-
-\section{Results}\label{results}
+Extended versions of the table can be found in
+Table~\ref{tbl-testpredicted}.
+
+\begingroup\fontsize{14}{16}\selectfont
+
+\begin{longtable}[t]{cc}
+
+\caption{\label{tbl-modelpredict}Summary of the life expectancy model,
+which includes gender, region and income group. The table presents the
+model RSME and out-of sample testing. Seeing the testing data slightly
+less than the training data, our model is under good generalization.}
+
+\tabularnewline
+
+\toprule
+Dataset & RMSE\\
+\midrule
+Test Data & 1.15\\
+Training Data & 1.17\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\section{Results}\label{sec-result}
+
+\subsection{Data results analysis}\label{data-results-analysis}
+
+According to Figure~\ref{fig-summary}, we could tell that the mean life
+expectancy over the 6 years is 72.2, with a relatively low standard
+deviation of 7.8. This suggests that, on average, life expectancy across
+the dataset is fairly consistent, with only moderate variation from the
+mean. However, the maximum life expectancy of 87.4 stands out
+significantly, indicating that some countries or regions are achieving
+substantially higher life expectancy.With the mean at 72.2 and the
+median at 73.1, it's apparent that the data is fairly symmetric, with
+the median being slightly higher than the mean, suggesting a mild left
+skew. This shift, combined with the large maximum value, hints at the
+presence of outliers---countries with exceptionally high life expectancy
+that pull the maximum up. The variance of 60.1 is relatively large,
+further supporting the idea that the data spans a wide range, with some
+observations considerably deviating from the central tendency.
+
+Given this, the high variance can be attributed to the diversity in life
+expectancy values across different regions, particularly when countries
+at the higher end of the spectrum (e.g., those with life expectancy
+around 87 years) are compared with those at the lower end. This
+variability suggests that while most countries have life expectancy near
+72 years, the outliers significantly influence the spread of the data,
+leading to a higher variance than what would be expected in a more
+homogenous dataset. Therefore, while the standard deviation is
+relatively small, the data is far from uniform, and a deeper analysis of
+the outliers could provide further insights into the factors
+contributing to the high life expectancy in certain regions.
+
+Table~\ref{tbl-sum_sta} summarizes global life expectancy across various
+categories such as gender, geographic regions, and income levels. We
+could tell that the global life expectancy is 72.13 years, providing a
+benchmark against which other categories can be compared. Women have a
+significantly higher life expectancy (74.62 years) than men (69.71
+years), which reflects a common global trend due to biological and
+social factors. Region variation does happens to influence the life
+expectncy. Europe has the highest life expectancy (78.50 years), which
+is likely due to better healthcare and living conditions, with having
+the most amount of high income countries. Africa has the lowest (64.17
+years), potentially reflecting challenges like limited healthcare
+infrastructure, poverty, and infectious diseases. Income level, as one
+of the most essential factor, significantly affect the life expectancy.
+High-income countries have the highest life expectancy (79.38 years),
+illustrating the correlation between economic wealth and longevity. High
+income level are believed to enable better living standard compared to
+other income groups. Upper middle income countries has an average of
+73.38 years, where we could observe that the difference is significant
+lower than high income group. Lower middle income group has the life
+expectancy drop to 68.40. While these countries usually face challenges
+such as infrastructure and limit access to health resources, economic
+growth may need to be taken seriously be policy makers. Lower-income
+countries have a significantly lower life expectancy of 62.35 years,
+which can be attributed to limited access to healthcare, education, and
+basic services. Table~\ref{tbl-sum_sta} highlights global inequalities
+and emphasizes the importance of improving living standards, especially
+in lower-income and underdeveloped regions.
 
@@
 
-Our results are summarized in Table~\ref{tbl-modelresults}. We are
-primarily interest in the
+Our results are summarized in Table~\ref{tbl-model}. We are primarily
+interest in the general life expectancy regarding to the related
+predictors. The multiple linear model provides us with the estimates for
+the intercept and coefficients for the predictors which are male,
+female, both genders, lower income, lower-middle, upper-middle, high
+income, Asia, Europe, Africa, Oceania, North America and South America.
+The intercept represents the estimate of region-standard life expectancy
+when all the predictors are zero. The coefficients represent the
+additional life expectancy associated with each predictor. The model
+results will display the estimates- posterior means or medians for each
+coefficient including the intercept, uncertainty measures- credible
+intervals. The output values of each predictor is the regression
+coefficient, meaning how much the outcome is expected to increase or
+decrease with one unit increase in the life expectancy (per year) of
+that predictor, holding all else constant. The value in the brackets
+represent the Median Absolute Deviation of the posterior distributions
+of the coefficients. It conveys the dispersion around the median of each
+coefficients' posterior distribution, exhibiting how spread the
+distributions are.
+
+Num.Obs represents the number of observations made in the model. R2 is
+the R-squared value which is the proportion of variance in the dependent
+variable that can be explained bu the independent variable. The R2 adj
+is the adjusted R squared which accounts for the number of predictors
+used. Log.lik is the log-likelihood which gives us an idea of the
+likelihood of the data, higher is the better, but this is typically used
+for comparison between the models. ELPD and ELPD s.e. explains the log
+predictive density and its standard error. The ELPD measures the sum of
+the log predictive densities for each observation, used for model
+comparison. LOOIC is an acronym for leave-one-out information criterion
+in which a lower value indicates a model with better out-of-sample
+predictive performance. WAIC stands for Watanabe-Akaike information
+criterion which is another measure of good fit; lower values are better
+fit. RMSE is the room mean squared error measuring the models's
+predictive performance where lower values means more accurate predicts.
+
+\begin{table}
+
+\caption{\label{tbl-model}Summary of the life expectancy model, which
+includes gender, region and income group. The table presents the model
+RSME and out-of sample testing.}
+
+\centering{
+
+\centering\centering
+\fontsize{7.5}{9.5}\selectfont
+\begin{tabular}[t]{lc}
+\toprule
+  & Gaussian(Normal)\\
+\midrule
+(Intercept) & \num{79.53}\\
+ & (\num{43.50})\\
+RegionAsia & \num{-6.22}\\
+ & \vphantom{1} (\num{21.20})\\
+RegionEurope & \num{-8.39}\\
+ & (\num{45.65})\\
+RegionNorth America & \num{-5.48}\\
+ & (\num{50.68})\\
+RegionOceania & \num{-8.43}\\
+ & (\num{80.66})\\
+RegionSouth America & \num{21.91}\\
+ & (\num{55.21})\\
+CountryAlbania & \num{0.68}\\
+ & (\num{28.99})\\
+CountryAlgeria & \num{9.41}\\
+ & (\num{47.74})\\
+CountryAngola & \num{-4.60}\\
+ & \vphantom{2} (\num{47.88})\\
+CountryAntigua and Barbuda & \num{2.12}\\
+ & (\num{31.15})\\
+CountryArgentina & \num{-28.26}\\
+ & (\num{65.45})\\
+CountryArmenia & \num{-3.20}\\
+ & (\num{29.08})\\
+CountryAustralia & \num{17.28}\\
+ & (\num{64.59})\\
+CountryAustria & \num{7.63}\\
+ & \vphantom{1} (\num{26.97})\\
+CountryAzerbaijan & \num{-2.97}\\
+ & (\num{29.29})\\
+CountryBahamas & \num{-1.15}\\
+ & (\num{31.29})\\
+CountryBahrain & \num{3.35}\\
+ & (\num{36.83})\\
+CountryBangladesh & \num{4.23}\\
+ & (\num{54.21})\\
+CountryBarbados & \num{2.55}\\
+ & (\num{30.97})\\
+CountryBelarus & \num{-3.11}\\
+ & (\num{29.12})\\
+CountryBelgium & \num{7.36}\\
+ & (\num{26.87})\\
+CountryBelize & \num{0.25}\\
+ & (\num{30.40})\\
+CountryBenin & \num{-3.17}\\
+ & \vphantom{1} (\num{48.20})\\
+CountryBhutan & \num{4.36}\\
+ & (\num{54.23})\\
+CountryBolivia (Plurinational State of) & \num{-24.08}\\
+ & (\num{76.01})\\
+CountryBosnia and Herzegovina & \num{-0.20}\\
+ & (\num{29.18})\\
+CountryBotswana & \num{-19.85}\\
+ & (\num{51.26})\\
+CountryBrazil & \num{-30.04}\\
+ & (\num{65.42})\\
+CountryBrunei Darussalam & \num{4.00}\\
+ & (\num{36.91})\\
+CountryBulgaria & \num{-2.45}\\
+ & (\num{29.09})\\
+CountryBurkina Faso & \num{-5.08}\\
+ & (\num{21.33})\\
+CountryBurundi & \num{-3.23}\\
+ & (\num{21.40})\\
+CountryCabo Verde & \num{7.65}\\
+ & (\num{47.94})\\
+CountryCambodia & \num{-0.02}\\
+ & \vphantom{1} (\num{54.13})\\
+CountryCameroon & \num{-5.86}\\
+ & (\num{48.02})\\
+CountryCanada & \num{7.86}\\
+ & (\num{30.96})\\
+CountryCentral African Republic & \num{-14.92}\\
+ & \vphantom{1} (\num{21.25})\\
+CountryChad & \num{-8.32}\\
+ & (\num{21.18})\\
+CountryChile & \num{-24.65}\\
+ & (\num{56.84})\\
+CountryChina & \num{-4.35}\\
+ & \vphantom{2} (\num{51.31})\\
+CountryColombia & \num{-27.30}\\
+ & (\num{65.38})\\
+CountryComoros & \num{1.26}\\
+ & (\num{48.11})\\
+CountryCongo & \num{-3.93}\\
+ & (\num{48.00})\\
+CountryCosta Rica & \num{5.85}\\
+ & (\num{30.49})\\
+CountryCote d'Ivoire & \num{-4.15}\\
+ & (\num{48.20})\\
+CountryCroatia & \num{4.47}\\
+ & \vphantom{3} (\num{26.98})\\
+CountryCuba & \num{3.41}\\
+ & (\num{30.53})\\
+CountryCyprus & \num{8.31}\\
+ & (\num{26.83})\\
+CountryCzechia & \num{5.01}\\
+ & \vphantom{1} (\num{27.04})\\
+CountryDemocratic People's Republic of Korea & \num{11.23}\\
+ & (\num{0.48})\\
+CountryDemocratic Republic of the Congo & \num{-5.91}\\
+ & \vphantom{1} (\num{21.28})\\
+CountryDenmark & \num{7.40}\\
+ & \vphantom{1} (\num{26.95})\\
+CountryDjibouti & \num{-1.98}\\
+ & (\num{47.97})\\
+CountryDominican Republic & \num{-0.78}\\
+ & \vphantom{1} (\num{30.48})\\
+CountryEcuador & \num{-28.26}\\
+ & (\num{65.51})\\
+CountryEgypt & \num{4.21}\\
+ & (\num{47.84})\\
+CountryEl Salvador & \num{-0.99}\\
+ & (\num{30.48})\\
+CountryEquatorial Guinea & \num{-22.60}\\
+ & (\num{51.41})\\
+CountryEritrea & \num{-3.74}\\
+ & (\num{21.28})\\
+CountryEstonia & \num{4.46}\\
+ & \vphantom{1} (\num{26.91})\\
+CountryEswatini & \num{-12.28}\\
+ & \vphantom{1} (\num{48.03})\\
+CountryEthiopia & \num{1.13}\\
+ & \vphantom{1} (\num{21.26})\\
+CountryFiji & \num{-0.68}\\
+ & (\num{71.02})\\
+CountryFinland & \num{7.61}\\
+ & (\num{27.08})\\
+CountryFrance & \num{8.48}\\
+ & \vphantom{2} (\num{26.98})\\
+CountryGabon & \num{-19.19}\\
+ & (\num{51.46})\\
+CountryGambia & \num{-2.56}\\
+ & (\num{21.32})\\
+CountryGeorgia & \num{-3.87}\\
+ & \vphantom{1} (\num{29.20})\\
+CountryGermany & \num{7.02}\\
+ & \vphantom{2} (\num{27.00})\\
+CountryGhana & \num{-1.35}\\
+ & (\num{47.86})\\
+CountryGreece & \num{7.16}\\
+ & \vphantom{1} (\num{26.98})\\
+CountryGrenada & \num{-1.25}\\
+ & \vphantom{1} (\num{30.43})\\
+CountryGuatemala & \num{-2.17}\\
+ & (\num{30.39})\\
+CountryGuinea & \num{-6.20}\\
+ & \vphantom{1} (\num{47.88})\\
+CountryGuinea-Bissau & \num{-8.80}\\
+ & \vphantom{1} (\num{21.23})\\
+CountryGuyana & \num{-37.07}\\
+ & (\num{56.78})\\
+CountryHaiti & \num{-1.41}\\
+ & (\num{33.25})\\
+CountryHonduras & \num{6.26}\\
+ & (\num{33.17})\\
+CountryHungary & \num{2.27}\\
+ & \vphantom{1} (\num{27.02})\\
+CountryIceland & \num{8.69}\\
+ & \vphantom{2} (\num{26.93})\\
+CountryIndia & \num{1.11}\\
+ & \vphantom{1} (\num{54.41})\\
+CountryIndonesia & \num{-10.63}\\
+ & \vphantom{1} (\num{51.36})\\
+CountryIran (Islamic Republic of) & \num{7.86}\\
+ & (\num{54.06})\\
+CountryIraq & \num{-9.81}\\
+ & (\num{51.25})\\
+CountryIreland & \num{8.03}\\
+ & \vphantom{1} (\num{26.93})\\
+CountryIsrael & \num{9.91}\\
+ & \vphantom{1} (\num{36.89})\\
+CountryItaly & \num{8.81}\\
+ & (\num{26.91})\\
+CountryJamaica & \num{-1.99}\\
+ & (\num{30.43})\\
+CountryJapan & \num{11.94}\\
+ & (\num{36.88})\\
+CountryJordan & \num{9.67}\\
+ & (\num{54.24})\\
+CountryKazakhstan & \num{-4.71}\\
+ & (\num{29.26})\\
+CountryKenya & \num{-0.86}\\
+ & (\num{47.87})\\
+CountryKiribati & \num{4.08}\\
+ & (\num{61.70})\\
+CountryKuwait & \num{9.87}\\
+ & (\num{36.84})\\
+CountryKyrgyzstan & \num{3.47}\\
+ & (\num{54.41})\\
+CountryLao People's Democratic Republic & \num{-1.48}\\
+ & (\num{54.13})\\
+CountryLatvia & \num{1.45}\\
+ & (\num{26.95})\\
+CountryLebanon & \num{9.14}\\
+ & (\num{54.11})\\
+CountryLesotho & \num{-15.82}\\
+ & \vphantom{1} (\num{48.08})\\
+CountryLiberia & \num{-4.50}\\
+ & (\num{21.35})\\
+CountryLibya & \num{-10.87}\\
+ & \vphantom{1} (\num{51.31})\\
+CountryLithuania & \num{1.52}\\
+ & (\num{27.02})\\
+CountryLuxembourg & \num{9.05}\\
+ & (\num{26.98})\\
+CountryMadagascar & \num{-3.54}\\
+ & \vphantom{2} (\num{21.21})\\
+CountryMalawi & \num{-4.38}\\
+ & (\num{21.25})\\
+CountryMalaysia & \num{-6.51}\\
+ & \vphantom{1} (\num{51.20})\\
+CountryMaldives & \num{-4.14}\\
+ & (\num{51.20})\\
+CountryMali & \num{-6.00}\\
+ & \vphantom{1} (\num{21.21})\\
+CountryMalta & \num{8.28}\\
+ & (\num{26.88})\\
+CountryMauritania & \num{2.98}\\
+ & \vphantom{1} (\num{47.95})\\
+CountryMauritius & \num{-9.94}\\
+ & (\num{51.30})\\
+CountryMexico & \num{0.67}\\
+ & (\num{30.33})\\
+CountryMicronesia (Federated States of) & \num{8.09}\\
+ & (\num{61.64})\\
+CountryMongolia & \num{1.06}\\
+ & (\num{54.16})\\
+CountryMontenegro & \num{-0.28}\\
+ & (\num{29.22})\\
+CountryMorocco & \num{6.69}\\
+ & (\num{48.03})\\
+CountryMozambique & \num{-9.56}\\
+ & (\num{21.26})\\
+CountryMyanmar & \num{-0.94}\\
+ & \vphantom{1} (\num{54.36})\\
+CountryNamibia & \num{-21.00}\\
+ & (\num{51.42})\\
+CountryNepal & \num{1.41}\\
+ & (\num{54.14})\\
+CountryNetherlands (Kingdom of the) & \num{8.02}\\
+ & (\num{27.04})\\
+CountryNew Zealand & \num{16.32}\\
+ & (\num{64.57})\\
+CountryNicaragua & \num{13.32}\\
+ & (\num{33.40})\\
+CountryNiger & \num{-6.88}\\
+ & (\num{21.20})\\
+CountryNigeria & \num{-4.28}\\
+ & (\num{48.05})\\
+CountryNorth Macedonia & \num{-1.40}\\
+ & (\num{29.34})\\
+CountryNorway & \num{8.78}\\
+ & (\num{26.93})\\
+CountryOman & \num{2.38}\\
+ & \vphantom{1} (\num{36.87})\\
+CountryPakistan & \num{-3.13}\\
+ & (\num{54.28})\\
+CountryPanama & \num{4.48}\\
+ & (\num{31.13})\\
+CountryPapua New Guinea & \num{8.94}\\
+ & \vphantom{1} (\num{61.59})\\
+CountryParaguay & \num{-29.48}\\
+ & (\num{65.36})\\
+CountryPeru & \num{-26.42}\\
+ & (\num{65.46})\\
+CountryPhilippines & \num{0.30}\\
+ & (\num{54.15})\\
+CountryPoland & \num{3.67}\\
+ & \vphantom{1} (\num{27.01})\\
+CountryPortugal & \num{7.36}\\
+ & (\num{27.07})\\
+CountryPuerto Rico & \num{6.28}\\
+ & (\num{31.19})\\
+CountryQatar & \num{5.93}\\
+ & (\num{36.80})\\
+CountryRepublic of Korea & \num{10.61}\\
+ & (\num{36.81})\\
+CountryRepublic of Moldova & \num{-4.72}\\
+ & (\num{29.13})\\
+CountryRomania & \num{1.39}\\
+ & (\num{26.96})\\
+CountryRussian Federation & \num{-9.31}\\
+ & (\num{51.36})\\
+CountryRwanda & \num{0.44}\\
+ & \vphantom{1} (\num{21.29})\\
+CountrySaint Lucia & \num{1.72}\\
+ & (\num{30.45})\\
+CountrySaint Vincent and the Grenadines & \num{-1.25}\\
+ & (\num{30.38})\\
+CountrySamoa & \num{12.64}\\
+ & (\num{61.59})\\
+CountrySao Tome and Principe & \num{4.58}\\
+ & (\num{47.96})\\
+CountrySaudi Arabia & \num{4.35}\\
+ & (\num{36.87})\\
+CountrySenegal & \num{1.47}\\
+ & (\num{48.01})\\
+CountrySerbia & \num{-1.59}\\
+ & (\num{29.20})\\
+CountrySeychelles & \num{-5.53}\\
+ & (\num{43.56})\\
+CountrySierra Leone & \num{-7.75}\\
+ & (\num{21.34})\\
+CountrySingapore & \num{10.98}\\
+ & (\num{36.89})\\
+CountrySlovakia & \num{3.40}\\
+ & \vphantom{1} (\num{27.00})\\
+CountrySlovenia & \num{7.13}\\
+ & (\num{27.00})\\
+CountrySolomon Islands & \num{7.87}\\
+ & (\num{61.68})\\
+CountrySomalia & \num{-12.52}\\
+ & (\num{21.30})\\
+CountrySouth Africa & \num{-19.37}\\
+ & (\num{51.43})\\
+CountrySouth Sudan & \num{-8.01}\\
+ & (\num{21.29})\\
+CountrySpain & \num{8.85}\\
+ & (\num{27.13})\\
+CountrySri Lanka & \num{7.99}\\
+ & (\num{54.25})\\
+CountrySudan & \num{1.81}\\
+ & (\num{21.31})\\
+CountrySuriname & \num{-31.76}\\
+ & (\num{65.41})\\
+CountrySweden & \num{8.42}\\
+ & (\num{26.97})\\
+CountrySwitzerland & \num{9.33}\\
+ & (\num{27.01})\\
+CountrySyrian Arab Republic & \num{3.97}\\
+ & \vphantom{1} (\num{0.40})\\
+CountryTajikistan & \num{3.09}\\
+ & (\num{53.97})\\
+CountryThailand & \num{-4.50}\\
+ & (\num{51.28})\\
+CountryTimor-Leste & \num{-0.90}\\
+ & (\num{54.22})\\
+CountryTogo & \num{-4.19}\\
+ & (\num{21.21})\\
+CountryTonga & \num{4.42}\\
+ & (\num{71.06})\\
+CountryTrinidad and Tobago & \num{0.20}\\
+ & (\num{31.16})\\
+CountryTunisia & \num{10.40}\\
+ & (\num{47.95})\\
+CountryTürkiye & \num{-4.47}\\
+ & (\num{51.31})\\
+CountryTurkmenistan & \num{-12.58}\\
+ & (\num{51.24})\\
+CountryUganda & \num{-1.74}\\
+ & (\num{21.23})\\
+CountryUkraine & \num{6.68}\\
+ & (\num{36.36})\\
+CountryUnited Arab Emirates & \num{8.68}\\
+ & (\num{36.79})\\
+CountryUnited Kingdom of Great Britain and Northern Ireland & \num{7.08}\\
+ & (\num{27.10})\\
+CountryUnited Republic of Tanzania & \num{-0.45}\\
+ & (\num{47.88})\\
+CountryUnited States of America & \num{4.57}\\
+ & (\num{31.22})\\
+CountryUruguay & \num{-27.80}\\
+ & (\num{56.83})\\
+CountryUzbekistan & \num{1.65}\\
+ & (\num{54.36})\\
+CountryVanuatu & \num{9.66}\\
+ & (\num{61.72})\\
+CountryVenezuela (Bolivarian Republic of) & \num{-31.90}\\
+ & (\num{65.65})\\
+CountryViet Nam & \num{3.94}\\
+ & (\num{53.92})\\
+CountryYemen & \num{6.61}\\
+ & (\num{0.40})\\
+CountryZambia & \num{-5.46}\\
+ & (\num{47.98})\\
+CountryZimbabwe & \num{-8.25}\\
+ & (\num{48.08})\\
+Income\_Grouplower\_income & \num{-12.06}\\
+ & (\num{36.90})\\
+Income\_Grouplower\_middle & \num{-4.04}\\
+ & (\num{23.94})\\
+Income\_Groupupper\_middle & \num{3.40}\\
+ & (\num{20.47})\\
+GenderFemale & \num{2.50}\\
+ & \vphantom{1} (\num{0.05})\\
+GenderMale & \num{-2.42}\\
+ & (\num{0.05})\\
+\midrule
+Num.Obs. & \num{3312}\\
+R2 & \num{0.976}\\
+R2 Adj. & \num{0.975}\\
+Log.Lik. & \num{-5231.038}\\
+ELPD & \num{-5409.7}\\
+ELPD s.e. & \num{94.5}\\
+LOOIC & \num{10819.4}\\
+LOOIC s.e. & \num{189.0}\\
+WAIC & \num{10816.6}\\
+RMSE & \num{4.37}\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table}%
 
@@
 
-\section{Discussion}\label{discussion}
-
-\subsection{Insights into different
-gender}\label{insights-into-different-gender}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The
-discussion is a chance to show off what you know and what you learnt
-from all this.
-
-\subsection{Second discussion point}\label{second-discussion-point}
-
-Please don't use these as sub-heading labels - change them to be what
-your point actually is.
+Table~\ref{tbl-model} is the table of the results from out model. The
+intercept serves as the baseline, which in this case is 79.53. Asia
+shows a negative coefficient of -6.22, indicating lower values compared
+to the baseline, with a relatively large standard error of 21.20. This
+suggests that as the predictor increases, the outcome tends to increase.
+In contrast, a negative coefficient implies a decrease in the outcome.
+Europe exhibits a negligible negative effect of -8.39, though it also
+has a large standard error of 45.65. The effect for females is more
+substantial, with a positive coefficient of 2.50 and a standard error of
+0.05, indicating considerable variability in the estimate. The male and
+lower-middle-income groups show minimal negative coefficients,
+suggesting slight decreases from the baseline. The upper-middle-income
+group, however, shows a positive effect of 3.40 relative to the
+baseline. Regions like North America, Oceania, Asia, and Europe all have
+notable negative coefficients, highlighting significant regional
+variations. In general, there is a downward trend in coefficients across
+countries. Most countries exhibit large standard errors, with European
+countries such as Ireland, Israel, and Italy showing slightly positive
+trends.
+
+With an R-squared value of 0.976, the model demonstrates a strong level
+of explanatory power, supporting the accuracy of the results. The
+adjusted R-squared value is 0.975, which is nearly identical to the
+R-squared value, indicating the model's robustness with 3,312
+observations. The RMSE of 4.37 reflects the average magnitude of the
+model's prediction errors, suggesting good predictive accuracy. Although
+values like LOOIC and WAIC are excluded due to the lack of alternative
+models for comparison, the overall results indicate that the model
+performs well on the cleaned dataset.Further evaluation of the model
+results will be done in Section~\ref{sec-model-details}.
+
+\section{Discussion}\label{sec-discussion}
+
+\subsection{Insights into Life Expectancy Differences by
+Gender}\label{insights-into-life-expectancy-differences-by-gender}
+
+Thought the result part we have noticed that female constantly have
+higher life expectancy than male. Figure~\ref{fig-gender} shows that
+female has around 4 years higher average age than male. Even during the
+sudden drop of 2020, female kept a more stable trend than male. Through
+literature research, we found that historically women tend to have
+longer life than men across most regions and cultures. (Kalben
+2000)These difference can be attributed to a variety of interconnected
+reasons. Women generally have stronger immune systems and are less prone
+to certain life-threatening diseases like cardiovascular diseases in
+early adulthood. Estrogen, a hormone prevalent in women, provides some
+protection against heart disease by improving cholesterol levels. On the
+other hand, men are more prone to risk factors such as hypertension and
+higher levels of LDL cholesterol, which contribute to shorter life
+spansehavioral patterns (Oksuzyan 2008a). What's more, male are more
+likely to engage in behaviours such as smoking, excessive alcohol
+consumption and hazardous occupations. These behaviors increase the risk
+of accidents, chronic diseases, and early mortality. Last but not least,
+globally, women tend to use healthcare services more frequently than
+men, which allows for earlier detection and treatment of illnesses. Men
+often delay seeking medical care, worsening outcomes for preventable or
+manageable diseases.(Saltonstall 1993)
+
+\subsection{Insights into Life Expectancy Differences by Income
+Group}\label{insights-into-life-expectancy-differences-by-income-group}
+
+From the summary and analysis of Table~\ref{tbl-sum_sta}, we have seen
+that high income group has the significant high life expectancy compared
+to the lower income group, which indicates that life expectancy is
+significantly influenced by income groups. It is known that income
+determines access to resources, healthcare and living conditions.
+Difference in life expectancy across income groups reflect broader
+inequalities in socioeconomic factors and highlight disparities in
+global health outcomes.
+
+High-income groups have greater access to quality healthcare services,
+including preventive care, advanced medical treatments, and regular
+health checkups.Conversely, lower-income groups often face barriers such
+as cost, lack of infrastructure, and insufficient health insurance
+coverage, leading to untreated or poorly managed health conditions (M.
+Marmot 2015). Other living conditions like access to nutritious food,
+safe drinking water and sanitary living environments are also linked
+with high economics. Low-income populations are more likely to
+experience malnutrition, exposure to environmental toxins, and
+overcrowded living conditions, all of which negatively impact health and
+life expectancy.
+
+What's more, lower-income individuals are often exposed to higher levels
+of chronic stress due to financial instability and job insecurity.
+Stress is linked to adverse health outcomes such as hypertension,
+cardiovascular diseases, and mental health issues (Public Health. 2020).
+Moreover, low-income workers frequently engage in physically demanding
+or hazardous jobs, increasing their risk of injury and illness. All
+these factors together makes the lower income countries disadvantage in
+life expectancy.
 
@@
 
-\section{Appendix}\label{sec-appendix}
+\section{Appendix}\label{sec-appx}
 
@@
 dataset. We created a new variable called ``Income\_Group'' by mapping
-over country name to four income group (lower\_income, lower\_middle,
-upper\_middle, high\_income) according to the index given by World Bank
-Income Group. This is a key variable in predicting life expectancy since
-it is believed that life expectancy is correlated to the income
-situation. We as well made a mapping to the countries according to its
-continent and saved as ``Region''. This is the variable indicates the
-geographic context to the analysis. Countries are mapped into six
-continents (``Africa'', ``Asia'', ``Europe'', ``North America'', ``South
-America'', ``Oceania'') one by one.
+over country name to four income group (``lower\_income'',
+``lower\_middle'', ``upper\_middle'', ``high\_income'') according to the
+index given by World Bank Income Group. This is a key variable in
+predicting life expectancy since it is believed that life expectancy is
+correlated to the income situation. We as well made a mapping to the
+countries according to its continent and saved as ``Region''. This is
+the variable indicates the geographic context to the analysis. Countries
+are mapped into six continents (``Africa'', ``Asia'', ``Europe'',
+``North America'', ``South America'', ``Oceania'') one by one.
 
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2895}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1754}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0614}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0965}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1404}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1140}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1228}}@{}}
-
-\caption{\label{tbl-cleaned_leab}Life expectancy over countries and
-years}
+\begingroup\fontsize{5.5}{7.5}\selectfont
+
+\begin{longtable}[t]{llll}
+
+\caption{\label{tbl-cleaned_average}Cleaned data of average life
+expectancy of 6 years by different countries.}
 
@@
 
-\caption{Life Expectancy over countries and years (first 200
-rows)}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Indicator
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Country
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Period
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Gender
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Life Expectancy
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Income\_Group
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Region
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Indicator
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Country
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Period
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Gender
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Life Expectancy
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Income\_Group
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Region
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Life expectancy at birth (years) & Afghanistan & 2020 & Male & 59.3 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2020 & Both sexes &
-60.5 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2020 & Female & 61.7 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2019 & Male & 60.0 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2019 & Both sexes &
-61.2 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2019 & Female & 62.5 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2018 & Male & 59.0 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2018 & Both sexes &
-60.5 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2018 & Female & 62.1 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2017 & Male & 59.8 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2017 & Both sexes &
-60.9 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2017 & Female & 62.1 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2016 & Male & 59.2 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2016 & Both sexes &
-60.4 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2016 & Female & 61.7 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2015 & Male & 59.3 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2015 & Both sexes &
-60.3 & lower\_income & Asia \\
-Life expectancy at birth (years) & Afghanistan & 2015 & Female & 61.5 &
-lower\_income & Asia \\
-Life expectancy at birth (years) & Albania & 2020 & Male & 74.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2020 & Both sexes & 76.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2020 & Female & 79.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2019 & Male & 76.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2019 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2019 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2018 & Male & 76.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2018 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2018 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2017 & Male & 76.1 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2017 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2017 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2016 & Male & 76.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2016 & Both sexes & 77.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2016 & Female & 79.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2015 & Male & 76.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2015 & Both sexes & 77.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Albania & 2015 & Female & 79.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Algeria & 2020 & Male & 73.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2020 & Both sexes & 74.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2020 & Female & 75.2 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2019 & Male & 76.2 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2019 & Both sexes & 76.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2019 & Female & 77.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2018 & Male & 76.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2018 & Both sexes & 76.4 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2018 & Female & 77.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2017 & Male & 76.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2017 & Both sexes & 76.4 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2017 & Female & 77.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2016 & Male & 75.9 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2016 & Both sexes & 76.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2016 & Female & 76.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2015 & Male & 75.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2015 & Both sexes & 76.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Algeria & 2015 & Female & 76.6 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2020 & Male & 60.4 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2020 & Both sexes & 62.6 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2020 & Female & 64.9 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2019 & Male & 60.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2019 & Both sexes & 62.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2019 & Female & 64.7 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2018 & Male & 60.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2018 & Both sexes & 62.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2018 & Female & 64.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2017 & Male & 59.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2017 & Both sexes & 62.0 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2017 & Female & 64.3 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2016 & Male & 59.5 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2016 & Both sexes & 61.8 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2016 & Female & 64.2 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2015 & Male & 59.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2015 & Both sexes & 61.6 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Angola & 2015 & Female & 64.1 &
-lower\_middle & Africa \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Male &
-75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Both
-sexes & 77.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Female &
-79.4 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Male &
-74.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Both
-sexes & 75.7 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Female &
-77.1 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Male &
-74.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Both
-sexes & 75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Female &
-77.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Male &
-73.9 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Both
-sexes & 75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Female &
-77.0 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Male &
-73.8 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Both
-sexes & 75.5 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Female &
-77.1 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Male &
-73.8 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Both
-sexes & 75.6 & high\_income & North America \\
-Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Female &
-77.2 & high\_income & North America \\
-Life expectancy at birth (years) & Argentina & 2020 & Male & 73.1 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2020 & Both sexes & 76.2
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2020 & Female & 79.4 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2019 & Male & 74.0 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2019 & Both sexes & 77.0
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2019 & Female & 79.9 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2018 & Male & 73.7 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2018 & Both sexes & 76.9
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2018 & Female & 79.9 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2017 & Male & 73.6 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2017 & Both sexes & 76.6
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2017 & Female & 79.6 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2016 & Male & 73.0 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2016 & Both sexes & 76.1
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2016 & Female & 79.2 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2015 & Male & 73.3 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2015 & Both sexes & 76.5
-& upper\_middle & South America \\
-Life expectancy at birth (years) & Argentina & 2015 & Female & 79.6 &
-upper\_middle & South America \\
-Life expectancy at birth (years) & Armenia & 2020 & Male & 62.7 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2020 & Both sexes & 69.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2020 & Female & 76.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2019 & Male & 70.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2019 & Both sexes & 75.7 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2019 & Female & 79.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2018 & Male & 71.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2018 & Both sexes & 75.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2018 & Female & 79.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2017 & Male & 70.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2017 & Both sexes & 75.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2017 & Female & 79.1 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2016 & Male & 69.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2016 & Both sexes & 74.4 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2016 & Female & 78.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2015 & Male & 69.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2015 & Both sexes & 74.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Armenia & 2015 & Female & 78.3 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Australia & 2020 & Male & 81.5 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2020 & Both sexes & 83.4
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2020 & Female & 85.2 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2019 & Male & 80.7 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2019 & Both sexes & 82.6
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2019 & Female & 84.6 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2018 & Male & 81.2 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2018 & Both sexes & 83.0
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2018 & Female & 84.9 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2017 & Male & 80.8 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2017 & Both sexes & 82.7
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2017 & Female & 84.5 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2016 & Male & 80.7 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2016 & Both sexes & 82.6
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2016 & Female & 84.5 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2015 & Male & 80.4 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2015 & Both sexes & 82.3
-& high\_income & Oceania \\
-Life expectancy at birth (years) & Australia & 2015 & Female & 84.2 &
-high\_income & Oceania \\
-Life expectancy at birth (years) & Austria & 2020 & Male & 78.8 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2020 & Both sexes & 81.1 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2020 & Female & 83.3 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2019 & Male & 79.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2019 & Both sexes & 81.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2019 & Female & 83.8 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2018 & Male & 79.2 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2018 & Both sexes & 81.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2018 & Female & 83.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2017 & Male & 79.2 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2017 & Both sexes & 81.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2017 & Female & 83.5 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2016 & Male & 79.1 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2016 & Both sexes & 81.4 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2016 & Female & 83.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2015 & Male & 78.6 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2015 & Both sexes & 81.0 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Austria & 2015 & Female & 83.3 &
-high\_income & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2020 & Male & 67.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2020 & Both sexes & 71.4
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2020 & Female & 75.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2019 & Male & 73.4 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2019 & Both sexes & 75.8
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2019 & Female & 78.1 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2018 & Male & 72.6 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2018 & Both sexes & 75.1
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2018 & Female & 77.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2017 & Male & 72.2 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2017 & Both sexes & 74.6
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2017 & Female & 76.9 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2016 & Male & 71.8 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2016 & Both sexes & 74.0
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2016 & Female & 76.0 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2015 & Male & 71.7 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2015 & Both sexes & 73.6
-& upper\_middle & Europe \\
-Life expectancy at birth (years) & Azerbaijan & 2015 & Female & 75.5 &
-upper\_middle & Europe \\
-Life expectancy at birth (years) & Bahamas & 2020 & Male & 69.2 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2020 & Both sexes & 72.6 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2020 & Female & 76.0 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2019 & Male & 68.1 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2019 & Both sexes & 70.7 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2019 & Female & 73.3 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2018 & Male & 70.2 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2018 & Both sexes & 73.4 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2018 & Female & 76.5 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2017 & Male & 70.0 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2017 & Both sexes & 73.2 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2017 & Female & 76.3 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2016 & Male & 69.7 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2016 & Both sexes & 72.9 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2016 & Female & 76.1 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2015 & Male & 69.8 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2015 & Both sexes & 72.9 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahamas & 2015 & Female & 76.0 &
-high\_income & North America \\
-Life expectancy at birth (years) & Bahrain & 2020 & Male & 73.6 &
-high\_income & Asia \\
-Life expectancy at birth (years) & Bahrain & 2020 & Both sexes & 74.9 &
-high\_income & Asia \\
+\toprule
+Country & Income Group & Region & Average Life Expectancy\\
+\midrule
+Afghanistan & lower\_income & Asia & 60.63\\
+Albania & upper\_middle & Europe & 77.65\\
+Algeria & lower\_middle & Africa & 75.95\\
+Angola & lower\_middle & Africa & 62.13\\
+Antigua and Barbuda & high\_income & North America & 75.93\\
+\addlinespace
+Argentina & upper\_middle & South America & 76.55\\
+Armenia & upper\_middle & Europe & 74.08\\
+Australia & high\_income & Oceania & 82.77\\
+Austria & high\_income & Europe & 81.32\\
+Azerbaijan & upper\_middle & Europe & 74.08\\
+\addlinespace
+Bahamas & high\_income & North America & 72.62\\
+Bahrain & high\_income & Asia & 75.67\\
+Bangladesh & lower\_middle & Asia & 73.48\\
+Barbados & high\_income & North America & 76.35\\
+Belarus & upper\_middle & Europe & 73.98\\
+\addlinespace
+Belgium & high\_income & Europe & 81.10\\
+Belize & upper\_middle & North America & 74.58\\
+Benin & lower\_middle & Africa & 63.52\\
+Bhutan & lower\_middle & Asia & 73.68\\
+Bolivia (Plurinational State of) & lower\_middle & South America & 71.53\\
+\addlinespace
+Bosnia and Herzegovina & upper\_middle & Europe & 76.90\\
+Botswana & upper\_middle & Africa & 63.93\\
+Brazil & upper\_middle & South America & 74.87\\
+Brunei Darussalam & high\_income & Asia & 76.55\\
+Bulgaria & upper\_middle & Europe & 74.58\\
+\addlinespace
+Burkina Faso & lower\_income & Africa & 62.02\\
+Burundi & lower\_income & Africa & 63.75\\
+Cabo Verde & lower\_middle & Africa & 74.38\\
+Cambodia & lower\_middle & Asia & 69.25\\
+Cameroon & lower\_middle & Africa & 60.83\\
+\addlinespace
+Canada & high\_income & North America & 81.67\\
+Central African Republic & lower\_income & Africa & 51.98\\
+Chad & lower\_income & Africa & 58.72\\
+Chile & high\_income & South America & 80.53\\
+China & upper\_middle & Asia & 77.00\\
+\addlinespace
+Colombia & upper\_middle & South America & 77.45\\
+Comoros & lower\_middle & Africa & 67.92\\
+Congo & lower\_middle & Africa & 62.80\\
+Costa Rica & upper\_middle & North America & 80.25\\
+Cote d'Ivoire & lower\_middle & Africa & 62.42\\
+\addlinespace
+Croatia & high\_income & Europe & 78.13\\
+Cuba & upper\_middle & North America & 77.82\\
+Cyprus & high\_income & Europe & 81.97\\
+Czechia & high\_income & Europe & 78.73\\
+Democratic People's Republic of Korea & lower\_income & Asia & 71.95\\
+\addlinespace
+Democratic Republic of the Congo & lower\_income & Africa & 61.07\\
+Denmark & high\_income & Europe & 80.95\\
+Djibouti & lower\_middle & Africa & 64.78\\
+Dominican Republic & upper\_middle & North America & 73.50\\
+Ecuador & upper\_middle & South America & 76.62\\
+\addlinespace
+Egypt & lower\_middle & Africa & 70.87\\
+El Salvador & upper\_middle & North America & 73.52\\
+Equatorial Guinea & upper\_middle & Africa & 61.20\\
+Eritrea & lower\_income & Africa & 63.28\\
+Estonia & high\_income & Europe & 78.22\\
+\addlinespace
+Eswatini & lower\_middle & Africa & 54.23\\
+Ethiopia & lower\_income & Africa & 68.15\\
+Fiji & upper\_middle & Oceania & 67.82\\
+Finland & high\_income & Europe & 81.35\\
+France & high\_income & Europe & 82.17\\
+\addlinespace
+Gabon & upper\_middle & Africa & 64.60\\
+Gambia & lower\_income & Africa & 64.42\\
+Georgia & upper\_middle & Europe & 73.30\\
+Germany & high\_income & Europe & 80.72\\
+Ghana & lower\_middle & Africa & 65.30\\
+\addlinespace
+Greece & high\_income & Europe & 80.73\\
+Grenada & upper\_middle & North America & 73.08\\
+Guatemala & upper\_middle & North America & 72.22\\
+Guinea & lower\_middle & Africa & 60.38\\
+Guinea-Bissau & lower\_income & Africa & 58.33\\
+\addlinespace
+Guyana & high\_income & South America & 67.85\\
+Haiti & lower\_middle & North America & 63.18\\
+Honduras & lower\_middle & North America & 70.82\\
+Hungary & high\_income & Europe & 75.97\\
+Iceland & high\_income & Europe & 82.35\\
+\addlinespace
+India & lower\_middle & Asia & 70.10\\
+Indonesia & upper\_middle & Asia & 70.77\\
+Iran (Islamic Republic of) & lower\_middle & Asia & 77.15\\
+Iraq & upper\_middle & Asia & 71.68\\
+Ireland & high\_income & Europe & 81.57\\
+\addlinespace
+Israel & high\_income & Asia & 82.35\\
+Italy & high\_income & Europe & 82.55\\
+Jamaica & upper\_middle & North America & 72.37\\
+Japan & high\_income & Asia & 84.35\\
+Jordan & lower\_middle & Asia & 78.90\\
+\addlinespace
+Kazakhstan & upper\_middle & Europe & 72.52\\
+Kenya & lower\_middle & Africa & 65.72\\
+Kiribati & lower\_middle & Oceania & 61.67\\
+Kuwait & high\_income & Asia & 81.78\\
+Kyrgyzstan & lower\_middle & Asia & 72.57\\
+\addlinespace
+Lao People's Democratic Republic & lower\_middle & Asia & 67.85\\
+Latvia & high\_income & Europe & 75.18\\
+Lebanon & lower\_middle & Asia & 78.77\\
+Lesotho & lower\_middle & Africa & 50.85\\
+Liberia & lower\_income & Africa & 62.53\\
+\addlinespace
+Libya & upper\_middle & Africa & 73.02\\
+Lithuania & high\_income & Europe & 75.25\\
+Luxembourg & high\_income & Europe & 82.68\\
+Madagascar & lower\_income & Africa & 63.52\\
+Malawi & lower\_income & Africa & 62.70\\
+\addlinespace
+Malaysia & upper\_middle & Asia & 74.85\\
+Maldives & upper\_middle & Asia & 77.25\\
+Mali & lower\_income & Africa & 61.05\\
+Malta & high\_income & Europe & 82.02\\
+Mauritania & lower\_middle & Africa & 69.68\\
+\addlinespace
+Mauritius & upper\_middle & Africa & 74.02\\
+Mexico & upper\_middle & North America & 75.03\\
+Micronesia (Federated States of) & lower\_middle & Oceania & 65.65\\
+Mongolia & lower\_middle & Asia & 70.48\\
+Montenegro & upper\_middle & Europe & 76.77\\
+\addlinespace
+Morocco & lower\_middle & Africa & 73.33\\
+Mozambique & lower\_income & Africa & 57.47\\
+Myanmar & lower\_middle & Asia & 68.27\\
+Namibia & upper\_middle & Africa & 62.75\\
+Nepal & lower\_middle & Asia & 70.78\\
+\addlinespace
+Netherlands (Kingdom of the) & high\_income & Europe & 81.62\\
+New Zealand & high\_income & Oceania & 81.72\\
+Nicaragua & lower\_middle & North America & 77.85\\
+Niger & lower\_income & Africa & 60.17\\
+Nigeria & lower\_middle & Africa & 62.45\\
+\addlinespace
+North Macedonia & upper\_middle & Europe & 75.65\\
+Norway & high\_income & Europe & 82.38\\
+Oman & high\_income & Asia & 74.30\\
+Pakistan & lower\_middle & Asia & 66.28\\
+Panama & high\_income & North America & 78.27\\
+\addlinespace
+Papua New Guinea & lower\_middle & Oceania & 66.35\\
+Paraguay & upper\_middle & South America & 75.15\\
+Peru & upper\_middle & South America & 78.33\\
+Philippines & lower\_middle & Asia & 69.50\\
+Poland & high\_income & Europe & 77.38\\
+\addlinespace
+Portugal & high\_income & Europe & 81.03\\
+Puerto Rico & high\_income & North America & 80.03\\
+Qatar & high\_income & Asia & 78.22\\
+Republic of Korea & high\_income & Asia & 83.15\\
+Republic of Moldova & upper\_middle & Europe & 72.35\\
+\addlinespace
+Romania & high\_income & Europe & 74.97\\
+Russian Federation & upper\_middle & Asia & 72.12\\
+Rwanda & lower\_income & Africa & 67.55\\
+Saint Lucia & upper\_middle & North America & 76.08\\
+Saint Vincent and the Grenadines & upper\_middle & North America & 72.98\\
+\addlinespace
+Samoa & lower\_middle & Oceania & 70.03\\
+Sao Tome and Principe & lower\_middle & Africa & 71.20\\
+Saudi Arabia & high\_income & Asia & 76.70\\
+Senegal & lower\_middle & Africa & 68.18\\
+Serbia & upper\_middle & Europe & 75.47\\
+\addlinespace
+Seychelles & high\_income & Africa & 73.82\\
+Sierra Leone & lower\_income & Africa & 59.28\\
+Singapore & high\_income & Asia & 83.43\\
+Slovakia & high\_income & Europe & 77.10\\
+Slovenia & high\_income & Europe & 80.78\\
+\addlinespace
+Solomon Islands & lower\_middle & Oceania & 65.43\\
+Somalia & lower\_income & Africa & 54.43\\
+South Africa & upper\_middle & Africa & 64.55\\
+South Sudan & lower\_income & Africa & 59.03\\
+Spain & high\_income & Europe & 82.58\\
+\addlinespace
+Sri Lanka & lower\_middle & Asia & 77.58\\
+Sudan & lower\_income & Africa & 68.85\\
+Suriname & upper\_middle & South America & 73.03\\
+Sweden & high\_income & Europe & 82.13\\
+Switzerland & high\_income & Europe & 83.07\\
+\addlinespace
+Syrian Arab Republic & lower\_income & Asia & 64.13\\
+Tajikistan & lower\_middle & Asia & 72.70\\
+Thailand & upper\_middle & Asia & 76.95\\
+Timor-Leste & lower\_middle & Asia & 68.32\\
+Togo & lower\_income & Africa & 62.77\\
+\addlinespace
+Tonga & upper\_middle & Oceania & 72.78\\
+Trinidad and Tobago & high\_income & North America & 73.98\\
+Tunisia & lower\_middle & Africa & 77.08\\
+Türkiye & upper\_middle & Asia & 76.98\\
+Turkmenistan & upper\_middle & Asia & 68.92\\
+\addlinespace
+Uganda & lower\_income & Africa & 65.37\\
+Ukraine & lower\_middle & Europe & 72.65\\
+United Arab Emirates & high\_income & Asia & 80.85\\
+United Kingdom of Great Britain and Northern Ireland & high\_income & Europe & 80.72\\
+United Republic of Tanzania & lower\_middle & Africa & 66.23\\
+\addlinespace
+United States of America & high\_income & North America & 78.32\\
+Uruguay & high\_income & South America & 77.17\\
+Uzbekistan & lower\_middle & Asia & 70.83\\
+Vanuatu & lower\_middle & Oceania & 66.98\\
+Venezuela (Bolivarian Republic of) & upper\_middle & South America & 72.87\\
+\addlinespace
+Viet Nam & lower\_middle & Asia & 73.62\\
+Yemen & lower\_income & Asia & 67.25\\
+Zambia & lower\_middle & Africa & 61.28\\
+Zimbabwe & lower\_middle & Africa & 58.47\\
+\bottomrule
 
 \end{longtable}
+
+\endgroup{}
 
@@
 
-\textbf{1. Outcome variable (yi)}
+\textbf{1. Outcome variable (}\(y_i\))
 
@@
 
-\textbf{2. Linear Predictor (μi)}
+\textbf{2. Linear Predictor (}\(μ_i\))
 
@@
 expectancy and the predictors
-\(\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)\)
+\(\mu_i = \alpha + \beta_1(Region) + \beta_2(Income Group) + \beta_3 (Gender)\).
 The values for these coefficients (betas) represent the expected change
@@
 
-\textbf{4. Residual Standard Deviation (σ)} The model also estimates
+\textbf{4. Residual Standard Deviation (}\(σ\)) The model also estimates
 \(σ\), which represents the standard deviation of the residuals --- the
@@
 
-\subsection{Additional graph for
-analysis}\label{additional-graph-for-analysis}
+\begingroup\fontsize{8.5}{10.5}\selectfont
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{0.35in}r>{\raggedleft\arraybackslash}p{1in}>{\raggedleft\arraybackslash}p{1in}>{\raggedleft\arraybackslash}p{1in}>{\raggedright\arraybackslash}p{1in}}
+
+\caption{\label{tbl-testpredicted}Partical table of the test and
+training RMSE of Life expectancy over countries and gender of average of
+6 years (First 100 rows). Through the model part we could tell that with
+comparing the training and testing data, the model is well generated
+without doubt.}
+
+\tabularnewline
+
+\toprule
+Country & Actual Life Expectancy & Predicted Life Expectancy & RMSE (Test) & RMSE (Train) & Indication\\
+\midrule
+Afghanistan & 59.3 & 58.23 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Afghanistan & 61.7 & 63.15 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Afghanistan & 62.1 & 63.15 & 1.15 & 1.17 & Model generalizes well \vphantom{1} (out-of-sample)\\
+Afghanistan & 62.1 & 63.15 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Albania & 74.3 & 75.27 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Albania & 76.2 & 75.27 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Albania & 79.9 & 80.19 & 1.15 & 1.17 & Model generalizes well \vphantom{2} (out-of-sample)\\
+Albania & 79.9 & 80.19 & 1.15 & 1.17 & Model generalizes well \vphantom{1} (out-of-sample)\\
+Albania & 79.9 & 80.19 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Algeria & 76.1 & 73.58 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Algeria & 76.0 & 73.58 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Algeria & 75.9 & 73.58 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Angola & 60.3 & 59.70 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Angola & 60.1 & 59.70 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Angola & 64.5 & 64.62 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Angola & 59.8 & 59.70 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Angola & 61.8 & 62.12 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Antigua and Barbuda & 73.8 & 73.42 & 1.15 & 1.17 & Model generalizes well \vphantom{1} (out-of-sample)\\
+Antigua and Barbuda & 75.5 & 75.84 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Antigua and Barbuda & 77.1 & 78.33 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Antigua and Barbuda & 73.8 & 73.42 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Argentina & 79.9 & 79.01 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Argentina & 76.6 & 76.51 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Argentina & 73.0 & 74.09 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Argentina & 76.1 & 76.51 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Armenia & 75.7 & 73.90 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Armenia & 79.8 & 76.39 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Armenia & 79.1 & 76.39 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Australia & 82.6 & 82.74 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Australia & 84.2 & 85.24 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Austria & 81.4 & 81.26 & 1.15 & 1.17 & Model generalizes well \vphantom{1} (out-of-sample)\\
+Austria & 83.6 & 83.76 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Austria & 81.4 & 81.26 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Austria & 83.3 & 83.76 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Azerbaijan & 67.5 & 71.62 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Azerbaijan & 75.8 & 74.04 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Azerbaijan & 72.2 & 71.62 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Azerbaijan & 71.7 & 71.62 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahamas & 76.0 & 75.07 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahamas & 76.5 & 75.07 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Bahamas & 73.2 & 72.58 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahamas & 69.7 & 70.16 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahamas & 72.9 & 72.58 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahamas & 76.1 & 75.07 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahamas & 69.8 & 70.16 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Bahrain & 74.9 & 75.74 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahrain & 75.9 & 75.74 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahrain & 75.7 & 75.74 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bahrain & 75.8 & 75.74 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bangladesh & 72.6 & 71.06 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Bangladesh & 75.0 & 75.97 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bangladesh & 73.4 & 73.48 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bangladesh & 73.2 & 73.48 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Barbados & 74.9 & 73.87 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Barbados & 76.3 & 76.30 & 1.15 & 1.17 & Model generalizes well \vphantom{1} (out-of-sample)\\
+\addlinespace
+Barbados & 77.4 & 78.79 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Barbados & 76.3 & 76.30 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Belarus & 79.7 & 76.42 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Belarus & 79.2 & 76.42 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Belarus & 78.9 & 76.42 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Belgium & 81.6 & 81.06 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Belize & 74.4 & 74.64 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Benin & 63.7 & 63.54 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Benin & 66.2 & 66.04 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Benin & 65.4 & 66.04 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Bhutan & 74.5 & 73.70 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bhutan & 72.3 & 71.28 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bhutan & 73.3 & 73.70 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bhutan & 74.2 & 76.19 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bolivia (Plurinational State of) & 73.8 & 74.04 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Bolivia (Plurinational State of) & 71.8 & 69.13 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bolivia (Plurinational State of) & 71.3 & 69.13 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bolivia (Plurinational State of) & 71.0 & 69.13 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bolivia (Plurinational State of) & 72.8 & 74.04 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bosnia and Herzegovina & 74.9 & 74.46 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Bosnia and Herzegovina & 74.6 & 74.46 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Botswana & 64.9 & 63.88 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Botswana & 64.5 & 63.88 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Botswana & 64.0 & 63.88 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Botswana & 66.1 & 66.37 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Botswana & 65.0 & 66.37 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Brazil & 75.3 & 74.84 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Brazil & 74.6 & 74.84 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Brunei Darussalam & 78.3 & 79.03 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Brunei Darussalam & 76.4 & 76.54 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Brunei Darussalam & 77.9 & 79.03 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bulgaria & 71.4 & 72.17 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Bulgaria & 78.4 & 77.09 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Burkina Faso & 60.3 & 59.54 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Burkina Faso & 62.4 & 61.97 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Burkina Faso & 58.9 & 59.54 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Burkina Faso & 60.9 & 61.97 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Burundi & 66.2 & 66.23 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Burundi & 63.7 & 63.73 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Burundi & 61.3 & 61.31 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\addlinespace
+Burundi & 60.8 & 61.31 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Cabo Verde & 78.2 & 76.82 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Cabo Verde & 69.7 & 71.91 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Cabo Verde & 72.0 & 71.91 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+Cabo Verde & 72.2 & 71.91 & 1.15 & 1.17 & Model generalizes well (out-of-sample)\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-IncomeGroupsandLongevity}
+Chetty, Stepner, R. 2016. \emph{The Association Between Income and Life
+Expectancy in the United States, 2001-2014}.
+\url{https://jamanetwork.com/journals/jama/fullarticle/2513561}.
+
+\bibitem[\citeproctext]{ref-janitor}
+Firke, Sam. 2024. \emph{Janitor: Simple Tools for Examining and Cleaning
+Dirty Data}. \url{https://github.com/sfirke/janitor}.
+
 \bibitem[\citeproctext]{ref-rstanarm}
-Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
-{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
-\url{https://mc-stan.org/rstanarm/}.
+Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2020.
+{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
+\url{https://mc-stan.org/rstanarm}.
+
+\bibitem[\citeproctext]{ref-whymandieyounger}
+Kalben, B. B. 2000. \emph{Why Men Die Younger: Causes of Mortality
+Differences by Sex.}
+https://doi.org/\url{https://doi.org/10.1080/10920277.2000.10595939}.
+
+\bibitem[\citeproctext]{ref-ggcorrplot}
+Kassambara, Alboukadel. 2029. \emph{Ggcorrplot: Visualization of a
+Correlation Matrix Using 'Ggplot2'}.
+\url{https://github.com/kassambara/ggcorrplot}.
+
+\bibitem[\citeproctext]{ref-RegionalVariations}
+Marmot, Friel, M. 2008. \emph{Closing the Gap in a Generation: Health
+Equity Through Action on the Social Determinants of Health.}
+\url{chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/https://iris.who.int/bitstream/handle/10665/43943/9789241563703_eng.pdf}.
+
+\bibitem[\citeproctext]{ref-inequalworld}
+Marmot, M. 2015. \emph{The Health Gap: The Challenge of an Unequal
+World.} \url{https://doi.org/10.1093/ije/dyx163}.
+
+\bibitem[\citeproctext]{ref-here}
+Müller, Kirill. 2023. \emph{Here: A Simpler Way to Find Your Files}.
+\url{https://CRAN.R-project.org/package=here}.
+
+\bibitem[\citeproctext]{ref-behaviouralfactor}
+Oksuzyan, Juel, A. 2008a. \emph{Behavioral Factors Associated with Life
+Expectancy Gaps.}
+\url{https://link.springer.com/article/10.1007/BF03324754}.
+
+\bibitem[\citeproctext]{ref-GenderandLifeExpectancy}
+---------. 2008b. \emph{Gender and Life Expectancy}.
+\url{https://link.springer.com/article/10.1007/BF03324754}.
+
+\bibitem[\citeproctext]{ref-sf}
+Pebesma, Edzer, and Roger Bivand. 2023. \emph{{Spatial Data Science:
+With applications in R}}. {Chapman and Hall/CRC}.
+\url{https://doi.org/10.1201/9780429459016}.
+
+\bibitem[\citeproctext]{ref-incomeinequality}
+Public Health., Harvard T. H. Chan School of. 2020. \emph{Income
+Inequality and Health Outcomes}.
+\url{chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/https://www.hsph.harvard.edu/horp/wp-content/uploads/sites/94/2020/01/Income-inequality-report-topline_January2020.pdf}.
 
@@
 
+\bibitem[\citeproctext]{ref-arrow}
+Richardson, Neal, Ian Cook, Nic Crane, Dewey Dunnington, Romain
+François, Jonathan Keane, Dragoș Moldovan-Grünfeld, et al. 2023.
+\emph{Arrow: Integration to 'Apache Arrow'}.
+\url{https://CRAN.R-project.org/package=arrow}.
+
+\bibitem[\citeproctext]{ref-womenhigherhealthcare}
+Saltonstall, R. 1993. \emph{Health and Gender: A Case for Women's Higher
+Healthcare Utilization.}
+https://doi.org/\url{https://doi.org/10.1016/0277-9536(93)90300-S}.
+
+\bibitem[\citeproctext]{ref-lifeexpectancy}
+WHO. 2020. \emph{Life Expectancy}.
+\url{https://www.who.int/data/gho/data/indicators/indicator-details/GHO/life-expectancy-at-age-60-(years)}.
+
+\bibitem[\citeproctext]{ref-tidyverse}
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
+D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
+4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+
+\bibitem[\citeproctext]{ref-ggplot2}
+Wickham, Hadley, Winston Chang, Lionel Henry, Thomas Lin Pedersen,
+Kohske Takahashi, Claus Wilke, Kara Woo, Hiroaki Yutani, Dewey
+Dunnington, and Teun van den Brand. 2023. \emph{Ggplot2: Create Elegant
+Data Visualisations Using the Grammar of Graphics}.
+\url{https://CRAN.R-project.org/package=ggplot2}.
+
+\bibitem[\citeproctext]{ref-dplyr}
+Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
+Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
+\url{https://CRAN.R-project.org/package=dplyr}.
+
+\bibitem[\citeproctext]{ref-purrr}
+Wickham, Hadley, and Lionel Henry. 2023. \emph{Purrr: Functional
+Programming Tools}. \url{https://purrr.tidyverse.org/}.
+
+\bibitem[\citeproctext]{ref-socialdeterminantsofhealth}
+Wilkinson, \& Marmot, R. G. 2003. \emph{Social Determinants of Health:
+The Solid Facts.} \url{https://iris.who.int/handle/10665/326568}.
+
+\bibitem[\citeproctext]{ref-knitr}
+Xie, Yihui. 2024. \emph{Knitr: A General-Purpose Package for Dynamic
+Report Generation in r}. \url{https://yihui.org/knitr/}.
+
+\bibitem[\citeproctext]{ref-kableExtra}
+Zhu, Hao. 2023. \emph{kableExtra: Construct Complex Table with 'Kable'
+and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
+
 \end{CSLReferences}

### 2024-12-04 paper/paper.qmd
min

@@
 toc: true
-pdf-engine: xelatex
-geometry: landscape
 toc-depth: 3
-keep-tex: true
-output:
-  pdf_document:
-    extra_dependencies: ["longtable"]
+geometry: portrait
 number-sections: true
